### 2019-05-01 tex/v1/screenkhorn.tex

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%\usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[preprint]{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

%--------------------------------------------------------------------------------------------------------------------------------%

\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
\usepackage[titletoc,title]{appendix}%
\usepackage{dsfont}%
\usepackage{caption} % 
\usepackage{subcaption}
\usepackage{float}%
\usepackage{graphicx, color}% 
\usepackage{bm}%bold equations

%% FORMATTING APPNENDICES
\usepackage{etoolbox}
\patchcmd{\appendices}{\quad}{. }{}{}

%% TABLE
\usepackage{pgfplots}%
\usepackage{booktabs,multirow,array,multicol}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

%% ALGORITHM
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

%% SECTIONS
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{fact}{Fact}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}%[section]
\newtheorem*{notation}{Notation}%[section]
\newtheorem{discus}{Discussion}%[section]
\newtheorem{remark}{Remark}%[section]
\newtheorem{example}{Example}%[section]
\newtheorem{exs}{Examples}%[section]
\newtheorem{ca}{Cas}
\newtheorem{remarks}{Remarks}%[section]
\newtheorem{assumption}{Assumption}{\bf}{\rm}%

% MATH MACROS

\usepackage{relsize}
\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}

\newcommand{\ba}{\mathbf{a}}%
\newcommand{\bb}{\mathbf{b}}%

\newcommand{\bC}{{\mathbf C}}%
\newcommand{\bP}{{\mathbf P}}%
\newcommand{\bU}{{\mathbf U}}%

\newcommand{\cX}{\mathcal X}%
\newcommand{\cY}{\mathcal Y}%
\newcommand{\cM}{\mathcal M}%
\newcommand{\cC}{\mathcal C}%

\newcommand{\td}{\text d}%
\newcommand*{\argminl}{\argmin\limits}%
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sumin}{\sum_{i=1}^n}
\newcommand{\sumip}{\sum_{j=1}^m}
\newcommand{\intt}{\int_{0}^{t}}
\newcommand{\inttau}{\int_{0}^{\gamma}}
\newcommand{\I}{1\!\mbox{I}}
\newcommand{\e}{{\mathrm e}}
\newcommand{\diff}{\mathrm d}
\newcommand{\noi}{\noindent}
\newcommand{\eps}{\varepsilon}
\usepackage{datenumber}
\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
\newcommand{\inr}[1]{\langle #1 \rangle}
\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\V}{\mathds{V}}
\newcommand{\Lim}{\displaystyle \lim\limits}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cT}{\mathcal T}
\newcommand{\bA}{{\boldsymbol A}}%
\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
\newcommand{\bB}{{\boldsymbol B}}%
\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
\newcommand{\bD}{{\boldsymbol D}}%
\newcommand{\bE}{{\boldsymbol E}}%
\newcommand{\bF}{{\boldsymbol F}}%
\newcommand{\bG}{{\boldsymbol G}}%
\newcommand{\bH}{{\boldsymbol H}}%
\newcommand{\bI}{{\boldsymbol I}}%
\newcommand{\bJ}{{\boldsymbol J}}%
\newcommand{\bK}{{\boldsymbol K}}%
\newcommand{\bL}{{\boldsymbol L}}%
\newcommand{\bM}{{\boldsymbol M}}%
\newcommand{\bN}{{\boldsymbol N}}%
\newcommand{\bO}{\boldsymbol 0}%
\newcommand{\bQ}{\boldsymbol Q}%
\newcommand{\bR}{\boldsymbol R}%
\newcommand{\cS}{{\mathcal{S}}}%
\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
\newcommand{\bV}{\boldsymbol V}%
\newcommand{\bW}{\boldsymbol W}%
\newcommand{\bX}{\boldsymbol  X}%
\newcommand{\bT}{\boldsymbol  T}%
\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
\newcommand{\by}{\boldsymbol y}%
\newcommand{\bu}{\boldsymbol u}%
\newcommand{\bv}{\boldsymbol  v}%
\newcommand{\bz}{\boldsymbol z}%
\newcommand{\bY}{\boldsymbol{Y}}%
\newcommand{\bZ}{\boldsymbol Z}
\newcommand{\bg}{\boldsymbol g}%
\newcommand{\beps}{\boldsymbol \varepsilon}%
\newcommand{\bSigma}{\boldsymbol \Sigma}%
\newcommand{\blambda}{\boldsymbol  \lambda}
\newcommand{\bbeta}{\boldsymbol  \beta}%
\newcommand{\bLambda}{\boldsymbol  \Lambda}%
\newcommand{\bTheta}{\boldsymbol  \Theta}
\newcommand{\bDelta}{\boldsymbol{\Delta}}%
\newcommand{\bXi}{\boldsymbol{\Xi}}%
\newcommand{\ov}{\overrightarrow}%
\newcommand{\cP}{\mathcal P}%
\newcommand{\cQ}{\mathcal Q}%
\renewcommand{\P}{\mathds{P}}
\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
\newcommand{\btheta}{\boldsymbol  \Theta}%
\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
\usepackage{accents}
\newcommand*{\dt}[1]{\accentset{\raisebox{0ex}{$\,\star$}}{#1}}
\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}

\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}

%% MATH OPERATORS
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

%--------------------------------------------------------------------------------------------------------------------------------%

\title{Screening Sinkhorn Algorithm via Dual Projections}

\begin{document}

\maketitle

\begin{abstract}
Computing optimal transport distances, such as the earth mover's distance is a fundamental problem in machine learning, statistics, and computer vision. 
% Despite the recent several introduction of several algorithms with good empirical performance, it is unknown whether general optimal transport distances can be approximated in near-linear time.
% This paper demonstrates that this ambitious goal is in fact achieved by Cuturi's Sinkhron divergence distance.
% This result relies on a new analysis of Sinkhorn iterations, which also directly suggests a new greedy coordinate descent algorithm GREENKHORN with the same theoretical  guarantees. 
% Numerical simulations illustrate that GREENKHORN significantly outperforms the classical SINKHORN Algorithm in practice.
\end{abstract}

\section{Introduction}

\paragraph{Related work.}

\paragraph{Our contribution.}

\paragraph{Notation.}

We denote $\Sigma_n$ the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively. The coordinates $r_i(T)$ and $c_j(T)$ denote the $i$-th row sum and the $j$-th column sum of $T$, respectively.
The scalar product between two matrices denotes the usual inner product, that is $\inr{T, W} = \text{tr}(T^\top W) = \sum_{i,j}T_{ij}W_{ij},$ where $T^\top$ is the transpose of $T$. 
We write $\mathbf{1}$ (resp. $\mathbf{0}$) the vector having all coordinates equal to one (resp. zero).
$\Delta(w)$ denotes the diag operator, such that if $w \in \R^n$, then $\Delta(w) = \text{diag}(w_1, \ldots, w_n)\in \R^{n\times n}$.
Throughout this paper, when applied to matrices and vectors,  $\odot$ and $\oslash$ (Hadamard product and division) and exponential notations refer to elementwise operators.
We also denote $|I|$ the cardinality of a finite set $I$.
Given two real numbers $a$ and $b$, we write $a\vee b = \max(a,b)$ and $a\wedge b = \min(a,b).$
% We denote by $\iota_C$ the indicator function of a convex set $C$, that is,
% \begin{equation*}
%   \iota_{C}(w) = \begin{cases}
%             0, &\text{ if } w\in C,\\
%             \infty, &\text{otherwise}.
%               \end{cases}
% \end{equation*}

\section{Regularized optimal transport}
\label{sec:optimal_transport}

 We briefly present in this section the setup of optimal transport between two discrete measures. We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$. 
We denote their probabilistic couplings set as $\Pi(\mu, \nu) = \{P \in \R_+^{n\times m}, P\mathbf{1}_m = \mu, P^\top \mathbf{1}_n = \nu\}.$ 
\paragraph{Sinkhorn divergence.}

 % Roughly speaking, the optimal transport aims at computing a minimal cost transportation between the two measures $\mu$ and $\nu$
Approximating the optimal transport distance between the two measures $\mu$ and $\nu$  amounts to solving a linear problem given by~\cite{kantorovich1942}
\begin{equation}
  \label{monge-kantorovich}
  \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{M, P},
\end{equation}
where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $M= (M_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements related to the energy needed to move a probability mass from $x_i$ to $y_j$. 
The entropic regularization of optimal transport distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
\begin{equation}
\label{sinkhorn-primal}
  \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{M, P} - \eta H(P)\},
\end{equation}
where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.

\paragraph{Dual of Sinkhorn divergence.}

Below we provide the derivation of the dual problem for the regularized optimal transport problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
\begin{equation*}
  \mathscr{L}(P,y, z) = \inr{M,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu},
\end{equation*}
which can be rewritten in the following form:
\begin{equation*}
  \mathscr{L}(P,y, z) = - \inr{y, \mu} - \inr{z, \nu} + \inr{P, M + \eta \log P} + \inr{y, P\mathbf{1}_m} + \inr{z, P^\top \mathbf{1}_n}.
\end{equation*}
The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$. It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable. Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$. Therefore, we get 
\begin{equation}
  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + M_{ij}) - 1\Big), 
\end{equation}
for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution, one has 
\begin{equation*}
  \min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z) = - \inr{y, \mu} - \inr{z, \nu} - \eta \sum_{i,j} \exp\Big(- \frac{1}{\eta} (y_i + z_j + M_{ij}) - 1\Big).
\end{equation*}
Setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, we get 
\begin{equation*}
  \min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z) = \eta \Big( \inr{u, \mu} + \inr{v, \nu} - \sum_{i,j} \exp\big(u_i + v_j - M_{ij}/\eta)\big) + 1\Big).
\end{equation*}
Recall that the dual problem is given by $\max_{y \in \R^n, z \in \R^m} \min_{P\in \R_+^{n\times m}}\mathscr{L}(P,y, z)$, that is 
\begin{equation*}
\max_{u \in \R^n, v\in\R^m} \Big\{\eta \Big(\inr{u, \mu} + \inr{v, \nu} - \sum_{i,j} \exp\big(u_i + v_j - M_{ij}/\eta)\big) + 1\Big)\Big\},
\end{equation*}
which is equivalent to solving 
\begin{equation*}
\max_{u \in \R^n, v\in\R^m} \Big\{\inr{u, \mu} + \inr{v, \nu} - \sum_{i,j} \exp\big(u_i + v_j - M_{ij}/\eta)\big) \Big\}
\end{equation*}
and which can be rewritten in the following matrix form:
% \begin{equation*}
% \max_{u \in \R^n, v\in\R^m} \big\{\inr{u, \mu} + \inr{v, \nu} - \mathbf{1}_n^\top B(u,v)\mathbf{1}_m\big\},
% \end{equation*}
\begin{equation}
\label{sinkhorn-dual}
\min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
\end{equation}
where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-M/\eta}$ stands for the Gibbs kernel associated to the cost matrix $M$. 
% Hence, 
% \begin{equation}
% \label{sinkhorn-dual}
% \min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
% \end{equation}
We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
Therefore, the optimal solution of Sinkhorn divergence is given by $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
where the couple $(u^\star, v^\star)$ satisfies:
\begin{align*}
\label{sinkhorn-dual}
  (u^\star, v^\star) &= \argmin_{u \in \R^{n}, v\in \R^m} \{\Psi(u,v)\}.
\end{align*}
Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.

\section{Screened dual of Sinkhorn divergence}

For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} 
\begin{equation} 
\label{screen-sinkhorn}
\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\kappa^{-1}v, \nu} \big\},
\end{equation}
where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.

The $\kappa$-parameter in problem~\eqref{screen-sinkhorn} plays a role of scaling factor, namely it allows to get a closed order of the potential vectors $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
Note that the setting of $\varepsilon=0$ and $\kappa=1$, the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.

The screening procedure presented in this work is based on constructing two \emph{active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:

\begin{lemma}
\label{lemma_actives_sets}
Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
Define
\begin{equation*}
\label{I_c_epsilon}
I_{\varepsilon,\kappa} = \Big\{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\Big\}, J_{\varepsilon,\kappa} = \Big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\Big\}
\end{equation*}
and $I^\complement_{\varepsilon,\kappa} = \{1, \ldots, n\} \backslash I_{\varepsilon, \kappa},$ and $J^\complement_{\varepsilon,\kappa} = \{1, \ldots, n\} \backslash J_{\varepsilon, \kappa}.$
Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
\end{lemma}

\begin{proof}

% The dual of problem~\eqref{screen-sinkhorn} reads as 
% \begin{align*} 
% &\max_{\lambda \succeq 0, \beta \succeq 0} \min_{u \in \R^n, v\in \R^m} \big\{\mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} + \inr{\lambda, \frac \varepsilon\kappa \mathbf{1}_n - e^{u}} + \inr{\beta, c \varepsilon\mathbf{1}_m - e^{v}}\big\}\\
% &=\max_{\lambda \succeq 0, \beta \succeq 0} \big\{\frac \varepsilon\kappa \inr{\lambda, \mathbf{1}_n} + c\varepsilon\inr{\beta, \mathbf{1}_m}\\
% & \qquad\qquad\qquad + \min_{u \in \R^n, v\in \R^m} \big\{\mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{u, \kappa\mu} - \inr{v, \frac \nu c} - \inr{\lambda,e^{u}} - \inr{\beta,e^{v}}\big\}\big\}. 
% \end{align*}
Introducing two dual variables $\lambda \in \R^n_{+}$ and $\beta \in \R^m_{+}$ for each constraint, the Lagrangian of problem~\eqref{screen-sinkhorn} reads as 
\begin{equation*}
  \mathscr{L}(u,v, \lambda, \beta) = \frac \varepsilon\kappa\inr{\lambda, \mathbf{1}_n} + \varepsilon\kappa\inr{\beta, \mathbf{1}_m} + \mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\kappa^{-1}v, \nu} -\inr{\lambda,e^{u}} - \inr{\beta,e^{v}}
\end{equation*}
First order conditions~\citep{boyd2004} then yield that the Lagrangian multiplicators solutions $\lambda^{*}$ and $\beta^{*}$ satisfy the following:
\begin{align*}
  &\nabla_u\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{u^{*}} \odot(Ke^{v^{*}} - \lambda^{*}) - \kappa\mu = \mathbf 0_n,\\
  & \text{ and } \nabla_v\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{v^{*}} \odot(K^\top e^{u^{*}} - \beta) - \kappa^{-1} \nu = \mathbf 0_m
\end{align*}
which leads to 
\begin{align*}
  &\lambda^{*} = K e^{v^{*}} - \kappa\mu \oslash e^{u^{*}} \text{ and }
  \beta^{*} = K^\top e^{u^{*}} - \nu \oslash \kappa e^{v^{*}}
\end{align*}
% We come up with the following two cases for solving an optimal $(u^{*},v^{*})$ of problem~\eqref{screen-sinkhorn}
% \begin{itemize}
% \item If $\lambda^{*}_i > 0$ then $e^{u^{*}_i} =\frac \varepsilon\kappa$. Then $\lambda_i = (K e^{v^{*}})_i - \frac{ c \mu_i}{\varepsilon} > 0.$
% \item  If $e^{u^{*}_i} > \frac \varepsilon\kappa$ then $\lambda^{*}_i = 0$. It implies that $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ ( ``nearly'' original Sinkhorn marginal conditions).
% \end{itemize}

% Analogously,
% \begin{itemize}
% \item If $\beta^{*}_j > 0$ and $e^{v^{*}_j} = \varepsilon\kappa$. Then $\beta_j = (K^\top e^{v^{*}})_j - \frac{\nu_j}{\varepsilon\kappa} > 0.$
% \item  If $\beta^{*}_j = 0$ and $e^{v^{*}_j} > \varepsilon\kappa$. Then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \frac{\nu_j}{c}$ (``nearly'' original Sinkhorn marginal conditions).
% \end{itemize}

For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \frac \varepsilon\kappa$. By the KKT optimality conditions, the condition on the dual variable $\lambda^{*}_i > 0$  ensures that $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and hence $i \in I^\complement_{\varepsilon,\kappa}$. Further, $\lambda^{*}_i > 0$ is equivalent to $e^{u^{*}_i}r_i(K) e^{v^{*}_j} >  \kappa{\mu_i}$ which  is satisfied when $\varepsilon^2r_i(K) >  \kappa{\mu_i}.$  
In a symmetric way we can prove the same statement for $e^{v^{*}_j}$.
\end{proof}

It is worth to note that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ which corresponds to one of the original Sinkhorn marginal conditions up to the scaling factor $\kappa$.

\paragraph{Screening with a fixed budget number of points.}

Recall that the approximate dual of Sinkhorn divergence is defined with respect to the parameters $\varepsilon$ and $\kappa$. 
The explicit determination of its values depends on a fixed budget numbers of points, to be chosen in a priori way, in problem~\eqref{screen-sinkhorn}.  
In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the budget number of points to be given for resolving problem~\eqref{screen-sinkhorn}. 
Towards this end, let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
To keep only a budget of $n_b$ and $m_b$ points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
\begin{equation}
\label{epsilon_kappa}
 \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}},
\end{equation}
we then obtain $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$.  %Using~\eqref{epsilon_kappa} we obtain
Using the previous analysis, we know, in a posterior way, that any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} should satisfy: $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$
% \begin{itemize}
% 	\item $e^{u^*_i} \geq \frac \varepsilon\kappa$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \frac \varepsilon\kappa$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa}).$
% 	\item $e^{u^*_i} = \frac \varepsilon\kappa$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa}).$
% \end{itemize}

Basing on that facts we ``screen'' the feasibility domain in problem~\eqref{screen-sinkhorn} to the following one:
\begin{align}
\label{screen-sinkhorn_second_def}
\min\{\Psi_{\varepsilon, \kappa}(u,v)\} \text { subject to } 
\begin{cases}
e^{u_i} \geq \varepsilon\kappa^{-1}, \text{ for all } i \in I_{\varepsilon,\kappa} \text{ and } e^{u_i} = \varepsilon\kappa^{-1} \text{ for all } i \in I^\complement_{\varepsilon,\kappa}\\
e^{v_j} \geq \varepsilon\kappa, \text{ for all } j \in J_{\varepsilon,\kappa} \text{ and } e^{v_i} = \varepsilon\kappa \text{ for all } j \in J^\complement_{\varepsilon,\kappa},
\end{cases}
\end{align}
where 
\begin{align*}
\Psi_{\varepsilon,\kappa}(u, v) &:= \sum_{i\in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}e^{u_i}K_{ij}e^{v_j} 
+ \varepsilon\kappa \sum_{i\in I_{\varepsilon,\kappa}, j\in J^\complement_{\varepsilon,\kappa}} e^{u_i}K_{ij} 
+ \varepsilon\kappa^{-1} \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}} K_{ij}e^{v_j}\\
& \qquad - \kappa\sum_{i \in I_{\varepsilon,\kappa}}\mu_i u_i - \kappa^{-1} \sum_{j\in J_{\varepsilon,\kappa}} \nu_jv_j
+ \Xi,
\end{align*}
with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
We refer to problem~\eqref{screen-sinkhorn_second_def} as the \emph{screened dual of Sinkhorn divergence}.

\paragraph{First order conditions for problem~\eqref{screen-sinkhorn_second_def}.}

Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}, then we have 
\begin{align*}
e^{u^{\text{sc}}_i} \sum_{j\in J_{\varepsilon,\kappa}}K_{ij}e^{v^{\text{sc}}_j} + \varepsilon\kappa e^{u^{\text{sc}}_i}\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij} - \kappa \mu_i = 0, \text{ for all } i \in I_{\varepsilon,\kappa},
\end{align*}
and 
\begin{align*}
e^{v^{\text{sc}}_j} \sum_{i\in I_{\varepsilon,\kappa}}K_{ij}e^{u^{\text{sc}}_i} + \varepsilon\kappa^{-1} e^{v^{\text{sc}}_j}\sum_{i\in I^\complement_{\varepsilon,\kappa}}K_{ij} - \kappa^{-1} \nu_j = 0, \text{ for all } j \in J_{\varepsilon,\kappa}.
\end{align*}
Therefore
\begin{align*}
e^{u^{\text{sc}}_i} = \frac{\kappa\mu_i}{\sum_{j\in J_{\varepsilon,\kappa}}K_{ij}e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}}, \text{ for all } i \in I_{\varepsilon,\kappa},
\end{align*}
and 
\begin{align*}
e^{v^{\text{sc}}_i} = \frac{\kappa^{-1}\nu_j}{\sum_{i \in I_{\varepsilon,\kappa}}K_{ij}e^{u^{\text{sc}}_i} + \varepsilon\kappa^{-1} \sum_{i\in I^\complement_{\varepsilon,\kappa}}K_{ij}}, \text{ for all } j \in J_{\varepsilon,\kappa},
\end{align*}

\begin{lemma}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
one has
\begin{equation}
\label{bound_on_u}
\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\kappa,\varepsilon}}\mu_i}{\varepsilon |J^\complement_{\varepsilon,\kappa}| + \varepsilon \vee \frac{\max_{j\in J_{\kappa,\varepsilon}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} |J_{\kappa,\varepsilon}|} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\kappa,\varepsilon}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
\end{equation}
and
\begin{equation}
\label{bound_on_v}
\varepsilon\kappa \vee \frac{\min_{j \in J_{\kappa,\varepsilon}}\nu_j}{\varepsilon|I^\complement_{\varepsilon,\kappa}| + \varepsilon \vee \frac{\kappa\max_{i\in I_{\kappa,\varepsilon}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} |I_{\kappa,\varepsilon}|} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\kappa,\varepsilon}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
\end{equation}
for all $i\in I_{\kappa,\varepsilon}$ and $j\in J_{\kappa,\varepsilon}$.
\end{lemma}

\begin{proof}
We prove only the first statement~\eqref{bound_on_u} and symmetrically we can prove the second statement~\eqref{bound_on_v} for $e^{v^{\text{sc}}_j}$.
For all $i\in I_{\varepsilon,\kappa}$, we have $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ or $e^{u^{\text{sc}}_i} = \frac \varepsilon\kappa$. In one hand, if $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ then according to the optimality conditions $\lambda^{\text{sc}}_i = 0.$ Then $e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i$.
In another hand, we have 
\begin{align*}
e^{u^{\text{sc}}_i} \min_{i,j}K_{ij} \sum_{j=1}^m e^{v^{\text{sc}}_j} \leq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i.
\end{align*}
We further observe that $\sum_{j=1}^m e^{v^{\text{sc}}_j} = \sum_{j \in J_{\kappa,\varepsilon}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} \geq \varepsilon\kappa |J_{\kappa,\varepsilon}| + \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| = \varepsilon\kappa (|J_{\kappa,\varepsilon}| + |J^\complement_{\varepsilon,\kappa}|) = \varepsilon\kappa m.$ Then
\begin{equation*}
\max_{i\in I_{\kappa,\varepsilon}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\kappa,\varepsilon}}\mu_i}{m\varepsilon \min_{i,j}K_{ij}}.
\end{equation*}
Analogously, one can obtain for all $j\in J_{\kappa,\varepsilon}$
\begin{equation}
\label{upper_bound_v_potential}
\max_{j\in J_{\kappa,\varepsilon}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\kappa,\varepsilon}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}.
\end{equation}

Now, since $K_{ij} \leq 1$, we have 
\begin{align*}
e^{u^{\text{sc}}_i} \sum_{j=1}^m e^{v^{\text{sc}}_j} \geq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij}e^{v^{\text{sc}}_j} = \kappa\mu_i.
\end{align*}
Moreover, using~\eqref{upper_bound_v_potential}, we get 
\begin{align*}
\sum_{j=1}^m e^{v^{\text{sc}}_j} &= \sum_{j \in J_{\kappa,\varepsilon}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j}
\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\kappa,\varepsilon}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} |J_{\kappa,\varepsilon}|.
\end{align*}
Therefore,
\begin{align*}
\min_{i \in I_{\kappa,\varepsilon}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\kappa,\varepsilon}}\mu_i}{\varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\kappa,\varepsilon}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} |J_{\kappa,\varepsilon}|}.
\end{align*}
\end{proof}

\section{Numerical experiments}

% \subsubsection*{Acknowledgments}

% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.

\small
\bibliography{biblio}
\bibliographystyle{plain}

\end{document}

% \begin{remark}
% We define the maximal value $\varepsilon_{\max}$ as follows:
% \begin{align*}
% \label{varepsilon_max}
% \varepsilon_{\max} = \max\bigg\{\max_{i}\sqrt{\frac{\mu_i}{\sum_{j}K_{ij}}}, \max_{j}\sqrt{\frac{\nu_j}{\sum_{i}K_{ij}}}\bigg\}
% \end{align*}
% and 
% \begin{equation*}
% \label{varepsilon_min}
% \varepsilon_{\min} = \min\bigg\{\min_{i}\sqrt{\frac{\mu_i}{\sum_{j}K_{ij}}}, \min_{j}\sqrt{\frac{\nu_j}{\sum_{i}K_{ij}}}\bigg\}.
% \end{equation*}
% It implies that for a choice of $\varepsilon > \varepsilon_{\max}$, the couple solution of $(u^{*}, v^{*}) \equiv (\frac \varepsilon\kappa\mathbf{1}_n, \varepsilon\kappa \mathbf{1}_m)$. 
% Indeed, we obtain that $I_{{c,\varepsilon_{\max}}} = \varnothing$ and $J_{{c,\varepsilon_{\max}}} = \varnothing$. Moreover, there exists and $\varepsilon_{\min}$ for which $I_{c,\varepsilon_{\min}} = \{1, \ldots, n\}$ and $J_{c,\varepsilon_{\min}} = \{1, \ldots, m\}$.

% We remark that $\varepsilon_{\max} \nearrow \infty$ and $\varepsilon_{\min} \nearrow \infty$ as $\eta \rightarrow 0,$ and we have 
% \begin{equation*}
% \varepsilon_{\max}(\eta=\infty)= \max\bigg\{\max_{i}\sqrt{\frac{\mu_i}{m}}, \max_{j}\sqrt{\frac{\nu_j}{n}}\bigg\}.
% \end{equation*}
% and 
% \begin{equation*}
% \varepsilon_{\min}(\eta=\infty)= \min\bigg\{\min_{i}\sqrt{\frac{\mu_i}{m}}, \min_{j}\sqrt{\frac{\nu_j}{n}}\bigg\}.
% \end{equation*}
% \end{remark}

### 2019-05-09 DA_toy.py
expe

@@ -23,19 +23,16 @@
 #
 # License: MIT License
 
+from time import process_time as time
 import matplotlib.pylab as pl
 import ot
 import ot.plot
 
-
-# In[2]:
-
-
-# PATH 
 import sys
-path_files = '/Users/mzalaya/PycharmProjects/OATMIL/oatmilrouen/screenkhorn/code'
+path_files = './code/'
 sys.path.insert(0, path_files) 
 import domain_adaptation as da_screenkhorn
+from sklearn.neighbors import KNeighborsClassifier
 
 
 # In[3]:
@@ -43,225 +40,61 @@ import domain_adaptation as da_screenkhorn
 
 # NUMPY
 import numpy as np
-np.random.seed(3946)
-# MATPLOTLIB
 import matplotlib.pyplot as plt
-plt.style.context('dark_background')
-get_ipython().run_line_magic('matplotlib', 'inline')
-from matplotlib import rc
-rc('font', **{'family': 'sans-serif', 'sans-serif': ['Computer Modern Roman']})
-params = {'axes.labelsize': 8, # 12
-          'font.size': 8, # 12
-          'legend.fontsize': 8, # 12
-          'xtick.labelsize': 8, # 10
-          'ytick.labelsize': 8, # 10
-          'text.usetex': True,
-          'figure.figsize': (16, 6)}
-plt.rcParams.update(params)
+
 
 # SEABORN 
 import seaborn as sns
-sns.set_context("poster")
-sns.set_style("ticks")
 
 
 # generate data
 # -------------
-# 
-# 
-
-# In[4]:
 
 
-n_samples_source = 10
-n_samples_target = 10
+n_samples_source = 5000
+n_samples_target = 5000
 
-Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source)
-Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target)
-
-# Cost matrix
+Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=1,random_state=None)
[…]

### 2019-05-09 code/domain_adaptation.py

@@ -1286,7 +1286,7 @@ class ScreenkhornTransport(BaseTransport):
         m_budget = int(np.ceil(self.cost_.shape[1] / p_m))
 
         screenkhorn = Screenkhorn(a=self.mu_s, b=self.mu_t, C=self.cost_, reg=self.reg_e,
-                                  n_b=n_budget, m_b=m_budget)
+                                  N=n_budget, M=m_budget)
         returned_ = screenkhorn.lbfgsb()[2]
 
         # returned_ = sinkhorn(

### 2019-05-09 code/wda_formulation_screekhorn.py

@@ -33,7 +33,6 @@ class Screenkhorn:
         self.verbose = verbose
         self.uniform = uniform
         # K
-        print(time() - tic_initial)
 
         self.K = np.empty_like(self.C)
         np.divide(self.C, - self.reg, out=self.K)

### 2019-05-09 new_formulation.py

@@ -7,6 +7,7 @@ __author__ = 'Mokhtar Z. Alaya'
 import numpy as np
 from scipy.optimize import fmin_l_bfgs_b
 from time import time
+from numba import jit
 
 class Screenkhorn:
 
@@ -25,11 +26,14 @@ class Screenkhorn:
         self.uniform = uniform
 
         # K
-        # self.K = np.empty_like(self.C)
-        # np.divide(self.C, - self.reg, out=self.K)
-        # np.exp(self.K, out=self.K)
+        self.K = np.empty_like(self.C)
+        np.divide(self.C, - self.reg, out=self.K)
+        np.exp(self.K, out=self.K)
 
-        self.K = np.exp(-self.C / self.reg)
+        #self.K = np.exp(-self.C / self.reg)
+ 
+        
+        print('K',time() - tic_initial)
 
         # Test
         if self.N == n and self.M == m:
@@ -65,6 +69,8 @@ class Screenkhorn:
             if not self.uniform:
                 a_sort = np.sort(a)
                 b_sort = np.sort(b)
+            else:
+                a_sort,b_sort = a,b
             aK_sort = np.sort(a / K_sum_cols)[::-1]
             bK_sort = np.sort(b / K_sum_rows)[::-1]
 
@@ -187,7 +193,7 @@ class Screenkhorn:
         u0 = np.full(len(self.I), (1. / len(self.I)) + self.epsilon / self.fact_scale)
         v0 = np.full(len(self.J), (1. / len(self.J)) + self.epsilon * self.fact_scale)
 
-        u, v = self.restricted_sinkhorn(u0, v0, max_iter=5)
+        u, v = self.restricted_sinkhorn(u0, v0, max_iter=10)
 
         # params of bfgs
         theta0 = np.hstack([u, v])

### 2019-05-09 code/domain_adaptation_maxime.py
fichiers modifie

@@ -1,0 +1,1434 @@
+# -*- coding: utf-8 -*-
+"""
+Domain adaptation with optimal transport
+"""
+
+# Author: Remi Flamary <remi.flamary@unice.fr>
+#         Nicolas Courty <ncourty@irisa.fr>
+#         Michael Perrot <michael.perrot@univ-st-etienne.fr>
+#
+# License: MIT License
+
+import numpy as np
+import scipy.linalg as linalg
+
+from ot.bregman import sinkhorn
+from ot.lp import emd
+from ot.utils import unif, dist, kernel, cost_normalization
+from ot.utils import check_params, BaseEstimator
+from ot.optim import cg
+from ot.optim import gcg
+
+from new_formulation_maxime import Screenkhorn
+
+def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
+                     numInnerItermax=200, stopInnerThr=1e-9, verbose=False,
+                     log=False, **kwargs):
+    """
+    Solve the entropic regularization optimal transport problem with nonconvex
+    group lasso regularization
+
+    The function solves the following optimization problem:
+
+    .. math::
+        \gamma = arg\min_\gamma <\gamma,M>_F + reg\cdot\Omega_e(\gamma)
+        + \eta \Omega_g(\gamma)
+
+        s.t. \gamma 1 = a
+
+             \gamma^T 1= b
+
+             \gamma\geq 0
+    where :
+
+    - M is the (ns,nt) metric cost matrix
+    - :math:`\Omega_e` is the entropic regularization term
+        :math:`\Omega_e(\gamma)=\sum_{i,j} \gamma_{i,j}\log(\gamma_{i,j})`
+    - :math:`\Omega_g` is the group lasso  regulaization term
+      :math:`\Omega_g(\gamma)=\sum_{i,c} \|\gamma_{i,\mathcal{I}_c}\|^{1/2}_1`
+      where  :math:`\mathcal{I}_c` are the index of samples from class c
+      in the source domain.
+    - a and b are source and target weights (sum to 1)
+
+    The algorithm used for solving the problem is the generalised conditional
+    gradient as proposed in  [5]_ [7]_
+
+
+    Parameters
+    ----------
+    a : np.ndarray (ns,)
+        samples weights in the source domain
+    labels_a : np.ndarray (ns,)
+        labels of samples in the source domain
+    b : np.ndarray (nt,)
[…]

### 2019-05-09 new_formulation_maxime.py

@@ -1,0 +1,304 @@
+# -*- coding: utf-8 -*-
+"""
+    screenkhorn: solver for screening Sinkhorn via dual projection
+"""
+__author__ = 'Mokhtar Z. Alaya'
+
+import numpy as np
+from scipy.optimize import fmin_l_bfgs_b
+from time import time
+
+class Screenkhorn:
+
+    def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True):
+
+        tic_initial = time()
+        self.a = np.asarray(a, dtype=np.float64)
+        self.b = np.asarray(b, dtype=np.float64)
+        
+        self.a_sort = np.copy(self.a)
+        self.b_sort = np.copy(self.b)
+        self.C = np.asarray(C, dtype=np.float64)
+        self.reg = reg
+        n = C.shape[0]
+        m = C.shape[1]
+        self.N = N
+        self.M = M
+        self.verbose = verbose
+        self.uniform = uniform
+
+        # K
+        # self.K = np.empty_like(self.C)
+        # np.divide(self.C, - self.reg, out=self.K)
+        # np.exp(self.K, out=self.K)
+
+        self.K = np.exp(-self.C / self.reg)
+
+        # Test
+        if self.N == n and self.M == m:
+
+            # I, J
+            self.I = list(range(n))
+            self.J = list(range(m))
+
+            # epsilon
+            self.epsilon = 0.0
+            # scale factor
+            self.fact_scale = 1.0
+
+            # restricted Sinkhron
+            self.cst_u = 0.
+            self.cst_v = 0.
+
+            # box BFGS
+            self.bounds_u = [(0.0, np.inf)] * n
+            self.bounds_v = [(0.0, np.inf)] * m
+
+        else:
+            
+            if self.verbose:
+                print(time() - tic_initial)
+            # sum of rows and columns of K
+            K_sum_cols = self.K.sum(axis=1)
+            K_sum_rows = self.K.T.sum(axis=1)
+
+            # K_min
+            K_min = self.K.min()
+
+            # 
+            if not self.uniform:
+                self.a_sort = np.sort(a)
+                self.b_sort = np.sort(b)
+          
+                
+                
+            aK_sort = np.sort(a / K_sum_cols)[::-1]
+            bK_sort = np.sort(b / K_sum_rows)[::-1]
+
[…]

### 2019-05-10 tex/v2/screenkhorn.tex
Add first draft of paper

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%\usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[preprint]{neurips_2019}
\usepackage[]{neurips_2019}
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

%--------------------------------------------------------------------------------------------------------------------------------%

\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
\usepackage[titletoc,title]{appendix}%
\usepackage{dsfont}%
\usepackage{caption} % 
\usepackage{subcaption}
\usepackage{float}%
\usepackage{graphicx, color}% 
\usepackage{bm}%bold equations

%% formatting appendices
\usepackage{etoolbox}
\patchcmd{\appendices}{\quad}{. }{}{}

%% tables
\usepackage{pgfplots}%
\usepackage{booktabs,multirow,array,multicol}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

%% algorithms
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

%% sections
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{fact}{Fact}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}%[section]
\newtheorem*{notation}{Notation}%[section]
\newtheorem{discus}{Discussion}%[section]
\newtheorem{remark}{Remark}%[section]
\newtheorem{example}{Example}%[section]
\newtheorem{exs}{Examples}%[section]
\newtheorem{ca}{Cas}
\newtheorem{remarks}{Remarks}%[section]
\newtheorem{assumption}{Assumption}{\bf}{\rm}%

% math macros

\usepackage{relsize}
\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}

\newcommand{\ba}{\mathbf{a}}%
\newcommand{\bb}{\mathbf{b}}%

\newcommand{\bC}{{\mathbf C}}%
\newcommand{\bP}{{\mathbf P}}%
\newcommand{\bU}{{\mathbf U}}%

\newcommand{\cX}{\mathcal X}%
\newcommand{\cY}{\mathcal Y}%
\newcommand{\cM}{\mathcal M}%
\newcommand{\cC}{\mathcal C}%

\newcommand{\td}{\text d}%
\newcommand*{\argminl}{\argmin\limits}%
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sumin}{\sum_{i=1}^n}
\newcommand{\sumip}{\sum_{j=1}^m}
\newcommand{\intt}{\int_{0}^{t}}
\newcommand{\inttau}{\int_{0}^{\gamma}}
\newcommand{\I}{1\!\mbox{I}}
\newcommand{\e}{{\mathrm e}}
\newcommand{\diff}{\mathrm d}
\newcommand{\noi}{\noindent}
\newcommand{\eps}{\varepsilon}
\usepackage{datenumber}
\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
\newcommand{\inr}[1]{\langle #1 \rangle}
\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\V}{\mathds{V}}
\newcommand{\Lim}{\displaystyle \lim\limits}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cT}{\mathcal T}
\newcommand{\bA}{{\boldsymbol A}}%
\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
\newcommand{\bB}{{\boldsymbol B}}%
\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
\newcommand{\bD}{{\boldsymbol D}}%
\newcommand{\bE}{{\boldsymbol E}}%
\newcommand{\bF}{{\boldsymbol F}}%
\newcommand{\bG}{{\boldsymbol G}}%
\newcommand{\bH}{{\boldsymbol H}}%
\newcommand{\bI}{{\boldsymbol I}}%
\newcommand{\bJ}{{\boldsymbol J}}%
\newcommand{\bK}{{\boldsymbol K}}%
\newcommand{\bL}{{\boldsymbol L}}%
\newcommand{\bM}{{\boldsymbol M}}%
\newcommand{\bN}{{\boldsymbol N}}%
\newcommand{\bO}{\boldsymbol 0}%
\newcommand{\bQ}{\boldsymbol Q}%
\newcommand{\bR}{\boldsymbol R}%
\newcommand{\cS}{{\mathcal{S}}}%
\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
\newcommand{\bV}{\boldsymbol V}%
\newcommand{\bW}{\boldsymbol W}%
\newcommand{\bX}{\boldsymbol  X}%
\newcommand{\bT}{\boldsymbol  T}%
\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
\newcommand{\by}{\boldsymbol y}%
\newcommand{\bu}{\boldsymbol u}%
\newcommand{\bv}{\boldsymbol  v}%
\newcommand{\bz}{\boldsymbol z}%
\newcommand{\bY}{\boldsymbol{Y}}%
\newcommand{\bZ}{\boldsymbol Z}
\newcommand{\bg}{\boldsymbol g}%
\newcommand{\beps}{\boldsymbol \varepsilon}%
\newcommand{\bSigma}{\boldsymbol \Sigma}%
\newcommand{\blambda}{\boldsymbol  \lambda}
\newcommand{\bbeta}{\boldsymbol  \beta}%
\newcommand{\bLambda}{\boldsymbol  \Lambda}%
\newcommand{\bTheta}{\boldsymbol  \Theta}
\newcommand{\bDelta}{\boldsymbol{\Delta}}%
\newcommand{\bXi}{\boldsymbol{\Xi}}%
\newcommand{\ov}{\overrightarrow}%
\newcommand{\cP}{\mathcal P}%
\newcommand{\cQ}{\mathcal Q}%
\renewcommand{\P}{\mathds{P}}
\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
\newcommand{\btheta}{\boldsymbol  \Theta}%
\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
\usepackage{accents}
\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
%{\accentset{\raisebox{0ex}{$.$}}{#1}}
\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}

\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}

%% math operators
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

% todo
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%--------------------------------------------------------------------------------------------------------------------------------%

\title{Screening Sinkhorn Algorithm via Dual Projections}

\begin{document}

\maketitle

\begin{abstract}

This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to define two appropriate active indices sets for the potential variables.
These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
\end{abstract}

\section{Introduction}

Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\cite{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
This effectively leads to improve performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally $\bigO(n^3\log n)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$

A remedy to the heavy computation burden of OT lies in a prevalent approach referred to as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.  
Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
Furthermore,~\cite{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\cite{sinkhorn1967,knight2008,kalantari2008}.

% \paragraph{Related work.}

Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
\cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.

% \paragraph{Our contribution.}

We give a new algorithm to approximate the regularized OT distance between discrete measures. 
Our algorithmic analysis is based on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.
We prove that dual solution of this approximation guarantees the existence of two active indices sets for the potential variables.
These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence, and hence we develop the Screenkhorn algorithm.
% The proposed algorithm consits of

% \paragraph{Outline of paper.}

The remainder of the paper is organized as follow. In Section~\ref{sec:optimal_transport} we briefly review the basic setup of regularized discrete OT. 
Section~\ref{sec:screenkhorn} contains our main contribution, that is, the Screenkhorn algorithm. 
Section~\ref{sec:error_analysis} devotes to theoretical guarantees for the marginal violations of Screenkhorn. 
In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
The proofs of theoretical results are postponed to the supplementary material.

\paragraph{Notation.}

For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively. The coordinates $r_i(T)$ and $c_j(T)$ denote the $i$-th row sum and the $j$-th column sum of $T$, respectively.
The scalar product between two matrices denotes the usual inner product, that is $\inr{T, W} = \text{tr}(T^\top W) = \sum_{i,j}T_{ij}W_{ij},$ where $T^\top$ is the transpose of $T$. 
We write $\mathbf{1}$ (resp. $\mathbf{0}$) the vector having all coordinates equal to one (resp. zero).
$\Delta(w)$ denotes the diag operator, such that if $w \in \R^n$, then $\Delta(w) = \text{diag}(w_1, \ldots, w_n)\in \R^{n\times n}$.
For a set of indices $L=\{i_1, \ldots, i_k\} \subseteq \{1, \ldots, n\}$ satisfying $i_1 < \cdots <i_k,$ we denote the complementary set of $L$ by $L^\complement = \{1, \ldots, n\} \backslash L$. We also denote $|L|$ the cardinality of $L$.
Given a vector $w \in \R^n$, we denote $w_L= (w_{i_1}, \ldots, w_{i_k})^\top \in \R^k$ and its complementary $w_{L^\complement} \in \R^{n- k}$.  The notation is similar for matrices; given another subset of indices $S = \{j_1, \ldots, j_l\} \subseteq \{1, \ldots, m\}$ with $j_1 < \cdots <j_l,$ and a matrix $T\in \R^{n\times m}$, we use $T_{(L,S)}$, to denote the submatrix of $T$, namely the rows and columns of $T_{(L,S)}$ are indexed by $L$ and $S$ respectively.
When applied to matrices and vectors,  $\odot$ and $\oslash$ (Hadamard product and division) and exponential notations refer to elementwise operators.
Given two real numbers $a$ and $b$, we write $a\vee b = \max(a,b)$ and $a\wedge b = \min(a,b).$

\section{Regularized discrete OT} 
\label{sec:optimal_transport}

 We briefly present in this section the setup of OT between two discrete measures. We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$, where $\Sigma_n$ is the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
We denote their probabilistic couplings set as $\Pi(\mu, \nu) = \{P \in \R_+^{n\times m}, P\mathbf{1}_m = \mu, P^\top \mathbf{1}_n = \nu\}.$ 
\paragraph{Sinkhorn divergence.}

Approximating OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
\begin{equation}
  \label{monge-kantorovich}
  \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{C, P},
\end{equation}
where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $C= (C_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements and related to the energy needed to move a probability mass from $x_i$ to $y_j$. 
The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
\begin{equation}
\label{sinkhorn-primal}
  \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
\end{equation}
where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.

\paragraph{Dual of Sinkhorn divergence.}

Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
\begin{equation*}
  \mathscr{L}(P,y, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
\end{equation*}
The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$. It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable. Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$. Therefore, we get 
\begin{equation}
  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
\end{equation}
for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
\begin{equation}
\label{sinkhorn-dual}
\min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
\end{equation}
where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
Therefore, the optimal solution of Sinkhorn divergence is given by $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
where the couple $(u^\star, v^\star)$ satisfies:
\begin{align*}
\label{sinkhorn-dual}
  (u^\star, v^\star) &= \argmin_{u \in \R^{n}, v\in \R^m} \{\Psi(u,v)\}.
\end{align*}
Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.

\section{Screened dual of Sinkhorn divergence}
\label{sec:screenkhorn}

% In this section we describe the main algorithm studied in this paper. 
For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
\begin{equation} 
\label{screen-sinkhorn}
\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
\end{equation}
where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.

The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:

\begin{lemma}
\label{lemma_actives_sets}
Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
Define
\begin{equation}
\label{I_epsilon_kappa_J_epsilon_kappa}
I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
\end{equation}
Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
\end{lemma}

First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$ 
which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.

\paragraph{Screening with a fixed number budget of points.}

Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.

Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
\begin{equation}
\label{epsilon_kappa}
 \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
\end{equation}
Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.

Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where 
\begin{equation*}
\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
\end{equation*}
and 
\begin{equation*}
	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
\end{equation*}
where the vector comparison $\succeq$ has to be understood elementwise.
Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as 
\begin{align}
\label{screen-sinkhorn_second_def}
\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
\end{align}
where 
\begin{align*} 
\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
\end{align*}
with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.

The Screenkhorn algorithm, presented in Algorithm~\ref{screenkhorn}, consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked vector $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}) \in \R^{n_b\times m_b}.$ 
It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. Furthermore, it Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ from the Gibbs matrix $K$, in contrast to Sinkhorn that performs alternating updates of all rows and columns of $K.$

The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
\begin{lemma}
\label{lemma_bounds_of_usc_and_vsc}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
one has
\begin{equation}
\label{bound_on_u}
\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
\end{equation}
and
\begin{equation}
\label{bound_on_v}
\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
\end{equation}
for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
\end{lemma}

\LinesNotNumbered
\begin{algorithm}[htbp]
\SetNlSty{textbf}{}{.}
\DontPrintSemicolon
\caption{Screenkhorn}
\label{screenkhorn}
\textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\

\textbf{step 1:} \textcolor{black}{Initialization}\\

% \nl   $K \gets \exp(-C/\eta);$\\
\nl   $\xi \gets \mu \oslash r(K);$ \\
\nl   $\zeta \gets \nu \oslash c(K);$\\
\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\

% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}

\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}

\textbf{step 2:} \textcolor{black}{L-BFGS}\\

\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\

% \textbf{step 4:} \textcolor{black}{Output}\\

\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
\end{algorithm}

\section{Analysis of marginal violations}
\label{sec:error_analysis}

This section is devoted to study the marginal violations of Screenkhorn. Towards this end, let us define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. % while Proposition~\ref{proposition_error_in_marginals} gives also an upper bound of the marginal errors.

\begin{lemma}
\label{lemma_bounds_on_marginals}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
Then one has 
\begin{equation*}
\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
\end{equation*}
and 
\begin{equation*}
\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\min_{i,j}K_{ij}} + (n-n_b)\varepsilon^2\Big).
\end{equation*}
\end{lemma}
The following Proposition gives also an upper bound of the marginal errors.
\begin{proposition}
\label{proposition_error_in_marginals}
One has 
\begin{align*}
\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq &7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
\end{align*}
and 
\begin{align*}
\norm{{\nu} -{\nu}^{\text{sc}}}^2_1 \leq &7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)% \bigg\}^{1/2}
\end{align*}

\end{proposition}

\section{Numerical experiments}
\label{sec:numerical_experiments}

% \subsubsection*{Acknowledgments}

% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.

\small
\bibliography{biblio}
\bibliographystyle{plain}

\end{document}

### 2019-05-13 tex/v2/screenkhorn.tex
Add first draft of paper

@@
 This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to define two appropriate active indices sets for the potential variables.
+Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
 These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
@@
 Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally $\bigO(n^3\log n)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
+For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
 
@@
 These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence, and hence we develop the Screenkhorn algorithm.
-% The proposed algorithm consits of
+We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
+The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS,cuturi2016SIAM,blondel2018ICML}.
 
@@
 We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
-Therefore, the optimal solution of Sinkhorn divergence is given by $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
+Therefore, the optimal solution $P^\star$ of Sinkhorn divergence takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
 where the couple $(u^\star, v^\star)$ satisfies:
@@
 Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
+Furthermore, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity.
 
@@
 
-The Screenkhorn algorithm, presented in Algorithm~\ref{screenkhorn}, consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$.
-The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked vector $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}) \in \R^{n_b\times m_b}.$ 
-It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$.
-Furthermore, it Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ from the Gibbs matrix $K$, in contrast to Sinkhorn that performs alternating updates of all rows and columns of $K.$
+Pseudocode of our proposed algorithm is given in Algorithm~\ref{screenkhorn}.
+Screenkhorn consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
+The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
+% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
+It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
 
@@
 \DontPrintSemicolon
-\caption{Screenkhorn}
+\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
 \label{screenkhorn}
-\textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
+% \textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
 
@@
 One has 
-\begin{align*}
-\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq &7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+\begin{align*} %{\norm{{\mu}^{\text{sc}}}_1} 
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
 &+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
@@
 and 
-\begin{align*}
-\norm{{\nu} -{\nu}^{\text{sc}}}^2_1 \leq &7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)% \bigg\}^{1/2}
+\begin{align*} %{\norm{{\nu}^{\text{sc}}}_1}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
+&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
 \end{align*}

### 2019-05-13 tex/v2/screenkhorn.tex
cleaning
change title
test
improve intro of paper

@@
 
-\title{Screening Sinkhorn Algorithm via Dual Projections}
+\title{Screening Sinkhorn Algorithm via Dual Projection}
 
@@
 
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred to as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
+A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
 Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.

### 2019-05-13 new_formulation.py
new

@@ -1,223 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-    screenkhorn: solver for screening Sinkhorn via dual projection
-"""
-__author__ = 'Mokhtar Z. Alaya'
-
-import numpy as np
-from scipy.optimize import fmin_l_bfgs_b
-from time import time
-from numba import jit
-
-class Screenkhorn:
-
-    def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True):
-
-        tic_initial = time()
-        self.a = np.asarray(a, dtype=np.float64)
-        self.b = np.asarray(b, dtype=np.float64)
-        self.C = np.asarray(C, dtype=np.float64)
-        self.reg = reg
-        n = C.shape[0]
-        m = C.shape[1]
-        self.N = N
-        self.M = M
-        self.verbose = verbose
-        self.uniform = uniform
-
-        # K
-        self.K = np.empty_like(self.C)
-        np.divide(self.C, - self.reg, out=self.K)
-        np.exp(self.K, out=self.K)
-
-        #self.K = np.exp(-self.C / self.reg)
- 
-        
-        print('K',time() - tic_initial)
-
-        # Test
-        if self.N == n and self.M == m:
-
-            # I, J
-            self.I = list(range(n))
-            self.J = list(range(m))
-
-            # epsilon
-            self.epsilon = 0.0
-            # scale factor
-            self.fact_scale = 1.0
-
-            # restricted Sinkhron
-            self.cst_u = 0.
-            self.cst_v = 0.
-
-            # box BFGS
-            self.bounds_u = [(0.0, np.inf)] * n
-            self.bounds_v = [(0.0, np.inf)] * m
-
-        else:
-            
-            print(time() - tic_initial)
-            # sum of rows and columns of K
-            K_sum_cols = self.K.sum(axis=1)
-            K_sum_rows = self.K.T.sum(axis=1)
-
-            # K_min
-            K_min = self.K.min()
-
-            # 
-            if not self.uniform:
-                a_sort = np.sort(a)
-                b_sort = np.sort(b)
-            else:
-                a_sort,b_sort = a,b
-            aK_sort = np.sort(a / K_sum_cols)[::-1]
-            bK_sort = np.sort(b / K_sum_rows)[::-1]
-
-            epsilon_u_square = aK_sort[self.N - 1: self.N].mean()
[…]

### 2019-05-13 DA_toy.py
new

@@ -28,10 +28,7 @@ import matplotlib.pylab as pl
 import ot
 import ot.plot
 
-import sys
-path_files = './code/'
-sys.path.insert(0, path_files) 
-import domain_adaptation as da_screenkhorn
+import domain_adaptation_maxime as da_screenkhorn
 from sklearn.neighbors import KNeighborsClassifier
 
 
@@ -51,8 +48,8 @@ import seaborn as sns
 # -------------
 
 
-n_samples_source = 5000
-n_samples_target = 5000
+n_samples_source = 2000
+n_samples_target = 2000
 
 Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=1,random_state=None)
 Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=1, random_state=None)
@@ -62,8 +59,8 @@ M = ot.dist(Xs, Xt, metric='sqeuclidean')
 #%% 
 # Sinkhorn Transport
 tic = time()
-ot_sinkhorn = ot.da.SinkhornTransport(reg_e=1e0)
-ot_sinkhorn.fit(Xs=Xs, Xt=Xt)
+ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1e0,reg_cl=10)
+ot_sinkhorn.fit(Xs=Xs,ys= ys, Xt=Xt)
 time_sink = time() - tic
 transp_Xs = ot_sinkhorn.transform(Xs=Xs)
 

### 2019-05-13 DA_toy_maxime.py

@@ -33,9 +33,9 @@ import time
 
 # PATH 
 import sys
-path_files = '/home/berar/github/Mokhtar/screenkhorn/code'
-sys.path.insert(0, path_files) 
-import domain_adaptation as da_screenkhorn
+#path_files = '/home/berar/github/Mokhtar/screenkhorn/code'
+#sys.path.insert(0, path_files) 
+import domain_adaptation_maxime as da_screenkhorn
 
 
 # In[3]:
@@ -72,8 +72,8 @@ sns.set_style("ticks")
 # In[4]:
 
 
-n_samples_source = 120
-n_samples_target = 120
+n_samples_source = 1000
+n_samples_target = 1000
 
 Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source)
 Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target)

### 2019-05-13 screenkhorn.py

@@ -13,6 +13,10 @@ class Screenkhorn:
     def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True):
 
         tic_initial = time()
+        # In wda_screen.py autograd package is used, we then have to change some arrays from "ArrayBox" type to "np.array".
+        if isinstance(C,np.ndarray) == False:
+            C = C._value
+        
         self.a = np.asarray(a, dtype=np.float64)
         self.b = np.asarray(b, dtype=np.float64)
         

### 2019-05-13 wda_expe.py

@@ -1,6 +1,3 @@
-
-
-
 import os
 os.environ["OMP_NUM_THREADS"] = "1"
 import numpy as np
@@ -14,8 +11,6 @@ warnings.filterwarnings("ignore", category=FutureWarning)
 from time import process_time as time
 import argparse
 import sys
-path_files = './code/'
-sys.path.insert(0, path_files) 
 import wda_screen as wda_screen
 from sklearn.neighbors import KNeighborsClassifier
 from sklearn.datasets import make_blobs

### 2019-05-13 domain_adaptation_maxime.py
new

@@ -1,0 +1,1434 @@
+# -*- coding: utf-8 -*-
+"""
+Domain adaptation with optimal transport
+"""
+
+# Author: Remi Flamary <remi.flamary@unice.fr>
+#         Nicolas Courty <ncourty@irisa.fr>
+#         Michael Perrot <michael.perrot@univ-st-etienne.fr>
+#
+# License: MIT License
+
+import numpy as np
+import scipy.linalg as linalg
+
+from ot.bregman import sinkhorn
+from ot.lp import emd
+from ot.utils import unif, dist, kernel, cost_normalization
+from ot.utils import check_params, BaseEstimator
+from ot.optim import cg
+from ot.optim import gcg
+
+from screenkhorn import Screenkhorn
+
+def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
+                     numInnerItermax=200, stopInnerThr=1e-9, verbose=False,
+                     log=False, **kwargs):
+    """
+    Solve the entropic regularization optimal transport problem with nonconvex
+    group lasso regularization
+
+    The function solves the following optimization problem:
+
+    .. math::
+        \gamma = arg\min_\gamma <\gamma,M>_F + reg\cdot\Omega_e(\gamma)
+        + \eta \Omega_g(\gamma)
+
+        s.t. \gamma 1 = a
+
+             \gamma^T 1= b
+
+             \gamma\geq 0
+    where :
+
+    - M is the (ns,nt) metric cost matrix
+    - :math:`\Omega_e` is the entropic regularization term
+        :math:`\Omega_e(\gamma)=\sum_{i,j} \gamma_{i,j}\log(\gamma_{i,j})`
+    - :math:`\Omega_g` is the group lasso  regulaization term
+      :math:`\Omega_g(\gamma)=\sum_{i,c} \|\gamma_{i,\mathcal{I}_c}\|^{1/2}_1`
+      where  :math:`\mathcal{I}_c` are the index of samples from class c
+      in the source domain.
+    - a and b are source and target weights (sum to 1)
+
+    The algorithm used for solving the problem is the generalised conditional
+    gradient as proposed in  [5]_ [7]_
+
+
+    Parameters
+    ----------
+    a : np.ndarray (ns,)
+        samples weights in the source domain
+    labels_a : np.ndarray (ns,)
+        labels of samples in the source domain
+    b : np.ndarray (nt,)
+        samples weights in the target domain
[…]

### 2019-05-13 wda_screenkhorn.py
new

@@ -1,0 +1,194 @@
+# -*- coding: utf-8 -*-
+"""
+Dimension reduction with optimal transport
+"""
+
+# Author: Remi Flamary <remi.flamary@unice.fr>
+#
+# License: MIT License
+
+from scipy import linalg
+# import numpy as np
+import autograd.numpy as np
+from pymanopt.manifolds import Stiefel
+from pymanopt import Problem
+from pymanopt.solvers import SteepestDescent, TrustRegions
+
+#from wda_formulation_screekhorn import Screenkhorn
+from screenkhorn import Screenkhorn
+
+def dist(x1, x2):
+    """ Compute squared euclidean distance between samples (autograd)
+    """
+    x1p2 = np.sum(np.square(x1), 1)
+    x2p2 = np.sum(np.square(x2), 1)
+    return x1p2.reshape((-1, 1)) + x2p2.reshape((1, -1)) - 2 * np.dot(x1, x2.T)
+
+
+def Sinkhorn(w1, w2, M, reg, k):
+    """Sinkhorn algorithm with fixed number of iteration (autograd)
+    """
+    K = np.exp(-M / reg)
+    ui = np.ones((M.shape[0],))
+    vi = np.ones((M.shape[1],))
+    for i in range(k):
+        vi = w2 / (np.dot(K.T, ui))
+        ui = w1 / (np.dot(K, vi))
+    G = ui.reshape((M.shape[0], 1)) * K * vi.reshape((1, M.shape[1]))
+    return G
+
+
+def split_classes(X, y):
+    """split samples in X by classes in y
+    """
+    lstsclass = np.unique(y)
+    return [X[y == i, :].astype(np.float64) for i in lstsclass]
+
+
+def fda(X, y, p=2, reg=1e-16):
+    mx = np.mean(X)
+    X -= mx.reshape((1, -1))
+
+    # data split between classes
+    d = X.shape[1]
+    xc = split_classes(X, y)
+    nc = len(xc)
+
+    p = min(nc - 1, p)
+
+    Cw = 0
+    for x in xc:
+        Cw += np.cov(x, rowvar=False)
+    Cw /= nc
+
+    mxc = np.zeros((d, nc))
+
+    for i in range(nc):
+        mxc[:, i] = np.mean(xc[i])
+
+    mx0 = np.mean(mxc, 1)
+    Cb = 0
+    for i in range(nc):
[…]

### 2019-05-13 DA_toy_maxime.py
expe

@@ -35,7 +35,7 @@ import time
 import sys
 #path_files = '/home/berar/github/Mokhtar/screenkhorn/code'
 #sys.path.insert(0, path_files) 
-import domain_adaptation_maxime as da_screenkhorn
+import   da_screenkhorn
 
 
 # In[3]:
@@ -72,8 +72,8 @@ sns.set_style("ticks")
 # In[4]:
 
 
-n_samples_source = 1000
-n_samples_target = 1000
+n_samples_source = 500
+n_samples_target = 500
 
 Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source)
 Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target)

### 2019-05-13 da_expe.py

@@ -1,97 +1,66 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-# 
-# # OT for domain adaptation on empirical distributions
-# 
-# 
-# This example introduces a domain adaptation in a 2D setting. It explicits
-# the problem of domain adaptation and introduces some optimal transport
-# approaches to solve it.
-# 
-# Quantities such as optimal couplings, greater coupling coefficients and
-# transported samples are represented in order to give a visual understanding
-# of what the transport methods are doing.
-# 
-# 
 
 # In[1]:
 
-
-# Authors: Remi Flamary <remi.flamary@unice.fr>
-#          Stanislas Chambon <stan.chambon@gmail.com>
-#
-# License: MIT License
 
 from time import process_time as time
 import matplotlib.pylab as pl
 import ot
 import ot.plot
 
-import domain_adaptation_maxime as da_screenkhorn
+import  da_screenkhorn
 from sklearn.neighbors import KNeighborsClassifier
-
-
-# In[3]:
-
-
-# NUMPY
 import numpy as np
-import matplotlib.pyplot as plt
-
-
-# SEABORN 
-import seaborn as sns
-
-
-# generate data
-# -------------
 
 
 n_samples_source = 2000
 n_samples_target = 2000
 
-Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=1,random_state=None)
-Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=1, random_state=None)
-M = ot.dist(Xs, Xt, metric='sqeuclidean')
+nb_iter = 10
 
+bc_sink = np.zeros(nb_iter)
+bc_screen = np.zeros(nb_iter)
+time_sink = np.zeros(nb_iter)
+time_screen = np.zeros(nb_iter)
+for i in range(nb_iter):
 
-#%% 
-# Sinkhorn Transport
-tic = time()
-ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1e0,reg_cl=10)
-ot_sinkhorn.fit(Xs=Xs,ys= ys, Xt=Xt)
-time_sink = time() - tic
-transp_Xs = ot_sinkhorn.transform(Xs=Xs)
-
-K = 3
[…]

### 2019-05-13 da_screenkhorn.py

@@ -1,4 +1,3 @@
-# -*- coding: utf-8 -*-
 """
 Domain adaptation with optimal transport
 """

### 2019-05-13 wda_expe.py

@@ -10,8 +10,7 @@ import warnings
 warnings.filterwarnings("ignore", category=FutureWarning)
 from time import process_time as time
 import argparse
-import sys
-import wda_screen as wda_screen
+import wda_screenkhorn as wda_screen
 from sklearn.neighbors import KNeighborsClassifier
 from sklearn.datasets import make_blobs
 from scipy.io import loadmat

### 2019-05-13 da_expe.py
figure

@@ -52,7 +52,7 @@ for i in range(nb_iter):
     # Screenkhorn Transport
     tic = time()
     ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1e0,reg_cl=10)
-    ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, n_b=5, m_b=5)
+    ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, n_b=10, m_b=10)
     time_screen[i] = time() - tic
     # transport source samples onto target samples
     transp_Xs_screenkhorn = ot_screenkhorn.transform(Xs=Xs)
@@ -62,5 +62,6 @@ for i in range(nb_iter):
     y_pred = clf_screened.predict(Xt)
     bc_screen[i] = np.mean(y_pred==yt)
     
-
-
+#%%
+print('gain : {:2.2f}'.format(time_sink.mean()/time_screen.mean()))
+print('perf sink : {:2.2f}, perf screen {:2.2f}'.format(bc_sink.mean(),bc_screen.mean()))

### 2019-05-13 wda_expe.py

@@ -95,7 +95,7 @@ reg = 1  # regularizer weight
 k = 10  # nb of sinkhorn iteration
 maxiter = 1000 # max iter in WDA
 nb_iter = 50
-K = 1 # K in KNN
+K = 5 # K in KNN
 p_vec = [2,10,20,30]
 pathres='./resultat/'
 

### 2019-05-13 da_expe.py
expe

@@ -6,7 +6,7 @@
 
 
 from time import process_time as time
-import matplotlib.pylab as pl
+import matplotlib.pylab as plt
 import ot
 import ot.plot
 
@@ -19,19 +19,23 @@ n_samples_source = 2000
 n_samples_target = 2000
 
 nb_iter = 10
+pathres='./resultat/'
+p_vec = [2,10,20,30]
+n_pvec=  len(p_vec)
 
 bc_sink = np.zeros(nb_iter)
-bc_screen = np.zeros(nb_iter)
+bc_screen = np.zeros((nb_iter,n_pvec))
 time_sink = np.zeros(nb_iter)
-time_screen = np.zeros(nb_iter)
+time_screen = np.zeros((nb_iter,n_pvec))
 for i in range(nb_iter):
 
-    
-    Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=1,random_state=None)
-    Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=1, random_state=None)
+    print('iter:',i)
+
+    Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=0.5,random_state=i)
+    Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=0.5, random_state=i)
     M = ot.dist(Xs, Xt, metric='sqeuclidean')
     
-    
+    filename = 'da'
     #%% 
     # Sinkhorn Transport
     tic = time()
@@ -48,20 +52,25 @@ for i in range(nb_iter):
     
     #%%
     
-    
-    # Screenkhorn Transport
-    tic = time()
-    ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1e0,reg_cl=10)
-    ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, n_b=10, m_b=10)
-    time_screen[i] = time() - tic
-    # transport source samples onto target samples
-    transp_Xs_screenkhorn = ot_screenkhorn.transform(Xs=Xs)
-    
-    clf_screened = KNeighborsClassifier(K)
-    clf_screened.fit(transp_Xs_screenkhorn, ys)
-    y_pred = clf_screened.predict(Xt)
-    bc_screen[i] = np.mean(y_pred==yt)
+    for j,p_n in enumerate(p_vec):
+        # Screenkhorn Transport
+        tic = time()
[…]

### 2019-05-14 da_expe.py
expe

@@ -18,7 +18,7 @@ import numpy as np
 n_samples_source = 2000
 n_samples_target = 2000
 
-nb_iter = 10
+nb_iter = 50
 pathres='./resultat/'
 p_vec = [2,10,20,30]
 n_pvec=  len(p_vec)

### 2019-05-14 da_expe.py
expe

@@ -9,18 +9,32 @@ from time import process_time as time
 import matplotlib.pylab as plt
 import ot
 import ot.plot
-
 import  da_screenkhorn
 from sklearn.neighbors import KNeighborsClassifier
 import numpy as np
+import argparse
 
 
-n_samples_source = 2000
-n_samples_target = 2000
+parser = argparse.ArgumentParser()
+parser.add_argument('-n', action='store', dest='n', default = 1000, type=int,
+                        help='number of samples ')
+parser.add_argument('-d', action='store', dest='d', default = 1, type=int,
+                        help='dataset type ')
+arguments = parser.parse_args()
+n = arguments.n # number of samples per class
+
+if arguments.d == 1:
+    data = 'toy'
+else:
+    data = 'mnist'
+    
+
+n_samples_source = n
+n_samples_target = n
 
 nb_iter = 50
 pathres='./resultat/'
-p_vec = [2,10,20,30]
+p_vec = [1.5,2,5,10]
 n_pvec=  len(p_vec)
 
 bc_sink = np.zeros(nb_iter)
@@ -31,11 +45,11 @@ for i in range(nb_iter):
 
     print('iter:',i)
 
-    Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=0.5,random_state=i)
-    Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=0.5, random_state=i)
+    Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=0.75,random_state=i)
+    Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=0.75, random_state=i)
     M = ot.dist(Xs, Xt, metric='sqeuclidean')
     
-    filename = 'da'
+    filename = 'da_{:}_{:d}'.format(data,n)
     #%% 
     # Sinkhorn Transport
     tic = time()
@@ -71,6 +85,9 @@ for i in range(nb_iter):
              bc_sink= bc_sink,  bc_screen= bc_screen,
              time_sink = time_sink,  time_screen = time_screen)
     
-    
-print('gain : {:2.2f}'.format(time_sink.mean()/time_screen.mean(axis=0)))
+#%%
+mean_screen_time = time_screen.mean(axis=0)
+for i,p in enumerate(p_vec):
[…]

### 2019-05-14 tex/v3/main.tex
added v3 in tex

--- 2019-05-10 tex/v2/screenkhorn.tex
@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[preprint]{neurips_2019}
 \usepackage[]{neurips_2019}
+
 % to avoid loading the natbib package, add option nonatbib:
@@
 
+\usepackage{accents}
+\usepackage{datenumber}
 %% sections
@@
 % math macros
-
-\usepackage{relsize}
-\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}
-
-\newcommand{\ba}{\mathbf{a}}%
-\newcommand{\bb}{\mathbf{b}}%
-
-\newcommand{\bC}{{\mathbf C}}%
-\newcommand{\bP}{{\mathbf P}}%
-\newcommand{\bU}{{\mathbf U}}%
-
-\newcommand{\cX}{\mathcal X}%
-\newcommand{\cY}{\mathcal Y}%
-\newcommand{\cM}{\mathcal M}%
-\newcommand{\cC}{\mathcal C}%
-
-\newcommand{\td}{\text d}%
-\newcommand*{\argminl}{\argmin\limits}%
 \newcommand{\bigO}{\mathcal{O}}
-\newcommand{\bs}{\boldsymbol}
-\newcommand{\sumin}{\sum_{i=1}^n}
-\newcommand{\sumip}{\sum_{j=1}^m}
-\newcommand{\intt}{\int_{0}^{t}}
-\newcommand{\inttau}{\int_{0}^{\gamma}}
-\newcommand{\I}{1\!\mbox{I}}
-\newcommand{\e}{{\mathrm e}}
-\newcommand{\diff}{\mathrm d}
-\newcommand{\noi}{\noindent}
-\newcommand{\eps}{\varepsilon}
-\usepackage{datenumber}
-\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
 \newcommand{\inr}[1]{\langle #1 \rangle}
-\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
 \newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
@@
 \newcommand{\E}{\mathds{E}}
-\newcommand{\V}{\mathds{V}}
-\newcommand{\Lim}{\displaystyle \lim\limits}
-\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-\newcommand{\cD}{\mathcal D}
-\newcommand{\cE}{\mathcal E}
-\newcommand{\cT}{\mathcal T}
-\newcommand{\bA}{{\boldsymbol A}}%
-\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
-\newcommand{\bB}{{\boldsymbol B}}%
-\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
-\newcommand{\bD}{{\boldsymbol D}}%
-\newcommand{\bE}{{\boldsymbol E}}%
-\newcommand{\bF}{{\boldsymbol F}}%
-\newcommand{\bG}{{\boldsymbol G}}%
-\newcommand{\bH}{{\boldsymbol H}}%
-\newcommand{\bI}{{\boldsymbol I}}%
-\newcommand{\bJ}{{\boldsymbol J}}%
-\newcommand{\bK}{{\boldsymbol K}}%
-\newcommand{\bL}{{\boldsymbol L}}%
-\newcommand{\bM}{{\boldsymbol M}}%
-\newcommand{\bN}{{\boldsymbol N}}%
-\newcommand{\bO}{\boldsymbol 0}%
-\newcommand{\bQ}{\boldsymbol Q}%
-\newcommand{\bR}{\boldsymbol R}%
-\newcommand{\cS}{{\mathcal{S}}}%
-\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
-\newcommand{\bV}{\boldsymbol V}%
-\newcommand{\bW}{\boldsymbol W}%
-\newcommand{\bX}{\boldsymbol  X}%
-\newcommand{\bT}{\boldsymbol  T}%
-\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
-\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
-\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
-\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
-\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
-\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
-\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
-\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
-\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
-\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
-\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
-\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
-\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
-\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
-\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
-\newcommand{\by}{\boldsymbol y}%
-\newcommand{\bu}{\boldsymbol u}%
-\newcommand{\bv}{\boldsymbol  v}%
-\newcommand{\bz}{\boldsymbol z}%
-\newcommand{\bY}{\boldsymbol{Y}}%
-\newcommand{\bZ}{\boldsymbol Z}
-\newcommand{\bg}{\boldsymbol g}%
-\newcommand{\beps}{\boldsymbol \varepsilon}%
-\newcommand{\bSigma}{\boldsymbol \Sigma}%
-\newcommand{\blambda}{\boldsymbol  \lambda}
-\newcommand{\bbeta}{\boldsymbol  \beta}%
-\newcommand{\bLambda}{\boldsymbol  \Lambda}%
-\newcommand{\bTheta}{\boldsymbol  \Theta}
-\newcommand{\bDelta}{\boldsymbol{\Delta}}%
-\newcommand{\bXi}{\boldsymbol{\Xi}}%
-\newcommand{\ov}{\overrightarrow}%
-\newcommand{\cP}{\mathcal P}%
-\newcommand{\cQ}{\mathcal Q}%
-\renewcommand{\P}{\mathds{P}}
-\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
-\newcommand{\btheta}{\boldsymbol  \Theta}%
 \newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
-\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
-\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
 \newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
-\usepackage{accents}
 \newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
-%{\accentset{\raisebox{0ex}{$.$}}{#1}}
-\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}
-
-\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
-\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}
 
@@
 \DeclareMathOperator*{\argmax}{\arg\!\max}
-
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-% todo
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
 %--------------------------------------------------------------------------------------------------------------------------------%
 
-\title{Screening Sinkhorn Algorithm via Dual Projections}
+\title{Screening Sinkhorn Algorithm for regularized Optimal Transport}
 
@@
 
-\section{Introduction}
-
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\cite{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
-In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
-This effectively leads to improve performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
-Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally $\bigO(n^3\log n)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
-
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred to as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
-Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\cite{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
-Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\cite{sinkhorn1967,knight2008,kalantari2008}.
-
-% \paragraph{Related work.}
-
-Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
-\cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
-
-% \paragraph{Our contribution.}
-
-We give a new algorithm to approximate the regularized OT distance between discrete measures. 
-Our algorithmic analysis is based on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
-These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.
-We prove that dual solution of this approximation guarantees the existence of two active indices sets for the potential variables.
-These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence, and hence we develop the Screenkhorn algorithm.
-% The proposed algorithm consits of
-
-% \paragraph{Outline of paper.}
-
-The remainder of the paper is organized as follow. In Section~\ref{sec:optimal_transport} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screenkhorn} contains our main contribution, that is, the Screenkhorn algorithm. 
-Section~\ref{sec:error_analysis} devotes to theoretical guarantees for the marginal violations of Screenkhorn. 
-In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
-The proofs of theoretical results are postponed to the supplementary material.
-
-\paragraph{Notation.}
-
-For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
-Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively.
-The coordinates $r_i(T)$ and $c_j(T)$ denote the $i$-th row sum and the $j$-th column sum of $T$, respectively.
-The scalar product between two matrices denotes the usual inner product, that is $\inr{T, W} = \text{tr}(T^\top W) = \sum_{i,j}T_{ij}W_{ij},$ where $T^\top$ is the transpose of $T$. 
-We write $\mathbf{1}$ (resp. $\mathbf{0}$) the vector having all coordinates equal to one (resp. zero).
-$\Delta(w)$ denotes the diag operator, such that if $w \in \R^n$, then $\Delta(w) = \text{diag}(w_1, \ldots, w_n)\in \R^{n\times n}$.
-For a set of indices $L=\{i_1, \ldots, i_k\} \subseteq \{1, \ldots, n\}$ satisfying $i_1 < \cdots <i_k,$ we denote the complementary set of $L$ by $L^\complement = \{1, \ldots, n\} \backslash L$.
-We also denote $|L|$ the cardinality of $L$.
-Given a vector $w \in \R^n$, we denote $w_L= (w_{i_1}, \ldots, w_{i_k})^\top \in \R^k$ and its complementary $w_{L^\complement} \in \R^{n- k}$.
-The notation is similar for matrices; given another subset of indices $S = \{j_1, \ldots, j_l\} \subseteq \{1, \ldots, m\}$ with $j_1 < \cdots <j_l,$ and a matrix $T\in \R^{n\times m}$, we use $T_{(L,S)}$, to denote the submatrix of $T$, namely the rows and columns of $T_{(L,S)}$ are indexed by $L$ and $S$ respectively.
-When applied to matrices and vectors,  $\odot$ and $\oslash$ (Hadamard product and division) and exponential notations refer to elementwise operators.
-Given two real numbers $a$ and $b$, we write $a\vee b = \max(a,b)$ and $a\wedge b = \min(a,b).$
-
-\section{Regularized discrete OT} 
-\label{sec:optimal_transport}
-
- We briefly present in this section the setup of OT between two discrete measures.
-We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$, where $\Sigma_n$ is the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
-We denote their probabilistic couplings set as $\Pi(\mu, \nu) = \{P \in \R_+^{n\times m}, P\mathbf{1}_m = \mu, P^\top \mathbf{1}_n = \nu\}.$ 
-\paragraph{Sinkhorn divergence.}
-
-Approximating OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
-\begin{equation}
-  \label{monge-kantorovich}
-  \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{C, P},
-\end{equation}
-where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $C= (C_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements and related to the energy needed to move a probability mass from $x_i$ to $y_j$.
-The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
-\begin{equation}
-\label{sinkhorn-primal}
-  \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
-\end{equation}
-where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.
-
-\paragraph{Dual of Sinkhorn divergence.}
-
-Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
-\begin{equation*}
-  \mathscr{L}(P,y, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
-\end{equation*}
-The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$.
-It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable.
-Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$.
-Therefore, we get
-\begin{equation}
-  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
-\end{equation}
-for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
-\begin{equation}
-\label{sinkhorn-dual}
-\min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
-\end{equation}
-where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
-We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
-Therefore, the optimal solution of Sinkhorn divergence is given by $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
-where the couple $(u^\star, v^\star)$ satisfies:
-\begin{align*}
-\label{sinkhorn-dual}
-  (u^\star, v^\star) &= \argmin_{u \in \R^{n}, v\in \R^m} \{\Psi(u,v)\}.
-\end{align*}
-Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-
-\section{Screened dual of Sinkhorn divergence}
-\label{sec:screenkhorn}
-
-% In this section we describe the main algorithm studied in this paper. 
-For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
-\begin{equation} 
-\label{screen-sinkhorn}
-\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
-\end{equation}
-where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-
-The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
-The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
-Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
-
-\begin{lemma}
-\label{lemma_actives_sets}
-Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
-Define
-\begin{equation}
-\label{I_epsilon_kappa_J_epsilon_kappa}
-I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
-\end{equation}
-Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
-\end{lemma}
-
-First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
-which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.
-
-\paragraph{Screening with a fixed number budget of points.}
-
-Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
-The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
-In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
-
-Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
-To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
-\begin{equation}
-\label{epsilon_kappa}
- \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
-\end{equation}
-Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
-Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
-\begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
-\end{equation*}
-and 
-\begin{equation*}
-	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
-\end{equation*}
-where the vector comparison $\succeq$ has to be understood elementwise.
-Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as 
-\begin{align}
-\label{screen-sinkhorn_second_def}
-\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
-\end{align}
-where 
-\begin{align*} 
-\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
-\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
-&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
-\end{align*}
-with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
-
-The Screenkhorn algorithm, presented in Algorithm~\ref{screenkhorn}, consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$.
-The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked vector $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}) \in \R^{n_b\times m_b}.$ 
-It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$.
-Furthermore, it Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ from the Gibbs matrix $K$, in contrast to Sinkhorn that performs alternating updates of all rows and columns of $K.$
-
-The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
-\begin{lemma}
-\label{lemma_bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
-one has
-\begin{equation}
-\label{bound_on_u}
-\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
-\end{equation}
-and
-\begin{equation}
-\label{bound_on_v}
-\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
-\end{equation}
-for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
-\end{lemma}
-
-\LinesNotNumbered
-\begin{algorithm}[htbp]
-\SetNlSty{textbf}{}{.}
-\DontPrintSemicolon
-\caption{Screenkhorn}
-\label{screenkhorn}
-\textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
-
-\textbf{step 1:} \textcolor{black}{Initialization}\\
-
-% \nl   $K \gets \exp(-C/\eta);$\\
-\nl   $\xi \gets \mu \oslash r(K);$ \\
-\nl   $\zeta \gets \nu \oslash c(K);$\\
-\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
-\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
-\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
-\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\
-
-% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}
-
-\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
-\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
-\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}
-
-\textbf{step 2:} \textcolor{black}{L-BFGS}\\
-
-\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
-\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
-\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
-
-% \textbf{step 4:} \textcolor{black}{Output}\\
-
-\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
-\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
-\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
-\end{algorithm}
-
-\section{Analysis of marginal violations}
-\label{sec:error_analysis}
-
-This section is devoted to study the marginal violations of Screenkhorn.
-Towards this end, let us define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$
-Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
-% while Proposition~\ref{proposition_error_in_marginals} gives also an upper bound of the marginal errors.
-
-\begin{lemma}
-\label{lemma_bounds_on_marginals}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
-Then one has 
-\begin{equation*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
-\end{equation*}
-and 
-\begin{equation*}
-\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\min_{i,j}K_{ij}} + (n-n_b)\varepsilon^2\Big).
-\end{equation*}
-\end{lemma}
-The following Proposition gives also an upper bound of the marginal errors.
-\begin{proposition}
-\label{proposition_error_in_marginals}
-One has 
-\begin{align*}
-\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq &7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
-\end{align*}
-and 
-\begin{align*}
-\norm{{\nu} -{\nu}^{\text{sc}}}^2_1 \leq &7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)% \bigg\}^{1/2}
-\end{align*}
-
-\end{proposition}
-
-\section{Numerical experiments}
-\label{sec:numerical_experiments}
+\input{section_1_introduction}
+\input{section_2_setup_OT}
+\input{section_3_algorithm}
+\input{section_4_marginal_viols}
+\input{section_5_numeric_expes}
 
@@
 \bibliography{biblio}
-\bibliographystyle{plain}
+\bibliographystyle{plain} %{abbrvnat} %{plainnat}
 

### 2019-05-14 tex/v3/section_1_introduction.tex
added v3 in tex

--- 2019-05-13 tex/v2/screenkhorn.tex
@@
-\documentclass{article}
+\section{Introduction} % (fold)
+\label{sec:introduction}
 
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-% \usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%\usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[preprint]{neurips_2019}
-\usepackage[]{neurips_2019}
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
-\usepackage[titletoc,title]{appendix}%
-\usepackage{dsfont}%
-\usepackage{caption} % 
-\usepackage{subcaption}
-\usepackage{float}%
-\usepackage{graphicx, color}% 
-\usepackage{bm}%bold equations
-
-%% formatting appendices
-\usepackage{etoolbox}
-\patchcmd{\appendices}{\quad}{. }{}{}
-
-%% tables
-\usepackage{pgfplots}%
-\usepackage{booktabs,multirow,array,multicol}
-\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
-
-%% algorithms
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-
-%% sections
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Fact}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}%[section]
-\newtheorem*{notation}{Notation}%[section]
-\newtheorem{discus}{Discussion}%[section]
-\newtheorem{remark}{Remark}%[section]
-\newtheorem{example}{Example}%[section]
-\newtheorem{exs}{Examples}%[section]
-\newtheorem{ca}{Cas}
-\newtheorem{remarks}{Remarks}%[section]
-\newtheorem{assumption}{Assumption}{\bf}{\rm}%
-
-% math macros
-
-\usepackage{relsize}
-\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}
-
-\newcommand{\ba}{\mathbf{a}}%
-\newcommand{\bb}{\mathbf{b}}%
-
-\newcommand{\bC}{{\mathbf C}}%
-\newcommand{\bP}{{\mathbf P}}%
-\newcommand{\bU}{{\mathbf U}}%
-
-\newcommand{\cX}{\mathcal X}%
-\newcommand{\cY}{\mathcal Y}%
-\newcommand{\cM}{\mathcal M}%
-\newcommand{\cC}{\mathcal C}%
-
-\newcommand{\td}{\text d}%
-\newcommand*{\argminl}{\argmin\limits}%
-\newcommand{\bigO}{\mathcal{O}}
-\newcommand{\bs}{\boldsymbol}
-\newcommand{\sumin}{\sum_{i=1}^n}
-\newcommand{\sumip}{\sum_{j=1}^m}
-\newcommand{\intt}{\int_{0}^{t}}
-\newcommand{\inttau}{\int_{0}^{\gamma}}
-\newcommand{\I}{1\!\mbox{I}}
-\newcommand{\e}{{\mathrm e}}
-\newcommand{\diff}{\mathrm d}
-\newcommand{\noi}{\noindent}
-\newcommand{\eps}{\varepsilon}
-\usepackage{datenumber}
-\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
-\newcommand{\inr}[1]{\langle #1 \rangle}
-\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
-\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
-\newcommand{\norm}[1]{\|#1\|}
-\newcommand{\R}{{\mathbb{R}}}
-\newcommand{\E}{\mathds{E}}
-\newcommand{\V}{\mathds{V}}
-\newcommand{\Lim}{\displaystyle \lim\limits}
-\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-\newcommand{\cD}{\mathcal D}
-\newcommand{\cE}{\mathcal E}
-\newcommand{\cT}{\mathcal T}
-\newcommand{\bA}{{\boldsymbol A}}%
-\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
-\newcommand{\bB}{{\boldsymbol B}}%
-\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
-\newcommand{\bD}{{\boldsymbol D}}%
-\newcommand{\bE}{{\boldsymbol E}}%
-\newcommand{\bF}{{\boldsymbol F}}%
-\newcommand{\bG}{{\boldsymbol G}}%
-\newcommand{\bH}{{\boldsymbol H}}%
-\newcommand{\bI}{{\boldsymbol I}}%
-\newcommand{\bJ}{{\boldsymbol J}}%
-\newcommand{\bK}{{\boldsymbol K}}%
-\newcommand{\bL}{{\boldsymbol L}}%
-\newcommand{\bM}{{\boldsymbol M}}%
-\newcommand{\bN}{{\boldsymbol N}}%
-\newcommand{\bO}{\boldsymbol 0}%
-\newcommand{\bQ}{\boldsymbol Q}%
-\newcommand{\bR}{\boldsymbol R}%
-\newcommand{\cS}{{\mathcal{S}}}%
-\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
-\newcommand{\bV}{\boldsymbol V}%
-\newcommand{\bW}{\boldsymbol W}%
-\newcommand{\bX}{\boldsymbol  X}%
-\newcommand{\bT}{\boldsymbol  T}%
-\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
-\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
-\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
-\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
-\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
-\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
-\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
-\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
-\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
-\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
-\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
-\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
-\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
-\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
-\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
-\newcommand{\by}{\boldsymbol y}%
-\newcommand{\bu}{\boldsymbol u}%
-\newcommand{\bv}{\boldsymbol  v}%
-\newcommand{\bz}{\boldsymbol z}%
-\newcommand{\bY}{\boldsymbol{Y}}%
-\newcommand{\bZ}{\boldsymbol Z}
-\newcommand{\bg}{\boldsymbol g}%
-\newcommand{\beps}{\boldsymbol \varepsilon}%
-\newcommand{\bSigma}{\boldsymbol \Sigma}%
-\newcommand{\blambda}{\boldsymbol  \lambda}
-\newcommand{\bbeta}{\boldsymbol  \beta}%
-\newcommand{\bLambda}{\boldsymbol  \Lambda}%
-\newcommand{\bTheta}{\boldsymbol  \Theta}
-\newcommand{\bDelta}{\boldsymbol{\Delta}}%
-\newcommand{\bXi}{\boldsymbol{\Xi}}%
-\newcommand{\ov}{\overrightarrow}%
-\newcommand{\cP}{\mathcal P}%
-\newcommand{\cQ}{\mathcal Q}%
-\renewcommand{\P}{\mathds{P}}
-\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
-\newcommand{\btheta}{\boldsymbol  \Theta}%
-\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
-\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
-\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
-\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
-\usepackage{accents}
-\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
-%{\accentset{\raisebox{0ex}{$.$}}{#1}}
-\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}
-
-\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
-\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}
-
-%% math operators
-\DeclareMathOperator*{\argmin}{\arg\!\min}
-\DeclareMathOperator*{\argmax}{\arg\!\max}
-
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-% todo
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\title{Screening Sinkhorn Algorithm via Dual Projection}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
-\end{abstract}
-
-\section{Introduction}
-
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\cite{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
+Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\citep{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
 In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
@@
 The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
+\citet{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
 \cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
@@
 
-The remainder of the paper is organized as follow. In Section~\ref{sec:optimal_transport} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screenkhorn} contains our main contribution, that is, the Screenkhorn algorithm. 
-Section~\ref{sec:error_analysis} devotes to theoretical guarantees for the marginal violations of Screenkhorn. 
+The remainder of the paper is organized as follow. In Section~\ref{sec:regularized_discrete_ot} we briefly review the basic setup of regularized discrete OT. 
+Section~\ref{sec:screened_dual_of_sinkhorn_divergence} contains our main contribution, that is, the Screenkhorn algorithm. 
+Section~\ref{sec:analysis_of_marginal_violations} devotes to theoretical guarantees for marginal violations of Screenkhorn. 
 In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
@@
 
-\section{Regularized discrete OT} 
-\label{sec:optimal_transport}
-
- We briefly present in this section the setup of OT between two discrete measures.
-We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$, where $\Sigma_n$ is the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
-We denote their probabilistic couplings set as $\Pi(\mu, \nu) = \{P \in \R_+^{n\times m}, P\mathbf{1}_m = \mu, P^\top \mathbf{1}_n = \nu\}.$ 
-\paragraph{Sinkhorn divergence.}
-
-Approximating OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
-\begin{equation}
-  \label{monge-kantorovich}
-  \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{C, P},
-\end{equation}
-where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $C= (C_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements and related to the energy needed to move a probability mass from $x_i$ to $y_j$.
-The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
-\begin{equation}
-\label{sinkhorn-primal}
-  \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
-\end{equation}
-where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.
-
-\paragraph{Dual of Sinkhorn divergence.}
-
-Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
-\begin{equation*}
-  \mathscr{L}(P,y, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
-\end{equation*}
-The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$.
-It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable.
-Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$.
-Therefore, we get
-\begin{equation}
-  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
-\end{equation}
-for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
-\begin{equation}
-\label{sinkhorn-dual}
-\min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
-\end{equation}
-where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
-We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
-Therefore, the optimal solution $P^\star$ of Sinkhorn divergence takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
-where the couple $(u^\star, v^\star)$ satisfies:
-\begin{align*}
-\label{sinkhorn-dual}
-  (u^\star, v^\star) &= \argmin_{u \in \R^{n}, v\in \R^m} \{\Psi(u,v)\}.
-\end{align*}
-Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-Furthermore, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity.
-
-\section{Screened dual of Sinkhorn divergence}
-\label{sec:screenkhorn}
-
-% In this section we describe the main algorithm studied in this paper. 
-For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
-\begin{equation} 
-\label{screen-sinkhorn}
-\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
-\end{equation}
-where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-
-The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
-The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
-Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
-
-\begin{lemma}
-\label{lemma_actives_sets}
-Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
-Define
-\begin{equation}
-\label{I_epsilon_kappa_J_epsilon_kappa}
-I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
-\end{equation}
-Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
-\end{lemma}
-
-First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
-which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.
-
-\paragraph{Screening with a fixed number budget of points.}
-
-Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
-The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
-In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
-
-Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
-To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
-\begin{equation}
-\label{epsilon_kappa}
- \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
-\end{equation}
-Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
-Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
-\begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
-\end{equation*}
-and 
-\begin{equation*}
-	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
-\end{equation*}
-where the vector comparison $\succeq$ has to be understood elementwise.
-Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as 
-\begin{align}
-\label{screen-sinkhorn_second_def}
-\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
-\end{align}
-where 
-\begin{align*} 
-\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
-\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
-&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
-\end{align*}
-with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
-
-Pseudocode of our proposed algorithm is given in Algorithm~\ref{screenkhorn}.
-Screenkhorn consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
-It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-
-The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
-\begin{lemma}
-\label{lemma_bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
-one has
-\begin{equation}
-\label{bound_on_u}
-\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
-\end{equation}
-and
-\begin{equation}
-\label{bound_on_v}
-\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
-\end{equation}
-for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
-\end{lemma}
-
-\LinesNotNumbered
-\begin{algorithm}[htbp]
-\SetNlSty{textbf}{}{.}
-\DontPrintSemicolon
-\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
-\label{screenkhorn}
-% \textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
-
-\textbf{step 1:} \textcolor{black}{Initialization}\\
-
-% \nl   $K \gets \exp(-C/\eta);$\\
-\nl   $\xi \gets \mu \oslash r(K);$ \\
-\nl   $\zeta \gets \nu \oslash c(K);$\\
-\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
-\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
-\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
-\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\
-
-% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}
-
-\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
-\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
-\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}
-
-\textbf{step 2:} \textcolor{black}{L-BFGS}\\
-
-\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
-\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
-\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
-
-% \textbf{step 4:} \textcolor{black}{Output}\\
-
-\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
-\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
-\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
-\end{algorithm}
-
-\section{Analysis of marginal violations}
-\label{sec:error_analysis}
-
-This section is devoted to study the marginal violations of Screenkhorn.
-Towards this end, let us define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$
-Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
-% while Proposition~\ref{proposition_error_in_marginals} gives also an upper bound of the marginal errors.
-
-\begin{lemma}
-\label{lemma_bounds_on_marginals}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
-Then one has 
-\begin{equation*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
-\end{equation*}
-and 
-\begin{equation*}
-\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\min_{i,j}K_{ij}} + (n-n_b)\varepsilon^2\Big).
-\end{equation*}
-\end{lemma}
-The following Proposition gives also an upper bound of the marginal errors.
-\begin{proposition}
-\label{proposition_error_in_marginals}
-One has 
-\begin{align*} %{\norm{{\mu}^{\text{sc}}}_1} 
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
-\end{align*}
-and 
-\begin{align*} %{\norm{{\nu}^{\text{sc}}}_1}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
-\end{align*}
-
-\end{proposition}
-
-\section{Numerical experiments}
-\label{sec:numerical_experiments}
-
-% \subsubsection*{Acknowledgments}
-
-% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
-
-\small
-\bibliography{biblio}
-\bibliographystyle{plain}
-
-\end{document}
+% section introduction (end)

### 2019-05-14 tex/v3/section_2_setup_OT.tex
added v3 in tex

--- 2019-05-13 tex/v2/screenkhorn.tex
@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-% \usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%\usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[preprint]{neurips_2019}
-\usepackage[]{neurips_2019}
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
-\usepackage[titletoc,title]{appendix}%
-\usepackage{dsfont}%
-\usepackage{caption} % 
-\usepackage{subcaption}
-\usepackage{float}%
-\usepackage{graphicx, color}% 
-\usepackage{bm}%bold equations
-
-%% formatting appendices
-\usepackage{etoolbox}
-\patchcmd{\appendices}{\quad}{. }{}{}
-
-%% tables
-\usepackage{pgfplots}%
-\usepackage{booktabs,multirow,array,multicol}
-\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
-
-%% algorithms
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-
-%% sections
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Fact}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}%[section]
-\newtheorem*{notation}{Notation}%[section]
-\newtheorem{discus}{Discussion}%[section]
-\newtheorem{remark}{Remark}%[section]
-\newtheorem{example}{Example}%[section]
-\newtheorem{exs}{Examples}%[section]
-\newtheorem{ca}{Cas}
-\newtheorem{remarks}{Remarks}%[section]
-\newtheorem{assumption}{Assumption}{\bf}{\rm}%
-
-% math macros
-
-\usepackage{relsize}
-\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}
-
-\newcommand{\ba}{\mathbf{a}}%
-\newcommand{\bb}{\mathbf{b}}%
-
-\newcommand{\bC}{{\mathbf C}}%
-\newcommand{\bP}{{\mathbf P}}%
-\newcommand{\bU}{{\mathbf U}}%
-
-\newcommand{\cX}{\mathcal X}%
-\newcommand{\cY}{\mathcal Y}%
-\newcommand{\cM}{\mathcal M}%
-\newcommand{\cC}{\mathcal C}%
-
-\newcommand{\td}{\text d}%
-\newcommand*{\argminl}{\argmin\limits}%
-\newcommand{\bigO}{\mathcal{O}}
-\newcommand{\bs}{\boldsymbol}
-\newcommand{\sumin}{\sum_{i=1}^n}
-\newcommand{\sumip}{\sum_{j=1}^m}
-\newcommand{\intt}{\int_{0}^{t}}
-\newcommand{\inttau}{\int_{0}^{\gamma}}
-\newcommand{\I}{1\!\mbox{I}}
-\newcommand{\e}{{\mathrm e}}
-\newcommand{\diff}{\mathrm d}
-\newcommand{\noi}{\noindent}
-\newcommand{\eps}{\varepsilon}
-\usepackage{datenumber}
-\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
-\newcommand{\inr}[1]{\langle #1 \rangle}
-\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
-\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
-\newcommand{\norm}[1]{\|#1\|}
-\newcommand{\R}{{\mathbb{R}}}
-\newcommand{\E}{\mathds{E}}
-\newcommand{\V}{\mathds{V}}
-\newcommand{\Lim}{\displaystyle \lim\limits}
-\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-\newcommand{\cD}{\mathcal D}
-\newcommand{\cE}{\mathcal E}
-\newcommand{\cT}{\mathcal T}
-\newcommand{\bA}{{\boldsymbol A}}%
-\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
-\newcommand{\bB}{{\boldsymbol B}}%
-\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
-\newcommand{\bD}{{\boldsymbol D}}%
-\newcommand{\bE}{{\boldsymbol E}}%
-\newcommand{\bF}{{\boldsymbol F}}%
-\newcommand{\bG}{{\boldsymbol G}}%
-\newcommand{\bH}{{\boldsymbol H}}%
-\newcommand{\bI}{{\boldsymbol I}}%
-\newcommand{\bJ}{{\boldsymbol J}}%
-\newcommand{\bK}{{\boldsymbol K}}%
-\newcommand{\bL}{{\boldsymbol L}}%
-\newcommand{\bM}{{\boldsymbol M}}%
-\newcommand{\bN}{{\boldsymbol N}}%
-\newcommand{\bO}{\boldsymbol 0}%
-\newcommand{\bQ}{\boldsymbol Q}%
-\newcommand{\bR}{\boldsymbol R}%
-\newcommand{\cS}{{\mathcal{S}}}%
-\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
-\newcommand{\bV}{\boldsymbol V}%
-\newcommand{\bW}{\boldsymbol W}%
-\newcommand{\bX}{\boldsymbol  X}%
-\newcommand{\bT}{\boldsymbol  T}%
-\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
-\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
-\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
-\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
-\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
-\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
-\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
-\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
-\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
-\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
-\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
-\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
-\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
-\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
-\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
-\newcommand{\by}{\boldsymbol y}%
-\newcommand{\bu}{\boldsymbol u}%
-\newcommand{\bv}{\boldsymbol  v}%
-\newcommand{\bz}{\boldsymbol z}%
-\newcommand{\bY}{\boldsymbol{Y}}%
-\newcommand{\bZ}{\boldsymbol Z}
-\newcommand{\bg}{\boldsymbol g}%
-\newcommand{\beps}{\boldsymbol \varepsilon}%
-\newcommand{\bSigma}{\boldsymbol \Sigma}%
-\newcommand{\blambda}{\boldsymbol  \lambda}
-\newcommand{\bbeta}{\boldsymbol  \beta}%
-\newcommand{\bLambda}{\boldsymbol  \Lambda}%
-\newcommand{\bTheta}{\boldsymbol  \Theta}
-\newcommand{\bDelta}{\boldsymbol{\Delta}}%
-\newcommand{\bXi}{\boldsymbol{\Xi}}%
-\newcommand{\ov}{\overrightarrow}%
-\newcommand{\cP}{\mathcal P}%
-\newcommand{\cQ}{\mathcal Q}%
-\renewcommand{\P}{\mathds{P}}
-\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
-\newcommand{\btheta}{\boldsymbol  \Theta}%
-\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
-\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
-\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
-\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
-\usepackage{accents}
-\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
-%{\accentset{\raisebox{0ex}{$.$}}{#1}}
-\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}
-
-\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
-\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}
-
-%% math operators
-\DeclareMathOperator*{\argmin}{\arg\!\min}
-\DeclareMathOperator*{\argmax}{\arg\!\max}
-
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-% todo
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\title{Screening Sinkhorn Algorithm via Dual Projection}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
-\end{abstract}
-
-\section{Introduction}
-
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\cite{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
-In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
-This effectively leads to improve performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
-Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
-
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
-Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\cite{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
-Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\cite{sinkhorn1967,knight2008,kalantari2008}.
-
-% \paragraph{Related work.}
-
-Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
-\cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
-
-% \paragraph{Our contribution.}
-
-We give a new algorithm to approximate the regularized OT distance between discrete measures. 
-Our algorithmic analysis is based on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
-These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.
-We prove that dual solution of this approximation guarantees the existence of two active indices sets for the potential variables.
-These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS,cuturi2016SIAM,blondel2018ICML}.
-
-% \paragraph{Outline of paper.}
-
-The remainder of the paper is organized as follow. In Section~\ref{sec:optimal_transport} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screenkhorn} contains our main contribution, that is, the Screenkhorn algorithm. 
-Section~\ref{sec:error_analysis} devotes to theoretical guarantees for the marginal violations of Screenkhorn. 
-In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
-The proofs of theoretical results are postponed to the supplementary material.
-
-\paragraph{Notation.}
-
-For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
-Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively.
-The coordinates $r_i(T)$ and $c_j(T)$ denote the $i$-th row sum and the $j$-th column sum of $T$, respectively.
-The scalar product between two matrices denotes the usual inner product, that is $\inr{T, W} = \text{tr}(T^\top W) = \sum_{i,j}T_{ij}W_{ij},$ where $T^\top$ is the transpose of $T$. 
-We write $\mathbf{1}$ (resp. $\mathbf{0}$) the vector having all coordinates equal to one (resp. zero).
-$\Delta(w)$ denotes the diag operator, such that if $w \in \R^n$, then $\Delta(w) = \text{diag}(w_1, \ldots, w_n)\in \R^{n\times n}$.
-For a set of indices $L=\{i_1, \ldots, i_k\} \subseteq \{1, \ldots, n\}$ satisfying $i_1 < \cdots <i_k,$ we denote the complementary set of $L$ by $L^\complement = \{1, \ldots, n\} \backslash L$.
-We also denote $|L|$ the cardinality of $L$.
-Given a vector $w \in \R^n$, we denote $w_L= (w_{i_1}, \ldots, w_{i_k})^\top \in \R^k$ and its complementary $w_{L^\complement} \in \R^{n- k}$.
-The notation is similar for matrices; given another subset of indices $S = \{j_1, \ldots, j_l\} \subseteq \{1, \ldots, m\}$ with $j_1 < \cdots <j_l,$ and a matrix $T\in \R^{n\times m}$, we use $T_{(L,S)}$, to denote the submatrix of $T$, namely the rows and columns of $T_{(L,S)}$ are indexed by $L$ and $S$ respectively.
-When applied to matrices and vectors,  $\odot$ and $\oslash$ (Hadamard product and division) and exponential notations refer to elementwise operators.
-Given two real numbers $a$ and $b$, we write $a\vee b = \max(a,b)$ and $a\wedge b = \min(a,b).$
-
-\section{Regularized discrete OT} 
-\label{sec:optimal_transport}
+\section{Regularized discrete OT} % (fold)
+\label{sec:regularized_discrete_ot}
 
@@
 
-Approximating OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
+Computing OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
 \begin{equation}
@@
 
-\section{Screened dual of Sinkhorn divergence}
-\label{sec:screenkhorn}
-
-% In this section we describe the main algorithm studied in this paper. 
-For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
-\begin{equation} 
-\label{screen-sinkhorn}
-\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
-\end{equation}
-where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-
-The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
-The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
-Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
-
-\begin{lemma}
-\label{lemma_actives_sets}
-Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
-Define
-\begin{equation}
-\label{I_epsilon_kappa_J_epsilon_kappa}
-I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
-\end{equation}
-Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
-\end{lemma}
-
-First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
-which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.
-
-\paragraph{Screening with a fixed number budget of points.}
-
-Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
-The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
-In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
-
-Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
-To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
-\begin{equation}
-\label{epsilon_kappa}
- \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
-\end{equation}
-Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
-Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
-\begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
-\end{equation*}
-and 
-\begin{equation*}
-	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
-\end{equation*}
-where the vector comparison $\succeq$ has to be understood elementwise.
-Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as 
-\begin{align}
-\label{screen-sinkhorn_second_def}
-\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
-\end{align}
-where 
-\begin{align*} 
-\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
-\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
-&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
-\end{align*}
-with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
-
-Pseudocode of our proposed algorithm is given in Algorithm~\ref{screenkhorn}.
-Screenkhorn consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
-It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-
-The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
-\begin{lemma}
-\label{lemma_bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
-one has
-\begin{equation}
-\label{bound_on_u}
-\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
-\end{equation}
-and
-\begin{equation}
-\label{bound_on_v}
-\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
-\end{equation}
-for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
-\end{lemma}
-
-\LinesNotNumbered
-\begin{algorithm}[htbp]
-\SetNlSty{textbf}{}{.}
-\DontPrintSemicolon
-\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
-\label{screenkhorn}
-% \textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
-
-\textbf{step 1:} \textcolor{black}{Initialization}\\
-
-% \nl   $K \gets \exp(-C/\eta);$\\
-\nl   $\xi \gets \mu \oslash r(K);$ \\
-\nl   $\zeta \gets \nu \oslash c(K);$\\
-\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
-\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
-\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
-\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\
-
-% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}
-
-\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
-\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
-\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}
-
-\textbf{step 2:} \textcolor{black}{L-BFGS}\\
-
-\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
-\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
-\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
-
-% \textbf{step 4:} \textcolor{black}{Output}\\
-
-\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
-\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
-\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
-\end{algorithm}
-
-\section{Analysis of marginal violations}
-\label{sec:error_analysis}
-
-This section is devoted to study the marginal violations of Screenkhorn.
-Towards this end, let us define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$
-Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
-% while Proposition~\ref{proposition_error_in_marginals} gives also an upper bound of the marginal errors.
-
-\begin{lemma}
-\label{lemma_bounds_on_marginals}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
-Then one has 
-\begin{equation*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
-\end{equation*}
-and 
-\begin{equation*}
-\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\min_{i,j}K_{ij}} + (n-n_b)\varepsilon^2\Big).
-\end{equation*}
-\end{lemma}
-The following Proposition gives also an upper bound of the marginal errors.
-\begin{proposition}
-\label{proposition_error_in_marginals}
-One has 
-\begin{align*} %{\norm{{\mu}^{\text{sc}}}_1} 
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
-\end{align*}
-and 
-\begin{align*} %{\norm{{\nu}^{\text{sc}}}_1}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
-\end{align*}
-
-\end{proposition}
-
-\section{Numerical experiments}
-\label{sec:numerical_experiments}
-
-% \subsubsection*{Acknowledgments}
-
-% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
-
-\small
-\bibliography{biblio}
-\bibliographystyle{plain}
-
-\end{document}
+% section regularized_discrete_ot (end)

### 2019-05-14 tex/v3/section_3_algorithm.tex
added v3 in tex

--- 2019-05-13 tex/v2/screenkhorn.tex
@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-% \usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%\usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[preprint]{neurips_2019}
-\usepackage[]{neurips_2019}
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
-\usepackage[titletoc,title]{appendix}%
-\usepackage{dsfont}%
-\usepackage{caption} % 
-\usepackage{subcaption}
-\usepackage{float}%
-\usepackage{graphicx, color}% 
-\usepackage{bm}%bold equations
-
-%% formatting appendices
-\usepackage{etoolbox}
-\patchcmd{\appendices}{\quad}{. }{}{}
-
-%% tables
-\usepackage{pgfplots}%
-\usepackage{booktabs,multirow,array,multicol}
-\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
-
-%% algorithms
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-
-%% sections
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Fact}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}%[section]
-\newtheorem*{notation}{Notation}%[section]
-\newtheorem{discus}{Discussion}%[section]
-\newtheorem{remark}{Remark}%[section]
-\newtheorem{example}{Example}%[section]
-\newtheorem{exs}{Examples}%[section]
-\newtheorem{ca}{Cas}
-\newtheorem{remarks}{Remarks}%[section]
-\newtheorem{assumption}{Assumption}{\bf}{\rm}%
-
-% math macros
-
-\usepackage{relsize}
-\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}
-
-\newcommand{\ba}{\mathbf{a}}%
-\newcommand{\bb}{\mathbf{b}}%
-
-\newcommand{\bC}{{\mathbf C}}%
-\newcommand{\bP}{{\mathbf P}}%
-\newcommand{\bU}{{\mathbf U}}%
-
-\newcommand{\cX}{\mathcal X}%
-\newcommand{\cY}{\mathcal Y}%
-\newcommand{\cM}{\mathcal M}%
-\newcommand{\cC}{\mathcal C}%
-
-\newcommand{\td}{\text d}%
-\newcommand*{\argminl}{\argmin\limits}%
-\newcommand{\bigO}{\mathcal{O}}
-\newcommand{\bs}{\boldsymbol}
-\newcommand{\sumin}{\sum_{i=1}^n}
-\newcommand{\sumip}{\sum_{j=1}^m}
-\newcommand{\intt}{\int_{0}^{t}}
-\newcommand{\inttau}{\int_{0}^{\gamma}}
-\newcommand{\I}{1\!\mbox{I}}
-\newcommand{\e}{{\mathrm e}}
-\newcommand{\diff}{\mathrm d}
-\newcommand{\noi}{\noindent}
-\newcommand{\eps}{\varepsilon}
-\usepackage{datenumber}
-\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
-\newcommand{\inr}[1]{\langle #1 \rangle}
-\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
-\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
-\newcommand{\norm}[1]{\|#1\|}
-\newcommand{\R}{{\mathbb{R}}}
-\newcommand{\E}{\mathds{E}}
-\newcommand{\V}{\mathds{V}}
-\newcommand{\Lim}{\displaystyle \lim\limits}
-\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-\newcommand{\cD}{\mathcal D}
-\newcommand{\cE}{\mathcal E}
-\newcommand{\cT}{\mathcal T}
-\newcommand{\bA}{{\boldsymbol A}}%
-\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
-\newcommand{\bB}{{\boldsymbol B}}%
-\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
-\newcommand{\bD}{{\boldsymbol D}}%
-\newcommand{\bE}{{\boldsymbol E}}%
-\newcommand{\bF}{{\boldsymbol F}}%
-\newcommand{\bG}{{\boldsymbol G}}%
-\newcommand{\bH}{{\boldsymbol H}}%
-\newcommand{\bI}{{\boldsymbol I}}%
-\newcommand{\bJ}{{\boldsymbol J}}%
-\newcommand{\bK}{{\boldsymbol K}}%
-\newcommand{\bL}{{\boldsymbol L}}%
-\newcommand{\bM}{{\boldsymbol M}}%
-\newcommand{\bN}{{\boldsymbol N}}%
-\newcommand{\bO}{\boldsymbol 0}%
-\newcommand{\bQ}{\boldsymbol Q}%
-\newcommand{\bR}{\boldsymbol R}%
-\newcommand{\cS}{{\mathcal{S}}}%
-\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
-\newcommand{\bV}{\boldsymbol V}%
-\newcommand{\bW}{\boldsymbol W}%
-\newcommand{\bX}{\boldsymbol  X}%
-\newcommand{\bT}{\boldsymbol  T}%
-\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
-\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
-\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
-\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
-\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
-\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
-\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
-\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
-\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
-\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
-\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
-\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
-\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
-\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
-\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
-\newcommand{\by}{\boldsymbol y}%
-\newcommand{\bu}{\boldsymbol u}%
-\newcommand{\bv}{\boldsymbol  v}%
-\newcommand{\bz}{\boldsymbol z}%
-\newcommand{\bY}{\boldsymbol{Y}}%
-\newcommand{\bZ}{\boldsymbol Z}
-\newcommand{\bg}{\boldsymbol g}%
-\newcommand{\beps}{\boldsymbol \varepsilon}%
-\newcommand{\bSigma}{\boldsymbol \Sigma}%
-\newcommand{\blambda}{\boldsymbol  \lambda}
-\newcommand{\bbeta}{\boldsymbol  \beta}%
-\newcommand{\bLambda}{\boldsymbol  \Lambda}%
-\newcommand{\bTheta}{\boldsymbol  \Theta}
-\newcommand{\bDelta}{\boldsymbol{\Delta}}%
-\newcommand{\bXi}{\boldsymbol{\Xi}}%
-\newcommand{\ov}{\overrightarrow}%
-\newcommand{\cP}{\mathcal P}%
-\newcommand{\cQ}{\mathcal Q}%
-\renewcommand{\P}{\mathds{P}}
-\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
-\newcommand{\btheta}{\boldsymbol  \Theta}%
-\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
-\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
-\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
-\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
-\usepackage{accents}
-\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
-%{\accentset{\raisebox{0ex}{$.$}}{#1}}
-\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}
-
-\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
-\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}
-
-%% math operators
-\DeclareMathOperator*{\argmin}{\arg\!\min}
-\DeclareMathOperator*{\argmax}{\arg\!\max}
-
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-% todo
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\title{Screening Sinkhorn Algorithm via Dual Projection}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
-\end{abstract}
-
-\section{Introduction}
-
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\cite{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
-In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
-This effectively leads to improve performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
-Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
-
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
-Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\cite{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
-Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\cite{sinkhorn1967,knight2008,kalantari2008}.
-
-% \paragraph{Related work.}
-
-Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
-\cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
-
-% \paragraph{Our contribution.}
-
-We give a new algorithm to approximate the regularized OT distance between discrete measures. 
-Our algorithmic analysis is based on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
-These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.
-We prove that dual solution of this approximation guarantees the existence of two active indices sets for the potential variables.
-These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS,cuturi2016SIAM,blondel2018ICML}.
-
-% \paragraph{Outline of paper.}
-
-The remainder of the paper is organized as follow. In Section~\ref{sec:optimal_transport} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screenkhorn} contains our main contribution, that is, the Screenkhorn algorithm. 
-Section~\ref{sec:error_analysis} devotes to theoretical guarantees for the marginal violations of Screenkhorn. 
-In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
-The proofs of theoretical results are postponed to the supplementary material.
-
-\paragraph{Notation.}
-
-For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
-Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively.
-The coordinates $r_i(T)$ and $c_j(T)$ denote the $i$-th row sum and the $j$-th column sum of $T$, respectively.
-The scalar product between two matrices denotes the usual inner product, that is $\inr{T, W} = \text{tr}(T^\top W) = \sum_{i,j}T_{ij}W_{ij},$ where $T^\top$ is the transpose of $T$. 
-We write $\mathbf{1}$ (resp. $\mathbf{0}$) the vector having all coordinates equal to one (resp. zero).
-$\Delta(w)$ denotes the diag operator, such that if $w \in \R^n$, then $\Delta(w) = \text{diag}(w_1, \ldots, w_n)\in \R^{n\times n}$.
-For a set of indices $L=\{i_1, \ldots, i_k\} \subseteq \{1, \ldots, n\}$ satisfying $i_1 < \cdots <i_k,$ we denote the complementary set of $L$ by $L^\complement = \{1, \ldots, n\} \backslash L$.
-We also denote $|L|$ the cardinality of $L$.
-Given a vector $w \in \R^n$, we denote $w_L= (w_{i_1}, \ldots, w_{i_k})^\top \in \R^k$ and its complementary $w_{L^\complement} \in \R^{n- k}$.
-The notation is similar for matrices; given another subset of indices $S = \{j_1, \ldots, j_l\} \subseteq \{1, \ldots, m\}$ with $j_1 < \cdots <j_l,$ and a matrix $T\in \R^{n\times m}$, we use $T_{(L,S)}$, to denote the submatrix of $T$, namely the rows and columns of $T_{(L,S)}$ are indexed by $L$ and $S$ respectively.
-When applied to matrices and vectors,  $\odot$ and $\oslash$ (Hadamard product and division) and exponential notations refer to elementwise operators.
-Given two real numbers $a$ and $b$, we write $a\vee b = \max(a,b)$ and $a\wedge b = \min(a,b).$
-
-\section{Regularized discrete OT} 
-\label{sec:optimal_transport}
-
- We briefly present in this section the setup of OT between two discrete measures.
-We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$, where $\Sigma_n$ is the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
-We denote their probabilistic couplings set as $\Pi(\mu, \nu) = \{P \in \R_+^{n\times m}, P\mathbf{1}_m = \mu, P^\top \mathbf{1}_n = \nu\}.$ 
-\paragraph{Sinkhorn divergence.}
-
-Approximating OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
-\begin{equation}
-  \label{monge-kantorovich}
-  \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{C, P},
-\end{equation}
-where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $C= (C_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements and related to the energy needed to move a probability mass from $x_i$ to $y_j$.
-The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
-\begin{equation}
-\label{sinkhorn-primal}
-  \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
-\end{equation}
-where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.
-
-\paragraph{Dual of Sinkhorn divergence.}
-
-Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
-\begin{equation*}
-  \mathscr{L}(P,y, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
-\end{equation*}
-The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$.
-It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable.
-Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$.
-Therefore, we get
-\begin{equation}
-  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
-\end{equation}
-for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
-\begin{equation}
-\label{sinkhorn-dual}
-\min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
-\end{equation}
-where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
-We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
-Therefore, the optimal solution $P^\star$ of Sinkhorn divergence takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
-where the couple $(u^\star, v^\star)$ satisfies:
-\begin{align*}
-\label{sinkhorn-dual}
-  (u^\star, v^\star) &= \argmin_{u \in \R^{n}, v\in \R^m} \{\Psi(u,v)\}.
-\end{align*}
-Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-Furthermore, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity.
-
-\section{Screened dual of Sinkhorn divergence}
-\label{sec:screenkhorn}
+\section{Screened dual of Sinkhorn divergence} % (fold)
+\label{sec:screened_dual_of_sinkhorn_divergence}
 
@@
 
-\section{Analysis of marginal violations}
-\label{sec:error_analysis}
-
-This section is devoted to study the marginal violations of Screenkhorn.
-Towards this end, let us define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$
-Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
-% while Proposition~\ref{proposition_error_in_marginals} gives also an upper bound of the marginal errors.
-
-\begin{lemma}
-\label{lemma_bounds_on_marginals}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
-Then one has 
-\begin{equation*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
-\end{equation*}
-and 
-\begin{equation*}
-\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\min_{i,j}K_{ij}} + (n-n_b)\varepsilon^2\Big).
-\end{equation*}
-\end{lemma}
-The following Proposition gives also an upper bound of the marginal errors.
-\begin{proposition}
-\label{proposition_error_in_marginals}
-One has 
-\begin{align*} %{\norm{{\mu}^{\text{sc}}}_1} 
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
-\end{align*}
-and 
-\begin{align*} %{\norm{{\nu}^{\text{sc}}}_1}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
-\end{align*}
-
-\end{proposition}
-
-\section{Numerical experiments}
-\label{sec:numerical_experiments}
-
-% \subsubsection*{Acknowledgments}
-
-% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
-
-\small
-\bibliography{biblio}
-\bibliographystyle{plain}
-
-\end{document}
+% section screened_dual_of_sinkhorn_divergence (end)

### 2019-05-14 tex/v3/section_4_marginal_viols.tex
added v3 in tex

--- 2019-05-13 tex/v2/screenkhorn.tex
@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-% \usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%\usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[preprint]{neurips_2019}
-\usepackage[]{neurips_2019}
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
-\usepackage[titletoc,title]{appendix}%
-\usepackage{dsfont}%
-\usepackage{caption} % 
-\usepackage{subcaption}
-\usepackage{float}%
-\usepackage{graphicx, color}% 
-\usepackage{bm}%bold equations
-
-%% formatting appendices
-\usepackage{etoolbox}
-\patchcmd{\appendices}{\quad}{. }{}{}
-
-%% tables
-\usepackage{pgfplots}%
-\usepackage{booktabs,multirow,array,multicol}
-\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
-
-%% algorithms
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-
-%% sections
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Fact}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}%[section]
-\newtheorem*{notation}{Notation}%[section]
-\newtheorem{discus}{Discussion}%[section]
-\newtheorem{remark}{Remark}%[section]
-\newtheorem{example}{Example}%[section]
-\newtheorem{exs}{Examples}%[section]
-\newtheorem{ca}{Cas}
-\newtheorem{remarks}{Remarks}%[section]
-\newtheorem{assumption}{Assumption}{\bf}{\rm}%
-
-% math macros
-
-\usepackage{relsize}
-\newcommand*{\defeq}{\stackrel{\mathsmaller{\mathsf{def.}}}{=}}
-
-\newcommand{\ba}{\mathbf{a}}%
-\newcommand{\bb}{\mathbf{b}}%
-
-\newcommand{\bC}{{\mathbf C}}%
-\newcommand{\bP}{{\mathbf P}}%
-\newcommand{\bU}{{\mathbf U}}%
-
-\newcommand{\cX}{\mathcal X}%
-\newcommand{\cY}{\mathcal Y}%
-\newcommand{\cM}{\mathcal M}%
-\newcommand{\cC}{\mathcal C}%
-
-\newcommand{\td}{\text d}%
-\newcommand*{\argminl}{\argmin\limits}%
-\newcommand{\bigO}{\mathcal{O}}
-\newcommand{\bs}{\boldsymbol}
-\newcommand{\sumin}{\sum_{i=1}^n}
-\newcommand{\sumip}{\sum_{j=1}^m}
-\newcommand{\intt}{\int_{0}^{t}}
-\newcommand{\inttau}{\int_{0}^{\gamma}}
-\newcommand{\I}{1\!\mbox{I}}
-\newcommand{\e}{{\mathrm e}}
-\newcommand{\diff}{\mathrm d}
-\newcommand{\noi}{\noindent}
-\newcommand{\eps}{\varepsilon}
-\usepackage{datenumber}
-\newcommand{\sptr}[2]{\langle #1 | #2 \rangle}
-\newcommand{\inr}[1]{\langle #1 \rangle}
-\newcommand{\inrbig}[1]{\bigg\langle #1 \bigg\rangle}
-\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
-\newcommand{\norm}[1]{\|#1\|}
-\newcommand{\R}{{\mathbb{R}}}
-\newcommand{\E}{\mathds{E}}
-\newcommand{\V}{\mathds{V}}
-\newcommand{\Lim}{\displaystyle \lim\limits}
-\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-\newcommand{\cD}{\mathcal D}
-\newcommand{\cE}{\mathcal E}
-\newcommand{\cT}{\mathcal T}
-\newcommand{\bA}{{\boldsymbol A}}%
-\newcommand{\bcA}{\boldsymbol{\mathcal{C}}}%
-\newcommand{\bB}{{\boldsymbol B}}%
-\newcommand{\bcB}{\boldsymbol{\mathcal{B}}}%
-\newcommand{\bD}{{\boldsymbol D}}%
-\newcommand{\bE}{{\boldsymbol E}}%
-\newcommand{\bF}{{\boldsymbol F}}%
-\newcommand{\bG}{{\boldsymbol G}}%
-\newcommand{\bH}{{\boldsymbol H}}%
-\newcommand{\bI}{{\boldsymbol I}}%
-\newcommand{\bJ}{{\boldsymbol J}}%
-\newcommand{\bK}{{\boldsymbol K}}%
-\newcommand{\bL}{{\boldsymbol L}}%
-\newcommand{\bM}{{\boldsymbol M}}%
-\newcommand{\bN}{{\boldsymbol N}}%
-\newcommand{\bO}{\boldsymbol 0}%
-\newcommand{\bQ}{\boldsymbol Q}%
-\newcommand{\bR}{\boldsymbol R}%
-\newcommand{\cS}{{\mathcal{S}}}%
-\newcommand{\bcQ}{\boldsymbol{\mathcal{Q}}}%
-\newcommand{\bV}{\boldsymbol V}%
-\newcommand{\bW}{\boldsymbol W}%
-\newcommand{\bX}{\boldsymbol  X}%
-\newcommand{\bT}{\boldsymbol  T}%
-\newcommand{\bcE}{\boldsymbol{\mathcal{E}}}%
-\newcommand{\bcH}{\boldsymbol{\mathcal{H}}}%
-\newcommand{\bcX}{\boldsymbol{\mathcal{X}}}%
-\newcommand{\bcJ}{\boldsymbol{\mathcal{J}}}%
-\newcommand{\bcY}{\boldsymbol{\mathcal{Y}}}%
-\newcommand{\bcW}{\boldsymbol{\mathcal{W}}}%
-\newcommand{\bcT}{\boldsymbol{\mathcal{T}}}%
-\newcommand{\bcM}{\boldsymbol{\mathcal{M}}}%
-\newcommand{\bcZ}{\boldsymbol{\mathcal{Z}}}%
-\newcommand{\bcO}{\boldsymbol{\mathcal{O}}}%
-\newcommand{\bcG}{\boldsymbol{\mathcal{G}}}%
-\newcommand{\bcU}{\boldsymbol{\mathcal{U}}}%
-\newcommand{\bcV}{\boldsymbol{\mathcal{V}}}%
-\newcommand{\bcR}{\boldsymbol{\mathcal{R}}}%
-\newcommand{\bcI}{\boldsymbol{\mathcal{I}}}%
-\newcommand{\by}{\boldsymbol y}%
-\newcommand{\bu}{\boldsymbol u}%
-\newcommand{\bv}{\boldsymbol  v}%
-\newcommand{\bz}{\boldsymbol z}%
-\newcommand{\bY}{\boldsymbol{Y}}%
-\newcommand{\bZ}{\boldsymbol Z}
-\newcommand{\bg}{\boldsymbol g}%
-\newcommand{\beps}{\boldsymbol \varepsilon}%
-\newcommand{\bSigma}{\boldsymbol \Sigma}%
-\newcommand{\blambda}{\boldsymbol  \lambda}
-\newcommand{\bbeta}{\boldsymbol  \beta}%
-\newcommand{\bLambda}{\boldsymbol  \Lambda}%
-\newcommand{\bTheta}{\boldsymbol  \Theta}
-\newcommand{\bDelta}{\boldsymbol{\Delta}}%
-\newcommand{\bXi}{\boldsymbol{\Xi}}%
-\newcommand{\ov}{\overrightarrow}%
-\newcommand{\cP}{\mathcal P}%
-\newcommand{\cQ}{\mathcal Q}%
-\renewcommand{\P}{\mathds{P}}
-\newcommand{\bctheta}{\boldsymbol{\mathcal{\Theta}}}%
-\newcommand{\btheta}{\boldsymbol  \Theta}%
-\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
-\newcommand{\cst}{\raisebox{-0.15ex}{\scalebox{1.30}{$c$}}}
-\newcommand{\Cst}{\raisebox{-0.15ex}{\scalebox{1.10}{$C$}}}
-\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
-\usepackage{accents}
-\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
-%{\accentset{\raisebox{0ex}{$.$}}{#1}}
-\newcommand*{\ddt}[1]{\accentset{\raisebox{0ex}{$\,\,\star$}}{#1}}
-
-\newcommand*{\fstderiv}[1]{\accentset{\mbox{\Large\bfseries .}}{#1}}
-\newcommand*{\scdderiv}[1]{\accentset{\mbox{\Large\bfseries .\hspace{-0.25ex}.}}{#1}}
-
-%% math operators
-\DeclareMathOperator*{\argmin}{\arg\!\min}
-\DeclareMathOperator*{\argmax}{\arg\!\max}
-
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-% todo
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\title{Screening Sinkhorn Algorithm via Dual Projection}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-
-This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
-\end{abstract}
-
-\section{Introduction}
-
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\cite{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
-In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
-This effectively leads to improve performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
-Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
-
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
-Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\cite{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
-Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\cite{sinkhorn1967,knight2008,kalantari2008}.
-
-% \paragraph{Related work.}
-
-Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
-\cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
-
-% \paragraph{Our contribution.}
-
-We give a new algorithm to approximate the regularized OT distance between discrete measures. 
-Our algorithmic analysis is based on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
-These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.
-We prove that dual solution of this approximation guarantees the existence of two active indices sets for the potential variables.
-These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS,cuturi2016SIAM,blondel2018ICML}.
-
-% \paragraph{Outline of paper.}
-
-The remainder of the paper is organized as follow. In Section~\ref{sec:optimal_transport} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screenkhorn} contains our main contribution, that is, the Screenkhorn algorithm. 
-Section~\ref{sec:error_analysis} devotes to theoretical guarantees for the marginal violations of Screenkhorn. 
-In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
-The proofs of theoretical results are postponed to the supplementary material.
-
-\paragraph{Notation.}
-
-For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
-Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively.
-The coordinates $r_i(T)$ and $c_j(T)$ denote the $i$-th row sum and the $j$-th column sum of $T$, respectively.
-The scalar product between two matrices denotes the usual inner product, that is $\inr{T, W} = \text{tr}(T^\top W) = \sum_{i,j}T_{ij}W_{ij},$ where $T^\top$ is the transpose of $T$. 
-We write $\mathbf{1}$ (resp. $\mathbf{0}$) the vector having all coordinates equal to one (resp. zero).
-$\Delta(w)$ denotes the diag operator, such that if $w \in \R^n$, then $\Delta(w) = \text{diag}(w_1, \ldots, w_n)\in \R^{n\times n}$.
-For a set of indices $L=\{i_1, \ldots, i_k\} \subseteq \{1, \ldots, n\}$ satisfying $i_1 < \cdots <i_k,$ we denote the complementary set of $L$ by $L^\complement = \{1, \ldots, n\} \backslash L$.
-We also denote $|L|$ the cardinality of $L$.
-Given a vector $w \in \R^n$, we denote $w_L= (w_{i_1}, \ldots, w_{i_k})^\top \in \R^k$ and its complementary $w_{L^\complement} \in \R^{n- k}$.
-The notation is similar for matrices; given another subset of indices $S = \{j_1, \ldots, j_l\} \subseteq \{1, \ldots, m\}$ with $j_1 < \cdots <j_l,$ and a matrix $T\in \R^{n\times m}$, we use $T_{(L,S)}$, to denote the submatrix of $T$, namely the rows and columns of $T_{(L,S)}$ are indexed by $L$ and $S$ respectively.
-When applied to matrices and vectors,  $\odot$ and $\oslash$ (Hadamard product and division) and exponential notations refer to elementwise operators.
-Given two real numbers $a$ and $b$, we write $a\vee b = \max(a,b)$ and $a\wedge b = \min(a,b).$
-
-\section{Regularized discrete OT} 
-\label{sec:optimal_transport}
-
- We briefly present in this section the setup of OT between two discrete measures.
-We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$, where $\Sigma_n$ is the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
-We denote their probabilistic couplings set as $\Pi(\mu, \nu) = \{P \in \R_+^{n\times m}, P\mathbf{1}_m = \mu, P^\top \mathbf{1}_n = \nu\}.$ 
-\paragraph{Sinkhorn divergence.}
-
-Approximating OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
-\begin{equation}
-  \label{monge-kantorovich}
-  \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{C, P},
-\end{equation}
-where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $C= (C_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements and related to the energy needed to move a probability mass from $x_i$ to $y_j$.
-The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
-\begin{equation}
-\label{sinkhorn-primal}
-  \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
-\end{equation}
-where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.
-
-\paragraph{Dual of Sinkhorn divergence.}
-
-Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
-\begin{equation*}
-  \mathscr{L}(P,y, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
-\end{equation*}
-The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$.
-It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable.
-Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$.
-Therefore, we get
-\begin{equation}
-  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
-\end{equation}
-for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
-\begin{equation}
-\label{sinkhorn-dual}
-\min_{u \in \R^n, v\in\R^m}\big\{\Psi(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{u, \mu} - \inr{v, \nu} \big\},
-\end{equation}
-where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
-We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
-Therefore, the optimal solution $P^\star$ of Sinkhorn divergence takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
-where the couple $(u^\star, v^\star)$ satisfies:
-\begin{align*}
-\label{sinkhorn-dual}
-  (u^\star, v^\star) &= \argmin_{u \in \R^{n}, v\in \R^m} \{\Psi(u,v)\}.
-\end{align*}
-Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-Furthermore, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity.
-
-\section{Screened dual of Sinkhorn divergence}
-\label{sec:screenkhorn}
-
-% In this section we describe the main algorithm studied in this paper. 
-For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
-\begin{equation} 
-\label{screen-sinkhorn}
-\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
-\end{equation}
-where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-
-The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
-The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
-Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
-
-\begin{lemma}
-\label{lemma_actives_sets}
-Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
-Define
-\begin{equation}
-\label{I_epsilon_kappa_J_epsilon_kappa}
-I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
-\end{equation}
-Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
-\end{lemma}
-
-First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
-which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.
-
-\paragraph{Screening with a fixed number budget of points.}
-
-Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
-The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
-In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
-
-Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
-To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
-\begin{equation}
-\label{epsilon_kappa}
- \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
-\end{equation}
-Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
-Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
-\begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
-\end{equation*}
-and 
-\begin{equation*}
-	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
-\end{equation*}
-where the vector comparison $\succeq$ has to be understood elementwise.
-Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as 
-\begin{align}
-\label{screen-sinkhorn_second_def}
-\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
-\end{align}
-where 
-\begin{align*} 
-\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
-\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
-&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
-\end{align*}
-with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
-
-Pseudocode of our proposed algorithm is given in Algorithm~\ref{screenkhorn}.
-Screenkhorn consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
-It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-
-The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
-\begin{lemma}
-\label{lemma_bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
-one has
-\begin{equation}
-\label{bound_on_u}
-\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
-\end{equation}
-and
-\begin{equation}
-\label{bound_on_v}
-\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
-\end{equation}
-for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
-\end{lemma}
-
-\LinesNotNumbered
-\begin{algorithm}[htbp]
-\SetNlSty{textbf}{}{.}
-\DontPrintSemicolon
-\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
-\label{screenkhorn}
-% \textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
-
-\textbf{step 1:} \textcolor{black}{Initialization}\\
-
-% \nl   $K \gets \exp(-C/\eta);$\\
-\nl   $\xi \gets \mu \oslash r(K);$ \\
-\nl   $\zeta \gets \nu \oslash c(K);$\\
-\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
-\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
-\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
-\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\
-
-% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}
-
-\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
-\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
-\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}
-
-\textbf{step 2:} \textcolor{black}{L-BFGS}\\
-
-\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
-\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
-\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
-
-% \textbf{step 4:} \textcolor{black}{Output}\\
-
-\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
-\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
-\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
-\end{algorithm}
-
-\section{Analysis of marginal violations}
-\label{sec:error_analysis}
+\section{Analysis of marginal violations} % (fold)
+\label{sec:analysis_of_marginal_violations}
 
@@
 
-\section{Numerical experiments}
-\label{sec:numerical_experiments}
-
-% \subsubsection*{Acknowledgments}
-
-% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
-
-\small
-\bibliography{biblio}
-\bibliographystyle{plain}
-
-\end{document}
+% section analysis_of_marginal_violations (end)

### 2019-05-14 tex/v3/section_5_numeric_expes.tex
added v3 in tex

\section{Numerical experiments} % (fold)
\label{sec:numerical_experiments}

% section numerical_experiments (end)

### 2019-05-14 tex/v3/section_1_introduction.tex
intro

@@
 The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\citet{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
+\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
 \cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.

### 2019-05-14 tex/v3/section_1_introduction.tex
intro

@@
 The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-\cite{altschulernips17} proposed the Greenkhorn algorithm, a greedy version of Sinkhorn algorithm that selects columns and rows to be updated that most violate the constraints.
-\cite{altschuler2018Nystrom} provided the Nys-Sink algorithm which is based on low-rank approximation of the cost matrix using Nystrom method.
+A greedy version of Sinkhorn algorithm, called Greenkhorn algorithm, proposed in~\cite{altschulernips17}, allowing to select columns and rows to be updated that most violate the constraints.
+Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\cite{altschuler2018Nystrom}. 
 Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
@@
 
-We give a new algorithm to approximate the regularized OT distance between discrete measures. 
-Our algorithmic analysis is based on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
+In this paper, we give new algorithm to approximate the regularized OT distance between discrete measures. 
+Our algorithmic analysis relies on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
 These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.

### 2019-05-14 tex/v3/section_1_introduction.tex
fix hyperlink citations in biblio

@@
+%!TEX root = main.tex
+
 \section{Introduction} % (fold)
@@
 The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-A greedy version of Sinkhorn algorithm, called Greenkhorn algorithm, proposed in~\cite{altschulernips17}, allowing to select columns and rows to be updated that most violate the constraints.
+A greedy version of Sinkhorn, called Greenkhorn algorithm, proposed in~\cite{altschulernips17} allowing to select columns and rows to be updated that most violate the constraints.                   
 Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\cite{altschuler2018Nystrom}. 
@@
 
-In this paper, we give new algorithm to approximate the regularized OT distance between discrete measures. 
-Our algorithmic analysis relies on an approximate of the dual of Sinkhorn divergence by adding new constraints feasibility. 
-These constraints are defined through a convex set which depends on two parameters, acting like threshold and scaling factor.
-We prove that dual solution of this approximation guarantees the existence of two active indices sets for the potential variables.
+Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures. 
+The proposed approach relies on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility, that are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
+We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
 These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
 We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS,cuturi2016SIAM,blondel2018ICML}.
+The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical}.
+The L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
 

### 2019-05-14 tex/v3/section_1_introduction.tex
working Intro

@@
 Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures. 
-The proposed approach relies on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility, that are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
+The proposed approach relies on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
+The constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
 We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
@@
 We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-The Screenkhorn algorithm developed in this paper relies on two steps; the first one consists of an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical}.
+Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical}.
 The L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.

### 2019-05-14 tex/v3/section_1_introduction.tex
working Intro

@@
 
-% \paragraph{Related work.}
-
 Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
@@
 
-% \paragraph{Our contribution.}
-
 Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures.
 The proposed approach relies on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
-The constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
+The constraints are defined through a convex set that depends on two parameters acting like threshold and scaling factor.
 We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
-These active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility with respect to the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
+Furthermore, these active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
+We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
 Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical}.
 The L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
-
-% \paragraph{Outline of paper.}
 
@@
 
-\paragraph{Notation.}
-
-For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
+\emph{Notation.} For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
 Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively.

### 2019-05-14 tex/v3/section_1_introduction.tex
update biblio

@@
 Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\cite{altschuler2018Nystrom}. 
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
+Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
 

### 2019-05-14 tex/v3/section_1_introduction.tex
working intro

@@
 Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures.
-The proposed approach relies on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
-The constraints are defined through a convex set that depends on two parameters acting like threshold and scaling factor.
+The proposed approach is based on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
+These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
 We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
-Furthermore, these active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
+Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
 We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical}.
-The L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
+Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical} that relies on an estimation of the inverse of the Hessian based on gradients differences.
+L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
 

### 2019-05-14 tex/v3/supplementary_material.tex
added supplementary to main

%!TEX root = main.tex
\newpage
\appendix

\begin{center}
\Large{\textbf{Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''}}
\end{center}

\section{Proof of Lemma~\ref{lemma_actives_sets}}

Introducing two dual variables $\lambda \in \R^n_{+}$ and $\beta \in \R^m_{+}$ for each constraint, the Lagrangian of problem~\eqref{screen-sinkhorn} reads as 
\begin{equation*}
  \mathscr{L}(u,v, \lambda, \beta) = \frac \varepsilon\kappa\inr{\lambda, \mathbf{1}_n} + \varepsilon\kappa\inr{\beta, \mathbf{1}_m} + \mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} -\inr{\lambda,e^{u}} - \inr{\beta,e^{v}}
\end{equation*}
First order conditions then yield that the Lagrangian multiplicators solutions $\lambda^{*}$ and $\beta^{*}$ satisfy 
\begin{align*}
  &\nabla_u\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{u^{*}} \odot(Ke^{v^{*}} - \lambda^{*}) - \kappa\mu = \mathbf 0_n,\\
  & \text{ and } \nabla_v\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{v^{*}} \odot(K^\top e^{u^{*}} - \beta) - \frac \nu\kappa = \mathbf 0_m
\end{align*}
which leads to 
\begin{align*}
  &\lambda^{*} = K e^{v^{*}} - \kappa\mu \oslash e^{u^{*}} \text{ and }
  \beta^{*} = K^\top e^{u^{*}} - \nu \oslash \kappa e^{v^{*}}
\end{align*}

For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \varepsilon\kappa^{-1}$. Further, the condition on the dual variable $\lambda^{*}_i > 0$  ensures that $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and hence $i \in I^\complement_{\varepsilon,\kappa}$. We have that $\lambda^{*}_i > 0$ is equivalent to $e^{u^{*}_i}r_i(K) e^{v^{*}_j} >  \kappa{\mu_i}$ which  is satisfied when $\varepsilon^2r_i(K) >  \kappa{\mu_i}.$  
In a symmetric way we can prove the same statement for $e^{v^{*}_j}$.

$\hfill\square$

\section{Proof of Lemma~\ref{lemma_bounds_of_usc_and_vsc}}

We prove only the first statement~\eqref{bound_on_u} and similarly we can prove the second statement~\eqref{bound_on_v}.
For all $i\in I_{\varepsilon,\kappa}$, we have $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ or $e^{u^{\text{sc}}_i} = \frac \varepsilon\kappa$. In one hand, if $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ then according to the optimality conditions $\lambda^{\text{sc}}_i = 0.$ Then $e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i$.
In another hand, we have 
\begin{align*}
e^{u^{\text{sc}}_i} \min_{i,j}K_{ij} \sum_{j=1}^m e^{v^{\text{sc}}_j} \leq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i.
\end{align*}
We further observe that $\sum_{j=1}^m e^{v^{\text{sc}}_j} = \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} \geq \varepsilon\kappa |J_{\varepsilon,\kappa}| + \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}|=\varepsilon\kappa m.$ Then
\begin{equation*}
\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon \min_{i,j}K_{ij}}.
\end{equation*}
Analogously, one can obtain for all $j\in J_{\varepsilon,\kappa}$
\begin{equation}
\label{upper_bound_v_potential}
\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}.
\end{equation}

Now, since $K_{ij} \leq 1$, we have 
\begin{align*}
e^{u^{\text{sc}}_i} \sum_{j=1}^m e^{v^{\text{sc}}_j} \geq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij}e^{v^{\text{sc}}_j} = \kappa\mu_i.
\end{align*}
Using~\eqref{upper_bound_v_potential}, we get 
\begin{align*}
\sum_{j=1}^m e^{v^{\text{sc}}_j} &= \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j}
\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} |J_{\varepsilon,\kappa}|.
\end{align*}
Therefore,
\begin{align*}
\min_{i \in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\varepsilon,\kappa}}\mu_i}{\varepsilon\kappa (m-m_b) + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} m_b}.
\end{align*}

$\hfill\square$

\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}

The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
\begin{align}
\label{i-th-marginal-mu} %=({B}({u}^{\text{sc}},{v}^{\text{sc}})\mathbf 1_m)_i
{\mu}^{\text{sc}}_i  &= 
\begin{cases}
e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I_{\varepsilon,\kappa},\\
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}
\end{cases}
=\begin{cases}
\kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}.
\end{cases}
\end{align}
Using Inequality~\eqref{bound_on_v}, we obtain 
\begin{align*}
\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
\end{align*}
Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.

$\hfill\square$

\section{Proof of Proposition~\ref{proposition_error_in_marginals}}

We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.

Straighforward, 
\begin{align*}
\varrho({\mu} ,{\mu}^{\text{sc}}) &= \sum_{i=1}^n  {\mu}^{\text{sc}}_i - {\mu}_i + {\mu}_i  \log\Big(\frac{{\mu}_i}{{\mu}^{\text{sc}}_i }\Big)\\
&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-1)\mu_i - \mu_i\log(\kappa) + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
&\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
\end{align*}
Using~\eqref{bound_on_v}, we have in one hand 
\begin{align*}
\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&= \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
&\leq \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(m_b \max_{i,j}K_{ij}\frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} + (m - m_b)\varepsilon\kappa\max_{i,j}K_{ij}\Big) \\
&\leq (n-n_b)\Big(\frac{m_b\max_{j} \nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2\Big).
\end{align*}
On the other hand 
\begin{align*}
\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&=\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
&\geq m_b\min_{i,j}K_{ij} \frac{m\varepsilon^2\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij} + m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
&\qquad +\varepsilon^2 (m- m_b) \min_{i,j}K_{ij}\\
&\geq \frac{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij}+ m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
&\qquad +\varepsilon^2 (m- m_b) \min_{i,j}K_{ij}\\
&\geq \frac{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij}+ m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
\end{align*}
Then 
\begin{align*}
\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij}+ m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
&\leq \frac{\kappa(n-n_b+ 1)}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
\end{align*}
Therefore
\begin{align*}
&\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i}\mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
\bigg)
\end{align*}
Therefore
\begin{align*}
\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
\end{align*}
Finally, by Lemma 6 in~\cite{altschulernips17} we get 
\begin{align*}
\norm{{\mu}^\star -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
\end{align*}
Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.

$\hfill\square$

### 2019-05-14 tex/v3/section_3_algorithm.tex
fix hyperlink citations in biblio
added supplementary to main
update sec3

@@
+%!TEX root = main.tex
+
 \section{Screened dual of Sinkhorn divergence} % (fold)
@@
 
-% In this section we describe the main algorithm studied in this paper. 
-For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
+\begin{wrapfigure}{o}{0.44\textwidth}
+\vspace{-15pt}
+\centering
+\includegraphics[width=0.45\textwidth]{./figs/fig0.pdf}%, height=0.2\textwidth
+\caption{Plotting of $e^{u^\star}, e^{v^\star}$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
+\label{fig:fig0}
+\vspace{-15pt}
+\end{wrapfigure}
+
+The key idea of our approach comes from the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning which is a method able to quickly identify inactive features, i.e., features that have $0$ components in the solution vector.
+Then, these inactive features can be removed from the optimization problem to reduce its scale.
+Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt the screening test to the Sinkhorn algorithm.
+Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
+In Figure~\ref{fig:fig0}, we plot $e^{u^\star}, e^{v^\star}$ potential solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \frac 1n \mathbf 1_n, \nu = \frac 1m \mathbf 1_m$, and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
+We also plot two lines correspond to $e^{u^\star} = \alpha_u$ and $e^{v^\star}= \alpha_v$ for some $\alpha_u, \alpha_v \in \R_+^*.$
+The core of static screening test developed in this paper aims at locating a subset of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
+$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
+Therefore, we can work on a "screened" dual of Sinkhorn divergence to reduce the computational cost by considering variables that belong only to $\R^{|I|} \times \R^{|J|}.$
+
+In the following, the parameters $\alpha_u$ and $\alpha_v$ are expressed via a fixed $\varepsilon > 0$ and $\kappa > 0$. 
+We then define a new formulation of problem~\eqref{sinkhorn-dual} called \emph{approximate dual of Sinkhorn divergence} as follows:
 \begin{equation} 
@@
 \end{equation}
-where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
 
-The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
+Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
 The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
 Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
+As explained above, the static screening test presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
 
@@
 
-First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
+Proof of Lemma~\ref{I_epsilon_kappa_J_epsilon_kappa} is postponed to the supplementary material.
+It is worth to note that first order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
 which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.
@@
 
-Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
+Now let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
 To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
@@
 \end{equation}
-Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
+Note that by construction we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$.
+
 Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-
 Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
@@
 The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
 It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
@@
 
-\textbf{step 2:} \textcolor{black}{L-BFGS}\\
+\noindent \textbf{step 2:} \textcolor{black}{L-BFGS-B}\\
 
@@
 \nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
+\nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
 \nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\

### 2019-05-15 da_expe.py
expe

@@ -6,7 +6,6 @@
 
 
 from time import process_time as time
-import matplotlib.pylab as plt
 import ot
 import ot.plot
 import  da_screenkhorn
@@ -14,14 +13,32 @@ from sklearn.neighbors import KNeighborsClassifier
 import numpy as np
 import argparse
 
+def toy(n_samples_source,n_samples_target,nz=0.75,random_state=None):
+    Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=nz,random_state=random_state)
+    Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=nz, random_state=random_state)
+    return Xs, ys, Xt, yt
+
+def subsample(x,y,n, nb_class=10):
+    ind_rand = np.random.permutation(x.shape[0])
+    x = x[ind_rand]
+    y = y[ind_rand]
+    x_r = np.empty((0,x.shape[1]))
+    y_r = np.empty(0)
+    for i in range(nb_class):
+        ind = np.where(y==i)[0]
+        ind_sub = ind[0:n]
+        x_r = np.vstack((x_r,x[ind_sub]))
+        y_r = np.hstack((y_r,y[ind_sub]))
+    return x_r, y_r
 
 parser = argparse.ArgumentParser()
-parser.add_argument('-n', action='store', dest='n', default = 1000, type=int,
+parser.add_argument('-n', action='store', dest='n', default = 3000, type=int,
                         help='number of samples ')
-parser.add_argument('-d', action='store', dest='d', default = 1, type=int,
+parser.add_argument('-d', action='store', dest='d', default = 2, type=int,
                         help='dataset type ')
 arguments = parser.parse_args()
 n = arguments.n # number of samples per class
+
 
 if arguments.d == 1:
     data = 'toy'
@@ -32,33 +49,50 @@ else:
 n_samples_source = n
 n_samples_target = n
 
-nb_iter = 50
+nb_iter = 20
+reg_cl = 10
+K = 1 # K of KNN
+
 pathres='./resultat/'
 p_vec = [1.5,2,5,10]
 n_pvec=  len(p_vec)
+filename = 'da_{:}_n{:d}_regcl{:d}.npz'.format(data,n,reg_cl)
 
[…]

### 2019-05-15 da_screenkhorn.py

@@ -122,6 +122,7 @@ def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
     n_budget = int(np.ceil(M.shape[0] / p_n))
     m_budget = int(np.ceil(M.shape[1] / p_m))
     
+    print(n_budget,m_budget)
     Mreg = M + eta * W
     screenkhorn = Screenkhorn(a, b, M, reg, N=n_budget, M=m_budget, verbose=False)
     transp = screenkhorn.lbfgsb()[2]
@@ -829,6 +830,7 @@ class BaseTransport(BaseEstimator):
 
             # pairwise distance
             self.cost_ = dist(Xs, Xt, metric=self.metric)
+            #self.cost_ = self.cost_/self.cost_.max()
             self.cost_ = cost_normalization(self.cost_, self.norm)
 
             if (ys is not None) and (yt is not None):
@@ -1415,7 +1417,7 @@ class ScreenkhornLpl1Transport(BaseTransport):
 
             p_n = kwargs.get('p_n', 2)# keep only 50% of points
             p_m = kwargs.get('p_m', 2)# keep only 50% of points
-
+            print(self.cost_)
             returned_ = screenkhorn_lpl1_mm(
                 a=self.mu_s, labels_a=ys, b=self.mu_t, M=self.cost_,
                 reg=self.reg_e, eta=self.reg_cl, numItermax=self.max_iter,

### 2019-05-15 screenkhorn.py

@@ -32,11 +32,11 @@ class Screenkhorn:
         self.uniform = uniform
 
         # K
-        # self.K = np.empty_like(self.C)
-        # np.divide(self.C, - self.reg, out=self.K)
-        # np.exp(self.K, out=self.K)
+        self.K = np.empty_like(self.C)
+        np.divide(self.C, - self.reg, out=self.K)
+        np.exp(self.K, out=self.K)
 
-        self.K = np.exp(-self.C / self.reg)
+        #self.K = np.exp(-self.C / self.reg)
 
         # Test
         if self.N == n and self.M == m:
@@ -70,15 +70,15 @@ class Screenkhorn:
             K_min = self.K.min()
 
             # 
-            if not self.uniform:
-                self.a_sort = np.sort(a)
-                self.b_sort = np.sort(b)
-          
+            #if not self.uniform:
+            #    self.a_sort = np.sort(a)
+            #    self.b_sort = np.sort(b)
+            self.a_sort = np.sort(a)
+            self.b_sort = np.sort(b)
                 
                 
             aK_sort = np.sort(a / K_sum_cols)[::-1]
             bK_sort = np.sort(b / K_sum_rows)[::-1]
-
             epsilon_u_square = aK_sort[self.N - 1: self.N].mean()
             epsilon_v_square = bK_sort[self.M - 1: self.M].mean()
 
@@ -99,7 +99,6 @@ class Screenkhorn:
             if self.verbose:
                 print('|I_active| = %s \t |J_active| = %s \t |I_active| + |J_active| = %s'\
                       %(len(self.I), len(self.J), len(self.I) + len(self.J)))
-
 
             # LBFGS box
             self.bounds_u = [(max(self.fact_scale * self.a_sort[self.I][-1] / (self.epsilon * (m - len(self.J)) \

### 2019-05-15 da_expe.py
tri partiels + bug da

@@ -34,7 +34,7 @@ n_samples_target = n
 
 nb_iter = 50
 pathres='./resultat/'
-p_vec = [1.5,2,5,10]
+p_vec = [1.5,2,5,10,20,50,100]
 n_pvec=  len(p_vec)
 
 bc_sink = np.zeros(nb_iter)
@@ -67,10 +67,11 @@ for i in range(nb_iter):
     #%%
     
     for j,p_n in enumerate(p_vec):
+        print(p_n)
         # Screenkhorn Transport
         tic = time()
         ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1e0,reg_cl=10)
-        ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, n_b=p_n, m_b=p_n)
+        ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, p_n=p_n, p_m=p_n)
         time_screen[i,j] = time() - tic
         # transport source samples onto target samples
         transp_Xs_screenkhorn = ot_screenkhorn.transform(Xs=Xs)

### 2019-05-15 da_screenkhorn.py

@@ -114,7 +114,7 @@ def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
         idxc, = np.where(labels_a == c)
         indices_labels.append(idxc)
 
-    W = np.zeros(M.shape)
+    #W = np.zeros(M.shape)
 
     p_n = kwargs.get('p_n', 1)
     p_m = kwargs.get('p_m', 1)
@@ -122,7 +122,7 @@ def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
     n_budget = int(np.ceil(M.shape[0] / p_n))
     m_budget = int(np.ceil(M.shape[1] / p_m))
     
-    Mreg = M + eta * W
+    #Mreg = M #+ eta * W
     screenkhorn = Screenkhorn(a, b, M, reg, N=n_budget, M=m_budget, verbose=False)
     transp = screenkhorn.lbfgsb()[2]
     

### 2019-05-15 screenkhorn.py

@@ -5,6 +5,8 @@
 __author__ = 'Mokhtar Z. Alaya'
 
 import numpy as np
+import bottleneck
+import heapq
 from scipy.optimize import fmin_l_bfgs_b
 from time import time
 
@@ -20,8 +22,8 @@ class Screenkhorn:
         self.a = np.asarray(a, dtype=np.float64)
         self.b = np.asarray(b, dtype=np.float64)
         
-        self.a_sort = np.copy(self.a)
-        self.b_sort = np.copy(self.b)
+        #self.a_sort = np.copy(self.a)
+        #self.b_sort = np.copy(self.b)
         self.C = np.asarray(C, dtype=np.float64)
         self.reg = reg
         n = C.shape[0]
@@ -57,6 +59,12 @@ class Screenkhorn:
             # box BFGS
             self.bounds_u = [(0.0, np.inf)] * n
             self.bounds_v = [(0.0, np.inf)] * m
+            
+            K_min = self.K.min()
+            #
+            self.K_IJ = self.K
+            self.a_I = self.a
+            self.b_J = self.b
 
         else:
             
@@ -64,24 +72,33 @@ class Screenkhorn:
                 print(time() - tic_initial)
             # sum of rows and columns of K
             K_sum_cols = self.K.sum(axis=1)
-            K_sum_rows = self.K.T.sum(axis=1)
+            K_sum_rows = self.K.sum(axis=0)
 
-            # K_min
-            K_min = self.K.min()
-
-            # 
-            if not self.uniform:
-                self.a_sort = np.sort(a)
-                self.b_sort = np.sort(b)
-          
+            if self.uniform:
+                if n/self.N < 4 :
+                    aK_sort = np.sort(K_sum_cols)
+                    epsilon_u_square = a[0]/aK_sort[self.N - 1]
+                else :
+                    aK_sort = bottleneck.partition(K_sum_cols, N-1)[N-1]
+                    epsilon_u_square =a[0]/aK_sort
+                    
+                if m/self.M < 4   :  
+                    bK_sort = np.sort(K_sum_rows)
+                    epsilon_v_square = b[0]/bK_sort[self.M - 1]
+                else:
+                    aK_sort = bottleneck.partition(K_sum_rows, M-1)[M-1]
+                    epsilon_v_square =b[0]/aK_sort
                 
+            else:
+                aK = a/K_sum_cols
[…]

### 2019-05-15 tex/v3/section_2_setup_OT.tex
fix hyperlink citations in biblio

@@
+%!TEX root = main.tex
+
 \section{Regularized discrete OT} % (fold)
@@
 \end{equation}
-where $B(u,v) = \Delta(e^{u}) K \Delta(e^{v})$ and $K = e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
-We refer to problem~\eqref{sinkhorn-dual} to the \emph{dual of Sinkhorn divergence}.
-Therefore, the optimal solution $P^\star$ of Sinkhorn divergence takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
+where $B(u,v) := \Delta(e^{u}) K \Delta(e^{v})$ and $K := e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
+We refer to problem~\eqref{sinkhorn-dual} as the \emph{dual of Sinkhorn divergence}, and its optimal solution $P^\star$ takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
 where the couple $(u^\star, v^\star)$ satisfies:
@@
 Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-Furthermore, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity.
+Moreover, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity~\cite{altschulernips17}.
 

### 2019-05-15 da_expe.py
modif mx

@@ -104,14 +104,9 @@ for i in range(nb_iter):
         print(p_n)
         # Screenkhorn Transport
         tic = time()
-<<<<<<< HEAD
-        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1e0,reg_cl=10)
+        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1e0,reg_cl=reg_cl)
         ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, p_n=p_n, p_m=p_n)
-=======
-        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
-        ot_screenkhorn.verbose=1
-        ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, n_b=p_n, m_b=p_n)
->>>>>>> 09c79757c659476e0f19801fe1e403fc06a9a380
+       
         time_screen[i,j] = time() - tic
         # transport source samples onto target samples
         transp_Xs_screenkhorn = ot_screenkhorn.transform(Xs=Xs)

### 2019-05-15 da_screenkhorn.py

@@ -122,12 +122,6 @@ def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
     n_budget = int(np.ceil(M.shape[0] / p_n))
     m_budget = int(np.ceil(M.shape[1] / p_m))
     
-<<<<<<< HEAD
-    #Mreg = M #+ eta * W
-=======
-    print(n_budget,m_budget)
-    Mreg = M + eta * W
->>>>>>> 09c79757c659476e0f19801fe1e403fc06a9a380
     screenkhorn = Screenkhorn(a, b, M, reg, N=n_budget, M=m_budget, verbose=False)
     transp = screenkhorn.lbfgsb()[2]
     

### 2019-05-15 screenkhorn.py

@@ -72,7 +72,6 @@ class Screenkhorn:
                 print(time() - tic_initial)
             # sum of rows and columns of K
             K_sum_cols = self.K.sum(axis=1)
-<<<<<<< HEAD
             K_sum_rows = self.K.sum(axis=0)
 
             if self.uniform:
@@ -89,38 +88,16 @@ class Screenkhorn:
                 else:
                     aK_sort = bottleneck.partition(K_sum_rows, M-1)[M-1]
                     epsilon_v_square =b[0]/aK_sort
-=======
-            K_sum_rows = self.K.T.sum(axis=1)
-
-            # K_min
-            K_min = self.K.min()
-
-            # 
-            #if not self.uniform:
-            #    self.a_sort = np.sort(a)
-            #    self.b_sort = np.sort(b)
-            self.a_sort = np.sort(a)
-            self.b_sort = np.sort(b)
->>>>>>> 09c79757c659476e0f19801fe1e403fc06a9a380
                 
             else:
                 aK = a/K_sum_cols
                 bK = b/K_sum_rows
                 
-<<<<<<< HEAD
                 aK_sort = np.sort(aK)[::-1]
                 epsilon_u_square = aK_sort[self.N - 1]
                 bK_sort = np.sort(bK)[::-1]
                 epsilon_v_square = bK_sort[self.M - 1]
-                          
-            
-=======
-            aK_sort = np.sort(a / K_sum_cols)[::-1]
-            bK_sort = np.sort(b / K_sum_rows)[::-1]
-            epsilon_u_square = aK_sort[self.N - 1: self.N].mean()
-            epsilon_v_square = bK_sort[self.M - 1: self.M].mean()
-
->>>>>>> 09c79757c659476e0f19801fe1e403fc06a9a380
+                                     
             self.epsilon = (epsilon_u_square * epsilon_v_square)**(1/4)
             self.fact_scale = (epsilon_v_square / epsilon_u_square)**(1/2)
             
@@ -137,7 +114,7 @@ class Screenkhorn:
             if self.verbose:
                 print('|I_active| = %s \t |J_active| = %s \t |I_active| + |J_active| = %s'\
                       %(len(self.I), len(self.J), len(self.I) + len(self.J)))
-<<<<<<< HEAD
+
             
             # Ic, Jc
             self.Ic = list(set(list(range(n))) - set(self.I))
@@ -170,9 +147,6 @@ class Screenkhorn:
             if len(self.J) != M:
[…]

### 2019-05-15 screenkhorn.py
modif bug 1.5

@@ -6,7 +6,6 @@ __author__ = 'Mokhtar Z. Alaya'
 
 import numpy as np
 import bottleneck
-import heapq
 from scipy.optimize import fmin_l_bfgs_b
 from time import time
 
@@ -78,6 +77,7 @@ class Screenkhorn:
                 if n/self.N < 4 :
                     aK_sort = np.sort(K_sum_cols)
                     epsilon_u_square = a[0]/aK_sort[self.N - 1]
+                    print(epsilon_u_square)
                 else :
                     aK_sort = bottleneck.partition(K_sum_cols, N-1)[N-1]
                     epsilon_u_square =a[0]/aK_sort
@@ -86,8 +86,8 @@ class Screenkhorn:
                     bK_sort = np.sort(K_sum_rows)
                     epsilon_v_square = b[0]/bK_sort[self.M - 1]
                 else:
-                    aK_sort = bottleneck.partition(K_sum_rows, M-1)[M-1]
-                    epsilon_v_square =b[0]/aK_sort
+                    bK_sort = bottleneck.partition(K_sum_rows, M-1)[M-1]
+                    epsilon_v_square =b[0]/bK_sort
                 
             else:
                 aK = a/K_sum_cols
@@ -95,9 +95,30 @@ class Screenkhorn:
                 
                 aK_sort = np.sort(aK)[::-1]
                 epsilon_u_square = aK_sort[self.N - 1]
+            
                 bK_sort = np.sort(bK)[::-1]
                 epsilon_v_square = bK_sort[self.M - 1]
-                                     
+            # I, J
+            self.I = np.where(self.a >=  epsilon_u_square * K_sum_cols)[0].tolist()
+            self.J = np.where(self.b >=  epsilon_v_square* K_sum_rows)[0].tolist()   
+             
+            if len(self.I) != self.N:
+                print("test error", len(self.I),self.N)
+                if self.uniform:
+                    aK = a/K_sum_cols
+                aK_sort = np.sort(aK)[::-1]
+                epsilon_u_square = aK_sort[self.N - 1:self.N+1].mean()
+                self.I = np.where(self.a >=  epsilon_u_square * K_sum_cols)[0].tolist()
+            
+            if len(self.J) != self.M:
+                print("test error", len(self.J),self.M)
+                if self.uniform:
+                    bK = b/K_sum_rows
[…]

### 2019-05-15 tex/v3/section_1_introduction.tex
new modif of tex

@@
 We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical} that relies on an estimation of the inverse of the Hessian based on gradients differences.
-L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
+Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences.
+L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
 

### 2019-05-15 tex/v3/section_3_algorithm.tex
new modif of tex

--- 2019-05-14 tex/v3/section_3_algorithm.tex
@@
 
-% In this section we describe the main algorithm studied in this paper. 
-For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
+\begin{wrapfigure}{o}{0.44\textwidth}
+\vspace{-15pt}
+\centering
+\includegraphics[width=0.4\textwidth]{./figs/motivations.pdf}%, height=0.2\textwidth
+\caption{Plotting of $e^{u^\star}, e^{v^\star}$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
+\label{fig:motivations}
+\vspace{-15pt}
+\end{wrapfigure}
+
+\paragraph{Motivation.} The key idea of our approach comes from the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, a method is able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
+Then, these inactive features can be removed from the optimization problem to reduce its scale.
+Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
+Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
+In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
+% \nu = \frac 1m \mathbf 1_m
+We also plot two lines correspond to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.
+
+\paragraph{Static screening test.} The core of the static screening test developed in this work aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
+$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
+The sets $I$ and $J$ will be called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
+Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
+
+In the following, the parameters $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ where $\varepsilon > 0$ and $\kappa > 0$ are fixed numeric constants to be given later. 
+Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, given by:
+
+% To construct our appropriate static screening test, the parameters $\alpha_u$ and $\alpha_v$ are expressed via a fixed numeric constants $\varepsilon > 0$ and $\kappa > 0$ to be given later. 
+% In spirit of To construct the screening test, we define a new form
+
 \begin{equation} 
@@
 \end{equation}
-where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
 
-The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
-The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
+% Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
+The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these variables.
 Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:
+As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows: %depended on $\varepsilon, \kappa$ and
 
@@
 
-First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$
-which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.
+Proof of Lemma~\ref{I_epsilon_kappa_J_epsilon_kappa} is postponed to the supplementary material.
+It is worth to note that first order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\cite{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.
 
@@
 
-Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
-The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
-In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
+Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$, where its values depend on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$.
+In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
+More precisely, we change the domain of the objective function $\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
+%\textbf{dom}\Psi_\kappa =
 
-Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
+\begin{wrapfigure}{o}{0.44\textwidth}
+\vspace{-15pt}
+\centering
+\includegraphics[width=0.4\textwidth]{./figs/kappa_epsilon.pdf}%, height=0.2\textwidth
+\caption{Convergence of $(\varepsilon, \kappa)$ to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$ for the same setting as in Figure~\eqref{fig:motivations}.}
+\label{fig:kappa_epsilon}
+\vspace{-15pt}
+\end{wrapfigure}
+
+In this spirit, let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
 To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
@@
 \end{equation}
-Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
+Note that in one hand we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction.
+On the other hand, $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, and the couple parameters $(\varepsilon, \kappa)$ tends to $(0,1)$ (see Figure~\ref{fig:kappa_epsilon}), which corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+
 Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
+Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
 \begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
+\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
 \end{equation*}
-and 
-\begin{equation*}
-	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
-\end{equation*}
+% and 
+% \begin{equation*}
+% 	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.
+%, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
+% \end{equation*}
 where the vector comparison $\succeq$ has to be understood elementwise.
@@
 \varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
-&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
+&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}}. %+ \Xi
 \end{align*}
-with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
+%with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
 
-Pseudocode of our proposed algorithm is given in Algorithm~\ref{screenkhorn}.
-Screenkhorn consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
-It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
+Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
+It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradients, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
+Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
+The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
+The L-BFGS-B solver handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
+The following lemma (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
 
-The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
 \begin{lemma}
 \label{lemma_bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}, and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$.
+Then,
 one has
@@
 \label{bound_on_u}
-\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
+\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa K_{\min}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min}},
 \end{equation}
@@
 \label{bound_on_v}
-\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
+\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min} } n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min} }
 \end{equation}
@@
 
-\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
+% \nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
 \nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\

### 2019-05-15 tex/v3/section_4_marginal_viols.tex
fix hyperlink citations in biblio
new modif of tex

@@
+%!TEX root = main.tex
+
 \section{Analysis of marginal violations} % (fold)
@@
 
-This section is devoted to study the marginal violations of Screenkhorn.
-Towards this end, let us define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$
+This section is devoted to establishing theoretical guarantees for the marginal violations of Screenkhorn. 
+We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
 Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
@@
 \begin{equation*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
+\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
 \end{equation*}
@@
 \begin{equation*}
-\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\min_{i,j}K_{ij}} + (n-n_b)\varepsilon^2\Big).
+\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\Big).
 \end{equation*}
@@
 \begin{align*} %{\norm{{\mu}^{\text{sc}}}_1} 
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)% \bigg\}^{1/2}
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7\norm{\mu^{\text{sc}}}_1 n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7\norm{\mu^{\text{sc}}}_1  (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\\
+&\qquad - \min_{i}\mu_i + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)\bigg)% \bigg\}^{1/2}
 \end{align*}
@@
 \begin{align*} %{\norm{{\nu}^{\text{sc}}}_1}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n\min_{i,j} K_{ij}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b\min_{i,j}K_{ij}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7\norm{\nu^{\text{sc}}}_1m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7\norm{\nu^{\text{sc}}}_1(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
+&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(K_{\min})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
 \end{align*}

### 2019-05-15 tex/v3/supplementary_material.tex
new modif of tex

@@
-%!TEX root = main.tex
-\newpage
-\appendix
+ \documentclass{article}
 
-\begin{center}
-\Large{\textbf{Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''}}
-\end{center}
+% if you need to pass options to natbib, use, e.g.:
+% \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading neurips_2019
+
+% ready for submission
+% \usepackage{neurips_2019}
+
+% to compile a preprint version, e.g., for submission to arXiv, add add the
+% [preprint] option:
+%\usepackage[preprint]{neurips_2019}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+\usepackage[]{neurips_2019}
+
+% to avoid loading the natbib package, add option nonatbib:
+% \usepackage[nonatbib]{neurips_2019}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+
+%--------------------------------------------------------------------------------------------------------------------------------%
+
+\usepackage{xr}
+\externaldocument{main}
+
+\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
+\usepackage[titletoc,title]{appendix}%
+\usepackage{dsfont}%
+\usepackage{caption} % 
+\usepackage{subcaption}
+\usepackage{float}%
+\usepackage{graphicx, color}% 
+\usepackage{bm}%bold equations
+
+%% formatting appendices
+\usepackage{etoolbox}
+\patchcmd{\appendices}{\quad}{. }{}{}
+
+%% tables
+\usepackage{pgfplots}%
+\usepackage{booktabs,multirow,array,multicol}
+\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
+
+%% algorithms
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+
+\usepackage{accents}
+\usepackage{datenumber}
+\usepackage{wrapfig}
+
+%% sections
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
+\newtheorem{fact}{Fact}
+\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}%[section]
+\newtheorem*{notation}{Notation}%[section]
+\newtheorem{discus}{Discussion}%[section]
+\newtheorem{remark}{Remark}%[section]
+\newtheorem{example}{Example}%[section]
+\newtheorem{exs}{Examples}%[section]
+\newtheorem{ca}{Cas}
+\newtheorem{remarks}{Remarks}%[section]
+\newtheorem{assumption}{Assumption}{\bf}{\rm}%
+
+% math macros
+\newcommand{\bigO}{\mathcal{O}}
+\newcommand{\inr}[1]{\langle #1 \rangle}
+\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
+\newcommand{\norm}[1]{\|#1\|}
+\newcommand{\R}{{\mathbb{R}}}
+\newcommand{\E}{\mathds{E}}
+\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
+\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
+\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
+
+%% math operators
+\DeclareMathOperator*{\argmin}{\arg\!\min}
+\DeclareMathOperator*{\argmax}{\arg\!\max}
+%--------------------------------------------------------------------------------------------------------------------------------%
+
+\title{Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''}
+
+\begin{document}
+
+\maketitle
 
@@
 
+Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty.
 Introducing two dual variables $\lambda \in \R^n_{+}$ and $\beta \in \R^m_{+}$ for each constraint, the Lagrangian of problem~\eqref{screen-sinkhorn} reads as 
@@
 \begin{equation*}
-\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon \min_{i,j}K_{ij}}.
+\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon \min_{i,j}K_{ij}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
 \end{equation*}
@@
 \label{upper_bound_v_potential}
-\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}.
+\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
 \end{equation}
@@
 \sum_{j=1}^m e^{v^{\text{sc}}_j} &= \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j}
-\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} |J_{\varepsilon,\kappa}|.
+\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} |J_{\varepsilon,\kappa}|.
 \end{align*}
@@
 \begin{align*}
-\min_{i \in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\varepsilon,\kappa}}\mu_i}{\varepsilon\kappa (m-m_b) + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} m_b}.
+\min_{i \in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\varepsilon,\kappa}}\mu_i}{\varepsilon\kappa (m-m_b) + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} m_b}.
 \end{align*}
@@
 $\hfill\square$
+
+\small
+\bibliography{biblio}
+\bibliographystyle{plain}
+
+\end{document}

### 2019-05-15 da_expe.py
expe

@@ -32,7 +32,7 @@ def subsample(x,y,n, nb_class=10):
     return x_r, y_r
 
 parser = argparse.ArgumentParser()
-parser.add_argument('-n', action='store', dest='n', default = 3000, type=int,
+parser.add_argument('-n', action='store', dest='n', default = 2000, type=int,
                         help='number of samples ')
 parser.add_argument('-d', action='store', dest='d', default = 2, type=int,
                         help='dataset type ')
@@ -49,7 +49,7 @@ else:
 n_samples_source = n
 n_samples_target = n
 
-nb_iter = 20
+nb_iter = 30
 reg_cl = 10
 K = 1 # K of KNN
 

### 2019-05-15 wda_expe.py

@@ -94,9 +94,9 @@ else:
 reg = 1  # regularizer weight
 k = 10  # nb of sinkhorn iteration
 maxiter = 1000 # max iter in WDA
-nb_iter = 50
+nb_iter = 30
 K = 5 # K in KNN
-p_vec = [2,10,20,30]
+p_vec = [1.5,2,5,10,20,50,100]
 pathres='./resultat/'
 
 

### 2019-05-15 da_expe.py
expe

@@ -4,7 +4,8 @@
 
 # In[1]:
 
-
+import os
+os.environ["OMP_NUM_THREADS"] = "1"
 from time import process_time as time
 import ot
 import ot.plot

### 2019-05-16 tex/v3/main.tex
fix hyperlink citations in biblio
added supplementary to main
new modif of tex
new

@@
 \usepackage{datenumber}
+\usepackage{wrapfig}
+
 %% sections
@@
 
-\title{Screening Sinkhorn Algorithm for regularized Optimal Transport}
+\title{Screening Sinkhorn Algorithm for Regularized Optimal Transport}
 
@@
 \begin{abstract}
+We introduce in this paper a novel strategy for efficiently approximate the Sinkhorn distance between two discrete measures. After identifying neglectible components
+of the dual solution of the regularized Sinkhorn problem, we propose to screen those components by directly setting them at that value before entering the Sinkhorn problem.
+This allows us to solve a smaller Sinkhorn problem while ensuring approximation with provable guarantees.
+More formally, the approach is based on a reformulation of  \emph{dual of Sinkhorn divergence problem} and on the KKT optimality conditions of this problem, which enable identification of dual components to be screened.
+This new analysis leads to the \emph{Screenkhorn} algorithm.
+We illustrate the efficiency of Screenkhorn on complex tasks such as dimensionality reduction or domain adaptation involving regularized optimal transport.
 
-This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
+%This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
+%Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
+%These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
+%This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
+%We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
 \end{abstract}
@@
 \bibliography{biblio}
-\bibliographystyle{plain} %{abbrvnat} %{plainnat}
+\bibliographystyle{plain}
+
+%\input{supplementary_material}
 

### 2019-05-16 tex/v3/main.tex
new

@@
 
-\title{Screening Sinkhorn Algorithm for Regularized Optimal Transport}
+\title{Screening Sinkhorn Algorithm for regularized Optimal Transport}
 
@@
 \begin{abstract}
-We introduce in this paper a novel strategy for efficiently approximate the Sinkhorn distance between two discrete measures. After identifying neglectible components
-of the dual solution of the regularized Sinkhorn problem, we propose to screen those components by directly setting them at that value before entering the Sinkhorn problem.
+
+We introduce in this paper a novel strategy for efficiently approximate the Sinkhorn distance between two discrete measures.
+After identifying neglectible components of the dual solution of the regularized Sinkhorn problem, we propose to screen those components by directly setting them at that value before entering the Sinkhorn problem.
 This allows us to solve a smaller Sinkhorn problem while ensuring approximation with provable guarantees.
@@
 
-%This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-%Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-%These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-%This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-%We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
+% This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
+% Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
+% These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
+% This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
+% We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
 \end{abstract}
@@
 
-%\input{supplementary_material}
-
 \end{document}

### 2019-05-16 tex/v3/section_3_algorithm.tex
new

@@
 \centering
-\includegraphics[width=0.4\textwidth]{./figs/motivations.pdf}%, height=0.2\textwidth
-\caption{Plotting of $e^{u^\star}, e^{v^\star}$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
+\includegraphics[width=0.45\textwidth]{./figs/motivations.pdf}
+\caption{Plots of $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
 \label{fig:motivations}
-\vspace{-15pt}
+\vspace{-11pt}
 \end{wrapfigure}
 
-\paragraph{Motivation.} The key idea of our approach comes from the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, a method is able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
+\paragraph{Motivation.}
+
+The key idea of our approach is motivated by the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, that is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
 Then, these inactive features can be removed from the optimization problem to reduce its scale.
@@
 In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
-% \nu = \frac 1m \mathbf 1_m
 We also plot two lines correspond to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.
@@
 
-% To construct our appropriate static screening test, the parameters $\alpha_u$ and $\alpha_v$ are expressed via a fixed numeric constants $\varepsilon > 0$ and $\kappa > 0$ to be given later. 
-% In spirit of To construct the screening test, we define a new form
-
 \begin{equation} 
@@
 \end{equation}
-
-% Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
 The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these variables.
 Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows: %depended on $\varepsilon, \kappa$ and
+As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows:
 
@@
 More precisely, we change the domain of the objective function $\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
-%\textbf{dom}\Psi_\kappa =
 
 \begin{wrapfigure}{o}{0.44\textwidth}
-\vspace{-15pt}
+\vspace{-18pt}
 \centering
-\includegraphics[width=0.4\textwidth]{./figs/kappa_epsilon.pdf}%, height=0.2\textwidth
-\caption{Convergence of $(\varepsilon, \kappa)$ to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$ for the same setting as in Figure~\eqref{fig:motivations}.}
+\includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
+\caption{Plots of $\varepsilon$ and $\kappa$ as a functions of budgets for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ as in Figure~\eqref{fig:motivations}.
+As can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
 \label{fig:kappa_epsilon}
@@
 Note that in one hand we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction.
-On the other hand, $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, and the couple parameters $(\varepsilon, \kappa)$ tends to $(0,1)$ (see Figure~\ref{fig:kappa_epsilon}), which corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$.
+In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence in this case corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 

### 2019-05-16 tex/v3/section_4_marginal_viols.tex
new

@@
 We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
-Lemma~\ref{lemma_bounds_on_marginals} expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
-% while Proposition~\ref{proposition_error_in_marginals} gives also an upper bound of the marginal errors.
+Lemma~\ref{lemma_bounds_on_marginals} expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$, while Proposition~\ref{proposition_error_in_marginals} gives an upper bound of the marginal errors.
 
@@
 Then one has 
-\begin{equation*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
-\end{equation*}
+\begin{align*}
+ \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 & + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i } + (m-m_b)\varepsilon^2K_{\min}\Big)\\
+ & \leq \norm{\mu^{\text{sc}}}_1  \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
+\end{align*}
 and 
-\begin{equation*}
-\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\Big).
-\end{equation*}
+\begin{align*}
+\kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}^{\text{}}}_1 & + (m -m_b) \Big(\frac{nn_b\varepsilon^2\kappa^2K_{\min}^2 \min_{i\in I_{\varepsilon, \kappa}} \mu_j}{ n(m-m_b)\varepsilon^2 \kappa K_{\min} + m_b\kappa \max_{j\in J_{\varepsilon,\kappa}}\nu_j } + (n-n_b)\varepsilon^2K_{\min}\Big)\\
+&\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\Big).
+\end{align*}
+
 \end{lemma}
-The following Proposition gives also an upper bound of the marginal errors.
 \begin{proposition}
 \label{proposition_error_in_marginals}
+% Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then, one has 
 One has 
-\begin{align*} %{\norm{{\mu}^{\text{sc}}}_1} 
+\begin{align*}
 {\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7\norm{\mu^{\text{sc}}}_1 n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7\norm{\mu^{\text{sc}}}_1  (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\\
-&\qquad - \min_{i}\mu_i + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)\bigg)% \bigg\}^{1/2}
+&\qquad - \min_{i}\mu_i + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)\bigg)
 \end{align*}
 and 
-\begin{align*} %{\norm{{\nu}^{\text{sc}}}_1}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7\norm{\nu^{\text{sc}}}_1m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7\norm{\nu^{\text{sc}}}_1(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
-&+ \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2(K_{\min})^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).% \bigg\}^{1/2}
+\begin{align*}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7\norm{\nu^{\text{sc}}}_1m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7\norm{\nu^{\text{sc}}}_1(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2\\
+&\qquad - \min_{j}\nu_j + \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)\bigg).
 \end{align*}
-
 \end{proposition}
+Proofs of Lemma~\ref{lemma_bounds_on_marginals} and Proposition~\ref{proposition_error_in_marginals} are presented in supplementary material. 
+Proof of Proposition~\ref{proposition_error_in_marginals} is based on a generalization of the Pinsker inequality~\cite{altschulernips17,khalilabid2018}.
 

### 2019-05-16 tex/v3/supplementary_material.tex
new

@@
 & \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa\min_{i,j}K_{ij}} + (m-m_b)\varepsilon^2 \Big)
+& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
 \end{align*}

### 2019-05-16 tex/v3/main.tex

@@
 \begin{abstract}
-
-We introduce in this paper a novel strategy for efficiently approximate the Sinkhorn distance between two discrete measures.
-After identifying neglectible components of the dual solution of the regularized Sinkhorn problem, we propose to screen those components by directly setting them at that value before entering the Sinkhorn problem.
+We introduce in this paper a novel strategy for efficiently approximate the Sinkhorn distance between two discrete measures. After identifying neglectible components
+of the dual solution of the regularized Sinkhorn problem, we propose to screen those components by directly setting them at that value before entering the Sinkhorn problem.
 This allows us to solve a smaller Sinkhorn problem while ensuring approximation with provable guarantees.
@@
 % We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
+
 \end{abstract}
@@
 
+%\input{supplementary_material}
+
 \end{document}

### 2019-05-16 tex/v3/section_1_introduction.tex
new

@@
 We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences.
+Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences.
 L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.

### 2019-05-16 tex/v3/section_3_algorithm.tex
new

@@
 
-The key idea of our approach is motivated by the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, that is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
+The key idea of our approach is motivated by the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, which is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
 Then, these inactive features can be removed from the optimization problem to reduce its scale.
@@
 $e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
-The sets $I$ and $J$ will be called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
+The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
 Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
@@
 In the following, the parameters $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ where $\varepsilon > 0$ and $\kappa > 0$ are fixed numeric constants to be given later. 
-Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, given by:
+Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, defined by:
 
@@
 \end{equation}
-The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these variables.
+The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
 Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.

### 2019-05-16 tex/v3/section_4_marginal_viols.tex
new

@@
 
+% We derive in this section 
 This section is devoted to establishing theoretical guarantees for the marginal violations of Screenkhorn. 
 We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
-Lemma~\ref{lemma_bounds_on_marginals} expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$, while Proposition~\ref{proposition_error_in_marginals} gives an upper bound of the marginal errors.
+Lemma~\ref{lemma_bounds_on_marginals} expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$, while Proposition~\ref{proposition_error_in_marginals} gives an upper bound of marginal errors.
 
@@
 \end{align*}
-
 \end{lemma}
@@
 \label{proposition_error_in_marginals}
-% Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then, one has 
-One has 
+One has %\norm{\mu^{\text{sc}}}_1
 \begin{align*}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7\norm{\mu^{\text{sc}}}_1 n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7\norm{\mu^{\text{sc}}}_1  (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\\
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7 n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\\
 &\qquad - \min_{i}\mu_i + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)\bigg)
@@
 \begin{align*}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7\norm{\nu^{\text{sc}}}_1m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7\norm{\nu^{\text{sc}}}_1(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2\\
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7 m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2\\ 
 &\qquad - \min_{j}\nu_j + \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)\bigg).

### 2019-05-16 tex/v3/supplementary_material.tex
new

@@
 % ready for submission
-% \usepackage{neurips_2019}
+\usepackage{neurips_2019}
 
@@
 % [preprint] option:
-%\usepackage[preprint]{neurips_2019}
+% \usepackage[preprint]{neurips_2019}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage[]{neurips_2019}
+% \usepackage[]{neurips_2019}
 
@@
 
+\author{%
+Mokhtar Z. Alaya \\
+LITIS EA4108\\
+University of Rouen\\
+\texttt{mokhtarzahdi.alaya@gmail.com} 
+\And
+Maxime Bérar\\
+LITIS EA4108\\
+University of Rouen\\
+\texttt{maxime.berar@univ-rouen.fr} \\
+\And
+Gilles Gasso \\
+LITIS EA4108\\
+INSA, University of Rouen\\
+\texttt{gilles.gasso@insa-rouen.fr} 
+\And
+Alain Rakotomamonjy\\
+LITIS EA4108 \\
+University of Rouen\\
+and Criteo AI Labs, Criteo Paris \\
+\texttt{alain.rakoto@insa-rouen.fr} \\
+}
 \maketitle
@@
 
-$\hfill\square$
-
 \section{Proof of Lemma~\ref{lemma_bounds_of_usc_and_vsc}}
 
-We prove only the first statement~\eqref{bound_on_u} and similarly we can prove the second statement~\eqref{bound_on_v}.
+We prove only the first statement~\eqref{bound_on_u} and similarly we can prove the second one~\eqref{bound_on_v}.
 For all $i\in I_{\varepsilon,\kappa}$, we have $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ or $e^{u^{\text{sc}}_i} = \frac \varepsilon\kappa$.
-In one hand, if $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ then according to the optimality conditions $\lambda^{\text{sc}}_i = 0.$ Then $e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i$.
+In one hand, if $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ then according to the optimality conditions $\lambda^{\text{sc}}_i = 0,$ which implies $e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i$.
 In another hand, we have 
@@
 \begin{equation*}
-\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon \min_{i,j}K_{ij}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
+\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
 \end{equation*}
@@
 \label{upper_bound_v_potential}
-\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
+\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
 \end{equation}
@@
 \end{align*}
-
-$\hfill\square$
 
@@
 While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
-
-Straighforward, 
+The violations are computed through the following function: 
+\begin{equation*}
+	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
+\end{equation*}
+Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
+The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
+\begin{lemma}
+For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
 \begin{align*}
-\varrho({\mu} ,{\mu}^{\text{sc}}) &= \sum_{i=1}^n  {\mu}^{\text{sc}}_i - {\mu}_i + {\mu}_i  \log\Big(\frac{{\mu}_i}{{\mu}^{\text{sc}}_i }\Big)\\
+\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
+\end{align*}
+\end{lemma}
+Straightforward, 
+\begin{align*}
+d_\varrho({\mu} ,{\mu}^{\text{sc}}) &= \sum_{i=1}^n  {\mu}^{\text{sc}}_i - {\mu}_i + {\mu}_i  \log\Big(\frac{{\mu}_i}{{\mu}^{\text{sc}}_i }\Big)\\
 &= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-1)\mu_i - \mu_i\log(\kappa) + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
@@
 \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&= \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\leq \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(m_b \max_{i,j}K_{ij}\frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}} + (m - m_b)\varepsilon\kappa\max_{i,j}K_{ij}\Big) \\
-&\leq (n-n_b)\Big(\frac{m_b\max_{j} \nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2\Big).
+&\leq \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(m_b \max_{i,j}K_{ij}\frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} + (m - m_b)\varepsilon\kappa\max_{i,j}K_{ij}\Big) \\
+&\leq (n-n_b)\Big(\frac{m_b\max_{j} \nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\Big).
 \end{align*}
-On the other hand 
+On the other hand, we get
 \begin{align*}
 \frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&=\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\geq m_b\min_{i,j}K_{ij} \frac{m\varepsilon^2\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij} + m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
-&\qquad +\varepsilon^2 (m- m_b) \min_{i,j}K_{ij}\\
-&\geq \frac{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij}+ m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
-&\qquad +\varepsilon^2 (m- m_b) \min_{i,j}K_{ij}\\
-&\geq \frac{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij}+ m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
+&\geq m_bK_{\min} \frac{m\varepsilon^2K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min} + m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
+&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
+&\geq \frac{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
+&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
+&\geq \frac{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
 \end{align*}
@@
 \begin{align*}
-\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2\min_{i,j}K_{ij}+ m\varepsilon^2\min_{i,j}K_{ij} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
-&\leq \frac{\kappa(n-n_b+ 1)}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
+\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
+&\leq \frac{\kappa(n-n_b+ 1)}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
+\end{align*}
+It entails 
+\begin{align*}
+&\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
+&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i}\mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
+\bigg).
 \end{align*}
@@
 \begin{align*}
-&\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i}\mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
-\bigg)
-\end{align*}
-Therefore
-\begin{align*}
-\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
+d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
 \end{align*}
@@
 \norm{{\mu}^\star -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b\min_{i,j}K_{ij}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2(\min_{i,j}K_{ij})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
+&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
 \end{align*}
 Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
-
-$\hfill\square$
 

### 2019-05-16 screenkhorn.py

@@ -174,7 +174,7 @@ class Screenkhorn:
 
         
 
-
+@
         self.vec_eps_IJc = self.epsilon * self.fact_scale * (self.K_IJc * np.ones(m-self.M).reshape((1, -1))).sum(axis=1)
         self.vec_eps_IcJ = (self.epsilon / self.fact_scale) * (np.ones(n-self.N).reshape((-1, 1)) * self.K_IcJ).sum(axis=0)
 

### 2019-05-16 tex/v3/section_3_algorithm.tex
new

@@
 The L-BFGS-B solver handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
-The following lemma (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
+The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
 
-\begin{lemma}
-\label{lemma_bounds_of_usc_and_vsc}
+\begin{proposition}
+\label{prop:bounds_of_usc_and_vsc}
 Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}, and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$.
@@
 for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
-\end{lemma}
+\end{proposition}
 

### 2019-05-16 tex/v3/supplementary_material.tex
new

@@
 
-\section{Proof of Lemma~\ref{lemma_bounds_of_usc_and_vsc}}
+\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
 
@@
 \end{align}
-Using Inequality~\eqref{bound_on_v}, we obtain 
+Using inequality~\eqref{bound_on_v}, we obtain 
 \begin{align*}
@@
 \end{align*}
+
 Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
-
-$\hfill\square$
 
@@
 \begin{lemma}
+\label{lem:pinsker}
 For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
@@
 \end{align*}
-Finally, by Lemma 6 in~\cite{altschulernips17} we get 
+Finally, by Lemma~\ref{lem:pinsker} we obtain
 \begin{align*}

### 2019-05-17 tex/v3/section_4_marginal_viols.tex
new
update supplmentary

@@
 \begin{align*}
- \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 & + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i } + (m-m_b)\varepsilon^2K_{\min}\Big)\\
- & \leq \norm{\mu^{\text{sc}}}_1  \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
+ \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1  + (n -n_b) &\bigg(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i } + (m-m_b)\varepsilon^2K_{\min}\bigg)\\
+ & \leq \norm{\mu^{\text{sc}}}_1\\
+ & \qquad \qquad \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \bigg(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \bigg)
 \end{align*}
@@
 \begin{align*}
-\kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}^{\text{}}}_1 & + (m -m_b) \Big(\frac{nn_b\varepsilon^2\kappa^2K_{\min}^2 \min_{i\in I_{\varepsilon, \kappa}} \mu_j}{ n(m-m_b)\varepsilon^2 \kappa K_{\min} + m_b\kappa \max_{j\in J_{\varepsilon,\kappa}}\nu_j } + (n-n_b)\varepsilon^2K_{\min}\Big)\\
-&\norm{\nu^{\text{sc}}}_1 \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\Big(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\Big).
+\kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}^{\text{}}}_1 + (m -m_b) &\bigg(\frac{nn_b\varepsilon^2\kappa^2K_{\min}^2 \min_{i\in I_{\varepsilon, \kappa}} \mu_j}{ n(m-m_b)\varepsilon^2 \kappa K_{\min} + m_b\kappa \max_{j\in J_{\varepsilon,\kappa}}\nu_j } + (n-n_b)\varepsilon^2K_{\min}\bigg)\\
+&\leq \norm{\nu^{\text{sc}}}_1\\
+ & \qquad \quad \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\bigg(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\bigg).
 \end{align*}
@@
 One has %\norm{\mu^{\text{sc}}}_1
+\begin{align}
+\label{maginal_mu}
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7 n_bc_\kappa \max_{i} \mu_i + 7 (n-n_b)\bigg[\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i \nonumber\\
+&\qquad \quad  + \max_{i} \mu_i\log\bigg(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\bigg)\bigg]
+\end{align}
+and 
+\begin{align}
+\label{maginal_nu}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7 m_bc_{\kappa^{-1}}\max_{j} \nu_j + 7(m-m_b)\bigg[\frac{n_b\kappa\max_{i}\mu_i}{m K_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\nonumber\\ 
+&\qquad  + \max_{j} \nu_j\log\bigg(\frac{(m-m_b+ 1)\max_{j} \nu_j}{n_b \kappa K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{m_b(\max_{j} \nu_j)^2}{nn_b\varepsilon^2\kappa^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\bigg)\bigg],
+\end{align}
+where $c_z = z-\log(z)-1.$
+\end{proposition}
+Proofs of Lemma~\ref{lemma_bounds_on_marginals} and Proposition~\ref{proposition_error_in_marginals} are presented in supplementary material. 
+Proving Proposition~\ref{proposition_error_in_marginals} is based on a generalization of Pinsker inequality (see Lemma 1 in supplementary). 
+Note that $c_\kappa$ and $c_{\kappa^{-1}}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b) $tends to the full one $(n,m)$.
+Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, we can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
 \begin{align*}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7 n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\\
-&\qquad - \min_{i}\mu_i + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)\bigg)
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nm}K_{\min}^{3/2}} &+ \frac{m-m_b}{(nm)^{1/4}\sqrt{K_{\min}}}
+ + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
+\bigg)\bigg]\Bigg)
 \end{align*}
+% + \frac{m^{1/4}}{n^{3/4}m_bK_{\min}^{5/2}\underline{\nu}}
 and 
 \begin{align*}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7 m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2\\ 
-&\qquad - \min_{j}\nu_j + \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)\bigg).
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_{\kappa^{-1}} + (n- n_b) \bigg[\frac{m_b}{\sqrt{nm}K_{\min}^{3/2}} &+ \frac{m-m_b}{(nm)^{1/4}\sqrt{K_{\min}}}
+ + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
+\bigg)\bigg]\Bigg).
 \end{align*}
-\end{proposition}
-Proofs of Lemma~\ref{lemma_bounds_on_marginals} and Proposition~\ref{proposition_error_in_marginals} are presented in supplementary material. 
-Proof of Proposition~\ref{proposition_error_in_marginals} is based on a generalization of the Pinsker inequality~\cite{altschulernips17,khalilabid2018}.
 

### 2019-05-17 tex/v3/section_4_marginal_viols.tex
new

--- 2019-05-16 tex/v3/section_4_marginal_viols.tex
@@
 One has %\norm{\mu^{\text{sc}}}_1
+\begin{align}
+\label{maginal_mu}
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7 n_bc_\kappa \max_{i} \mu_i + 7 (n-n_b)\bigg[\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i \nonumber\\
+&\qquad \quad  + \max_{i} \mu_i\log\bigg(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\bigg)\bigg]
+\end{align}
+and 
+\begin{align}
+\label{maginal_nu}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7 m_bc_{\kappa^{-1}}\max_{j} \nu_j + 7(m-m_b)\bigg[\frac{n_b\kappa\max_{i}\mu_i}{m K_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\nonumber\\ 
+&\qquad  + \max_{j} \nu_j\log\bigg(\frac{(m-m_b+ 1)\max_{j} \nu_j}{n_b \kappa K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{m_b(\max_{j} \nu_j)^2}{nn_b\varepsilon^2\kappa^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\bigg)\bigg],
+\end{align}
+where $c_z = z-\log(z)-1.$
+\end{proposition}
+Proofs of Lemma~\ref{lemma_bounds_on_marginals} and Proposition~\ref{proposition_error_in_marginals} are presented in supplementary material and they are based on the first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def}.
+Furthermore, in proof of Proposition~\ref{proposition_error_in_marginals} we use a generalization of Pinsker inequality (see Lemma 1 in supplementary). 
+Note that $c_\kappa$ and $c_{\kappa^{-1}}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.
+Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, we can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ and $c_{\mu\nu} = \underline{\mu}\wedge \underline{\nu}$ with $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
 \begin{align*}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7 n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7 (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\\
-&\qquad - \min_{i}\mu_i + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)\bigg)
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}{K_{\min}}}
+ + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
+\bigg)\bigg]\Bigg)
 \end{align*}
-and 
-\begin{align*}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7 m_b(\kappa-\log(\kappa)-1)\max_{j} \nu_j + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{n K_{\min}} + (n- n_b) \varepsilon^2\\ 
-&\qquad - \min_{j}\nu_j + \max_{j} \nu_j\log\Big(\frac{\kappa(m-m_b+ 1)\max_{j} \nu_j}{n_b K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{\kappa^2\max_{j} \nu_j}{nn_b\varepsilon^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big)\bigg).
-\end{align*}
-\end{proposition}
-Proofs of Lemma~\ref{lemma_bounds_on_marginals} and Proposition~\ref{proposition_error_in_marginals} are presented in supplementary material. 
-Proof of Proposition~\ref{proposition_error_in_marginals} is based on a generalization of the Pinsker inequality~\cite{altschulernips17,khalilabid2018}.
+% + \frac{m^{1/4}}{n^{3/4}m_bK_{\min}^{5/2}\underline{\nu}}
+% and 
+% \begin{align*}
+% {\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_{\kappa^{-1}} + (n- n_b) \bigg[\frac{m_b}{\sqrt{nm}K_{\min}^{3/2}} &+ \frac{m-m_b}{(nm)^{1/4}\sqrt{K_{\min}}}
+%  + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
+% \bigg)\bigg]\Bigg).
+% \end{align*}
 

### 2019-05-17 tex/v3/section_4_marginal_viols.tex
new

@@
 Note that $c_\kappa$ and $c_{\kappa^{-1}}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.
-Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, we can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ and $c_{\mu\nu} = \underline{\mu}\wedge \underline{\nu}$ with $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
-\begin{align*}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}{K_{\min}}}
- + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
-\bigg)\bigg]\Bigg)
-\end{align*}
+%Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, 
+% We can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ and $c_{\mu\nu} = \underline{\mu}\wedge \underline{\nu}$ with $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
+% \begin{align*}
+% {\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}{K_{\min}}}
+%  + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
+% \bigg)\bigg]\Bigg)
+% \end{align*}
 % + \frac{m^{1/4}}{n^{3/4}m_bK_{\min}^{5/2}\underline{\nu}}

### 2019-05-17 screenkhorn.py
minibug

@@ -106,7 +106,7 @@ class Screenkhorn:
                 print("test error", len(self.I),self.N)
                 if self.uniform:
                     aK = a/K_sum_cols
-                aK_sort = np.sort(aK)[::-1]
+                    aK_sort = np.sort(aK)[::-1]
                 epsilon_u_square = aK_sort[self.N - 1:self.N+1].mean()
                 self.I = np.where(self.a >=  epsilon_u_square * K_sum_cols)[0].tolist()
             
@@ -114,7 +114,7 @@ class Screenkhorn:
                 print("test error", len(self.J),self.M)
                 if self.uniform:
                     bK = b/K_sum_rows
-                bK_sort = np.sort(bK)[::-1]
+                    bK_sort = np.sort(bK)[::-1]
                 epsilon_v_square = bK_sort[self.M - 1:self.M+1].mean()
                 self.J = np.where(self.b >=  epsilon_v_square* K_sum_rows)[0].tolist() 
                 

### 2019-05-17 tex/v3/section_3_algorithm.tex

@@
 \label{prop:bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}, and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$.
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def} and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$.
 Then,

### 2019-05-17 tex/v3/supplementary_material.tex

@@
 \begin{align}
-\label{i-th-marginal-mu} %=({B}({u}^{\text{sc}},{v}^{\text{sc}})\mathbf 1_m)_i
+\label{i-th-marginal-mu} 
 {\mu}^{\text{sc}}_i  &= 
@@
 \kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}.
+\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa},
 \end{cases}
 \end{align}
+and 
+\begin{align}
+\label{i-th-marginal-nu} 
+{\nu}^{\text{sc}}_j  &= 
+\begin{cases}
+e^{v^{\text{sc}}_j} \sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
+\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}
+\end{cases}
+=\begin{cases}
+\frac{\nu_j}{\kappa}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
+\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}.
+\end{cases}
+\end{align}
+
 Using inequality~\eqref{bound_on_v}, we obtain 
@@
 \end{align*}
-
+Again by left-hand-side of inequaltiy~\eqref{bound_on_v}, we arrive at 
+\begin{align*}
+\norm{\mu^{\text{sc}}}_1 %&= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
+%& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+& \overset{}{\geq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i }+ (m-m_b)\varepsilon^2K_{\min}\Big),
+\end{align*}
+which gives the claimed result.
 Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
@@
 \end{lemma}
-Straightforward, 
+By~\eqref{i-th-marginal-mu}, we have
 \begin{align*}
@@
 &= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-1)\mu_i - \mu_i\log(\kappa) + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
+&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big).
+% &\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
 \end{align*}
-Using~\eqref{bound_on_v}, we have in one hand 
+Now by~\eqref{bound_on_v}, we have in one hand 
 \begin{align*}
@@
 \frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&=\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\geq m_bK_{\min} \frac{m\varepsilon^2K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min} + m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
+&\geq m_bK_{\min} \frac{m\varepsilon^2K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min} + m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
 &\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
-&\geq \frac{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
+&\geq \frac{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
 &\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
-&\geq \frac{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
+&\geq \frac{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
 \end{align*}
@@
 \begin{align*}
-\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
-&\leq \frac{\kappa(n-n_b+ 1)}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
+\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
+&\leq \frac{\kappa(n-n_b+ 1)}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
 \end{align*}
@@
 &\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i}\mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
+&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i}\mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
 \bigg).
@@
 d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
+&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
 \end{align*}
@@
 \begin{align*}
-\norm{{\mu}^\star -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
+\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
 \end{align*}

### 2019-05-17 wda_expe.py
expe

@@ -42,7 +42,7 @@ def circle_data(n,nz = 0.2,nbnoise = 8):
 #%%
 def multi_gauss(n,nb_noise=8,s_noise=0.1):
     centers = [(1, 0), (-1, 0), (0.4, 0.8), (-0.4, -0.8),(-0.4, 0.8), (0.4, -0.8)]
-    x, y = make_blobs(n_samples=n, n_features=2, cluster_std= s_noise,
+    x, y = make_blobs(n_samples=n, n_features=200, cluster_std= s_noise,
                   centers=centers, shuffle=False)
     y[y==0] = 1
     y[y==3] = 2

### 2019-05-17 wda_screenkhorn.py

@@ -164,11 +164,13 @@ def wda_screenkhorn(X, y, p=2, reg=1, k=10, solver=None, maxiter=1000, verbose=1
                 p_m = kwargs.get('p_m', 2) # keep only 50% of points
                 n_budget = int(np.ceil(M.shape[0] / p_n))
                 m_budget = int(np.ceil(M.shape[1] / p_m))
-                tic=time()
+                #tic=time()
                 screenkhornWDA = Screenkhorn(wc[i], wc[j + i], M, reg, n_budget, m_budget, verbose=False)
+                #timing = time() - tic
+                #print('----',timing)
                 G = screenkhornWDA.lbfgsb()[2]
-                timing = time() - tic
-                print(timing)
+                #timing = time() - tic
+                #print(timing)
                 if j == 0:
                     loss_w += np.sum(G * M)
                 else:

### 2019-05-17 marg_expe.py
code expe marginals

@@ -1,0 +1,202 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu May 16 10:12:46 2019
+
+@author: GGilles
+"""
+
+# NUMPY
+import numpy as np
+from numpy.linalg import norm as norm
+import scipy.stats as stats
+
+np.random.seed(3946)
+
+# MATPLOTLIB
+import matplotlib.pyplot as plt
+plt.close('all')
+
+# WARNINGS
+import warnings
+warnings.filterwarnings("ignore", category=FutureWarning)
+
+# TIME
+from time import time 
+
+# POT
+from ot.datasets import make_data_classif
+from ot import dist, sinkhorn
+
+# SCREENKHORN
+from screenkhorn import Screenkhorn
+
+#%% Datasets
+def subsample(x,y,n, nb_class=10):
+    ind_rand = np.random.permutation(x.shape[0])
+    x = x[ind_rand]
+    y = y[ind_rand]
+    x_r = np.empty((0,x.shape[1]))
+    y_r = np.empty(0)
+    for i in range(nb_class):
+        ind = np.where(y==i)[0]
+        ind_sub = ind[0:n]
+        x_r = np.vstack((x_r,x[ind_sub]))
+        y_r = np.hstack((y_r,y[ind_sub]))
+    return x_r, y_r
+
+#%%
+def toy(n_samples_source,n_samples_target,nz=0.75,random_state=None):
+    Xs, ys = make_data_classif('3gauss', n_samples_source,nz=nz,random_state=random_state)
+    Xt, yt = make_data_classif('3gauss2', n_samples_target,nz=nz, random_state=random_state)
+    return Xs, ys, Xt, yt
+
+#%%
+def plot_mean_and_CI(pvect, mean, margin, color_mean=None, color_shading=None):
+    plt.fill_between(pvect, mean+margin, mean-margin, 
+                     color=color_shading, alpha=.15)
+    plt.semilogx(pvect, mean, color_mean, marker='s', markersize=8)
+    #plt.xlim(max(pvect), min(pvect))
+    #plt.xticks(pvect, pvect)
+
+#%%
+def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
+    n_pvect = len(pvect)
+    rel_time_vect = np.empty(n_pvect)
+    diff_a_vect   = np.empty(n_pvect)
+    diff_b_vect   = np.empty(n_pvect)
+    
[…]

### 2019-05-17 da_expe.py
expe

@@ -10,6 +10,8 @@ from time import process_time as time
 import ot
 import ot.plot
 import  da_screenkhorn
+import  da_sinkhorn
+
 from sklearn.neighbors import KNeighborsClassifier
 import numpy as np
 import argparse
@@ -50,8 +52,8 @@ else:
 n_samples_source = n
 n_samples_target = n
 
-nb_iter = 1
-reg_cl = 10
+nb_iter = 30
+reg_cl = 1
 K = 1 # K of KNN
 
 pathres='./resultat/'
@@ -89,7 +91,8 @@ for i in range(nb_iter):
     #%% 
     # Sinkhorn Transport
     tic = time()
-    ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
+    #ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
+    ot_sinkhorn = da_sinkhorn.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
     ot_sinkhorn.fit(Xs=Xs,ys= ys, Xt=Xt)
     time_sink[i] = time() - tic
     transp_Xs = ot_sinkhorn.transform(Xs=Xs)
@@ -119,7 +122,7 @@ for i in range(nb_iter):
     
 #%%
     
-    np.savez(pathres + filename, 
+    np.savez(pathres + filename, bc_none = bc_none,
              bc_sink= bc_sink,  bc_screen= bc_screen,
              time_sink = time_sink,  time_screen = time_screen)
     

### 2019-05-17 da_screenkhorn.py

@@ -10,6 +10,7 @@ Domain adaptation with optimal transport
 
 import numpy as np
 import scipy.linalg as linalg
+from time import process_time as time
 
 from ot.bregman import sinkhorn
 from ot.lp import emd
@@ -135,8 +136,12 @@ def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
         
         Mreg = M + eta * W
         # screenkhorn
+        #tic = time()
+
         screenkhorn.update(Mreg)
         transp = screenkhorn.lbfgsb()[2]
+        #toc = time() - tic
+        #print('screen',toc)
         # transp = sinkhorn(a, b, Mreg, reg, numItermax=numInnerItermax, stopThr=stopInnerThr)
         # the transport has been computed. Check if classes are really
         # separated

### 2019-05-17 da_expe.py
expe

@@ -91,8 +91,8 @@ for i in range(nb_iter):
     #%% 
     # Sinkhorn Transport
     tic = time()
-    #ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
-    ot_sinkhorn = da_sinkhorn.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
+    ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
+    #ot_sinkhorn = da_sinkhorn.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
     ot_sinkhorn.fit(Xs=Xs,ys= ys, Xt=Xt)
     time_sink[i] = time() - tic
     transp_Xs = ot_sinkhorn.transform(Xs=Xs)

### 2019-05-17 da_screenkhorn.py

@@ -1420,7 +1420,6 @@ class ScreenkhornLpl1Transport(BaseTransport):
 
             p_n = kwargs.get('p_n', 2)# keep only 50% of points
             p_m = kwargs.get('p_m', 2)# keep only 50% of points
-            print(self.cost_)
             returned_ = screenkhorn_lpl1_mm(
                 a=self.mu_s, labels_a=ys, b=self.mu_t, M=self.cost_,
                 reg=self.reg_e, eta=self.reg_cl, numItermax=self.max_iter,

### 2019-05-17 da_expe.py
expe

@@ -10,7 +10,6 @@ from time import process_time as time
 import ot
 import ot.plot
 import  da_screenkhorn
-import  da_sinkhorn
 
 from sklearn.neighbors import KNeighborsClassifier
 import numpy as np

### 2019-05-18 da_expe.py
expe

@@ -52,7 +52,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 30
-reg_cl = 1
+reg_cl = 10
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-18 tex/v3/section_5_numeric_expes.tex
new
expe

@@
+%!TEX root = main.tex
+
 \section{Numerical experiments} % (fold)
@@
 
+\subsection{Setup}
+the lbfgs is the one of scipy
+
+\subsection{Analysing on toy problem}
+
+\subsection{Integrating \emph{Screenkhorn} into machine learning pipelines}
+
+In this subsection, we analyse the impact of using \emph{Screenkhorn}
+instead of Sinkhorn in a complex machine learning pipeline. Our two applications
+are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
+through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
+on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
+
+WDA aims at finding a linear projection which minimize the ratio of distance between intra-class samples and distance inter-class samples, where the distance is understood
+in a Sinkhorn divergence sense. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
+largest component of the projected gradient is smaller than $10^{-9}$, when the
+number of iterations of number of objective function evaluations reach $10^{6}$.
+
+Figure \ref{fig:wda} presents the gain in computational time we get as the number
+of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
+
+\begin{figure*}[t]
+	\centering
+%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
+%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
+	\includegraphics[width=6.cm]{../../figure/wda_gain_toy.pdf}
+\includegraphics[width=6.cm]{../../figure/wda_gain_mnist.pdf}
+	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\label{fig:wda}
+\end{figure*}
+\begin{figure*}[t]
+	\centering
+	%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
+	%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_gain_toy.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_gain_mnist.pdf}
+	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\label{fig:otda}
+\end{figure*}
+
 % section numerical_experiments (end)

### 2019-05-18 screenkhorn.py

@@ -11,7 +11,7 @@ from time import time
 
 class Screenkhorn:
 
-    def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True):
+    def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True, restricted=True):
 
         tic_initial = time()
         # In wda_screen.py autograd package is used, we then have to change some arrays from "ArrayBox" type to "np.array".
@@ -31,6 +31,7 @@ class Screenkhorn:
         self.M = M
         self.verbose = verbose
         self.uniform = uniform
+        self.restricted = restricted
 
         # K
         self.K = np.empty_like(self.C)
@@ -189,8 +190,11 @@ class Screenkhorn:
 
         u0 = np.full(self.N, (1. / self.N) + self.epsilon / self.fact_scale)
         v0 = np.full(self.M, (1. / self.M) + self.epsilon * self.fact_scale)
-        
-        self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
+        if self.restricted:
+            self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
+        else:
+            self.u0=u0
+            self.v0=v0
 
         if self.verbose :
             print(time() - tic_initial)
@@ -332,7 +336,11 @@ class Screenkhorn:
         u0 = np.full(self.N, (1. / self.N) + self.epsilon / self.fact_scale)
         v0 = np.full(self.M, (1. / self.M) + self.epsilon * self.fact_scale)
         
-        self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
+        if self.restricted:
+            self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
+        else:
+            self.u0=u0
+            self.v0=v0
 
 
 
@@ -392,8 +400,8 @@ class Screenkhorn:
         
         # params of bfgs
         theta0 = np.hstack([self.u0, self.v0])
-        maxiter = 1000 # max number of iterations
-        maxfun = 1000 # max  number of function evaluations
+        maxiter = 1000000 # max number of iterations
+        maxfun = 1000000 # max  number of function evaluations
         pgtol = 1e-09 # final objective function accuracy
 
         obj = lambda theta: self._bfgspost(theta)

### 2019-05-18 tex/v3/section_5_numeric_expes.tex
expe

@@
 
+* compared restricted/non-restricted
+
 \subsection{Integrating \emph{Screenkhorn} into machine learning pipelines}
@@
 on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
-
-WDA aims at finding a linear projection which minimize the ratio of distance between intra-class samples and distance inter-class samples, where the distance is understood
-in a Sinkhorn divergence sense. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
+We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
 largest component of the projected gradient is smaller than $10^{-9}$, when the
@@
 
-Figure \ref{fig:wda} presents the gain in computational time we get as the number
-of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
+WDA aims at finding a linear projection which minimize the ratio of distance between intra-class samples and distance inter-class samples, where the distance is understood
+in a Sinkhorn divergence sense. We have used a toy problem involving Gaussian classes with $2$ discriminative features and $8$ noisy features and the MNIST dataset. For the
+former problem, we aim at find the best two-dimensional linear subspace in a WDA sense whereas for MNIST, we look for a subspace of dimension $20$ starting from the original
+$728$ dimensions.  Quality of the retrieved subspace are evaluated using classification task
+based on a $1$-nearest neighbour approach.
+
+Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
+Analysis of the quality of the subspace have been deported to the supplementary material, but we can remark a small loss of performance of Screenkhorn for the toy problem, while
+for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
+that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
+whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.
 
@@
 	\centering
-	%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
-	%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_gain_toy.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_gain_mnist.pdf}
+
+	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
 	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
@@
 
+For the optimal transport based domain adaptation problem, we have considered the
+OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
+for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/Screenkhorn has to be computed. As a domain-adaptation problem, we have
+used a MNIST to USPS problem in which features have been extracted from the
+feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full
+convergence of the networks (so as to leave room for OT adaptation).
+
 % section numerical_experiments (end)

### 2019-05-18 tex/v3/appendix.tex
new

--- 2019-05-17 tex/v3/supplementary_material.tex
@@
- \documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-\usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-% \usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[]{neurips_2019}
-
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{neurips_2019}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\usepackage{xr}
-\externaldocument{main}
-
-\RequirePackage{mathrsfs, amsthm, amsmath, amsfonts, amssymb, mathtools}%
-\usepackage[titletoc,title]{appendix}%
-\usepackage{dsfont}%
-\usepackage{caption} % 
-\usepackage{subcaption}
-\usepackage{float}%
-\usepackage{graphicx, color}% 
-\usepackage{bm}%bold equations
-
-%% formatting appendices
-\usepackage{etoolbox}
-\patchcmd{\appendices}{\quad}{. }{}{}
-
-%% tables
-\usepackage{pgfplots}%
-\usepackage{booktabs,multirow,array,multicol}
-\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
-
-%% algorithms
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-
-\usepackage{accents}
-\usepackage{datenumber}
-\usepackage{wrapfig}
-
-%% sections
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Fact}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}%[section]
-\newtheorem*{notation}{Notation}%[section]
-\newtheorem{discus}{Discussion}%[section]
-\newtheorem{remark}{Remark}%[section]
-\newtheorem{example}{Example}%[section]
-\newtheorem{exs}{Examples}%[section]
-\newtheorem{ca}{Cas}
-\newtheorem{remarks}{Remarks}%[section]
-\newtheorem{assumption}{Assumption}{\bf}{\rm}%
-
-% math macros
-\newcommand{\bigO}{\mathcal{O}}
-\newcommand{\inr}[1]{\langle #1 \rangle}
-\newcommand{\ind}[1]{{\mathds{1}}_{{#1}}}%
-\newcommand{\norm}[1]{\|#1\|}
-\newcommand{\R}{{\mathbb{R}}}
-\newcommand{\E}{\mathds{E}}
-\newcommand{\bcdot}{\raisebox{-0.80ex}{\scalebox{1.8}{$\cdot$}}}
-\newcommand{\varsig}{\raisebox{-0.15ex}{\scalebox{1.30}{$\varsigma$}}}
-\newcommand*{\dt}[1]{\accentset{\mbox{\large\bfseries .}}{#1}}
-
-%% math operators
-\DeclareMathOperator*{\argmin}{\arg\!\min}
-\DeclareMathOperator*{\argmax}{\arg\!\max}
-%--------------------------------------------------------------------------------------------------------------------------------%
-
-\title{Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''}
-
-\begin{document}
-
-\author{%
-Mokhtar Z. Alaya \\
-LITIS EA4108\\
-University of Rouen\\
-\texttt{mokhtarzahdi.alaya@gmail.com} 
-\And
-Maxime Bérar\\
-LITIS EA4108\\
-University of Rouen\\
-\texttt{maxime.berar@univ-rouen.fr} \\
-\And
-Gilles Gasso \\
-LITIS EA4108\\
-INSA, University of Rouen\\
-\texttt{gilles.gasso@insa-rouen.fr} 
-\And
-Alain Rakotomamonjy\\
-LITIS EA4108 \\
-University of Rouen\\
-and Criteo AI Labs, Criteo Paris \\
-\texttt{alain.rakoto@insa-rouen.fr} \\
-}
-\maketitle
-
-\section{Proof of Lemma~\ref{lemma_actives_sets}}
+\subsection{Proof of Lemma~\ref{lemma_actives_sets}}
 
@@
 
-\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
+\subsection{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
 
@@
 
-\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
+\subsection{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
 
@@
 
-\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
+\subsection{Proof of Proposition~\ref{proposition_error_in_marginals}}
 
@@
 Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
-
-\small
-\bibliography{biblio}
-\bibliographystyle{plain}
-
-\end{document}

### 2019-05-18 da_expe.py
expe

@@ -52,7 +52,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 30
-reg_cl = 10
+reg_cl = 1
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-18 da_expe.py
expe

@@ -36,7 +36,7 @@ def subsample(x,y,n, nb_class=10):
 parser = argparse.ArgumentParser()
 parser.add_argument('-n', action='store', dest='n', default = 2000, type=int,
                         help='number of samples ')
-parser.add_argument('-d', action='store', dest='d', default = 2, type=int,
+parser.add_argument('-d', action='store', dest='d', default = 1, type=int,
                         help='dataset type ')
 arguments = parser.parse_args()
 n = arguments.n # number of samples per class
@@ -52,7 +52,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 30
-reg_cl = 1
+reg_cl = 10
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-18 screenkhorn.py

@@ -400,9 +400,9 @@ class Screenkhorn:
         
         # params of bfgs
         theta0 = np.hstack([self.u0, self.v0])
-        maxiter = 1000000 # max number of iterations
-        maxfun = 1000000 # max  number of function evaluations
-        pgtol = 1e-09 # final objective function accuracy
+        maxiter = 10000 # max number of iterations
+        maxfun = 10000 # max  number of function evaluations
+        pgtol = 1e-06 # final objective function accuracy
 
         obj = lambda theta: self._bfgspost(theta)
         bounds = self.bounds_u + self.bounds_v

### 2019-05-18 da_expe.py
expe

@@ -51,7 +51,7 @@ else:
 n_samples_source = n
 n_samples_target = n
 
-nb_iter = 30
+nb_iter = 50
 reg_cl = 10
 K = 1 # K of KNN
 

### 2019-05-18 da_expe.py
expe

@@ -51,7 +51,7 @@ else:
 n_samples_source = n
 n_samples_target = n
 
-nb_iter = 50
+nb_iter = 30
 reg_cl = 10
 K = 1 # K of KNN
 

### 2019-05-18 da_expe.py
expe

@@ -120,7 +120,8 @@ for i in range(nb_iter):
         bc_screen[i,j] = np.mean(y_pred==yt)
     
 #%%
-    
+    print(time_sink[i])
+    print(time_screen[i])
     np.savez(pathres + filename, bc_none = bc_none,
              bc_sink= bc_sink,  bc_screen= bc_screen,
              time_sink = time_sink,  time_screen = time_screen)

### 2019-05-18 da_expe.py
expe

@@ -34,7 +34,7 @@ def subsample(x,y,n, nb_class=10):
     return x_r, y_r
 
 parser = argparse.ArgumentParser()
-parser.add_argument('-n', action='store', dest='n', default = 2000, type=int,
+parser.add_argument('-n', action='store', dest='n', default = 200, type=int,
                         help='number of samples ')
 parser.add_argument('-d', action='store', dest='d', default = 1, type=int,
                         help='dataset type ')

### 2019-05-18 da_expe.py
expe

@@ -51,8 +51,8 @@ else:
 n_samples_source = n
 n_samples_target = n
 
-nb_iter = 30
-reg_cl = 10
+nb_iter = 50
+reg_cl = 1
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-18 da_expe.py
expe

@@ -52,7 +52,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 50
-reg_cl = 1
+reg_cl = 10
 K = 1 # K of KNN
 
 pathres='./resultat/'
@@ -72,7 +72,7 @@ for i in range(nb_iter):
     np.random.seed(i)
 
     if data =='toy':
-        Xs,ys,Xt,yt = toy(n_samples_source,n_samples_target,nz=1,random_state=i)
+        Xs,ys,Xt,yt = toy(n_samples_source,n_samples_target,nz=0.75,random_state=i)
     else:
         data = np.load('mnist_usps_feat10.npz')
         Xs,ys = subsample(data['X_s'], data['y_s'],n//10)

### 2019-05-18 da_expe.py
expe

@@ -52,7 +52,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 50
-reg_cl = 10
+reg_cl = 1
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-19 tex/v3/appendix.tex
expe

@@
 Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
+
+\subsection{Additional experimental results}
+
+\begin{figure*}[t]
+	\centering
+
+	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
+	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\label{fig:otda}
+\end{figure*}

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
new
expe

@@
 We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
-largest component of the projected gradient is smaller than $10^{-9}$, when the
-number of iterations of number of objective function evaluations reach $10^{6}$.
+largest component of the projected gradient is smaller than $10^{-6}$, when the
+number of iterations of number of objective function evaluations reach $10^{5}$. For all
+applications, we have set $\eta=1$.
 
@@
 
-	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
 	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
+	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl10.pdf}
 	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.

### 2019-05-19 da_expe.py

@@ -15,9 +15,10 @@ from sklearn.neighbors import KNeighborsClassifier
 import numpy as np
 import argparse
 
-def toy(n_samples_source,n_samples_target,nz=0.75,random_state=None):
+def toy(n_samples_source,n_samples_target,nz=0.75,translate = 3, random_state=None):
     Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=nz,random_state=random_state)
     Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=nz, random_state=random_state)
+    Xt = Xt + translate
     return Xs, ys, Xt, yt
 
 def subsample(x,y,n, nb_class=10):

### 2019-05-19 da_expe.py
expe

@@ -53,7 +53,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 50
-reg_cl = 1
+reg_cl = 10
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-19 tex/v3/appendix.tex
expe

@@
 	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
-	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\caption{OT Domain Adaptation on a toy problem : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
 	\label{fig:otda}
 \end{figure*}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
+	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$.
+Note that this
+	value impact of the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
+	also report the performance of a $1$-NN when no-adaptation is performed.  
+	We remark that the strenght of the class-based has influence on the performance of \emph{Screenkhorn} given a decimation factor.
+For small value on the left, Screenkhorn slightly performs better than Sinkhorn, while for large value, some
+	decimation factors leads to loss of performances.
+	Regarding, running time, we can note that Sinkhorn is far less efficient than
+	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
+	\label{fig:otda:mnist:extra}}
+\end{figure*}

### 2019-05-19 da_expe.py

@@ -10,15 +10,33 @@ from time import process_time as time
 import ot
 import ot.plot
 import  da_screenkhorn
+from sklearn.datasets import make_blobs
 
 from sklearn.neighbors import KNeighborsClassifier
 import numpy as np
 import argparse
 
-def toy(n_samples_source,n_samples_target,nz=0.75,translate = 3, random_state=None):
-    Xs, ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=nz,random_state=random_state)
+def toy(n_samples_source,n_samples_target,nz=0.8,translate = 0.2, random_state=None):
+    Xs , ys = ot.datasets.make_data_classif('3gauss', n_samples_source,nz=nz,random_state=random_state)
     Xt, yt = ot.datasets.make_data_classif('3gauss2', n_samples_target,nz=nz, random_state=random_state)
     Xt = Xt + translate
+    
+#    n_features = 50
+#    s_noise = nz
+#    centers = np.array([(1, 0), (-1, 0), (0.4, 0.8)])
+#    Xs, ys = make_blobs(n_samples=n_samples_source, n_features= n_features, cluster_std= s_noise,
+#                  centers=centers, shuffle=False)
+#    ys[ys==2] = 3
+#    ys[ys==1] = 2
+#    ys[ys==0] = 1
+#    
+#    centers = centers + translate
+#    Xt, yt = make_blobs(n_samples=n_samples_target, n_features= n_features, cluster_std= s_noise,
+#                  centers=centers, shuffle=False)
+#    yt[yt==2] = 3
+#    yt[yt==1] = 2
+#    yt[yt==0] = 1
+    
     return Xs, ys, Xt, yt
 
 def subsample(x,y,n, nb_class=10):
@@ -35,7 +53,7 @@ def subsample(x,y,n, nb_class=10):
     return x_r, y_r
 
 parser = argparse.ArgumentParser()
-parser.add_argument('-n', action='store', dest='n', default = 200, type=int,
+parser.add_argument('-n', action='store', dest='n', default = 1000, type=int,
                         help='number of samples ')
 parser.add_argument('-d', action='store', dest='d', default = 1, type=int,
                         help='dataset type ')
@@ -52,14 +70,14 @@ else:
[…]

### 2019-05-19 da_expe.py
expe

@@ -71,7 +71,7 @@ n_samples_source = n
 n_samples_target = n
 
 nb_iter = 10
-reg_cl = 2   # toy, 2 and 0
+reg_cl = 10   # toy, 2 and 0
 K = 1 # K of KNN
 
 pathres='./resultat/'

### 2019-05-19 tex/v3/appendix.tex
new figure

@@
 	\centering
+	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{../../figure/wda_accur_toy.pdf}~\hfill~
+	\includegraphics[width=6.cm]{../../figure/wda_accur_mnist.pdf}~\hfill~\\
+	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
+		(right) MNIST). We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance. 
+		\label{fig:wda_gain}}
+\end{figure*}
 
-	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
-	\caption{OT Domain Adaptation on a toy problem : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
-	\label{fig:otda}
+\begin{figure*}[t]
+	\centering
+	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~
+	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl100.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{../../figure/da_time_toy_regcl100.pdf}
+	~\hfill~\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl100.pdf}~\hfill~\\
+	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem.
+(top-left) Examples of source and target samples.
+(top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples.
+(bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
+	factors.
+(bottom-right).
+Gain in computation time.
+This toy problem is a problem in which classes are overlapping and distance between samples are rather limited.
+According to our analysis, this may be a situation in which \emph{Screenkhorn} may
+	result in smaller computational gain. We can remark that with respect to the accuracy
+	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance.
+Regarding computational time, for this example, small decimation factors does not  result in gain.
+However for above  $5$-factor decimation, the gain goes from  $2$ to $10$ depending on
+	the number of samples. 
+	\label{fig:otda}}
 \end{figure*}

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
new figure

@@
 former problem, we aim at find the best two-dimensional linear subspace in a WDA sense whereas for MNIST, we look for a subspace of dimension $20$ starting from the original
-$728$ dimensions.  Quality of the retrieved subspace are evaluated using classification task
-based on a $1$-nearest neighbour approach.
+$728$ dimensions.  Quality of the retrieved subspace are evaluated using classification task based on a $1$-nearest neighbour approach.
 
 Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
-Analysis of the quality of the subspace have been deported to the supplementary material, but we can remark a small loss of performance of Screenkhorn for the toy problem, while
+Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of Screenkhorn for the toy problem, while
 for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
@@
 used a MNIST to USPS problem in which features have been extracted from the
-feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full
-convergence of the networks (so as to leave room for OT adaptation).
+feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
+Figure \ref{fig:otda} reports the gain in running time for $2$ fifferent values
+of the group-lasso regularizer hyperparameter, while the curves of performances are
+reported in the supplementary material.
+We can note that for all the  \emph{Screenkhorn} with different decimation factors, the gain in computation goes from a factor of $4$ to $12$, while accuracies are somewhat equivalent.
 

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
new figure

@@
 
+In this section, we present some numerical analyses of our
+\emph{Screenkhorn} algorithm and show how it behaves when
+integrated into some complex machine learning pipelines.
+
 \subsection{Setup}
-the lbfgs is the one of scipy
+
+We have implemented our Screenkhorn in Python and used the LBFGS of
+Scipy. Regarding the machine-learning based comparison, we have based our code
+on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
+We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
+largest component of the projected gradient is smaller than $10^{-6}$, when the number of iterations of number of objective function evaluations reach $10^{5}$.
+For all applications, we have set $\eta=1$.
 
@@
 are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
-through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
-on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
-We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
-largest component of the projected gradient is smaller than $10^{-6}$, when the
-number of iterations of number of objective function evaluations reach $10^{5}$. For all
-applications, we have set $\eta=1$.
+through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA.
 

### 2019-05-19 screenkhorn.py

@@ -193,6 +193,7 @@ class Screenkhorn:
         if self.restricted:
             self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
         else:
+            print('no restricted')
             self.u0=u0
             self.v0=v0
 
@@ -339,6 +340,7 @@ class Screenkhorn:
         if self.restricted:
             self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
         else:
+            print('no_restricted')
             self.u0=u0
             self.v0=v0
 

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
mes commit

--- 2019-05-19 tex/v3/section_5_numeric_expes.tex
@@
 \subsection{Analysing on toy problem}
+We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{see \url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
+The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
+We consider an unsupervised domain adaptation using optimal transport with entropic regularization.
+Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and finally, whether the cost matrix $C$ is normalized or not.
 

### 2019-05-19 marg_expe.py

@@ -97,7 +97,7 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
 
 #%%
 pathres= './resultat/'
-nvect = [100, 500, 1000, 2500, 3000]
+nvect = [500, 1000, 2500, 3000]
 pvect = [0.99, 0.95, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 
          0.2, 0.1, 0.05, 0.01]
 regvect = [1e-1, 5e-1, 1, 10]

### 2019-05-19 marg_expe.py
mes commit

@@ -65,12 +65,14 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
     rel_time_vect = np.empty(n_pvect)
     diff_a_vect   = np.empty(n_pvect)
     diff_b_vect   = np.empty(n_pvect)
-    
+    rel_cost_vect   = np.empty(n_pvect)
+
     # sinkhorn 
     tic = time()
-    _ = sinkhorn(a, b, M, reg)
+    P_sink = sinkhorn(a, b, M, reg)
     time_sink = time() - tic
-    
+    Pstar = P_sink[0]    
+
     for j,p in enumerate(pvect):
         print('p:', p)
         # screenkhorn
@@ -82,6 +84,7 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
         lbfgsb = screenkhorn.lbfgsb()
         time_bfgs = time() - tic
         P_sc= lbfgsb[2]
+        rel_cost_vect = np.abs(np.sum(M*(P_sc - Pstar)))/np.sum(M*Pstar)
         
         # screenkhorn marginals
         a_sc = P_sc @ np.ones(b.shape)
@@ -91,7 +94,7 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
         rel_time_vect[j] = time_bfgs/time_sink
         diff_a_vect[j]   = norm(a - a_sc, ord=1)**2
         diff_b_vect[j]   = norm(b - b_sc, ord=1)**2
-    return diff_a_vect, diff_b_vect, rel_time_vect
+    return diff_a_vect, diff_b_vect, rel_time_vect,rel_cost_vect
 
 
 
@@ -113,7 +116,8 @@ for n in nvect:
     M_diff_a = np.empty((n_iter, len(regvect), len(pvect)))
     M_diff_b = np.empty((n_iter, len(regvect), len(pvect)))
     M_time   = np.empty((n_iter, len(regvect), len(pvect)))
-    
+    M_cost   = np.empty((n_iter, len(regvect), len(pvect)))
+
     for i in range(n_iter):
         np.random.seed(i)
         # gen data
@@ -134,14 +138,14 @@ for n in nvect:
         
         for j, reg in enumerate(regvect):
             print('reg:', reg)
-            d_av, d_bv, rel_timev = compare_marginals(a, b, M, reg, pvect)
[…]

### 2019-05-19 marg_expe.py
new figure

@@ -84,7 +84,6 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
         lbfgsb = screenkhorn.lbfgsb()
         time_bfgs = time() - tic
         P_sc= lbfgsb[2]
-        rel_cost_vect = np.abs(np.sum(M*(P_sc - Pstar)))/np.sum(M*Pstar)
         
         # screenkhorn marginals
         a_sc = P_sc @ np.ones(b.shape)
@@ -93,14 +92,16 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
         # comparisons
         rel_time_vect[j] = time_bfgs/time_sink
         diff_a_vect[j]   = norm(a - a_sc, ord=1)**2
-        diff_b_vect[j]   = norm(b - b_sc, ord=1)**2
+        diff_b_vect[j]   = norm(b - b_sc, ord=1)**2       
+        rel_cost_vect[j] = np.abs(np.sum(M*(P_sc - Pstar)))/np.sum(M*Pstar)
+
     return diff_a_vect, diff_b_vect, rel_time_vect,rel_cost_vect
 
 
 
 #%%
 pathres= './resultat/'
-nvect = [100, 500, 1000, 2500, 3000]
+nvect = [200,500, 1000, 2500, 3000]
 pvect = [0.99, 0.95, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 
          0.2, 0.1, 0.05, 0.01]
 regvect = [1e-1, 5e-1, 1, 10]
@@ -122,7 +123,7 @@ for n in nvect:
         np.random.seed(i)
         # gen data
         if datatype =='toy':
-            Xs,ys,Xt,yt = toy(n_samples_source=n, n_samples_target=n, nz=1, random_state=i)
+            Xs,ys,Xt,yt = toy(n_samples_source=n, n_samples_target=n, nz=0.8, random_state=i)
         else:
             data = np.load('./data/mnist_usps_feat10.npz')
             Xs,ys = subsample(data['X_s'], data['y_s'],n//10)
@@ -130,7 +131,7 @@ for n in nvect:
             
         # cost matrix
         M = dist(Xs, Xt)
-        M /= M.max()
+        #M /= M.max()
         
         # Marginals
         a = np.ones(n)/n
@@ -204,3 +205,16 @@ for n in nvect:
[…]

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
mes commit
expe

@@
 \subsection{Analysing on toy problem}
+
 We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{see \url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
@@
 Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and finally, whether the cost matrix $C$ is normalized or not.
-
-* compared restricted/non-restricted
 
@@
 feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
-Figure \ref{fig:otda} reports the gain in running time for $2$ fifferent values
+Figure \ref{fig:otda} reports the gain in running time for $2$ different values
 of the group-lasso regularizer hyperparameter, while the curves of performances are

### 2019-05-20 tex/v3/appendix.tex
expe

@@
 	\centering
-	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
-	~\hfill~\includegraphics[width=6.cm]{../../figure/wda_accur_toy.pdf}~\hfill~
-	\includegraphics[width=6.cm]{../../figure/wda_accur_mnist.pdf}~\hfill~\\
+	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/wda_accur_toy.pdf}~\hfill~
+	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
 	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
@@
 	\centering
-	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
-	~\hfill~\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~
-	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl100.pdf}~\hfill~\\
-	~\hfill~\includegraphics[width=6.cm]{../../figure/da_time_toy_regcl100.pdf}
-	~\hfill~\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl100.pdf}~\hfill~\\
+	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~
+	\includegraphics[width=6.cm]{./figs/da_accur_toy_regcl100.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_time_toy_regcl100.pdf}
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_gain_toy_regcl100.pdf}~\hfill~\\
 	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem.

### 2019-05-20 tex/v3/appendix.tex
new appendix

--- 2019-05-19 tex/v3/appendix.tex
@@
+%!TEX root = main.tex
 \subsection{Proof of Lemma~\ref{lemma_actives_sets}}
@@
 
+\subsection{Bounding dual objective values}
+
+For each vectors $u \in \mathcal{U}_{\text{sc}}$ and $v\in \mathcal{V}_{\text{sc}}$ we define its rearrgement 
+\begin{equation*}
+\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top = (u_{I_{\varepsilon,\kappa}}^\top, \log(\frac\varepsilon\kappa)\mathbf1_{n- n_b}^\top)^\top,
+\end{equation*}
+and 
+\begin{equation*}
+\dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top = (v_{J_{\varepsilon,\kappa}}^\top, \log(\varepsilon\kappa)\mathbf 1_{m- m_b}^\top)^\top.
+\end{equation*}
+
+\begin{proposition}
+Let $k\geq 1$ and $u^{sc}_k, v^{sc}_k$ be generated by Screenkhorn. Then, ones has 
+\begin{align*}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
+&\leq \norm{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
+\end{align*}
+
+\begin{align*}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
+&\leq \norm{\kappa {u}^{\text{sc}}_k - {u}^\star}_\infty \norm{\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)\mathbf 1_m - {\mu}}_1 + \norm{\kappa^{-1}{v}^{\text{sc}}_k - {v}^\star}_\infty \norm{\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{{u}^{\text{sc}}_k ,\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{{v}^{\text{sc}}_k ,\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
+\end{align*}
+
+\newpage
+\begin{align*}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
+&\leq \norm{\kappa {u}^{\text{sc}}_k - {u}^\star}_\infty \norm{\mu ^{\text{sc}}_k- {\mu}}_1 + \norm{\kappa^{-1}{v}^{\text{sc}}_k - {v}^\star}_\infty \norm{\nu^{\text{sc}}_k - {\nu}}_1\\
+&\qquad + (1- \kappa)\inr{{u}^{\text{sc}}_k ,\mu ^{\text{sc}}_k} + (1- \kappa^{-1})\inr{{v}^{\text{sc}}_k ,\nu ^{\text{sc}}_k}.
+\end{align*}
+
+\end{proposition}
+
+\newpage
+\begin{proof}
+
+Let $k\geq 0$ and $u^{sc}_k, v^{sc}_k$ be generated by Algorithm~\ref{screenkhorn} and $(u^\star, v^\star)$ be a solution of~\ref{sinkhorn-dual}. Then 
+\begin{align*}
+&\Psi_{\varepsilon, \kappa}(u^{sc}_k,v^{sc}_k) - \Psi(u^\star, v^\star)\\
+& = \mathbf1_{n_b}^\top B(u_{I_{\varepsilon,\kappa}}, v_{J_{\varepsilon,\kappa}}) \mathbf 1_{m_b} + \varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})} + \varepsilon \kappa^{-1} K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
+&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
+\end{align*}
+
+% \begin{proof}
+Let us define $\tilde{K}$ a rearrgement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
+\begin{equation*}
+\tilde{K} = 
+\begin{bmatrix}
+K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
+K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &K_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
+\end{bmatrix}.
+\end{equation*}
+For each vectors $u \in \mathcal{U}_{\text{sc}}$ and $v\in \mathcal{V}_{\text{sc}}$ we define its rearrgement 
+\begin{equation*}
+\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top = (u_{I_{\varepsilon,\kappa}}^\top, \log(\frac\varepsilon\kappa)\mathbf1_{n- n_b}^\top)^\top,
+\end{equation*}
+and 
+\begin{equation*}
+\dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top = (v_{J_{\varepsilon,\kappa}}^\top, \log(\varepsilon\kappa)\mathbf 1_{m- m_b}^\top)^\top.
+\end{equation*}
+We then have 
+\begin{equation*}
+\Psi_{\varepsilon, \kappa} (u,v) = \mathbf 1_n^\top \tilde{B}(\dt{u}, \dt{v}) \mathbf 1_m - \kappa \dt{\mu}^\top \dt{u} - \kappa^{-1} \dt{\nu}^\top \dt{v},
+\end{equation*}
+where
+\begin{equation*}
+  \tilde{B}(\dt{u}, \dt{v}) = \Delta(e^{\dt{u}})\tilde{K} \Delta(e^{\dt{v}}).
+\end{equation*}
+
+Let us fix $k\geq 1$ and consider the convex function
+\begin{equation*}
+	(\hat u, \hat v) \mapsto \inr{\mathbf 1_n, \tilde{B}(\dt{\hat u}^{\text{}} ,\dt{\hat v}^{\text{}})\mathbf 1_m} - \inr{\kappa\dt{\hat u}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa^{-1}\dt{\hat v}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
+\end{equation*}
+Gradient inequality of any convex function g at point $x_o$ reads as $g(x_o) \geq g(x) + \inr{\nabla g(x), x_o - x}, \text{ for all } x \in \textbf{dom}(g).$
+Applying the latter fact to the above function at point ($u^{\star}, v^{\star})$ we obtain
+\begin{align*}
+&\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}_k, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}_k, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}\\
+& - \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)\\
+& \leq \inr{\dt{u}^{\text{sc}}_k - \dt{u}^\star, (1-\kappa) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}}_k - \dt{v}^\star, (1-\kappa^{-1}) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
+\end{align*}
+Moreover,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
+&= \inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}_k, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}_k^{\text{sc}}, \tilde{B}(\dt{u}_k^{\text{sc}}, \dt{v}^{\text{sc}}_k)\mathbf 1_n^\top}\\
+& - \big( 
+\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+- \inr{\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)\\
+&+ \inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}.
+\end{align*}
+Hence,
+\begin{align*}
+&\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
+&\qquad + \big( \inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+- \inr{\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)\\
+& \qquad -\inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} -\inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}\\
+& \leq \inr{\dt{u}^{\text{sc}}_k - \dt{u}^\star, (1-\kappa) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}}_k - \dt{v}^\star, (1-\kappa^{-1}) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}\\
+&\qquad + \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)
+\end{align*}
+Then,
+\begin{align*}
+&\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
+&\leq \inr{\dt{u}^{\text{sc}}_k - \dt{u}^\star, (1-\kappa) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}}_k - \dt{v}^\star, (1-\kappa^{-1}) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}\\
+&\qquad + \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)
+\\
+&\qquad + \inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}\\
+&\qquad - \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+- \inr{\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top \mathbf 1_n} \big).
+\end{align*}
+So
+\begin{align*}
+&\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
+&\leq  \inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} +\inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
+\end{align*}
+Applying Holder's inequality entails
+\begin{align*}
+&\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
+&\leq \norm{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
+\end{align*}
+Next, we bound the right-hand side of this inequality.
+
+If $r \in I^\complement_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|(\dt{u}^{\text{sc}}_k)_{r} - \dt{u}^\star_r| &= \bigg| \log(\frac \varepsilon\kappa) - \log(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}})\bigg|\\
+&= \bigg|\log\Big(\frac{\frac \varepsilon\kappa}{\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}}\Big) \bigg|\\
+&= \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m \frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
+& \leq \bigg|\log\bigg(\max_{1\leq j \leq m} \frac{K_{rj}e^{v^\star_j}}{\frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
+& \leq \big|\max_{1\leq j \leq m} (v_j^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})\big|\\
+& \leq \norm{v^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
+& \leq \norm{v^\star - v^{\text{sc}}_k - \log(\frac{\mu_r}{m\varepsilon^2})}_\infty \\
+& \leq \norm{v^\star - v^{\text{sc}}_k}_\infty +  \log(m\varepsilon^2).
+\end{align*}
+
+If $r \in I_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|(\dt{u}^{\text{sc}}_k)_{r} - \dt{u}^\star_r| &= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j\in J_{\varepsilon,\kappa}}K_{rj}e^{(v^{\text{sc}}_k)_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{rj}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
+&= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
+&= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
+& \leq \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
+& \leq \norm{(v^{\text{sc}}_k) - v^\star - \log(\kappa)}_\infty\\
+& \leq \norm{(v^{\text{sc}}_k) - v^\star}_\infty (\kappa \leq 1)
+\end{align*}
+
+If $s \in J^\complement_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|(\dt{v}^{\text{sc}}_k)_{s} - \dt{v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
+&= \bigg|\log\Big(\frac{\varepsilon\kappa}{\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}}}\Big) \bigg|\\
+&= \bigg|\log\bigg(\frac{\sum_{j=1}^n K_{is}e^{u^\star_i}}{\sum_{i=1}^n \frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
+& \leq \bigg|\log\bigg(\max_{1\leq i \leq n} \frac{K_{is}e^{u^\star_i}}{\frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
+& \leq \big|\max_{1\leq i \leq n} (u_i^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})\big|\\
+& \leq \norm{u^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
+& \leq \norm{u^\star - u^{\text{sc}}_k - \log(\frac{\nu_s}{n\varepsilon^2})}_\infty \\
+& \leq \norm{u^\star - u^{\text{sc}}_k}_\infty +  \log(n\varepsilon^2).
+\end{align*}
+
+If $r \in I_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|(\dt{u}^{\text{sc}}_k)_{r} - \dt{u}^\star_r| &= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j\in J_{\varepsilon,\kappa}}K_{rj}e^{(v^{\text{sc}}_k)_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{rj}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
+&= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
+&= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
+& \leq \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
+& \leq \norm{(v^{\text{sc}}_k) - v^\star - \log(\kappa)}_\infty\\
+& \leq \norm{(v^{\text{sc}}_k) - v^\star}_\infty (\kappa \leq 1)
+\end{align*}
+
+\newpage
+\begin{align*} 
+\nabla_u \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) &= e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}} \odot K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}} + \varepsilon\kappa e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}} \odot K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})} \mathbf 1_{m_b} - \kappa \mu_{I_{\varepsilon,\kappa}}\\
+&= 
+\begin{bmatrix}
+e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}}\\
+e^{u^{\text{sc}}_{I^\complement_{\varepsilon,\kappa}}}
+\end{bmatrix}
+\tilde{K}^1_O
+\begin{bmatrix}
+e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}}\\
+e^{v^{\text{sc}}_{J^\complement_{\varepsilon,\kappa}}}
+\end{bmatrix}
+- \kappa \mu_{I_{\varepsilon,\kappa}},\\
+\end{align*}
+where 
+\begin{equation*}
+\tilde{K}^1_O = 
+\begin{bmatrix}
+K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
+\mathbf O_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &\mathbf O_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
+\end{bmatrix}.
+\end{equation*}
+and 
+\begin{align*} 
+\nabla_v \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) &= e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}} \odot K^\top_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}} + \frac\varepsilon\kappa e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}} \odot K^\top_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} \mathbf 1_{n_b} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}\\
+&= 
+\begin{bmatrix}
+e^{v^{\text{sc}}_{J_{\varepsilon, \kappa}}}\\
+e^{v^{\text{sc}}_{J^\complement_{\varepsilon, \kappa}}}
+\end{bmatrix}
+\tilde{K}^2_O
+\begin{bmatrix}
+e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}}\\
+e^{u^{\text{sc}}_{I^\complement_{\varepsilon,\kappa}}}
+\end{bmatrix}
+- \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}\\
+\end{align*}
+where 
+\begin{equation*}
+\tilde{K}^2_O = 
+\begin{bmatrix}
+K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &\mathbf O_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
+K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &\mathbf O_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
+\end{bmatrix}.
+\end{equation*}
+Therefore, we obtain 
+\begin{equation*}
+\nabla_u \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) = \tilde{B}^1_O(\dt{u}^{\text{sc}},\dt{v}^{\text{sc}}) \mathbf 1_m - \kappa \mu_{I_{\varepsilon,\kappa}} \text{ and } \nabla_v \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) = \tilde{B}^2_O(\dt{u}^{\text{sc}},\dt{v}^{\text{sc}})^\top \mathbf 1_n- \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}
+\end{equation*}
+
+Analogously, one can define 
+\begin{align*}
+\Psi(u^\star, v^\star) = \mathbf{1}_n \tilde{B}(\dt{u}^\star, \dt{v}^\star) \mathbf{1}_m - \dt{\mu}^\top \dt{u}^\star - \dt{\nu}^\top \dt{v}^\star
+\end{align*}
+Hence,
+\begin{align*} 
+ \Psi_{\varepsilon, \kappa} (u^{\text{}} ,v^{\text{}}) -\Psi(u^\star, v^\star)
+& = \inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\text{}} ,\dt{v}^{\text{}})\mathbf 1_m} - \inr{\mathbf{1}_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m} + \inr{\dt{u}^{\star} - \kappa \dt{u}^{\text{}}, \dt{\mu}} + \inr{\dt{v}^{\star} - \kappa^{-1}\dt{v}^{\text{}}, \dt{\nu}}.
+\end{align*}
+\end{proof}
+
 \subsection{Additional experimental results}
-
-\begin{figure*}[t]
-	\centering
-
-	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
-	\caption{OT Domain Adaptation on a toy problem : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
-	\label{fig:otda}
-\end{figure*}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
-	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
-	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
-	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
-	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$.
-Note that this
-	value impact of the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
-	also report the performance of a $1$-NN when no-adaptation is performed.  
-	We remark that the strenght of the class-based has influence on the performance of \emph{Screenkhorn} given a decimation factor.
-For small value on the left, Screenkhorn slightly performs better than Sinkhorn, while for large value, some
-	decimation factors leads to loss of performances.
-	Regarding, running time, we can note that Sinkhorn is far less efficient than
-	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
-	\label{fig:otda:mnist:extra}}
-\end{figure*}

### 2019-05-20 tex/v3/section_5_numeric_expes.tex
new appendix

--- 2019-05-19 tex/v3/section_5_numeric_expes.tex
@@
 \subsection{Analysing on toy problem}
-We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{see \url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
-The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
-We consider an unsupervised domain adaptation using optimal transport with entropic regularization.
-Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and finally, whether the cost matrix $C$ is normalized or not.
 
@@
 We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
-largest component of the projected gradient is smaller than $10^{-6}$, when the
-number of iterations of number of objective function evaluations reach $10^{5}$. For all
+largest component of the projected gradient is smaller than $10^{-9}$, when the
+number of iterations of number of objective function evaluations reach $10^{6}$. For all
 applications, we have set $\eta=1$.
@@
 %	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
-	\includegraphics[width=6.cm]{../../figure/wda_gain_toy.pdf}
-\includegraphics[width=6.cm]{../../figure/wda_gain_mnist.pdf}
+   \includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
+\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
 	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
@@
 
-	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
-	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl10.pdf}
+	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl1.pdf}
+	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl10.pdf}
 	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.

### 2019-05-20 tex/v3/main.tex
new

--- 2019-05-16 tex/v3/main.tex
@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage[]{neurips_2019}
+% \usepackage[]{neurips_2019}
 
@@
 
+\author{%
+Mokhtar Z. Alaya \\
+LITIS EA4108\\
+University of Rouen\\
+\texttt{mokhtarzahdi.alaya@gmail.com} 
+\And
+Maxime Bérar\\
+LITIS EA4108\\
+University of Rouen\\
+\texttt{maxime.berar@univ-rouen.fr} \\
+\And
+Gilles Gasso \\
+LITIS EA4108\\
+INSA, University of Rouen\\
+\texttt{gilles.gasso@insa-rouen.fr} 
+\And
+Alain Rakotomamonjy\\
+LITIS EA4108 \\
+University of Rouen\\
+and Criteo AI Labs, Criteo Paris \\
+\texttt{alain.rakoto@insa-rouen.fr} \\
+}
+
 \maketitle
@@
 We illustrate the efficiency of Screenkhorn on complex tasks such as dimensionality reduction or domain adaptation involving regularized optimal transport.
-
-%This paper deals with the problem of approximating optimal transport (OT) distance between two discrete measures.
-%Our proposed approach involves a convex projection of the \emph{dual of Sinkhorn divergence}, allowing to formulate two appropriate active indices sets for the potential variables.
-%These indices sets depend on two parameters acting like a threshold and a scaling factor and they are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-%This new analysis induces a screened version of the dual of Sinkhorn divergence and suggests the \emph{Screenkhorn} algorithm.
-%We illustrate the favorable performance of Screenkhorn in practice with numerical experiments on synthetic and real datasets.
 \end{abstract}
@@
 \input{section_5_numeric_expes}
+
+\section{Conclusion}
+The paper proposed a novel efficient approximation of the Sinkhorn divergence
+based on a screening strategy. Screening some of the Sinkhorn dual variables
+has been made possible by defining a novel constrained dual problem and by 
+carefully analyzing its optimality conditions. From the latter, we derived some
+sufficient conditions depending on the ground cost matrix, that some dual variables are smaller than a given threshold. Hence, we need just to solve a restricted
+dual Sinkhorn problem using an off-the-shelf LBFGS algorithm. We also provided
+some theoretical guarantees of the quality of the approximation with respect to
+the number of variables that has been screened. Numerical experiments show 
+the behaviour of our \emph{Screenkhorn} algorithm and computational time gain it can
+achieve when integrated in some complex machine learning pipelines.
 
@@
 
-%\input{supplementary_material}
+\newpage
+\section{Supplementary material}
+\input{appendix}
 

### 2019-05-20 tex/v3/section_5_numeric_expes.tex

--- 2019-05-19 tex/v3/section_5_numeric_expes.tex
@@
 	\centering
+
 %	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
 %	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
-	\includegraphics[width=6.cm]{../../figure/wda_gain_toy.pdf}
-\includegraphics[width=6.cm]{../../figure/wda_gain_mnist.pdf}
+   \includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
+
+%	\includegraphics[width=4.cm]{./figs/wda_accur_toy.pdf}
+%	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
+	\includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
+\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
 	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.

### 2019-05-20 tex/v3/section_1_introduction.tex
change intro

--- 2019-05-14 tex/v3/section_1_introduction.tex
@@
 
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\cite{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\citep{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\cite{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\cite{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\cite{bonnel2011,Rubner2000,solomon2015}, among other applications~\cite{klouri17,peyre2019COTnowpublisher}.
+Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\citep{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\citep{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\citep{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\citep{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\citep{bonnel2011,Rubner2000,solomon2015}, among other applications~\citep{klouri17,peyre2019COTnowpublisher}.
 In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
@@
 Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\cite{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
+For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\citep{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
 
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\cite{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
+A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\citep{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
 Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\cite{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
-Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\cite{sinkhorn1967,knight2008,kalantari2008}.
+Furthermore,~\citet{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
+Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.
 
 Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-The main idea is to improve the matrix-vector operations that are the true computational bottleneck of Sinkhorn’s algorithm. 
-A greedy version of Sinkhorn, called Greenkhorn algorithm, proposed in~\cite{altschulernips17} allowing to select columns and rows to be updated that most violate the constraints.                   
-Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\cite{altschuler2018Nystrom}. 
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\cite{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi Newton methods~\cite{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\cite{genevay2016stochOT,khalilabid2018}.
+The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
+\citet{altschulernips17} proposed a greedy version of Sinkhorn, called Greenkhorn algorithm, allowing to select columns and rows to be updated that most violate the constraints.                   
+Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\citep{altschuler2018Nystrom}. 
+Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\citep{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi Newton methods~\citep{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\citep{genevay2016stochOT,khalilabid2018}.
 
-Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures.
-The proposed approach is based on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
-These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
-We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
-Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical} that relies on an estimation of the inverse of the Hessian based on gradients differences.
-L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.
+\rev{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
+is strongly related to a screening strategy when solving a \emph{Lasso}
+problem in sparse supervised learning \citep{Ghaoui2010SafeFE}. Based on the fact
+that a  transport plan resulting from an OT problem is sparse or presents a large
+number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization.
+Within this global context, our contributions are the following :
+\begin{itemize}
+	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
+	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to
+	a ``screened'' version of the dual of Sinkhorn divergence. 
+	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
+	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \cite{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
+	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning
+	pipelines, we show that \emph{Screenkhorn} can lead to strong gain in efficiency
+	while not compromising on accuracy.
+\end{itemize}}
+%	
+%
+%These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
+%We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
+%Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
+%We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
+%Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences.
+%L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.}
 

### 2019-05-20 tex/v3/section_5_numeric_expes.tex
change intro
mes commit

--- 2019-05-19 tex/v3/section_5_numeric_expes.tex
@@
 
-We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{see \url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
+We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
 The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
 We consider an unsupervised domain adaptation using optimal transport with entropic regularization.
-Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and finally, whether the cost matrix $C$ is normalized or not.
+Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and, whether the cost matrix $C$ is normalized or not.
+We empirically measure  marginal violations $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ as well as running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$
+Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings.
+We choose to only report results for $n=m=1000$ as we get similar findings for other values of $n$ and $m$.
+
+\begin{figure*}[t]
+	\begin{center}
+		\includegraphics[width=14.cm]{../../figure/norm_M_marginals_toy_n1000} \\
+		\includegraphics[width=8.cm]{../../figure/norm_M_time_toy_n1000}
+	\end{center}
+	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix.
+(Top panel) marginal violations in relation with the budget of points and (Bottom panel) ratio of computation times $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$.
+The results are averaged over 10 runs.}
+		\label{fig:margin_expe}
+\end{figure*}
+
+\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$).
+The approximation quality diminishes for small $\eta$.
+As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge to zero when increasing the budget of points.
+Remarkably those quantities are all almost null whatever the budget for high $\eta$.
+According to computational gain, \emph{Screenkhorn} is, up to 2 times; faster than Sinkhorn at low budget $n_b/n$
 

### 2019-05-20 tex/v3/appendix.tex

@@
 \subsection{Additional experimental results}
+
+\subsection{Additional experimental results}
+
+\begin{figure*}[t]
+	\centering
+	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/wda_accur_toy.pdf}~\hfill~
+	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
+	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
+		(right) MNIST). We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance. 
+		\label{fig:wda_gain}}
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~
+	\includegraphics[width=6.cm]{./figs/da_accur_toy_regcl100.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_time_toy_regcl100.pdf}
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_gain_toy_regcl100.pdf}~\hfill~\\
+	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem.
+(top-left) Examples of source and target samples.
+(top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples.
+(bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
+	factors.
+(bottom-right).
+Gain in computation time.
+This toy problem is a problem in which classes are overlapping and distance between samples are rather limited.
+According to our analysis, this may be a situation in which \emph{Screenkhorn} may
+	result in smaller computational gain. We can remark that with respect to the accuracy
+	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance.
+Regarding computational time, for this example, small decimation factors does not  result in gain.
+However for above  $5$-factor decimation, the gain goes from  $2$ to $10$ depending on
+	the number of samples. 
+	\label{fig:otda}}
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
+	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$.
+Note that this
+	value impact of the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
+	also report the performance of a $1$-NN when no-adaptation is performed.  
+	We remark that the strenght of the class-based has influence on the performance of \emph{Screenkhorn} given a decimation factor.
+For small value on the left, Screenkhorn slightly performs better than Sinkhorn, while for large value, some
+	decimation factors leads to loss of performances.
+	Regarding, running time, we can note that Sinkhorn is far less efficient than
+	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
+	\label{fig:otda:mnist:extra}}
+\end{figure*}

### 2019-05-20 tex/v3/section_5_numeric_expes.tex

@@
 	\centering
-%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
-%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
-	\includegraphics[width=6.cm]{../../figure/wda_gain_toy.pdf}
-\includegraphics[width=6.cm]{../../figure/wda_gain_mnist.pdf}
+%	\includegraphics[width=4.cm]{./figs/wda_accur_toy.pdf}
+%	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
+	\includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
+\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
 	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.

### 2019-05-20 tex/v3/supplementary_material.tex

--- 2019-05-16 tex/v3/supplementary_material.tex
@@
 \maketitle
-
-\section{Proof of Lemma~\ref{lemma_actives_sets}}
-
-Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty.
-Introducing two dual variables $\lambda \in \R^n_{+}$ and $\beta \in \R^m_{+}$ for each constraint, the Lagrangian of problem~\eqref{screen-sinkhorn} reads as 
-\begin{equation*}
-  \mathscr{L}(u,v, \lambda, \beta) = \frac \varepsilon\kappa\inr{\lambda, \mathbf{1}_n} + \varepsilon\kappa\inr{\beta, \mathbf{1}_m} + \mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} -\inr{\lambda,e^{u}} - \inr{\beta,e^{v}}
-\end{equation*}
-First order conditions then yield that the Lagrangian multiplicators solutions $\lambda^{*}$ and $\beta^{*}$ satisfy 
-\begin{align*}
-  &\nabla_u\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{u^{*}} \odot(Ke^{v^{*}} - \lambda^{*}) - \kappa\mu = \mathbf 0_n,\\
-  & \text{ and } \nabla_v\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{v^{*}} \odot(K^\top e^{u^{*}} - \beta) - \frac \nu\kappa = \mathbf 0_m
-\end{align*}
-which leads to 
-\begin{align*}
-  &\lambda^{*} = K e^{v^{*}} - \kappa\mu \oslash e^{u^{*}} \text{ and }
-  \beta^{*} = K^\top e^{u^{*}} - \nu \oslash \kappa e^{v^{*}}
-\end{align*}
-
-For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \varepsilon\kappa^{-1}$.
+%
+%\section{Proof of Lemma~\ref{lemma_actives_sets}}
+%
+%Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty.
+%Introducing two dual variables $\lambda \in \R^n_{+}$ and $\beta \in \R^m_{+}$ for each constraint, the Lagrangian of problem~\eqref{screen-sinkhorn} reads as 
+%\begin{equation*}
+%  \mathscr{L}(u,v, \lambda, \beta) = \frac \varepsilon\kappa\inr{\lambda, \mathbf{1}_n} + \varepsilon\kappa\inr{\beta, \mathbf{1}_m} + \mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} -\inr{\lambda,e^{u}} - \inr{\beta,e^{v}}
+%\end{equation*}
+%First order conditions then yield that the Lagrangian multiplicators solutions $\lambda^{*}$ and $\beta^{*}$ satisfy 
+%\begin{align*}
+%  &\nabla_u\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{u^{*}} \odot(Ke^{v^{*}} - \lambda^{*}) - \kappa\mu = \mathbf 0_n,\\
+%  & \text{ and } \nabla_v\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{v^{*}} \odot(K^\top e^{u^{*}} - \beta) - \frac \nu\kappa = \mathbf 0_m
+%\end{align*}
+%which leads to 
+%\begin{align*}
+%  &\lambda^{*} = K e^{v^{*}} - \kappa\mu \oslash e^{u^{*}} \text{ and }
+%  \beta^{*} = K^\top e^{u^{*}} - \nu \oslash \kappa e^{v^{*}}
+%\end{align*}
+%
+%For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \varepsilon\kappa^{-1}$.
 Further, the condition on the dual variable $\lambda^{*}_i > 0$  ensures that $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and hence $i \in I^\complement_{\varepsilon,\kappa}$.
 We have that $\lambda^{*}_i > 0$ is equivalent to $e^{u^{*}_i}r_i(K) e^{v^{*}_j} >  \kappa{\mu_i}$ which  is satisfied when $\varepsilon^2r_i(K) >  \kappa{\mu_i}.$
-In a symmetric way we can prove the same statement for $e^{v^{*}_j}$.
-
-\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
-
-We prove only the first statement~\eqref{bound_on_u} and similarly we can prove the second one~\eqref{bound_on_v}.
-For all $i\in I_{\varepsilon,\kappa}$, we have $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ or $e^{u^{\text{sc}}_i} = \frac \varepsilon\kappa$.
+%In a symmetric way we can prove the same statement for $e^{v^{*}_j}$.
+%
+%\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
+%
+%We prove only the first statement~\eqref{bound_on_u} and similarly we can prove the second one~\eqref{bound_on_v}.
+%For all $i\in I_{\varepsilon,\kappa}$, we have $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ or $e^{u^{\text{sc}}_i} = \frac \varepsilon\kappa$.
 In one hand, if $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ then according to the optimality conditions $\lambda^{\text{sc}}_i = 0,$ which implies $e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i$.
-In another hand, we have 
-\begin{align*}
-e^{u^{\text{sc}}_i} \min_{i,j}K_{ij} \sum_{j=1}^m e^{v^{\text{sc}}_j} \leq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i.
-\end{align*}
-We further observe that $\sum_{j=1}^m e^{v^{\text{sc}}_j} = \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} \geq \varepsilon\kappa |J_{\varepsilon,\kappa}| + \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}|=\varepsilon\kappa m.$ Then
-\begin{equation*}
-\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
-\end{equation*}
-Analogously, one can obtain for all $j\in J_{\varepsilon,\kappa}$
-\begin{equation}
-\label{upper_bound_v_potential}
-\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
-\end{equation}
-
-Now, since $K_{ij} \leq 1$, we have 
-\begin{align*}
-e^{u^{\text{sc}}_i} \sum_{j=1}^m e^{v^{\text{sc}}_j} \geq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij}e^{v^{\text{sc}}_j} = \kappa\mu_i.
-\end{align*}
-Using~\eqref{upper_bound_v_potential}, we get 
-\begin{align*}
-\sum_{j=1}^m e^{v^{\text{sc}}_j} &= \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j}
-\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} |J_{\varepsilon,\kappa}|.
-\end{align*}
-Therefore,
-\begin{align*}
-\min_{i \in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\varepsilon,\kappa}}\mu_i}{\varepsilon\kappa (m-m_b) + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} m_b}.
-\end{align*}
-
-\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
-
-The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
-\begin{align}
-\label{i-th-marginal-mu} %=({B}({u}^{\text{sc}},{v}^{\text{sc}})\mathbf 1_m)_i
-{\mu}^{\text{sc}}_i  &= 
-\begin{cases}
-e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I_{\varepsilon,\kappa},\\
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}
-\end{cases}
-=\begin{cases}
-\kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}.
-\end{cases}
-\end{align}
-Using inequality~\eqref{bound_on_v}, we obtain 
-\begin{align*}
-\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
-& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
-\end{align*}
-
-Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
-
-\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
-
-We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
-While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
-The violations are computed through the following function: 
-\begin{equation*}
-	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
-\end{equation*}
-Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
+%In another hand, we have 
+%\begin{align*}
+%e^{u^{\text{sc}}_i} \min_{i,j}K_{ij} \sum_{j=1}^m e^{v^{\text{sc}}_j} \leq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i.
+%\end{align*}
+%We further observe that $\sum_{j=1}^m e^{v^{\text{sc}}_j} = \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} \geq \varepsilon\kappa |J_{\varepsilon,\kappa}| + \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}|=\varepsilon\kappa m.$ Then
+%\begin{equation*}
+%\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
+%\end{equation*}
+%Analogously, one can obtain for all $j\in J_{\varepsilon,\kappa}$
+%\begin{equation}
+%\label{upper_bound_v_potential}
+%\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
+%\end{equation}
+%
+%Now, since $K_{ij} \leq 1$, we have 
+%\begin{align*}
+%e^{u^{\text{sc}}_i} \sum_{j=1}^m e^{v^{\text{sc}}_j} \geq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij}e^{v^{\text{sc}}_j} = \kappa\mu_i.
+%\end{align*}
+%Using~\eqref{upper_bound_v_potential}, we get 
+%\begin{align*}
+%\sum_{j=1}^m e^{v^{\text{sc}}_j} &= \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j}
+%\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} |J_{\varepsilon,\kappa}|.
+%\end{align*}
+%Therefore,
+%\begin{align*}
+%\min_{i \in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\varepsilon,\kappa}}\mu_i}{\varepsilon\kappa (m-m_b) + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} m_b}.
+%\end{align*}
+%
+%\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
+%
+%
+%The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
+%\begin{align}
+%\label{i-th-marginal-mu} 
+%{\mu}^{\text{sc}}_i  &= 
+%\begin{cases}
+%e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I_{\varepsilon,\kappa},\\
+%\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}
+%\end{cases}
+%=\begin{cases}
+%\kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
+%\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa},
+%\end{cases}
+%\end{align}
+%and 
+%\begin{align}
+%\label{i-th-marginal-nu} 
+%{\nu}^{\text{sc}}_j  &= 
+%\begin{cases}
+%e^{v^{\text{sc}}_j} \sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
+%\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}
+%\end{cases}
+%=\begin{cases}
+%\frac{\nu_j}{\kappa}, \text{ if  }j \in J_{\varepsilon,\kappa},\\
+%\varepsilon\kappa\sum_{i=1}^n K_{ij} e^{u^{\text{sc}}_i}, \text{ if  }j \in J^\complement_{\varepsilon,\kappa}.
+%\end{cases}
+%\end{align}
+%
+%Using inequality~\eqref{bound_on_v}, we obtain 
+%\begin{align*}
+%\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
+%& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+%& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
+%\end{align*}
+%Again by left-hand-side of inequaltiy~\eqref{bound_on_v}, we arrive at 
+%\begin{align*}
+%\norm{\mu^{\text{sc}}}_1 %&= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
+%%& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+%& \overset{}{\geq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i }+ (m-m_b)\varepsilon^2K_{\min}\Big),
+%\end{align*}
+%which gives the claimed result.
+%Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
+%
+%\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
+%
+%We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
+%While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
+%The violations are computed through the following function: 
+%\begin{equation*}
+%	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
+%\end{equation*}
+%Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
 The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
-\begin{lemma}
-\label{lem:pinsker}
-For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
-\begin{align*}
-\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
-\end{align*}
-\end{lemma}
-Straightforward, 
-\begin{align*}
-d_\varrho({\mu} ,{\mu}^{\text{sc}}) &= \sum_{i=1}^n  {\mu}^{\text{sc}}_i - {\mu}_i + {\mu}_i  \log\Big(\frac{{\mu}_i}{{\mu}^{\text{sc}}_i }\Big)\\
-&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-1)\mu_i - \mu_i\log(\kappa) + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
-\end{align*}
-Using~\eqref{bound_on_v}, we have in one hand 
-\begin{align*}
-\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&= \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\leq \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(m_b \max_{i,j}K_{ij}\frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} + (m - m_b)\varepsilon\kappa\max_{i,j}K_{ij}\Big) \\
-&\leq (n-n_b)\Big(\frac{m_b\max_{j} \nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\Big).
-\end{align*}
-On the other hand, we get
-\begin{align*}
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&=\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\geq m_bK_{\min} \frac{m\varepsilon^2K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min} + m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
-&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
-&\geq \frac{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
-&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
-&\geq \frac{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
-\end{align*}
-Then 
-\begin{align*}
-\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
-&\leq \frac{\kappa(n-n_b+ 1)}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
-\end{align*}
-It entails 
-\begin{align*}
-&\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i}\mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
-\bigg).
-\end{align*}
-Therefore
-\begin{align*}
-d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
-\end{align*}
-Finally, by Lemma~\ref{lem:pinsker} we obtain
-\begin{align*}
-\norm{{\mu}^\star -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
-\end{align*}
-Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
-
+%\begin{lemma}
+%\label{lem:pinsker}
+%For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
+%\begin{align*}
+%\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
+%\end{align*}
+%\end{lemma}
+%By~\eqref{i-th-marginal-mu}, we have
+%\begin{align*}
+%d_\varrho({\mu} ,{\mu}^{\text{sc}}) &= \sum_{i=1}^n  {\mu}^{\text{sc}}_i - {\mu}_i + {\mu}_i  \log\Big(\frac{{\mu}_i}{{\mu}^{\text{sc}}_i }\Big)\\
+%&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-1)\mu_i - \mu_i\log(\kappa) + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
+%&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big).
+%% &\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
+%\end{align*}
+%Now by~\eqref{bound_on_v}, we have in one hand 
+%\begin{align*}
+%\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&= \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+%&\leq \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(m_b \max_{i,j}K_{ij}\frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} + (m - m_b)\varepsilon\kappa\max_{i,j}K_{ij}\Big) \\
+%&\leq (n-n_b)\Big(\frac{m_b\max_{j} \nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\Big).
+%\end{align*}
+%On the other hand, we get
+%\begin{align*}
+%\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&=\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+%&\geq m_bK_{\min} \frac{m\varepsilon^2K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min} + m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
+%&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
+%&\geq \frac{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
+%&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
+%&\geq \frac{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
+%\end{align*}
+%Then 
+%\begin{align*}
+%\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + n_b\kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
+%&\leq \frac{\kappa(n-n_b+ 1)}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
+%\end{align*}
+%It entails 
+%\begin{align*}
+%&\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
+%&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+%&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i}\mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
+%\bigg).
+%\end{align*}
+%Therefore
+%\begin{align*}
+%d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+%&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
+%\end{align*}
+%Finally, by Lemma~\ref{lem:pinsker} we obtain
+%\begin{align*}
+%\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+%&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
+%\end{align*}
+%Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
+\input{appendix.tex}
 \small

### 2019-05-20 screenkhorn.py
bug K_min

@@ -143,7 +143,8 @@ class Screenkhorn:
             self.K_IJc = self.K[np.ix_(self.I, self.Jc)]
             # K_min
             K_min = self.K_IJ.min()
-            
+            if K_min == 0:
+                K_min = np.finfo(float).tiny
             # a_I,b_J,a_Ic,b_Jc
             self.a_I = self.a[self.I]
             self.b_J = self.b[self.J]
@@ -158,7 +159,7 @@ class Screenkhorn:
                 self.b_J_max = self.b_J [0]
                 self.b_J_min = self.b_J[0]
             
-          
+           
     
             # LBFGS box
             self.bounds_u = [(max(self.fact_scale * self.a_I_min / (self.epsilon * (m - self.M) \
@@ -287,6 +288,8 @@ class Screenkhorn:
         self.K_IJc = self.K[np.ix_(self.I, self.Jc)]
         
         K_min = self.K_IJ.min()
+        if K_min == 0:
+            K_min = np.finfo(float).tiny
         # a_I,b_J,a_Ic,b_Jc
         self.a_I = self.a[self.I]
         self.b_J = self.b[self.J]

### 2019-05-20 da_expe.py
new

@@ -55,7 +55,7 @@ def subsample(x,y,n, nb_class=10):
 parser = argparse.ArgumentParser()
 parser.add_argument('-n', action='store', dest='n', default = 1000, type=int,
                         help='number of samples ')
-parser.add_argument('-d', action='store', dest='d', default = 1, type=int,
+parser.add_argument('-d', action='store', dest='d', default = 2, type=int,
                         help='dataset type ')
 arguments = parser.parse_args()
 n = arguments.n # number of samples per class
@@ -126,7 +126,7 @@ for i in range(nb_iter):
         print(p_n)
         # Screenkhorn Transport
         tic = time()
-        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
+        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1,reg_cl=reg_cl,one_init=False)
         ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, p_n=p_n, p_m=p_n)
        
         time_screen[i,j] = time() - tic

### 2019-05-20 da_screenkhorn.py

@@ -119,11 +119,12 @@ def screenkhorn_lpl1_mm(a, labels_a, b, M, reg, eta=0.1, numItermax=10,
 
     p_n = kwargs.get('p_n', 1)
     p_m = kwargs.get('p_m', 1)
+    one_init =  kwargs.get('one_init', False)
 
     n_budget = int(np.ceil(M.shape[0] / p_n))
     m_budget = int(np.ceil(M.shape[1] / p_m))
     
-    screenkhorn = Screenkhorn(a, b, M, reg, N=n_budget, M=m_budget, verbose=False)
+    screenkhorn = Screenkhorn(a, b, M, reg, N=n_budget, M=m_budget, verbose=False,one_init=one_init)
     transp = screenkhorn.lbfgsb()[2]
     
     W = np.ones(M.shape)
@@ -1247,7 +1248,7 @@ class ScreenkhornTransport(BaseTransport):
 
     def __init__(self, reg_e=1., max_iter=1000,
                  tol=10e-9, verbose=False, log=False,
-                 metric="sqeuclidean", norm=None,
+                 metric="sqeuclidean", norm=None,one_init=False,
                  distribution_estimation=distribution_estimation_uniform,
                  out_of_sample_map='ferradans', limit_max=np.infty):
 
@@ -1261,7 +1262,7 @@ class ScreenkhornTransport(BaseTransport):
         self.limit_max = limit_max
         self.distribution_estimation = distribution_estimation
         self.out_of_sample_map = out_of_sample_map
-
+        self.one_init=one_init
     def fit(self, Xs=None, ys=None, Xt=None, yt=None, **kwargs):
         """Build a coupling matrix from source and target sets of samples
         (Xs, ys) and (Xt, yt)
@@ -1298,7 +1299,9 @@ class ScreenkhornTransport(BaseTransport):
         n_budget = int(np.ceil(self.cost_.shape[0] / p_n))
         m_budget = int(np.ceil(self.cost_.shape[1] / p_m))
 
-        screenkhorn = Screenkhorn(a=self.mu_s, b=self.mu_t, C=self.cost_, reg=self.reg_e,N=n_budget, M=m_budget,verbose = False)
+        screenkhorn = Screenkhorn(a=self.mu_s, b=self.mu_t, C=self.cost_, reg=self.reg_e,
+                                  N=n_budget, M=m_budget, one_init=self.one_init_init,
+                                  verbose = False)
         returned_ = screenkhorn.lbfgsb()[2]
 
         # returned_ = sinkhorn(
[…]

### 2019-05-20 screenkhorn.py

@@ -11,7 +11,7 @@ from time import time
 
 class Screenkhorn:
 
-    def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True, restricted=True):
+    def __init__(self, a, b, C, reg, N, M, verbose = True, uniform = True, restricted=True,one_init=False):
 
         tic_initial = time()
         # In wda_screen.py autograd package is used, we then have to change some arrays from "ArrayBox" type to "np.array".
@@ -32,6 +32,7 @@ class Screenkhorn:
         self.verbose = verbose
         self.uniform = uniform
         self.restricted = restricted
+        self.one_init = one_init
 
         # K
         self.K = np.empty_like(self.C)
@@ -189,8 +190,14 @@ class Screenkhorn:
             self.cst_u = self.fact_scale * self.epsilon * self.K_IJc.sum(axis=1)
             self.cst_v = self.epsilon * self.K_IcJ.sum(axis=0) / self.fact_scale
 
-        u0 = np.full(self.N, (1. / self.N) + self.epsilon / self.fact_scale)
-        v0 = np.full(self.M, (1. / self.M) + self.epsilon * self.fact_scale)
+        if not self.one_init:
+            u0 = np.full(self.N, (1. / self.N) + self.epsilon / self.fact_scale)
+            v0 = np.full(self.M, (1. / self.M) + self.epsilon * self.fact_scale)
+        else:
+            print('ONE INIT')
+            u0 = np.full(self.N,1.)
+            v0 = np.full(self.M,1.)
+        
         if self.restricted:
             self.u0, self.v0 = self.restricted_sinkhorn(u0, v0, max_iter=5)
         else:
@@ -337,8 +344,16 @@ class Screenkhorn:
             self.cst_v = self.epsilon * self.K_IcJ.sum(axis=0) / self.fact_scale
 
         
-        u0 = np.full(self.N, (1. / self.N) + self.epsilon / self.fact_scale)
-        v0 = np.full(self.M, (1. / self.M) + self.epsilon * self.fact_scale)
+        #u0 = np.full(self.N, (1. / self.N) + self.epsilon / self.fact_scale)
+        # v0 = np.full(self.M, (1. / self.M) + self.epsilon * self.fact_scale)
+        #u0 = np.full(self.N,1.)
+        #v0 = np.full(self.M,1.)
+        if not self.one_init:
[…]

### 2019-05-20 tex/v3/section_5_numeric_expes.tex
add figures

@@
 	\begin{center}
-		\includegraphics[width=14.cm]{../../figure/norm_M_marginals_toy_n1000} \\
-		\includegraphics[width=8.cm]{../../figure/norm_M_time_toy_n1000}
+		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
+		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
+		\includegraphics[width=4.55cm]{../../figure/norm_M_time_toy_n1000}
 	\end{center}
@@
 Remarkably those quantities are all almost null whatever the budget for high $\eta$.
-According to computational gain, \emph{Screenkhorn} is, up to 2 times; faster than Sinkhorn at low budget $n_b/n$
+According to computational gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$.
+The inverse situation occurs when $n_b/n$ gets close to 1.
+The computational benefit
 

### 2019-05-20 marg_expe_v2.py

@@ -17,11 +17,11 @@ np.random.seed(3946)
 import matplotlib.pyplot as plt
 from matplotlib import rc
 rc('font', **{'family': 'sans-serif', 'sans-serif': ['Computer Modern Roman']})
-params = {'axes.labelsize': 16, # 12
-          'font.size': 16, # 12
+params = {'axes.labelsize': 18, # 12
+          'font.size': 18, # 12
           'legend.fontsize': 18, # 12
-          'xtick.labelsize': 14, # 10
-          'ytick.labelsize': 14, # 10
+          'xtick.labelsize': 16, # 10
+          'ytick.labelsize': 16, # 10
           #'text.usetex': True,
           #'figure.figsize': (8, 6)
           }
@@ -119,7 +119,7 @@ regvect = [1e-1, 5e-1, 1, 10]
 #regvect = [1e-1, 1, 10]
 datatype = 'toy' # change to mnist to run on Mnist dataset
 n_iter = 10 # we repeat n_iter times 
-normalize = False
+normalize = True
 
 #%%
 for n in nvect:
@@ -183,7 +183,7 @@ for n in nvect:
     
     plt.figure(1, figsize=(9, 6))
     plt.figure(2, figsize=(9, 6))
-    plt.figure(1, figsize=(9, 6))
+    plt.figure(3, figsize=(9, 6))
     
     for j, reg in enumerate(regvect):       
         diff_a      = M_diff_a[:, j, :]
@@ -196,7 +196,7 @@ for n in nvect:
                      label='$\eta = ${:}'.format(reg))
         plt.fill_between(pvect, diff_a_mean+diff_a_std*coeff, 
                          diff_a_mean-diff_a_std*coeff, alpha=.15)
-        plt.yscale('log')
+        #plt.yscale('log')
         plt.xlabel(r'$n_b/n$')
         plt.ylabel(r'$\|\|\, \mu - \mu^{sc} \, \|\|_1$')
         plt.xticks(pvect, pvect, rotation='vertical')
@@ -214,7 +214,7 @@ for n in nvect:
         plt.fill_between(pvect, diff_b_mean+diff_b_std*coeff, 
                          diff_b_mean-diff_b_std*coeff, alpha=.15)
         
-        plt.yscale('log')
+        #plt.yscale('log')
         plt.xlabel(r'$m_b/m$')
         plt.ylabel(r'$\||\, \nu - \nu^{sc} \, \|\|_1$')
[…]

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
test

@@
 (Top panel) marginal violations in relation with the budget of points and (Bottom panel) ratio of computation times $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$.
-The results are averaged over 10 runs.}
+The results are averaged over 10 trials.}
 		\label{fig:margin_expe}
@@
 Remarkably those quantities are all almost null whatever the budget for high $\eta$.
-According to computational gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$.
-The inverse situation occurs when $n_b/n$ gets close to 1.
-The computational benefit
+According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to 1.
+Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
 

### 2019-05-21 marg_expe_v2.py

@@ -76,11 +76,13 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
     rel_time_vect = np.empty(n_pvect)
     diff_a_vect   = np.empty(n_pvect)
     diff_b_vect   = np.empty(n_pvect)
+    rel_cost_vect = np.empty(n_pvect)
     
     # sinkhorn 
     tic = time()
-    _ = sinkhorn(a, b, M, reg)
+    P_sink = sinkhorn(a, b, M, reg)
     time_sink = time() - tic
+    Pstar = P_sink[0]
     
     for j,p in enumerate(pvect):
         print('p:', p)
@@ -102,7 +104,9 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
         rel_time_vect[j] = time_bfgs/time_sink
         diff_a_vect[j]   = norm(a - a_sc, ord=1)
         diff_b_vect[j]   = norm(b - b_sc, ord=1)
-    return diff_a_vect, diff_b_vect, rel_time_vect
+        rel_cost_vect[j] = np.abs(np.sum(M*(P_sc - Pstar)))/np.sum(M*Pstar)
+        
+    return diff_a_vect, diff_b_vect, rel_time_vect, rel_cost_vect
 
 
 
@@ -133,9 +137,10 @@ for n in nvect:
     M_diff_a = np.empty((n_iter, len(regvect), len(pvect)))
     M_diff_b = np.empty((n_iter, len(regvect), len(pvect)))
     M_time   = np.empty((n_iter, len(regvect), len(pvect)))
+    M_cost   = np.empty((n_iter, len(regvect), len(pvect)))
     
     for i in range(n_iter):
-        np.random.seed(i)
+        #np.random.seed(i)
         # gen data
         if datatype =='toy':
             Xs,ys,Xt,yt = toy(n_samples_source=n, n_samples_target=n, nz=1, random_state=i)
@@ -155,14 +160,15 @@ for n in nvect:
         
         for j, reg in enumerate(regvect):
             print('reg:', reg)
-            d_av, d_bv, rel_timev = compare_marginals(a, b, M, reg, pvect)
+            d_av, d_bv, rel_timev, rel_costv = compare_marginals(a, b, M, reg, pvect)
             M_diff_a[i, j, :] = d_av
             M_diff_b[i, j, :] = d_bv
             M_time[i, j, :]   = rel_timev
[…]

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
add figures to the right place

@@
 	\begin{center}
-		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
-		\includegraphics[width=4.55cm]{../../figure/norm_M_Mu_marginals_toy_n1000} \hfill
-		\includegraphics[width=4.55cm]{../../figure/norm_M_time_toy_n1000}
+		\includegraphics[width=4.55cm]{.figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
+		\includegraphics[width=4.55cm]{.figs/norm_M_Mu_marginals_toy_n1000} ~\hfill \\
+		\includegraphics[width=4.55cm]{.figs/figure/norm_M_time_toy_n1000} ~\hfill~
+		\includegraphics[width=4.55cm]{.figs/figure/norm_M_div_toy_n1000}
 	\end{center}
@@
 The approximation quality diminishes for small $\eta$.
-As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge to zero when increasing the budget of points.
+As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge towards zero when increasing the budget of points.
 Remarkably those quantities are all almost null whatever the budget for high $\eta$.

### 2019-05-21 marg_expe_v2.py

@@ -203,7 +203,7 @@ for n in nvect:
                      label='$\eta = ${:}'.format(reg))
         plt.fill_between(pvect, diff_a_mean+diff_a_std*coeff, 
                          diff_a_mean-diff_a_std*coeff, alpha=.15)
-        #plt.yscale('log')
+        plt.yscale('log')
         plt.xlabel(r'$n_b/n$')
         plt.ylabel(r'$\|\|\, \mu - \mu^{sc} \, \|\|_1$')
         plt.xticks(pvect, pvect, rotation='vertical')
@@ -221,7 +221,7 @@ for n in nvect:
         plt.fill_between(pvect, diff_b_mean+diff_b_std*coeff, 
                          diff_b_mean-diff_b_std*coeff, alpha=.15)
         
-        #plt.yscale('log')
+        plt.yscale('log')
         plt.xlabel(r'$m_b/m$')
         plt.ylabel(r'$\||\, \nu - \nu^{sc} \, \|\|_1$')
         plt.title('$n=m=${:d}'.format(n))
@@ -252,12 +252,10 @@ for n in nvect:
                      label='$\eta = ${:}'.format(reg))
         plt.fill_between(pvect, rel_cost_mean+rel_cost_std*coeff, 
                          rel_cost_mean-rel_cost_std*coeff, alpha=.15)
+        plt.yscale('log')
         plt.xlabel(r'$n_b/n$')
         plt.ylabel('Divergence Ratio')
         plt.title('$n=m=${:d}'.format(n))
-        
-        filename_fig_time = 'divergence_{:}_n{:d}_reg{:d}.pdf'.format(datatype,n, int(10*reg))
-        plt.savefig(pathfig+filename_fig_time, bbox_inches='tight')
         
         
     plt.figure(1)
@@ -275,12 +273,12 @@ for n in nvect:
         filename_fig_mu = 'norm_M_Mu_marginals_{:}_n{:d}.pdf'.format(datatype, n)
         filename_fig_nu = 'norm_M_Nu_marginals_{:}_n{:d}.pdf'.format(datatype, n)
         filename_fig_time = 'norm_M_time_{:}_n{:d}.pdf'.format(datatype,n)
-        filename_fig_div = 'norm_divergence_{:}_n{:d}.pdf'.format(datatype,n)
+        filename_fig_div = 'norm_M_div_{:}_n{:d}.pdf'.format(datatype,n)
     else:
[…]

### 2019-05-21 tex/v3/section_1_introduction.tex
change intro
Ref with chicago style

@@
 
-\rev{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
+{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
 is strongly related to a screening strategy when solving a \emph{Lasso}
@@
 \begin{itemize}
+	  \setlength\itemsep{-0.1cm}
+
 	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.

### 2019-05-21 tex/v3/section_3_algorithm.tex
new appendix
Ref with chicago style

@@
 
-The key idea of our approach is motivated by the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, which is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
+The key idea of our approach is motivated by the so-called \emph{static screening test}~\citep{Ghaoui2010SafeFE} in supervised learning, which is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
 Then, these inactive features can be removed from the optimization problem to reduce its scale.
 Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
-Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
+Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
 In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
@@
 \label{lemma_actives_sets}
-Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
+Let $(u^{*}, v^{*})$ be an optimal solution of problem~\eqref{screen-sinkhorn}. 
 Define
@@
 \varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
-&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}}. %+ \Xi
+&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
 \end{align*}
-%with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
+with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.
 
@@
 \end{proposition}
-
 \LinesNotNumbered
@@
 \label{screenkhorn}
-% \textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\
 
@@
 
-% \nl   $K \gets \exp(-C/\eta);$\\
 \nl   $\xi \gets \mu \oslash r(K);$ \\
@@
 \nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\ 
-
-% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}
-
-% \nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
 \nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
@@
 \nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}
+\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
 
@@
 
-\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
+\nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
 \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
@@
 \nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
-
-% \textbf{step 4:} \textcolor{black}{Output}\\
-
 \nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
update sec4
Ref with chicago style

--- 2019-05-17 tex/v3/section_4_marginal_viols.tex
@@
 We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
-Lemma~\ref{lemma_bounds_on_marginals} expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$, while Proposition~\ref{proposition_error_in_marginals} gives an upper bound of marginal errors.
+Our first theoretical result, Proposition~\ref{proposition_error_in_marginals}, gives an upper bound of marginal errors of Screenkhorn algorithm with respect to $\ell_1$-norm.
 
-\begin{lemma}
-\label{lemma_bounds_on_marginals}
+\begin{proposition}
+\label{proposition_error_in_marginals}
 Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
 Then one has
-\begin{align*}
- \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1  + (n -n_b) &\bigg(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i } + (m-m_b)\varepsilon^2K_{\min}\bigg)\\
- & \leq \norm{\mu^{\text{sc}}}_1\\
- & \qquad \qquad \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \bigg(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \bigg)
-\end{align*}
-and 
-\begin{align*}
-\kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}^{\text{}}}_1 + (m -m_b) &\bigg(\frac{nn_b\varepsilon^2\kappa^2K_{\min}^2 \min_{i\in I_{\varepsilon, \kappa}} \mu_j}{ n(m-m_b)\varepsilon^2 \kappa K_{\min} + m_b\kappa \max_{j\in J_{\varepsilon,\kappa}}\nu_j } + (n-n_b)\varepsilon^2K_{\min}\bigg)\\
-&\leq \norm{\nu^{\text{sc}}}_1\\
- & \qquad \quad \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\bigg(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\bigg).
-\end{align*}
-\end{lemma}
-\begin{proposition}
-\label{proposition_error_in_marginals}
-One has %\norm{\mu^{\text{sc}}}_1
+
 \begin{align}
-\label{maginal_mu}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1}&\leq 7 n_bc_\kappa \max_{i} \mu_i + 7 (n-n_b)\bigg[\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i \nonumber\\
-&\qquad \quad  + \max_{i} \mu_i\log\bigg(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_b K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\bigg)\bigg]
+\label{marginal-error-mu}
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\bigg(n_bc_\kappa + (n- n_b) \bigg(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}K_{\min}}
+ + \log\bigg(\frac{\sqrt{nm}}{m_b(c_{\mu\nu}K_{\min})^{5/2}} 
+\bigg)\bigg)\bigg)
 \end{align}
@@
 \begin{align}
-\label{maginal_nu}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} &\leq 7 m_bc_{\kappa^{-1}}\max_{j} \nu_j + 7(m-m_b)\bigg[\frac{n_b\kappa\max_{i}\mu_i}{m K_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\nonumber\\ 
-&\qquad  + \max_{j} \nu_j\log\bigg(\frac{(m-m_b+ 1)\max_{j} \nu_j}{n_b \kappa K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{m_b(\max_{j} \nu_j)^2}{nn_b\varepsilon^2\kappa^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\bigg)\bigg],
+\label{marginal-error-nu}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} = \bigO\bigg(m_bc_{\frac1\kappa} + (m- m_b) \bigg(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{n-n_b}{\sqrt{nm}K_{\min}}
+ + \log\bigg(\frac{\sqrt{nm}}{n_b (c_{\mu\nu}K_{\min})^{5/2}}
+\bigg)\bigg)\bigg),
 \end{align}
-where $c_z = z-\log(z)-1.$
+where $c_z = z - \log z - 1$ for $z>0$ and $c_{\mu\nu} = \underline{\mu}\wedge \underline{\nu}$ with $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i$ and $\underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$.
+
 \end{proposition}
-Proofs of Lemma~\ref{lemma_bounds_on_marginals} and Proposition~\ref{proposition_error_in_marginals} are presented in supplementary material. 
-Proving Proposition~\ref{proposition_error_in_marginals} is based on a generalization of Pinsker inequality (see Lemma 1 in supplementary). 
-Note that $c_\kappa$ and $c_{\kappa^{-1}}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b) $tends to the full one $(n,m)$.
-Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, we can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
+Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma~\ref{lem:pinsker} in supplementary).
+Note that $c_\kappa$ and $c_{\frac 1\kappa}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.
+
+Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of Screenkhorn and the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+\begin{proposition}
+\label{prop:objective-error}
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def} and $(u^\star, v^\star)$ is the solution of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+Then we have
 \begin{align*}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nm}K_{\min}^{3/2}} &+ \frac{m-m_b}{(nm)^{1/4}\sqrt{K_{\min}}}
- + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
-\bigg)\bigg]\Bigg)
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+= \bigO\bigg(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1)  + \omega_{\kappa}\bigg).
 \end{align*}
-% + \frac{m^{1/4}}{n^{3/4}m_bK_{\min}^{5/2}\underline{\nu}}
-and 
-\begin{align*}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_{\kappa^{-1}} + (n- n_b) \bigg[\frac{m_b}{\sqrt{nm}K_{\min}^{3/2}} &+ \frac{m-m_b}{(nm)^{1/4}\sqrt{K_{\min}}}
- + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
-\bigg)\bigg]\Bigg).
-\end{align*}
-
+where $\omega_{\kappa} = o(1)$  as $\kappa$ tends to $1.$
+\end{proposition}
 % section analysis_of_marginal_violations (end)

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
Ref with chicago style

@@
 	\begin{center}
-		\includegraphics[width=4.55cm]{.figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{.figs/norm_M_Mu_marginals_toy_n1000} ~\hfill \\
-		\includegraphics[width=4.55cm]{.figs/figure/norm_M_time_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{.figs/figure/norm_M_div_toy_n1000}
+		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
+		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill \\
+		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~
+		\includegraphics[width=4.55cm]{./figs/norm_M_div_toy_n1000}
 	\end{center}

### 2019-05-21 tex/v3/section_1_introduction.tex
intro

@@
 	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
-	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \cite{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
+	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \citep{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
 	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 largest component of the projected gradient is smaller than $10^{-6}$, when the number of iterations of number of objective function evaluations reach $10^{5}$.
-For all applications, we have set $\eta=1$.
+For all applications, we have set $\eta=1$ unless otherwise specified.
 
@@
 Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and, whether the cost matrix $C$ is normalized or not.
-We empirically measure  marginal violations $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ as well as running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$
+We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $\| \inr{C, P^\star} - \inr{C, P^{sc}}\|$ between \emph{Screenkhorn} and Sinkhorn.
+
 Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings.
@@
 	\begin{center}
-		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill \\
-		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_div_toy_n1000}
+		~\hfill~\includegraphics[width=5.5cm]{./figs/norm_M_Mu_marginals_toy_n1000}~\hfill~
+		\includegraphics[width=5.5cm]{./figs/norm_M_Mu_marginals_toy_n1000}~\hfill~\\
+		~\hfill~\includegraphics[width=5.5cm]{./figs/norm_M_time_toy_n1000}
+		~\hfill~\includegraphics[width=5.5cm]{./figs/norm_M_div_toy_n1000}~\hfill~\\
 	\end{center}
 	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix.
-(Top panel) marginal violations in relation with the budget of points and (Bottom panel) ratio of computation times $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$.
+Top panel: marginal violations in relation with the budget of points.
+Bottom panel: (left) ratio of computation times    $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and, (right) relative divergence variation.
 The results are averaged over 10 trials.}
@@
 \end{figure*}
-
+%
 \emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$).
@@
 As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge towards zero when increasing the budget of points.
-Remarkably those quantities are all almost null whatever the budget for high $\eta$.
+Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.
 According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to 1.
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
+Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn.
 

### 2019-05-21 tex/v3/appendix.tex

--- 2019-05-20 tex/v3/appendix.tex
@@
+%!TEX root = main.tex
+
 \subsection{Proof of Lemma~\ref{lemma_actives_sets}}
@@
 
-\subsection{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
+\subsection{Proof of Proposition~\ref{proposition_error_in_marginals}}
 
-The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
+We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
+While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
+The violations are computed through the following function: 
+\begin{equation*}
+	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
+\end{equation*}
+Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
+The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
+\begin{lemma}
+\label{lem:pinsker}
+For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
+\begin{align*}
+\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}.
+\end{align*}
+\end{lemma}
+
+The optimality conditions for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
 \begin{align}
@@
 
-Using inequality~\eqref{bound_on_v}, we obtain 
-\begin{align*}
-\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
-& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
-\end{align*}
-Again by left-hand-side of inequaltiy~\eqref{bound_on_v}, we arrive at 
-\begin{align*}
-\norm{\mu^{\text{sc}}}_1 %&= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
-%& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{}{\geq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i }+ (m-m_b)\varepsilon^2K_{\min}\Big),
-\end{align*}
-which gives the claimed result.
-Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
-
-\subsection{Proof of Proposition~\ref{proposition_error_in_marginals}}
-
-We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
-While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
-The violations are computed through the following function: 
-\begin{equation*}
-	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
-\end{equation*}
-Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
-The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
-\begin{lemma}
-\label{lem:pinsker}
-For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
-\begin{align*}
-\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
-\end{align*}
-\end{lemma}
 By~\eqref{i-th-marginal-mu}, we have
@@
 &= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big).
-% &\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
 \end{align*}
@@
 &\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i}\mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
+&\qquad \leq (n-n_b)\bigg(\frac{m_b}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+&\qquad \qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i}\mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
 \bigg).
@@
 \begin{align*}
-d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b c_{\kappa}\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
 &\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
@@
 \begin{align*}
-\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
+\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_bc_{\kappa}\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
 \end{align*}
-Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
+Following the same lines as above, we also have
+\begin{align*}
+\norm{{\nu} -{\nu}^{\text{sc}}}^2_1 \leq & m_bc_{\frac 1\kappa}\max_{i} \mu_i + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{mK_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
+&+ \max_{j} \nu_j\log\Big(\frac{(m-m_b+ 1)\max_{j} \nu_j}{n_b\kappa K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{m_b(\max_{j} \nu_j)^2}{nn_b\varepsilon^2\kappa^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).%\bigg\}^{1/2}
+\end{align*}
+To get the closed forms~\eqref{marginal-error-mu} and~\eqref{marginal-error-nu}, we used the follwoing facts:
+\begin{remark}
+\label{rem:orders_of_epsilonappa}
+ We have 
+$\varepsilon = \bigO((mnK_{\min}^2)^{-1/4})$, $\kappa= \bigO(\sqrt{m/(nc_{\mu\nu}K_{\min})}),$ $\kappa^{-1} = \bigO(\sqrt{n/(mK_{\min}c_{\mu\nu}})$, $(\kappa/\varepsilon)^2 = \bigO( m^{3/2} / \sqrt{nK_{\min}}(c_{\mu\nu})^{3/2})$, and $(\varepsilon\kappa)^{-2} = \bigO(n^{3/2}/\sqrt{mK_{\min}}c^{3/2}_{\mu\nu}).$
+\end{remark}
+
+\subsection{Proof of Proposition~\ref{prop:objective-error}}
+
+We first define $\widetilde{K}$ a rearrgement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
+\begin{equation*}
+\widetilde{K} = 
+\begin{bmatrix}
+K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
+K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &K_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
+\end{bmatrix}.
+\end{equation*}
+Setting $\dt{\mu} = (\mu_{I_{\varepsilon,\kappa}}^\top, \mu_{I^\complement_{\varepsilon,\kappa}}^\top)^\top$, $\dt{\nu} = (\nu_{J_{\varepsilon,\kappa}}^\top, \nu_{J^\complement_{\varepsilon,\kappa}}^\top)^\top$ and for each vectors $u \in \R^n$ and $v\in \R^m$ we set $\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top  \text{ and } \dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top.$
+We then have 
+\begin{equation*}
+\Psi_{\varepsilon, \kappa} (u,v) = \mathbf 1_n^\top \widetilde{K}(\dt{u}, \dt{v}) \mathbf 1_m - \kappa \dt{\mu}^\top \dt{u} - \kappa^{-1} \dt{\nu}^\top \dt{v},
+\end{equation*}
+and 
+\begin{equation*}
+\Psi_{} (u,v) = \mathbf 1_n^\top \widetilde{K}(\dt{u}, \dt{v}) \mathbf 1_m - \dt{\mu}^\top \dt{u} - \dt{\nu}^\top \dt{v},
+\end{equation*}
+where
+\begin{equation*}
+  \widetilde{B}(\dt{u}, \dt{v}) = \Delta(e^{\dt{u}})\widetilde{K} \Delta(e^{\dt{v}}).
+\end{equation*}
+Let us consider the convex function
+\begin{equation*}
+	(\hat u, \hat v) \mapsto \inr{\mathbf 1_n, \widetilde{B}(\dt{\hat u}^{\text{}} ,\dt{\hat v}^{\text{}})\mathbf 1_m} - \inr{\kappa\dt{\hat u}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{\hat v}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
+\end{equation*}
+Gradient inequality of any convex function g at point $x_o$ reads as $g(x_o) \geq g(x) + \inr{\nabla g(x), x_o - x}, \text{ for all } x \in \textbf{dom}(g).$
+Applying the latter fact to the above function at point ($u^{\star}, v^{\star})$ we obtain
+\begin{align*}
+\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} &- \inr{\kappa\dt{u}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+& - \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
+&\qquad \qquad  \leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
+\end{align*}
+Moreover,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&= \inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}}, \dt{v}^{\text{sc}})\mathbf 1_n^\top}\\
+&\qquad - \big( 
+\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
+&\qquad + \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}.
+\end{align*}
+Hence,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
++& \big( \inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m} \\
+&- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
+& \qquad -\inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} -\inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
+& \leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\qquad + \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big).
+\end{align*}
+Then,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&\leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\qquad + \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)
+\\
+&\qquad + \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
+&\qquad - \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top \mathbf 1_n} \big),
+\end{align*}
+which yields 
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&\leq  \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} +\inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
+\end{align*}
+Applying Holder's inequality gives 
+\begin{align*}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&\leq \norm{\kappa \dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\leq \norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+\end{align*}
+Note that
+\begin{align*}
+\begin{cases}
+\norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty = \norm{{u}^{\text{sc}} - {u}^\star}_\infty,\\
+\norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty = \norm{{v}^{\text{sc}} - {v}^\star}_\infty,
+\end{cases}
+\text{ and }
+\begin{cases}
+\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 = \norm{{B}({u}^{\text{sc}} ,{v}^{\text{sc}})\mathbf 1_m - {\mu}}_1 = \norm{\mu^{\text{sc}} - \mu}_1,\\
+\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1 = \norm{{B}({u}^{\text{sc}} ,{v}^{\text{sc}})^\top\mathbf 1_n - {\nu}}_1 = \norm{\nu^{\text{sc}} - \nu}_1.
+\end{cases}
+\end{align*}
+Then
+\begin{align}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) &
+\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty \norm{\nu^{\text{sc}} - \nu}_1\nonumber\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\dt{\mu}^{\text{sc}}} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\dt{\nu}^{\text{sc}}}\nonumber\\
+&\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty\norm{\nu^{\text{sc}} - \nu}_1 \nonumber\\
+&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{priori_bounds_induction}
+\end{align}
+
+\paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.
+
+If $r \in I^\complement_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|({u}^{\text{sc}})_{r} - {u}^\star_r| 
+&= \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m \frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
+& \overset{(\star)}{\leq} \bigg|\log\bigg(\max_{1\leq i \leq m} \frac{K_{rj}e^{v^\star_j}}{\frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
+& \leq \big|\max_{1\leq j \leq m} (v_j^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})\big|\\
+& \leq \norm{v^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
+& \leq \norm{v^\star - {v}^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}}).
+\end{align*}
+where the inequality $(\star)$ comes from the fact that $\frac{\sum_{j=1}^na_j}{\sum_{j'=1}^nb_{j'}} \leq \max_{1\leq j \leq n} \frac{a_j}{b_j}, \forall a_j, b_j>0.$
+Now, if $r \in I_{\varepsilon, \kappa}$, then  we have 
+\begin{align*}
+|({u}^{\text{sc}})_{r} - {u}^\star_r|
+= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
+\leq \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
+\overset{(\star)}{\leq}\norm{v^{\text{sc}} - v^\star}_\infty.
+\end{align*}
+If $s \in J^\complement_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|({v}^{\text{sc}})_{s} - {v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
+& \leq \bigg|\log\bigg(\max_{1\leq i \leq n} \frac{K_{is}e^{u^\star_i}}{\frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
+& \overset{(\star)}{\leq} \big|\max_{1\leq i \leq n} (u_i^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})\big|\\
+& \leq \norm{u^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})}_\infty \\
+& \leq \norm{u^\star - u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}).
+\end{align*}
+If $s \in J_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|({v}^{\text{sc}})_{s} - {v}^\star_s| 
+= \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{u^\star_i}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
+ \leq \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{v^\star_j}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
+\overset{(\star)}{\leq} \norm{u^{\text{sc}} - u^\star}_\infty.
+\end{align*}
+Therefore, we obtain the followoing bound:
+\begin{align}
+\label{induction_uppers_bounds}
+\max\{\norm{u^\star - u^{\text{sc}}}_\infty, \norm{v^\star - v^{\text{sc}}}_\infty\} %&\leq \max\{\norm{u^\star - u^{\text{sc}}_0}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star - v^{\text{sc}}_0}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\}\nonumber\\
+&\leq \max\Big\{\norm{u^\star}_\infty + \norm{u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star}_\infty + \norm{v^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\Big\}\nonumber\\
+&\leq 2\Big(\norm{u^\star}_\infty + \norm{v^\star}_\infty +  \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}}\big)\Big).
+\end{align}
+%where we used $u^{\text{sc}}_0 = \mathbf 0_n$ and $v^{\text{sc}}_0 = \mathbf 0_m.$ 
+Now, Lemma 3.2 in~\cite{lin2019} provides an upper bound for the $\ell_\infty$ of the optimal solution pair $(u^\star, v^\star)$ of problem~\eqref{sinkhorn-dual} as follows:
+$\norm{u^\star}_\infty \leq R$ and $\norm{v^\star}_\infty\leq R,$ where 
+\begin{align}
+\label{R_constant}
+R = \frac{\norm{C}_\infty}{\eta} + \log\big(\frac{n\vee m}{c^2_{\mu\nu}}\big).
+\end{align}
+Plugging~\eqref{induction_uppers_bounds} and~\eqref{R_constant} in~\eqref{priori_bounds_induction}, we obtain
+\begin{align}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
+&\leq 2\big(R + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
+&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{post_bounds_induction_2}
+\end{align}
+By Proposition~\ref{prop:bounds_of_usc_and_vsc}, we have 
+\begin{align*} %\max_{i \in I_{\varepsilon,\kappa}} \mu_i %\max_{j \in J_{\varepsilon,\kappa}} \nu_j
+\norm{u^{\text{sc}}}_\infty \leq \log\big(\frac \varepsilon\kappa\vee \frac{1}{m\varepsilon K_{\min}}\big) \text{ and } \norm{v^{\text{sc}}}_\infty \leq \log\big(\varepsilon\kappa \vee \frac{1}{n\varepsilon K_{\min} }\big)
+\end{align*}
+and hence by Remark~\ref{rem:orders_of_epsilonappa}, 
+\begin{equation*}
+\norm{u^{\text{sc}}}_\infty = \bigO\big(\log({n^{1/4}}/{(mK_{\min})^{3/4}c_{\mu\nu}^{1/4}})\big) \text{ and }\norm{u^{\text{sc}}}_\infty =\bigO\big(\log({m^{1/4}}/{(nK_{\min})^{3/4}c_{\mu\nu}^{1/4}})\big).
+\end{equation*}
+Hence, we have 
+\begin{align*}
+R + \norm{u^{\text{sc}}}_\infty  + \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) = \bigO\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big).
+\end{align*}
+Letting $\omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1,$
+Moreover, we have 
+\begin{align*}
+\omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1
+\end{align*}
+
+We arrive at 
+\begin{align}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
+&\leq 2\big(R + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
+&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{post_bounds_induction_2}
+\end{align}
+
+\paragraph{Bounds of}$\norm{\mu^{\text{sc}}}_1$  and $\norm{\nu^{\text{sc}}}_1.$
+
+Lemma~\ref{lemma_bounds_on_marginals} expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$, while 
+\begin{lemma}
+\label{lemma_bounds_on_marginals}
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
+Then one has 
+\begin{align*}
+\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \bigg(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon
+ ^2 \bigg)
+\end{align*}
+and 
+\begin{align*}
+\norm{\nu^{\text{sc}}}_1  \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\bigg(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\bigg).
+\end{align*}
+\end{lemma}
+
+\begin{proof}
+Using inequality~\eqref{bound_on_v}, we obtain 
+\begin{align*}
+\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
+& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
+% &\leq n_b\kappa + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
+\end{align*}
+Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
+\end{proof}
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}[htbp]
 	\centering

### 2019-05-21 tex/v3/section_2_setup_OT.tex

@@
 
-Computing OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\cite{kantorovich1942} given by
+Computing OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\citep{kantorovich1942} given by
 \begin{equation}
@@
 Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-Moreover, $P^\star$ can be solved efficiently by iterative Bregman projections~\cite{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity~\cite{altschulernips17}.
+Moreover, $P^\star$ can be solved efficiently by iterative Bregman projections~\citep{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity~\citep{altschulernips17}.
 

### 2019-05-21 tex/v3/section_5_numeric_expes.tex

@@
 	\begin{center}
-		~\hfill~\includegraphics[width=5.5cm]{./figs/norm_M_Mu_marginals_toy_n1000}~\hfill~
-		\includegraphics[width=5.5cm]{./figs/norm_M_Mu_marginals_toy_n1000}~\hfill~\\
-		~\hfill~\includegraphics[width=5.5cm]{./figs/norm_M_time_toy_n1000}
-		~\hfill~\includegraphics[width=5.5cm]{./figs/norm_M_div_toy_n1000}~\hfill~\\
+		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
+		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill \\
+		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~
+		\includegraphics[width=4.55cm]{./figs/norm_M_div_toy_n1000}
 	\end{center}

### 2019-05-21 tex/v3/section_3_algorithm.tex
typo sec 5 in Ref

@@
 Proof of Lemma~\ref{I_epsilon_kappa_J_epsilon_kappa} is postponed to the supplementary material.
-It is worth to note that first order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\cite{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.
+It is worth to note that first order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\citep{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.
 
@@
 
-\textbf{step 1:} \textcolor{black}{Initialization}\\
+\textbf{Step 1:} \textcolor{black}{Initialization}\\
 
@@
 
-\noindent \textbf{step 2:} \textcolor{black}{L-BFGS-B}\\
+\noindent \textbf{Step 2:} \textcolor{black}{L-BFGS-B}\\
 

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
typo sec 5 in Ref

@@
 \label{marginal-error-mu}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\bigg(n_bc_\kappa + (n- n_b) \bigg(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}K_{\min}}
- + \log\bigg(\frac{\sqrt{nm}}{m_b(c_{\mu\nu}K_{\min})^{5/2}} 
-\bigg)\bigg)\bigg)
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Big(n_bc_\kappa + (n- n_b) \Big(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}K_{\min}}
+ + \log\Big(\frac{\sqrt{nm}}{m_b(c_{\mu\nu}K_{\min})^{5/2}} 
+\Big)\Big)\Big)
 \end{align}
@@
 \label{marginal-error-nu}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} = \bigO\bigg(m_bc_{\frac1\kappa} + (m- m_b) \bigg(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{n-n_b}{\sqrt{nm}K_{\min}}
- + \log\bigg(\frac{\sqrt{nm}}{n_b (c_{\mu\nu}K_{\min})^{5/2}}
-\bigg)\bigg)\bigg),
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} = \bigO\Big(m_bc_{\frac1\kappa} + (m- m_b) \Big(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{n-n_b}{\sqrt{nm}K_{\min}}
+ + \log\Big(\frac{\sqrt{nm}}{n_b (c_{\mu\nu}K_{\min})^{5/2}}
+\Big)\Big)\Big),
 \end{align}
@@
 
-Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of Screenkhorn and the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of Screenkhorn and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+%It depends on the quantity $\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1$
 \begin{proposition}
@@
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
-= \bigO\bigg(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1)  + \omega_{\kappa}\bigg).
+= \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1)  + \omega_{\kappa}\Big).
 \end{align*}

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
typo sec 5 in Ref

--- 2019-05-21 tex/v3/section_5_numeric_expes.tex
@@
 are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
-through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA.
+through Sinkhorn divergence \citep{flamary2018WDA} and a domain-adaptation using optimal transport mapping \citep{courty2017optimal}, named OTDA.
 
@@
 used a MNIST to USPS problem in which features have been extracted from the
-feature extractor of an domain adversarial neural networks \cite{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
+feature extractor of an domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
 Figure \ref{fig:otda} reports the gain in running time for $2$ different values

### 2019-05-21 tex/v3/appendix.tex
typo sec 5 in Ref
new sec 4 bounds

@@
 \leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty \norm{\nu^{\text{sc}} - \nu}_1\nonumber\\
-&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\dt{\mu}^{\text{sc}}} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\dt{\nu}^{\text{sc}}}\nonumber\\
+&\qquad + (1- \kappa)\inr{{u}^{\text{sc}} ,{\mu}^{\text{sc}}} + (1- \kappa^{-1})\inr{{v}^{\text{sc}} ,{\nu}^{\text{sc}}}\nonumber\\
 &\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty\norm{\nu^{\text{sc}} - \nu}_1 \nonumber\\
@@
 
-If $r \in I^\complement_{\varepsilon, \kappa}$ then 
+If $r \in I^\complement_{\varepsilon, \kappa}$, then we have 
 \begin{align*}
@@
 where the inequality $(\star)$ comes from the fact that $\frac{\sum_{j=1}^na_j}{\sum_{j'=1}^nb_{j'}} \leq \max_{1\leq j \leq n} \frac{a_j}{b_j}, \forall a_j, b_j>0.$
-Now, if $r \in I_{\varepsilon, \kappa}$, then  we have 
+Now, if $r \in I_{\varepsilon, \kappa}$, we get 
 \begin{align*}
-|({u}^{\text{sc}})_{r} - {u}^\star_r|
+|{u}^{\text{sc}}_{r} - {u}^\star_r|
 = \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
@@
 \begin{align*}
-|({v}^{\text{sc}})_{s} - {v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
+|{v}^{\text{sc}}_{s} - {v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
 & \leq \bigg|\log\bigg(\max_{1\leq i \leq n} \frac{K_{is}e^{u^\star_i}}{\frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
@@
 \begin{align*}
-|({v}^{\text{sc}})_{s} - {v}^\star_s| 
+|{v}^{\text{sc}}_{s} - {v}^\star_s| 
 = \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{u^\star_i}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
@@
 \end{align*}
-
 We arrive at 
-\begin{align}
+\begin{align*}
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
-&\leq 2\big(R + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
-&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{post_bounds_induction_2}
-\end{align}
-
-\paragraph{Bounds of}$\norm{\mu^{\text{sc}}}_1$  and $\norm{\nu^{\text{sc}}}_1.$
-
-Lemma~\ref{lemma_bounds_on_marginals} expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$, while 
+& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1) + \omega_{\kappa}\Big).\label{post_bounds_induction_2}
+\end{align*}
+Note that $\omega_{\kappa}$ tends to zeros as $(n_b,m_b)$ tends to $(n,m)$ (i.e., $\kappa \rightarrow 1)$. To more characterize $\omega_\kappa$, the following 
+lemma expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 
 \begin{lemma}
@@
 \begin{align*}
-\norm{\mu^{\text{sc}}}_1 \leq \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{}}}_1 + (n-n_b) \bigg(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon
- ^2 \bigg)
+\norm{\mu^{\text{sc}}}_1 = \bigO\Big(\frac{n_b\sqrt{m}}{\sqrt{nK_{\min}c_{\mu\nu}}} + (n-n_b)\Big(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} + \frac{m-m_b}{\sqrt{nm}K_{\min}}\Big)\Big),
 \end{align*}
@@
 \begin{align*}
-\norm{\nu^{\text{sc}}}_1  \leq \kappa^{-1} \norm{\nu_{J_{\varepsilon,\kappa}}}_1 + (m-m_b)\bigg(\frac{n_b\kappa \max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m K_{\min}} + (n-n_b)\varepsilon^2\bigg).
+\norm{\nu^{\text{sc}}}_1 = \bigO\Big(\frac{m_b\sqrt{n}}{\sqrt{mK_{\min}c_{\mu\nu}}} + (m-m_b)\Big(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} + \frac{n-n_b}{\sqrt{nm}K_{\min}}\Big)\Big).
 \end{align*}

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
new sec 4 bounds

@@
 Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of Screenkhorn and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
-%It depends on the quantity $\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1$
 \begin{proposition}
@@
 \end{proposition}
+Proof of Proposition~\ref{prop:objective-error} is postponed to the supplemntary material.
+Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, i.e., $\kappa$ goes to $1.$
 % section analysis_of_marginal_violations (end)

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 We consider an unsupervised domain adaptation using optimal transport with entropic regularization.
-Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and, whether the cost matrix $C$ is normalized or not.
+Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$.
+% and, whether the cost matrix $C$ is normalized or not.
  We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $\| \inr{C, P^\star} - \inr{C, P^{sc}}\|$ between \emph{Screenkhorn} and Sinkhorn.
@@
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
-Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn.
+Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
 

### 2019-05-21 tex/v3/section_3_algorithm.tex
new section 3

@@
 
-\paragraph{Static screening test.} The core of the static screening test developed in this work aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
+\paragraph{Static screening test.} The core of the static screening test developed in this paper aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
 $e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
-The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
+The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the LBFGS solver.
 Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
@@
 Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-The L-BFGS-B solver handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
+The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}),$ 
+that handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
 The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
new sections 3 and 4

--- 2019-05-21 tex/v3/section_4_marginal_viols.tex
@@
 \label{proposition_error_in_marginals}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal pair solution of problem~\eqref{screen-sinkhorn_second_def}.
 Then one has 
-
 \begin{align}
@@
 Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of Screenkhorn and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
-%It depends on the quantity $\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1$
 \begin{proposition}
 \label{prop:objective-error}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def} and $(u^\star, v^\star)$ is the solution of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal pair solution of problem~\eqref{screen-sinkhorn_second_def} and $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 Then we have
@@
 \end{proposition}
+Proof of Proposition~\ref{prop:objective-error} is postponed to the supplemntary material.
+Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
 % section analysis_of_marginal_violations (end)

### 2019-05-21 tex/v3/section_3_algorithm.tex

@@
 \label{prop:bounds_of_usc_and_vsc}
-Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def} and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$.
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal pair solution of problem~\eqref{screen-sinkhorn_second_def} and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$.
 Then,
@@
 
-\noindent \textbf{Step 2:} \textcolor{black}{L-BFGS-B}\\
+\noindent \textbf{Step 2:} \textcolor{black}{LBFGS}\\
 
@@
 \nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
+\nl   $\theta \gets \text{LBFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
 \nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\

### 2019-05-21 tex/v3/section_4_marginal_viols.tex

@@
 % We derive in this section 
-This section is devoted to establishing theoretical guarantees for the marginal violations of Screenkhorn. 
+This section is devoted to establishing theoretical guarantees for Screenkhorn algorithm. %the marginal violations of
 We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
-Our first theoretical result, Proposition~\ref{proposition_error_in_marginals}, gives an upper bound of marginal errors of Screenkhorn algorithm with respect to $\ell_1$-norm.
+Our first theoretical result, Proposition~\ref{proposition_error_in_marginals}, gives an upper bound of the screened marginal violations with respect to $\ell_1$-norm.
 

### 2019-05-21 tex/v3/section_3_algorithm.tex
update sec 3

@@
 \includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
-\caption{Plots of $\varepsilon$ and $\kappa$ as a functions of budgets for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ as in Figure~\eqref{fig:motivations}.
+\caption{Plots of $\varepsilon$ and $\kappa$ as a functions of number budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are setting as in Figure~\eqref{fig:motivations}.
 As can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
@@
 Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
-It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradients, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}),$ 
-that handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
+It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
+Furthermore, Screenkhorn consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
+The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
+LBFGS handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
 The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.

### 2019-05-21 tex/v3/section_1_introduction.tex
update

@@
 number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization.
-Within this global context, our contributions are the following :
+Within this global context, our contributions are the following:
 \begin{itemize}
@@
 
-	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
+	\item From a methodological point of view, we propose a reformulation of the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
 	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 % and, whether the cost matrix $C$ is normalized or not.
- We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $\| \inr{C, P^\star} - \inr{C, P^{sc}}\|$ between \emph{Screenkhorn} and Sinkhorn.
+ We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{sc}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn.
 
@@
 		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill \\
+		\includegraphics[width=4.55cm]{./figs/norm_M_Nu_marginals_toy_n1000} ~\hfill \\
 		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 % and, whether the cost matrix $C$ is normalized or not.
- We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{sc}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn.
+ We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
 

### 2019-05-21 tex/v3/section_2_setup_OT.tex
update sec 2

@@
 Computing OT distance between the two discrete measures $\mu$ and $\nu$  amounts to solving a linear problem~\citep{kantorovich1942} given by
-\begin{equation}
+\begin{equation*}
   \label{monge-kantorovich}
   \mathcal{S}(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \inr{C, P},
-\end{equation}
+\end{equation*}
 where $P= (P_{ij}) \in \R^{n\times m}$ is called the transportation plan, namely each entry $P_{ij}$ represents the fraction of mass moving from $x_i$ to $y_j$, and $C= (C_{ij}) \in \R^{n\times m}$ is a cost matrix comprised of nonnegative elements and related to the energy needed to move a probability mass from $x_i$ to $y_j$.
 The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
-\begin{equation}
+\begin{equation*}
 \label{sinkhorn-primal}
   \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
-\end{equation}
+\end{equation*}
 where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.
@@
 Therefore, we get
-\begin{equation}
+\begin{equation*}
   P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
-\end{equation}
+\end{equation*}
 for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update sec 5

@@
 Scipy. Regarding the machine-learning based comparison, we have based our code
-on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
+on the ones of POT~\citep{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
 We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the

### 2019-05-21 tex/v3/section_1_introduction.tex
update

@@
 	\item From a methodological point of view, we propose a reformulation of the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
-	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to
+	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to  strictly satisfy its constraint, leading then to
 	a ``screened'' version of the dual of Sinkhorn divergence. 
@@
 The remainder of the paper is organized as follow. In Section~\ref{sec:regularized_discrete_ot} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screened_dual_of_sinkhorn_divergence} contains our main contribution, that is, the Screenkhorn algorithm. 
-Section~\ref{sec:analysis_of_marginal_violations} devotes to theoretical guarantees for marginal violations of Screenkhorn. 
+Section~\ref{sec:screened_dual_of_sinkhorn_divergence} contains our main contribution, that is, the \emph{Screenkhorn} algorithm. 
+Section~\ref{sec:analysis_of_marginal_violations} devotes to theoretical guarantees for marginal violations of \emph{Screenkhorn}. 
 In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 

### 2019-05-21 tex/v3/section_3_algorithm.tex
update sec 2
update

@@
 Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
-We also plot two lines correspond to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.
+In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
+We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.
 

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 \includegraphics[width=0.45\textwidth]{./figs/motivations.pdf}
-\caption{Plots of $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
+\caption{Plots of $(e^{u^\star}, e^{v^\star})$ pair solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
 \label{fig:motivations}
@@
 \includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
-\caption{Plots of $\varepsilon$ and $\kappa$ as a functions of number budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are setting as in Figure~\eqref{fig:motivations}.
-As can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
+\caption{Plots of $\varepsilon$ and $\kappa$ as a function of budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are set as in Figure~\eqref{fig:motivations}.
+As it can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
 \label{fig:kappa_epsilon}

### 2019-05-21 tex/v3/section_1_introduction.tex
update intro

@@
 
-Computing OT distances between pairs of probability measures or histograms, such as the earth mover's distance~\citep{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\citep{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\citep{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\citep{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\citep{bonnel2011,Rubner2000,solomon2015}, among other applications~\citep{klouri17,peyre2019COTnowpublisher}.
+Computing optimal transport (OT) distances between pairs of probability measures or histograms, such as the earth mover's distance~\citep{werman1985,Rubner2000} and Monge-Kantorovich or Wasserstein distance~\citep{villani09optimal}, are currently generating an increasing attraction in different machine learning tasks~\citep{pmlr-v32-solomon14,kusnerb2015,pmlr-v70-arjovsky17a,ho2017}, statistics~\citep{frogner2015nips,panaretos2016,ebert2017ConstructionON,bigot2017,flamary2018WDA}, and computer vision~\citep{bonnel2011,Rubner2000,solomon2015}, among other applications~\citep{klouri17,peyre2019COTnowpublisher}.
 In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.

### 2019-05-21 tex/v3/main.tex
change intro
update conclusion

@@
 \usepackage{etoolbox}
+\usepackage{natbib}
 \patchcmd{\appendices}{\quad}{. }{}{}
@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage{enumitem}
+
+\setlist[itemize]{leftmargin=4.5mm}
 
@@
 \usepackage{wrapfig}
+
+\newcommand{\rev}[1]{{\color{blue} #1}}
+\newcommand{\ar}[1]{{\color{red} #1}}
+\newcommand{\rf}[1]{{\color{green} #1}}
 
@@
 University of Rouen\\
-and Criteo AI Labs, Criteo Paris \\
+and Criteo AI Lab, Criteo Paris \\
 \texttt{alain.rakoto@insa-rouen.fr} \\
@@
 \section{Conclusion}
-The paper proposed a novel efficient approximation of the Sinkhorn divergence
+The paper introduces a novel efficient approximation of the Sinkhorn divergence
 based on a screening strategy. Screening some of the Sinkhorn dual variables
@@
 \bibliography{biblio}
-\bibliographystyle{plain}
+\bibliographystyle{chicago}
+%well as with those for harvard, apalike, chicago, astron, authordate, and of course natbib.
 

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$.
-In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence in this case corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence in this case the approximate dual in problem \eqref{screen-sinkhorn} corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 
-Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
+Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
 Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
@@
 Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
-It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-Furthermore, Screenkhorn consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
+It is worth to note that \emph{Screenkhorn} algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
+Furthermore, \emph{Screenkhorn} consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
 The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
 LBFGS handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
-The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
+The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of \emph{Screenkhorn}.
 

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
update

@@
 
-Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of Screenkhorn and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of \emph{Screenkhorn} and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 \begin{proposition}

### 2019-05-21 tex/v3/section_1_introduction.tex
update sec 1&3

@@
 	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
-	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \citep{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
+	\item From an algorithmic standpoint, we use a constrained L-BFGS-B algorithm \citep{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
 	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning

### 2019-05-21 tex/v3/section_3_algorithm.tex
update sec 1&3

--- 2019-05-21 tex/v3/section_3_algorithm.tex
@@
 $e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
-The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the LBFGS solver.
+The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
 Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
@@
 Furthermore, Screenkhorn consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-LBFGS handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
+The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
+L-BFGS-B handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
 The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
@@
 
-\noindent \textbf{Step 2:} \textcolor{black}{LBFGS}\\
+\noindent \textbf{Step 2:} \textcolor{black}{L-BFGS-B}\\
 
@@
 \nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
-\nl   $\theta \gets \text{LBFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
+\nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
 \nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\

### 2019-05-21 tex/v3/section_3_algorithm.tex

@@
 The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
-
 \begin{proposition}

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
update sec 4

@@
 Proof of Proposition~\ref{prop:objective-error} is postponed to the supplemntary material.
-Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
+Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero as pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
 % section analysis_of_marginal_violations (end)

### 2019-05-21 marg_expe_v2.py
update

@@ -123,7 +123,7 @@ regvect = [1e-1, 5e-1, 1, 10]
 #regvect = [1e-1, 1, 10]
 datatype = 'toy' # change to mnist to run on Mnist dataset
 n_iter = 10 # we repeat n_iter times 
-normalize = False
+normalize = True
 
 #%%
 for n in nvect:

### 2019-05-21 tex/v3/main.tex
update sec 1&3

@@
 sufficient conditions depending on the ground cost matrix, that some dual variables are smaller than a given threshold. Hence, we need just to solve a restricted
-dual Sinkhorn problem using an off-the-shelf LBFGS algorithm. We also provided
+dual Sinkhorn problem using an off-the-shelf L-BFGS-B algorithm. We also provide
 some theoretical guarantees of the quality of the approximation with respect to

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 L-BFGS-B handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
-The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
+The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of \emph{Screenkhorn}.
 \begin{proposition}
@@
 \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
+\nl  $\theta^{(0)} \gets \texttt{stack}[u^{(0)}, v^{(0)}];$\\
 \nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update sec 5

@@
 
-We have implemented our Screenkhorn in Python and used the LBFGS of
+We have implemented our Screenkhorn in Python and used the L-BFGS-B of
 Scipy. Regarding the machine-learning based comparison, we have based our code
 on the ones of POT~\citep{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
-We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
+We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the L-BFGS-B algorithm is stopped when the
 largest component of the projected gradient is smaller than $10^{-6}$, when the number of iterations of number of objective function evaluations reach $10^{5}$.

### 2019-05-21 tex/v3/appendix.tex

@@
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
-& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1) + \omega_{\kappa}\Big).\label{post_bounds_induction_2}
+& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1) + \omega_{\kappa}\Big).
 \end{align*}
@@
 Then one has 
-\begin{align*}
+\begin{align}
+\label{l1-norm-mu-sc}
 \norm{\mu^{\text{sc}}}_1 = \bigO\Big(\frac{n_b\sqrt{m}}{\sqrt{nK_{\min}c_{\mu\nu}}} + (n-n_b)\Big(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} + \frac{m-m_b}{\sqrt{nm}K_{\min}}\Big)\Big),
-\end{align*}
+\end{align}
 and
-\begin{align*}
+\begin{align}
+\label{l1-norm-nu-sc}
 \norm{\nu^{\text{sc}}}_1 = \bigO\Big(\frac{m_b\sqrt{n}}{\sqrt{mK_{\min}c_{\mu\nu}}} + (m-m_b)\Big(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} + \frac{n-n_b}{\sqrt{nm}K_{\min}}\Big)\Big).
-\end{align*}
+\end{align}
 \end{lemma}
@@
 \end{align*}
+Using Remark~\ref{rem:orders_of_epsilonappa}, we get the desired closed form in~\eqref{l1-norm-mu-sc}.
 Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.

### 2019-05-21 tex/v3/section_3_algorithm.tex
update algo
update

@@
 Proof of Lemma~\ref{I_epsilon_kappa_J_epsilon_kappa} is postponed to the supplementary material.
-It is worth to note that first order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\citep{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.
+It is worth to note that first order optimality conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\citep{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.
 
@@
 Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
-It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-Furthermore, Screenkhorn consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
+It is worth to note that \emph{Screenkhorn} algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
+Furthermore, \emph{Screenkhorn} consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
 The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
@@
 \DontPrintSemicolon
-\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
+\caption{\emph{Screenkhorn}$(C,\eta,\mu,\nu,n_b,m_b)$}
 \label{screenkhorn}
@@
 \nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
+\nl   $ \bar{\theta} \gets \texttt{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
+\nl   $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
 
@@
 \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \texttt{stack}[u^{(0)}, v^{(0)}];$\\
+\nl  $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
 \nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\

### 2019-05-21 tex/v3/section_4_marginal_viols.tex
update

@@
 % We derive in this section 
-This section is devoted to establishing theoretical guarantees for Screenkhorn algorithm. %the marginal violations of
+This section is devoted to establishing theoretical guarantees for \emph{Screenkhorn} algorithm. %the marginal violations of
 We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
@@
 \end{proposition}
-Proof of Proposition~\ref{prop:objective-error} is postponed to the supplemntary material.
+Proof of Proposition~\ref{prop:objective-error} is exposed in the supplementary material.
 Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero as pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

--- 2019-05-21 tex/v3/section_5_numeric_expes.tex
@@
 
-We have implemented our Screenkhorn in Python and used the LBFGS of
+We have implemented our \emph{Screenkhorn} algorithm in Python and used the L-BFGS-B of
 Scipy. Regarding the machine-learning based comparison, we have based our code
-on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one.
-We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the
+on the ones of Python Optimal Transport toolbox (POT)~\citep{flamary2017pot} and just replaced the Sinkhorn function call with a \emph{Screenkhorn} one.
+We have considered the POT's default Sinkhorn stopping criterion parameters and for \emph{Screenkhorn}, the L-BFGS-B algorithm is stopped when the
 largest component of the projected gradient is smaller than $10^{-6}$, when the number of iterations of number of objective function evaluations reach $10^{5}$.
@@
 Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
-Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of Screenkhorn for the toy problem, while
+Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
 for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
@@
 OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
-for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/Screenkhorn has to be computed. As a domain-adaptation problem, we have
+for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/\emph{Screenkhorn} has to be computed. As a domain-adaptation problem, we have
 used a MNIST to USPS problem in which features have been extracted from the

### 2019-05-21 tex/v3/section_3_algorithm.tex
update algo

@@
 On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$.
-In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence in this case the approximate dual in problem \eqref{screen-sinkhorn} corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence the objective of approximate dual in problem \eqref{screen-sinkhorn} converges to the objective of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 \includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
-\caption{Plots of $\varepsilon$ and $\kappa$ as a function of budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are set as in Figure~\eqref{fig:motivations}.
+\caption{Plots of $\varepsilon$ and $\kappa$ as a function of number budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are set as in Figure~\eqref{fig:motivations}.
 As it can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 \includegraphics[width=0.45\textwidth]{./figs/motivations.pdf}
-\caption{Plots of $(e^{u^\star}, e^{v^\star})$ pair solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
+\caption{Plots of $(e^{u^\star}, e^{v^\star})$ with $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} and the thresholds $\alpha_u, \alpha_v$.}
 \label{fig:motivations}
@@
 Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
+In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ where $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
 We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 
-We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
-The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
+We first compare \emph{Screenkhorn} to Sinkhorn on  a single call basis.
+The dataset we use is a synthetic one that consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
 We consider an unsupervised domain adaptation using optimal transport with entropic regularization.
-Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$.
+Several settings are explored: different values of $\eta$ the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m}$ ranging from $0.01$ to $0.99$ and, different values of $n$ and $m$.
 % and, whether the cost matrix $C$ is normalized or not.
@@
 %
-\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$).
+\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for "high" values of the regularization parameter $\eta$ ($\eta > 1$).
 The approximation quality diminishes for small $\eta$.
@@
 former problem, we aim at find the best two-dimensional linear subspace in a WDA sense whereas for MNIST, we look for a subspace of dimension $20$ starting from the original
-$728$ dimensions.  Quality of the retrieved subspace are evaluated using classification task based on a $1$-nearest neighbour approach.
+$728$ dimensions.  Quality of the retrieved subspace is evaluated using classification task based on a $1$-nearest neighbour approach.
 
 Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
-Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
+Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{fig:wda_gain}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
 for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
@@
 \includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
-	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor (the budget) in \emph{Screenkhorn}}.
 	\label{fig:wda}

### 2019-05-21 tex/v3/appendix.tex

@@
 
-For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \varepsilon\kappa^{-1}$.
-Further, the condition on the dual variable $\lambda^{*}_i > 0$  ensures that $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and hence $i \in I^\complement_{\varepsilon,\kappa}$.
+For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \frac\varepsilon\kappa$.
+Further, the condition on the dual variable $\lambda^{*}_i > 0$  ensures that $e^{u^{*}_i} = \frac\varepsilon\kappa$ and hence $i \in I^\complement_{\varepsilon,\kappa}$.
 We have that $\lambda^{*}_i > 0$ is equivalent to $e^{u^{*}_i}r_i(K) e^{v^{*}_j} >  \kappa{\mu_i}$ which  is satisfied when $\varepsilon^2r_i(K) >  \kappa{\mu_i}.$

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 used a MNIST to USPS problem in which features have been extracted from the
-feature extractor of an domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
+feature extractor of domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
 Figure \ref{fig:otda} reports the gain in running time for $2$ different values

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 	\begin{center}
-		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_Nu_marginals_toy_n1000} ~\hfill \\
-		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_div_toy_n1000}
+		\includegraphics[width=5.25cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{12pt} 
+		\includegraphics[width=5.25cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		\includegraphics[width=5cm]{./figs/norm_M_time_toy_n1000}\hspace*{18pt}
+		\includegraphics[width=5cm]{./figs/norm_M_div_toy_n1000}
 	\end{center}
 	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix.
-Top panel: marginal violations in relation with the budget of points.
-Bottom panel: (left) ratio of computation times    $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and, (right) relative divergence variation.
-The results are averaged over 10 trials.}
+Top panel: marginal violations as a function of the budget expressed as the decimation factor $n/n_b$.
+Bottom panel: (left) Running time gain and, (right) relative divergence variation.
+The results are averaged over 30 trials.}
 		\label{fig:margin_expe}

### 2019-05-21 marg_expe_v2.py

@@ -18,10 +18,10 @@ import matplotlib.pyplot as plt
 from matplotlib import rc
 rc('font', **{'family': 'sans-serif', 'sans-serif': ['Computer Modern Roman']})
 params = {'axes.labelsize': 18, # 12
-          'font.size': 18, # 12
-          'legend.fontsize': 18, # 12
-          'xtick.labelsize': 16, # 10
-          'ytick.labelsize': 16, # 10
+          'font.size': 20, # 12
+          'legend.fontsize': 20, # 12
+          'xtick.labelsize': 18, # 10
+          'ytick.labelsize': 18, # 10
           #'text.usetex': True,
           #'figure.figsize': (8, 6)
           }
@@ -71,12 +71,12 @@ def plot_mean_and_CI(pvect, mean, margin, color_mean=None, color_shading=None, l
     plt.xticks(pvect, pvect, rotation='vertical')
 
 #%%
-def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
-    n_pvect = len(pvect)
-    rel_time_vect = np.empty(n_pvect)
-    diff_a_vect   = np.empty(n_pvect)
-    diff_b_vect   = np.empty(n_pvect)
-    rel_cost_vect = np.empty(n_pvect)
+def compare_marginals(a, b, M, reg, decvect = [50, 10, 5, 2, 1.1]):
+    n_decvect = len(decvect)
+    rel_time_vect = np.empty(n_decvect)
+    diff_a_vect   = np.empty(n_decvect)
+    diff_b_vect   = np.empty(n_decvect)
+    rel_cost_vect = np.empty(n_decvect)
     
     # sinkhorn 
     tic = time()
@@ -84,11 +84,11 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
     time_sink = time() - tic
     Pstar = P_sink[0]
     
-    for j,p in enumerate(pvect):
+    for j,p in enumerate(decvect):
         print('p:', p)
         # screenkhorn
-        n_budget = int(np.ceil(a.shape[0]*p))
-        m_budget = int(np.ceil(b.shape[0]*p))
+        n_budget = int(np.ceil(a.shape[0]/p))
+        m_budget = int(np.ceil(b.shape[0]/p))
         
         tic = time()
         screenkhorn = Screenkhorn(a, b, M, reg, n_budget, m_budget, verbose=False)
[…]

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

@@
 
-Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings.
-We choose to only report results for $n=m=1000$ as we get similar findings for other values of $n$ and $m$.
+Figure \ref{fig:margin_expe} shows the behaviors of both algorithms under these settings and a normalized cost matrix.
+We choose to only report results for $n=m=1000$ as we get similar findings for other $n$ and $m$.
 
@@
 	\end{center}
-	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix.
+	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn.
 Top panel: marginal violations as a function of the budget expressed as the decimation factor $n/n_b$.
 Bottom panel: (left) Running time gain and, (right) relative divergence variation.
-The results are averaged over 30 trials.}
+The results are averaged over 30 trials}
 		\label{fig:margin_expe}
@@
 Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.
-According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to 1.
+According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at high decimation factor $n/n_b$ while the reverse holds when $n_b/n$ gets close to 1.
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.

### 2019-05-21 marg_expe_v2.py

@@ -17,11 +17,11 @@ np.random.seed(3946)
 import matplotlib.pyplot as plt
 from matplotlib import rc
 rc('font', **{'family': 'sans-serif', 'sans-serif': ['Computer Modern Roman']})
-params = {'axes.labelsize': 18, # 12
-          'font.size': 20, # 12
-          'legend.fontsize': 20, # 12
-          'xtick.labelsize': 18, # 10
-          'ytick.labelsize': 18, # 10
+params = {'axes.labelsize': 24, # 12
+          'font.size': 24, # 12
+          'legend.fontsize': 22, # 12
+          'xtick.labelsize': 22, # 10
+          'ytick.labelsize': 22, # 10
           #'text.usetex': True,
           #'figure.figsize': (8, 6)
           }
@@ -113,9 +113,8 @@ def compare_marginals(a, b, M, reg, decvect = [50, 10, 5, 2, 1.1]):
 #%%
 pathres= './resultat/'
 nvect = [500, 1000, 2500]
-#pvect = [0.99, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 
- #        0.2, 0.1, 0.05, 0.01]
-decvect = [1.1, 1.25, 1.5, 2, 2.5, 5, 10, 20, 50, 100]
+#decvect = [1.1, 1.25, 1.5, 2, 2.5, 5, 10, 20, 50, 100]
+decvect = [1.1, 1.25, 2, 5, 10, 20, 50, 100]
 regvect = [1e-1, 5e-1, 1, 10]
 datatype = 'toy' # change to mnist to run on Mnist dataset
 n_iter = 30 # we repeat n_iter times 
@@ -197,7 +196,7 @@ for n in nvect:
         diff_a_std  = diff_a.std(axis=0)
         
         plt.figure(1)
-        plt.semilogx(decvect, diff_a_mean, marker='s', markersize=6, 
+        plt.semilogx(decvect, diff_a_mean, marker='s', markersize=10, linewidth=4,
                      label='$\eta = ${:}'.format(reg))
         plt.fill_between(decvect, diff_a_mean+diff_a_std*coeff, 
                          diff_a_mean-diff_a_std*coeff, alpha=.15)
@@ -214,7 +213,7 @@ for n in nvect:
         diff_b_std  = diff_b.std(axis=0)
         
         plt.figure(2)
-        plt.semilogx(decvect, diff_b_mean, marker='s', markersize=6, 
[…]

### 2019-05-21 tex/v3/appendix.tex
update

@@
 	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
-	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
-		(right) MNIST). We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance. 
+	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem and, (right) MNIST).
+We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance.
 		\label{fig:wda_gain}}
@@
 	the number of samples. 
-	\label{fig:otda}}
+	\label{fig:otda:extra}}
 \end{figure*}
@@
 Note that this
-	value impact of the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
+	value impacts the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
 	also report the performance of a $1$-NN when no-adaptation is performed.  
-	We remark that the strenght of the class-based has influence on the performance of \emph{Screenkhorn} given a decimation factor.
-For small value on the left, Screenkhorn slightly performs better than Sinkhorn, while for large value, some
+	We remark that the strenght of the class-based regularization has influence on the performance of \emph{Screenkhorn} given a decimation factor.
+For small value on the left, \emph{Screenkhorn} slightly performs better than Sinkhorn, while for large value, some
 	decimation factors leads to loss of performances.

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 \caption{Plots of $\varepsilon$ and $\kappa$ as a function of number budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are set as in Figure~\eqref{fig:motivations}.
-As it can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
+$(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
 \label{fig:kappa_epsilon}
@@
 On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$.
-In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence the objective of approximate dual in problem \eqref{screen-sinkhorn} converges to the objective of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence the objective in problem \eqref{screen-sinkhorn} converges to the objective of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 
@@
 
-\nl   $\xi \gets \mu \oslash r(K);$ \\
-\nl   $\zeta \gets \nu \oslash c(K);$\\
-\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
+\nl   $\xi \gets \texttt{sort}(\mu \oslash r(K)),$ $\zeta \gets \texttt{sort}(\nu \oslash c(K));$ //(decreasing order)\\
+% \nl   $\zeta \gets \texttt{sort}(\nu \oslash c(K));$\\
+% \nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
+% \nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
 \nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
@@
 \nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-\nl   $ \bar{\theta} \gets \texttt{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
-\nl   $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
+\nl   $ \bar{\theta} \gets \texttt{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b}),$ $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
+% \nl   $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
 
@@
 
-\nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
-\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-\nl  $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
+\nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b},$ $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b},$ $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
+% \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
+% \nl  $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
 \nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\

### 2019-05-21 tex/v3/section_3_algorithm.tex
update

@@
 Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where
+Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$,
 \begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
+\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
 \end{equation*}

### 2019-05-22 da_expe.py
figure file

@@ -9,7 +9,7 @@ os.environ["OMP_NUM_THREADS"] = "1"
 from time import process_time as time
 import ot
 import ot.plot
-import  da_screenkhorn
+import  da_screenkhorn, da_sinkhorn
 from sklearn.datasets import make_blobs
 
 from sklearn.neighbors import KNeighborsClassifier
@@ -73,7 +73,7 @@ n_samples_target = n
 nb_iter = 10
 reg_cl = 10   # toy, 2 and 0
 K = 1 # K of KNN
-
+reg = 1
 pathres='./resultat/'
 p_vec = [1.5,2,5,10,20,50,100]
 n_pvec=  len(p_vec)
@@ -109,8 +109,8 @@ for i in range(nb_iter):
     #%% 
     # Sinkhorn Transport
     tic = time()
-    ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
-    #ot_sinkhorn = da_sinkhorn.SinkhornLpl1Transport(reg_e=1,reg_cl=reg_cl)
+    ot_sinkhorn = ot.da.SinkhornLpl1Transport(reg_e=reg,reg_cl=reg_cl)
+    #ot_sinkhorn = da_sinkhorn.SinkhornLpl1Transport(reg_e=reg,reg_cl=reg_cl)
     ot_sinkhorn.fit(Xs=Xs,ys= ys, Xt=Xt)
     time_sink[i] = time() - tic
     transp_Xs = ot_sinkhorn.transform(Xs=Xs)
@@ -126,7 +126,7 @@ for i in range(nb_iter):
         print(p_n)
         # Screenkhorn Transport
         tic = time()
-        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=1,reg_cl=reg_cl,one_init=False)
+        ot_screenkhorn = da_screenkhorn.ScreenkhornLpl1Transport(reg_e=reg,reg_cl=reg_cl,one_init=False)
         ot_screenkhorn.fit(Xs=Xs,ys=ys, Xt=Xt, p_n=p_n, p_m=p_n)
        
         time_screen[i,j] = time() - tic

### 2019-05-22 figure_da.py

@@ -1,0 +1,201 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue May  7 10:11:50 2019
+
+@author: alain
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import seaborn as sns
+
+color_pal_t = sns.color_palette("colorblind", 11).as_hex()
+color_pal = color_pal_t.copy()
+
+
+colors = ["black", "salmon pink", "neon pink", "cornflower","cobalt blue"
+          ,"blue green", "aquamarine", "bright yellow", "golden yellow", "reddish pink" , "reddish purple"]
+
+color_pal = sns.xkcd_palette(colors)
+
+plt.close("all")
+
+pathres = './resultat/da/'
+
+data = 'toy'
+if data == 'toy':
+    n_vec = [200,500,1000,2000,3000,5000]
+    nb_p_vec = 7
+    p = 2 
+    regcl = 100
+else:
+    data = 'mnist'
+    n_vec = [200,500,1000,2000,3000,4000]
+    nb_p_vec = 7
+    p = 20
+    regcl = 1
+
+method_vec = ['wda', 'swda']
+legend_vec_accur = ['Sinkhorn','dec=1.5','dec=2','dec=5','dec=10','dec=20','dec=50','dec=100','No Adapt']
+legend_vec_time = ['dec=1.5','dec=2','dec=5','dec=10','dec=20','dec=50','dec=100']
+t = 1
+in_sample = 0
+
+Mres = np.zeros((len(n_vec), nb_p_vec+2))
+Sres = np.zeros((len(n_vec), nb_p_vec+2))
+
+Mtime = np.zeros((len(n_vec), nb_p_vec+1))
+Stime = np.zeros((len(n_vec), nb_p_vec+1))
+
+Mgain = np.zeros((len(n_vec), nb_p_vec+1))
+Sgain = np.zeros((len(n_vec), nb_p_vec+1))
+
+for i_k, n in enumerate(n_vec):                
+    if data == 'toy':
+        filename = 'da_{:}_n{:d}_regcl{:2.2f}'.format(data,n,regcl)
+    else:
+        filename = 'da_{:}_n{:d}_regcl{:d}'.format(data,n,regcl)
+
+    # reading files and performance
+    res = np.load(pathres + filename + '.npz')
+    
+    
+    
+    
+    aux = res['bc_sink']
[…]

### 2019-05-22 figure_wda.py

@@ -1,0 +1,149 @@
+                #!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue May  7 10:11:50 2019
+
+@author: alain
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import seaborn as sns
+
+color_pal_t = sns.color_palette("colorblind", 11).as_hex()
+color_pal = color_pal_t.copy()
+
+
+colors = ["black", "salmon pink", "neon pink", "cornflower","cobalt blue"
+          ,"blue green", "aquamarine", "bright yellow", "golden yellow", "reddish pink" , "reddish purple"]
+
+color_pal = sns.xkcd_palette(colors)
+
+plt.close("all")
+
+pathres = './resultat/wda/'
+
+data = 'mnist'
+if data == 'toy':
+    n_vec = [200,500,1000,2000,3500,5000]
+    nb_p_vec = 7
+    p = 2
+else:
+    data = 'mnist'
+    n_vec = [200,500,1000,2000,3000,4000]
+    nb_p_vec = 7
+    p = 20
+    
+
+method_vec = ['wda', 'swda']
+legend_vec_accur = ['Sinkhorn','dec=1.5','dec=2','dec=5','dec=10','dec=20','dec=50','dec=100']
+legend_vec_time = ['dec=1.5','dec=2','dec=5','dec=10','dec=20','dec=50','dec=100']
+
+t = 1
+in_sample = 0
+
+Mres = np.zeros((len(n_vec), nb_p_vec+1))
+Sres = np.zeros((len(n_vec), nb_p_vec+1))
+
+Mtime = np.zeros((len(n_vec), nb_p_vec+1))
+Stime = np.zeros((len(n_vec), nb_p_vec+1))
+
+for i_k, n in enumerate(n_vec):                
+    filename = 'wda_{:}_n{:d}_p{:d}'.format(data,n,p)
+    
+    
+    # reading files and performance
+    res = np.load(pathres + filename + '.npz')
+    aux = res['bc_wda']
+    nb_computed = np.where(aux)[0].shape[0]
+    print(nb_computed)
+    print(' \t\t {:2.2f} \t\t{:d}'.format( aux[np.where(aux)].sum()/nb_computed*100, nb_computed ))
+    Mres[i_k,0] = aux[np.where(aux)].mean()
+    Sres[i_k,0] = aux[np.where(aux)].std()
+    
[…]

### 2019-05-22 marg_expe.py

@@ -104,12 +104,14 @@ def compare_marginals(a, b, M, reg, pvect = [0.9, 0.7, 0.5, 0.3, 0.1]):
 pathres= './resultat/'
 
 nvect = [200,500, 1000, 2500, 3000]
+regvect = [1e-1, 5e-1, 1, 10]
 
-
+nvect = [1000]
+regvect=[1]
 
 pvect = [0.99, 0.95, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 
          0.2, 0.1, 0.05, 0.01]
-regvect = [1e-1, 5e-1, 1, 10]
+
 datatype = 'toy' # change to mnist to run on Mnist dataset
 n_iter = 10 # we repeat n_iter times 
 

### 2019-05-22 screenkhorn.py

@@ -66,6 +66,8 @@ class Screenkhorn:
             self.K_IJ = self.K
             self.a_I = self.a
             self.b_J = self.b
+            self.K_IJc = []
+            self.K_IcJ = []
 
         else:
             

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

--- 2019-05-21 tex/v3/section_5_numeric_expes.tex
@@
 
-We first compare \emph{Screenkhorn} to Sinkhorn on  a single call basis.
-The dataset we use is a synthetic one that consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
+We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
+The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.
 We consider an unsupervised domain adaptation using optimal transport with entropic regularization.
-Several settings are explored: different values of $\eta$ the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m}$ ranging from $0.01$ to $0.99$ and, different values of $n$ and $m$.
+Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$.
 % and, whether the cost matrix $C$ is normalized or not.
  We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
-
 Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings.
@@
 %
-\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for "high" values of the regularization parameter $\eta$ ($\eta > 1$).
+\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$).
 The approximation quality diminishes for small $\eta$.
@@
 former problem, we aim at find the best two-dimensional linear subspace in a WDA sense whereas for MNIST, we look for a subspace of dimension $20$ starting from the original
-$728$ dimensions.  Quality of the retrieved subspace is evaluated using classification task based on a $1$-nearest neighbour approach.
+$728$ dimensions.  Quality of the retrieved subspace are evaluated using classification task based on a $1$-nearest neighbour approach.
 
 Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
-Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{fig:wda_gain}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
+Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
 for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
@@
 \includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
-	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor (the budget) in \emph{Screenkhorn}}.
+	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
 	\label{fig:wda}
@@
 used a MNIST to USPS problem in which features have been extracted from the
-feature extractor of domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
+feature extractor of an domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
 Figure \ref{fig:otda} reports the gain in running time for $2$ different values

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 \includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
-	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
 	\label{fig:wda}
@@
 	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl10.pdf}
-	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
+	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
 	\label{fig:otda}

### 2019-05-22 marg_expe_v2.py
update figures

@@ -28,6 +28,16 @@ params = {'axes.labelsize': 24, # 12
 plt.rcParams.update(params)
 plt.close('all')
 
+# SEABORN
+import seaborn as sns
+
+color_pal_t = sns.color_palette("colorblind", 11).as_hex()
+color_pal = color_pal_t.copy()
+
+colors = ["black", "salmon pink", "neon pink", "cornflower","cobalt blue"
+          ,"blue green", "aquamarine", "bright yellow", "golden yellow", "reddish pink" , "reddish purple"]
+color_pal = sns.xkcd_palette(colors)
+
 # WARNINGS
 import warnings
 warnings.filterwarnings("ignore", category=FutureWarning)
@@ -101,18 +111,16 @@ def compare_marginals(a, b, M, reg, decvect = [50, 10, 5, 2, 1.1]):
         b_sc = P_sc.T @ np.ones(a.shape)
         
         # comparisons
-        rel_time_vect[j] = time_bfgs/time_sink
+        rel_time_vect[j] = time_sink/time_bfgs
         diff_a_vect[j]   = norm(a - a_sc, ord=1)
         diff_b_vect[j]   = norm(b - b_sc, ord=1)
         rel_cost_vect[j] = np.abs(np.sum(M*(P_sc - Pstar)))/np.sum(M*Pstar)
         
     return diff_a_vect, diff_b_vect, rel_time_vect, rel_cost_vect
 
-
-
 #%%
 pathres= './resultat/'
-nvect = [500, 1000, 2500]
+nvect = [1000]
 #decvect = [1.1, 1.25, 1.5, 2, 2.5, 5, 10, 20, 50, 100]
 decvect = [1.1, 1.25, 2, 5, 10, 20, 50, 100]
 regvect = [1e-1, 5e-1, 1, 10]
@@ -171,6 +179,8 @@ for n in nvect:
 #%% Plots
 pathfig = './figure/'
 z_crit = stats.norm.ppf(q = 0.975)
+markert = ['o','p','s','d','h','o','p','<','>','8','P']
+colort = color_pal
 for n in nvect:
     print('n samples :',n)
     # filename
@@ -184,10 +194,10 @@ for n in nvect:
     coeff = z_crit/np.sqrt(n_iter)    
     plt.close('all')
     
-    plt.figure(1, figsize=(9, 6))
-    plt.figure(2, figsize=(9, 6))
-    plt.figure(3, figsize=(9, 6))
[…]

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 %	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
-	\includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
-\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
+	\includegraphics[width=0.4\textwidth]{./figs/wda_gain_toy.pdf}
+\includegraphics[width=0.4\textwidth]{./figs/wda_gain_mnist.pdf}
 	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
@@
 
-	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl1.pdf}
-	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl10.pdf}
+	\includegraphics[width=0.42\textwidth]{./figs/da_gain_mnist_regcl1.pdf}
+	\includegraphics[width=0.42\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
 	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}

### 2019-05-22 tex/v3/appendix.tex
seperate suppl

@@
 
-\subsection{Proof of Lemma~\ref{lemma_actives_sets}}
+\section{Proof of Lemma~\ref{lemma_actives_sets}}
 
@@
 
-\subsection{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
+\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
 
@@
 
-\subsection{Proof of Proposition~\ref{proposition_error_in_marginals}}
+\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
 
@@
 
-\subsection{Proof of Proposition~\ref{prop:objective-error}}
+\section{Proof of Proposition~\ref{prop:objective-error}}
 
@@
 
-\subsection{Additional experimental results}
+\section{Additional experimental results}
 

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 %
-\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$).
+\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ``high'' values of the regularization parameter $\eta$ ($\eta > 1$).
 The approximation quality diminishes for small $\eta$.

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 	\begin{center}
-		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_Nu_marginals_toy_n1000} ~\hfill \\
-		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_div_toy_n1000}
+		\includegraphics[width=0.33\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
+		\includegraphics[width=0.33\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} ~\hfill \\
+		\includegraphics[width=0.33\textwidth]{./figs/norm_M_time_toy_n1000} ~\hfill~
+		\includegraphics[width=0.33\textwidth]{./figs/norm_M_div_toy_n1000}
 	\end{center}

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 %	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
-	\includegraphics[width=0.4\textwidth]{./figs/wda_gain_toy.pdf}
-\includegraphics[width=0.4\textwidth]{./figs/wda_gain_mnist.pdf}
+	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}~\hfill~
+	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_mnist.pdf}
 	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
@@
 
-	\includegraphics[width=0.42\textwidth]{./figs/da_gain_mnist_regcl1.pdf}
-	\includegraphics[width=0.42\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
+	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}~\hfill~
+	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
 	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update figures

--- 2019-05-22 tex/v3/section_5_numeric_expes.tex
@@
 	\begin{center}
-		\includegraphics[width=4.55cm]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_Nu_marginals_toy_n1000} ~\hfill \\
-		\includegraphics[width=4.55cm]{./figs/norm_M_time_toy_n1000} ~\hfill~
-		\includegraphics[width=4.55cm]{./figs/norm_M_div_toy_n1000}
+		\includegraphics[width=6cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
+		\includegraphics[width=6cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		\includegraphics[width=6cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
+		\includegraphics[width=6cm]{./figs/norm_M_div_toy_n1000}
 	\end{center}
@@
 Bottom panel: (left) ratio of computation times    $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and, (right) relative divergence variation.
-The results are averaged over 10 trials.}
+The results are averaged over 30 trials.}
 		\label{fig:margin_expe}
@@
 %
-\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ``high'' values of the regularization parameter $\eta$ ($\eta > 1$).
+\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ''high'' values of the regularization parameter $\eta$ ($\eta > 1$).
 The approximation quality diminishes for small $\eta$.
@@
 %	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
-	\includegraphics[width=0.4\textwidth]{./figs/wda_gain_toy.pdf}
-\includegraphics[width=0.4\textwidth]{./figs/wda_gain_mnist.pdf}
+	\includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
+\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
 	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
@@
 
-	\includegraphics[width=0.42\textwidth]{./figs/da_gain_mnist_regcl1.pdf}
-	\includegraphics[width=0.42\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
+	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl1.pdf}
+	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl10.pdf}
 	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}

### 2019-05-22 marg_expe_v2.py

@@ -15,17 +15,17 @@ np.random.seed(3946)
 
 # MATPLOTLIB
 import matplotlib.pyplot as plt
-from matplotlib import rc
-rc('font', **{'family': 'sans-serif', 'sans-serif': ['Computer Modern Roman']})
-params = {'axes.labelsize': 24, # 12
-          'font.size': 24, # 12
-          'legend.fontsize': 22, # 12
-          'xtick.labelsize': 22, # 10
-          'ytick.labelsize': 22, # 10
-          #'text.usetex': True,
-          #'figure.figsize': (8, 6)
-          }
-plt.rcParams.update(params)
+#from matplotlib import rc
+#rc('font', **{'family': 'sans-serif', 'sans-serif': ['Computer Modern Roman']})
+#params = {'axes.labelsize': 34, # 12
+#          'font.size': 24, # 12
+#          'legend.fontsize': 22, # 12
+#          'xtick.labelsize': 32, # 10
+#          'ytick.labelsize': 32, # 10
+#          #'text.usetex': True,
+#          #'figure.figsize': (8, 6)
+#          }
+#plt.rcParams.update(params)
 plt.close('all')
 
 # SEABORN
@@ -214,10 +214,11 @@ for n in nvect:
                          diff_a_mean-diff_a_std*coeff, 
                          facecolor=colort[j], alpha=.15)
         plt.yscale('log')
-        plt.xlabel(r'Decimation factor $n/n_b$')
-        plt.ylabel(r'$\|\|\, \mu - \mu^{sc} \, \|\|_1$')
-        plt.xticks(decvect, decvect, rotation='vertical')
-        plt.title('$n=m=${:d}'.format(n))
+        plt.xlabel(r'Decimation factor $n/n_b$', fontsize = 16)
+        plt.ylabel(r'$\|\|\, \mu - \mu^{sc} \, \|\|_1$', fontsize = 16)
+        plt.xticks(decvect, decvect, rotation='vertical', fontsize = 14)
+        plt.yticks(fontsize=14)
+        plt.title('$n=m=${:d}'.format(n), fontsize = 16)
         
         
         # -------
@@ -233,9 +234,11 @@ for n in nvect:
                          facecolor=colort[j], alpha=.15)
         
         plt.yscale('log')
-        plt.xlabel(r'Decimation factor $m_b/m$')
-        plt.ylabel(r'$\||\, \nu - \nu^{sc} \, \|\|_1$')
[…]

### 2019-05-22 tex/v3/section_4_marginal_viols.tex

@@
 \end{proposition}
-Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma~\ref{lem:pinsker} in supplementary).
+Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma 1 in supplementary).
 Note that $c_\kappa$ and $c_{\frac 1\kappa}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.
@@
 Proof of Proposition~\ref{prop:objective-error} is exposed in the supplementary material.
-Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero as pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
+Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero as the pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
 % section analysis_of_marginal_violations (end)

### 2019-05-22 tex/v3/section_5_numeric_expes.tex

--- 2019-05-22 tex/v3/section_5_numeric_expes.tex
@@
 	\begin{center}
-		\includegraphics[width=0.33\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000} ~\hfill~
-		\includegraphics[width=0.33\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} ~\hfill \\
-		\includegraphics[width=0.33\textwidth]{./figs/norm_M_time_toy_n1000} ~\hfill~
-		\includegraphics[width=0.33\textwidth]{./figs/norm_M_div_toy_n1000}
+		\includegraphics[width=6cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
+		\includegraphics[width=6cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		\includegraphics[width=6cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
+		\includegraphics[width=6cm]{./figs/norm_M_div_toy_n1000}
 	\end{center}
@@
 Top panel: marginal violations in relation with the budget of points.
-Bottom panel: (left) ratio of computation times    $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and, (right) relative divergence variation.
-The results are averaged over 10 trials.}
+Bottom panel: (left) ratio of computation times    $\frac{T_{\text{Sinkhorn}}}{T_{\text{\emph{Screenkhorn}}}}$ and, (right) relative divergence variation.
+The results are averaged over 30 trials.}
 		\label{fig:margin_expe}

### 2019-05-22 tex/v3/supplementary_material.tex

--- 2019-05-16 tex/v3/supplementary_material.tex
@@
 
-\title{Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''}
+\title{Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''}
 
@@
 
-\section{Proof of Lemma~\ref{lemma_actives_sets}}
-
-Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty.
-Introducing two dual variables $\lambda \in \R^n_{+}$ and $\beta \in \R^m_{+}$ for each constraint, the Lagrangian of problem~\eqref{screen-sinkhorn} reads as 
-\begin{equation*}
-  \mathscr{L}(u,v, \lambda, \beta) = \frac \varepsilon\kappa\inr{\lambda, \mathbf{1}_n} + \varepsilon\kappa\inr{\beta, \mathbf{1}_m} + \mathbf{1}_n^\top B(u,v) \mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} -\inr{\lambda,e^{u}} - \inr{\beta,e^{v}}
-\end{equation*}
-First order conditions then yield that the Lagrangian multiplicators solutions $\lambda^{*}$ and $\beta^{*}$ satisfy 
-\begin{align*}
-  &\nabla_u\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{u^{*}} \odot(Ke^{v^{*}} - \lambda^{*}) - \kappa\mu = \mathbf 0_n,\\
-  & \text{ and } \nabla_v\mathscr{L}(u^{*},v^{*}, \lambda^{*}, \beta^{*})=  e^{v^{*}} \odot(K^\top e^{u^{*}} - \beta) - \frac \nu\kappa = \mathbf 0_m
-\end{align*}
-which leads to 
-\begin{align*}
-  &\lambda^{*} = K e^{v^{*}} - \kappa\mu \oslash e^{u^{*}} \text{ and }
-  \beta^{*} = K^\top e^{u^{*}} - \nu \oslash \kappa e^{v^{*}}
-\end{align*}
-
-For all $i=1, \ldots, n$ we have that $e^{u^{*}_i} \geq \varepsilon\kappa^{-1}$.
-Further, the condition on the dual variable $\lambda^{*}_i > 0$  ensures that $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and hence $i \in I^\complement_{\varepsilon,\kappa}$.
-We have that $\lambda^{*}_i > 0$ is equivalent to $e^{u^{*}_i}r_i(K) e^{v^{*}_j} >  \kappa{\mu_i}$ which  is satisfied when $\varepsilon^2r_i(K) >  \kappa{\mu_i}.$
-In a symmetric way we can prove the same statement for $e^{v^{*}_j}$.
-
-\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}
-
-We prove only the first statement~\eqref{bound_on_u} and similarly we can prove the second one~\eqref{bound_on_v}.
-For all $i\in I_{\varepsilon,\kappa}$, we have $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ or $e^{u^{\text{sc}}_i} = \frac \varepsilon\kappa$.
-In one hand, if $e^{u^{\text{sc}}_i} > \frac \varepsilon\kappa$ then according to the optimality conditions $\lambda^{\text{sc}}_i = 0,$ which implies $e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i$.
-In another hand, we have 
-\begin{align*}
-e^{u^{\text{sc}}_i} \min_{i,j}K_{ij} \sum_{j=1}^m e^{v^{\text{sc}}_j} \leq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} = \kappa\mu_i.
-\end{align*}
-We further observe that $\sum_{j=1}^m e^{v^{\text{sc}}_j} = \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} \geq \varepsilon\kappa |J_{\varepsilon,\kappa}| + \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}|=\varepsilon\kappa m.$ Then
-\begin{equation*}
-\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
-\end{equation*}
-Analogously, one can obtain for all $j\in J_{\varepsilon,\kappa}$
-\begin{equation}
-\label{upper_bound_v_potential}
-\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
-\end{equation}
-
-Now, since $K_{ij} \leq 1$, we have 
-\begin{align*}
-e^{u^{\text{sc}}_i} \sum_{j=1}^m e^{v^{\text{sc}}_j} \geq e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij}e^{v^{\text{sc}}_j} = \kappa\mu_i.
-\end{align*}
-Using~\eqref{upper_bound_v_potential}, we get 
-\begin{align*}
-\sum_{j=1}^m e^{v^{\text{sc}}_j} &= \sum_{j \in J_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j} + \sum_{j \in J^\complement_{\varepsilon,\kappa}} e^{v^{\text{sc}}_j}
-\leq \varepsilon\kappa |J^\complement_{\varepsilon,\kappa}| + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} |J_{\varepsilon,\kappa}|.
-\end{align*}
-Therefore,
-\begin{align*}
-\min_{i \in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i}  \geq \frac \varepsilon\kappa \vee \frac{\kappa\min_{I_{\varepsilon,\kappa}}\mu_i}{\varepsilon\kappa (m-m_b) + \varepsilon\kappa \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} m_b}.
-\end{align*}
-
-\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
-
-The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
-\begin{align}
-\label{i-th-marginal-mu} %=({B}({u}^{\text{sc}},{v}^{\text{sc}})\mathbf 1_m)_i
-{\mu}^{\text{sc}}_i  &= 
-\begin{cases}
-e^{u^{\text{sc}}_i} \sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I_{\varepsilon,\kappa},\\
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}
-\end{cases}
-=\begin{cases}
-\kappa \mu_i, \text{ if  }i \in I_{\varepsilon,\kappa},\\
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}, \text{ if  }i \in I^\complement_{\varepsilon,\kappa}.
-\end{cases}
-\end{align}
-Using inequality~\eqref{bound_on_v}, we obtain 
-\begin{align*}
-\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
-& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
-\end{align*}
-
-Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
-
-\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
-
-We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
-While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
-The violations are computed through the following function: 
-\begin{equation*}
-	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
-\end{equation*}
-Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
-The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
-\begin{lemma}
-\label{lem:pinsker}
-For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
-\begin{align*}
-\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
-\end{align*}
-\end{lemma}
-Straightforward, 
-\begin{align*}
-d_\varrho({\mu} ,{\mu}^{\text{sc}}) &= \sum_{i=1}^n  {\mu}^{\text{sc}}_i - {\mu}_i + {\mu}_i  \log\Big(\frac{{\mu}_i}{{\mu}^{\text{sc}}_i }\Big)\\
-&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-1)\mu_i - \mu_i\log(\kappa) + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&= \sum_{i\in I_{\varepsilon,\kappa}} (\kappa-\log(\kappa)-1)\mu_i  + \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq  \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)
-\end{align*}
-Using~\eqref{bound_on_v}, we have in one hand 
-\begin{align*}
-\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&= \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\leq \sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa \Big(m_b \max_{i,j}K_{ij}\frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} + (m - m_b)\varepsilon\kappa\max_{i,j}K_{ij}\Big) \\
-&\leq (n-n_b)\Big(\frac{m_b\max_{j} \nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2\Big).
-\end{align*}
-On the other hand, we get
-\begin{align*}
-\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}&=\frac \varepsilon\kappa \Big(\sum_{j\in J_{\varepsilon,\kappa}}K_{ij} e^{v^{\text{sc}}_j} + \varepsilon \kappa\sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-&\geq m_bK_{\min} \frac{m\varepsilon^2K_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min} + m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
-&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
-&\geq \frac{mm_b\varepsilon^2(K_{\min})^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}\\
-&\qquad +\varepsilon^2 (m- m_b) K_{\min}\\
-&\geq \frac{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}.
-\end{align*}
-Then 
-\begin{align*}
-\frac{1}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}} &\leq \frac{\kappa((n-n_b)m\varepsilon^2K_{\min}+ m\varepsilon^2K_{\min} + \kappa\max_{i\in I_{\varepsilon,\kappa}}\mu_i)}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\\
-&\leq \frac{\kappa(n-n_b+ 1)}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}.
-\end{align*}
-It entails 
-\begin{align*}
-&\sum_{i\in I^\complement_{\varepsilon,\kappa}}\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j} - \mu_i + \mu_i \log\Big(\frac{\mu_i}{\frac \varepsilon\kappa\sum_{j=1}^m K_{ij} e^{v^{\text{sc}}_j}}\Big)\\
-&\leq (n-n_b)\bigg(\frac{m_b}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i}\mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i}\mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i}\mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big)
-\bigg).
-\end{align*}
-Therefore
-\begin{align*}
-d_\varrho({\mu},{\mu}^{\text{sc}}) &\leq n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + (n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&\qquad + \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2 K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
-\end{align*}
-Finally, by Lemma~\ref{lem:pinsker} we obtain
-\begin{align*}
-\norm{{\mu}^\star -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{\kappa^2\max_{i} \mu_i}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
-\end{align*}
-Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
-
+\input{appendix.tex}
 \small

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
customize figures

@@
 	\begin{center}
-		\includegraphics[width=6cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
-		\includegraphics[width=6cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
-		\includegraphics[width=6cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
-		\includegraphics[width=6cm]{./figs/norm_M_div_toy_n1000}
+		% \includegraphics[width=6cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
+		% \includegraphics[width=6cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		% \includegraphics[width=6cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
+		% \includegraphics[width=6cm]{./figs/norm_M_div_toy_n1000}
+		% 
+		\includegraphics[width=0.35\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
+		\includegraphics[width=0.35\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		\includegraphics[width=0.35\textwidth]{./figs/norm_M_time_toy_n1000}\hspace{2cm}
+		\includegraphics[width=0.35\textwidth]{./figs/norm_M_div_toy_n1000}
 	\end{center}
@@
 %	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
-	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}~\hfill~
+	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}\hspace{1.5cm}
 	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_mnist.pdf}
@@
 
-	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}~\hfill~
+	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
 	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 Bottom panel: (left) ratio of computation times    $\frac{T_{\text{Sinkhorn}}}{T_{\text{\emph{Screenkhorn}}}}$ and, (right) relative divergence variation.
-The results are averaged over 30 trials.}
+The results are averaged over $30$ trials.}
 		\label{fig:margin_expe}
@@
 Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.
-According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to 1.
+According to computation gain, \emph{Screenkhorn} is, up to $2$ times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to $1$.
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.

### 2019-05-22 tex/v3/section_1_introduction.tex
update suppl

@@
 Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\citet{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
+Furthermore, ~\citet{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
 Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update suppl

@@
 
-Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Sinkhorn} problem.
-Analysis of the quality of the subspace have been deported to the supplementary material (see Figure \ref{}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
+Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Screenkorn} problem.
+Analysis of the quality of the subspace have been deported to the supplementary material (see Figure 1), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
 for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_mnist.pdf}
-	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
+	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for MNIST as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
 	\label{fig:wda}
@@
 	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
-	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
+	\caption{OT Domain adaptation : running time gain for a toy dataset and for MNIST as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
 	\label{fig:otda}

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

--- 2019-05-22 tex/v3/section_5_numeric_expes.tex
@@
 	\begin{center}
-		% \includegraphics[width=6cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
-		% \includegraphics[width=6cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
-		% \includegraphics[width=6cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
-		% \includegraphics[width=6cm]{./figs/norm_M_div_toy_n1000}
-		% 
-		\includegraphics[width=0.35\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
-		\includegraphics[width=0.35\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} \\
-		\includegraphics[width=0.35\textwidth]{./figs/norm_M_time_toy_n1000}\hspace{2cm}
-		\includegraphics[width=0.35\textwidth]{./figs/norm_M_div_toy_n1000}
+		\includegraphics[width=4.5cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
+		\includegraphics[width=4.5cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		\includegraphics[width=4.5cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
+		\includegraphics[width=4.5cm]{./figs/norm_M_div_toy_n1000}
 	\end{center}
@@
 Bottom panel: (left) ratio of computation times    $\frac{T_{\text{Sinkhorn}}}{T_{\text{\emph{Screenkhorn}}}}$ and, (right) relative divergence variation.
-The results are averaged over $30$ trials.}
+The results are averaged over 30 trials.}
 		\label{fig:margin_expe}
@@
 Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.
-According to computation gain, \emph{Screenkhorn} is, up to $2$ times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to $1$.
+According to computation gain, \emph{Screenkhorn} is almost  2 times faster than Sinkhorn at high decimation factor $n/n_b$ (low budget) while the reverse holds when $n/n_b$ gets close to 1.
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
-Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
+Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a  divergence $\inr{C, P}$ close to the one of Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
+\emph{Screenkhorn} will be practically useful in cases when modest accuracy on the divergence is sufficient as a loss function a gradient descent method optimizes over.
 
@@
 
-In this subsection, we analyse the impact of using \emph{Screenkhorn}
+Here, we analyse the impact of using \emph{Screenkhorn}
 instead of Sinkhorn in a complex machine learning pipeline. Our two applications
@@
 %	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
-	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}\hspace{1.5cm}
+	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}~\hfill~
 	\includegraphics[width=0.39\textwidth]{./figs/wda_gain_mnist.pdf}
@@
 
-	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
+	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}~\hfill~
 	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}

### 2019-05-22 marg_expe_v2.py

@@ -214,11 +214,11 @@ for n in nvect:
                          diff_a_mean-diff_a_std*coeff, 
                          facecolor=colort[j], alpha=.15)
         plt.yscale('log')
-        plt.xlabel(r'Decimation factor $n/n_b$', fontsize = 16)
-        plt.ylabel(r'$\|\|\, \mu - \mu^{sc} \, \|\|_1$', fontsize = 16)
-        plt.xticks(decvect, decvect, rotation='vertical', fontsize = 14)
-        plt.yticks(fontsize=14)
-        plt.title('$n=m=${:d}'.format(n), fontsize = 16)
+        plt.xlabel(r'Decimation factor $n/n_b$', fontsize = 30)
+        plt.ylabel(r'$\|\|\, \mu - \mu^{sc} \, \|\|_1$', fontsize = 30)
+        plt.xticks(decvect, decvect, rotation='vertical', fontsize = 26)
+        plt.yticks(fontsize=26)
+        plt.title('$n=m=${:d}'.format(n), fontsize = 30)
         
         
         # -------
@@ -234,11 +234,11 @@ for n in nvect:
                          facecolor=colort[j], alpha=.15)
         
         plt.yscale('log')
-        plt.xlabel(r'Decimation factor $m_b/m$', fontsize = 16)
-        plt.ylabel(r'$\||\, \nu - \nu^{sc} \, \|\|_1$', fontsize = 16)
-        plt.xticks(decvect, decvect, rotation='vertical', fontsize = 14)
-        plt.yticks(fontsize=14)
-        plt.title('$n=m=${:d}'.format(n), fontsize = 16)
+        plt.xlabel(r'Decimation factor $m_b/m$', fontsize = 30)
+        plt.ylabel(r'$\||\, \nu - \nu^{sc} \, \|\|_1$', fontsize = 30)
+        plt.xticks(decvect, decvect, rotation='vertical', fontsize = 26)
+        plt.yticks(fontsize=26)
+        plt.title('$n=m=${:d}'.format(n), fontsize = 30)
         
         
         # -------
@@ -253,11 +253,11 @@ for n in nvect:
                          rel_time_mean-rel_time_std*coeff, 
                          facecolor=colort[j], alpha=.15)
         #plt.yscale('log')
-        plt.xlabel(r'Decimation factor $n/n_b$', fontsize = 16)
-        plt.ylabel('Running Time Gain', fontsize = 16)
[…]

### 2019-05-22 tex/v3/section_1_introduction.tex

--- 2019-05-21 tex/v3/section_1_introduction.tex
@@
 Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore,~\citet{cuturinips13} proposed the so-called {dual of Sinkhorn divergence} as the dual of the entropic problem and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
+Furthermore, the dual of the entropic problem, referred to as {dual of Sinkhorn divergence}, was studied in~\cite{cuturinips13} and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
 Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.
@@
 The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
-\citet{altschulernips17} proposed a greedy version of Sinkhorn, called Greenkhorn algorithm, allowing to select columns and rows to be updated that most violate the constraints.                   
+A greedy version of Sinkhorn, called Greenkhorn algorithm and proposed in~\cite{altschulernips17}, allows to select columns and rows to be updated that most violate the constraints.                   
 Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\citep{altschuler2018Nystrom}. 

### 2019-05-22 tex/v3/section_5_numeric_expes.tex

--- 2019-05-22 tex/v3/section_5_numeric_expes.tex
@@
 	\begin{center}
-		% \includegraphics[width=6cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{9pt}
-		% \includegraphics[width=6cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
-		% \includegraphics[width=6cm]{./figs/norm_M_time_toy_n1000} \hspace*{9pt}
-		% \includegraphics[width=6cm]{./figs/norm_M_div_toy_n1000}
-		% 
 		\includegraphics[width=0.35\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
@@
 Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.
-According to computation gain, \emph{Screenkhorn} is, up to $2$ times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to $1$.
+According to computation gain, \emph{Screenkhorn} is almost  2 times faster than Sinkhorn at high decimation factor $n/n_b$ (low budget) while the reverse holds when $n/n_b$ gets close to 1.
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
-Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
+Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a  divergence $\inr{C, P}$ close to the one of Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
+\emph{Screenkhorn} will be practically useful in cases when modest accuracy on the divergence is sufficient as a loss function a gradient descent method optimizes over (see next section).
 

### 2019-05-22 tex/v3/supplementary_material.tex
update suppl
update

--- 2019-05-17 tex/v3/supplementary_material.tex
@@
 \begin{equation*}
-\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
+\max_{i\in I_{\varepsilon,\kappa}} e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa \vee \frac{\max_{i\in I_{\varepsilon,\kappa}}\mu_i}{m\varepsilon K_{\min}}.
 \end{equation*}
@@
 \label{upper_bound_v_potential}
-\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}} .
+\max_{j\in J_{\varepsilon,\kappa}}e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min}}.
 \end{equation}
@@
 
-\section{Proof of Lemma~\ref{lemma_bounds_on_marginals}}
+\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
 
-The optimality condition for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
+We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
+While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
+The violations are computed through the following function: 
+\begin{equation*}
+	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
+\end{equation*}
+Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
+The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
+\begin{lemma}
+\label{lem:pinsker}
+For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
+\begin{align*}
+\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}.
+\end{align*}
+\end{lemma}
+
+The optimality conditions for $({u}^{\text{sc}}, {v}^{\text{sc}})$ entails 
 \begin{align}
@@
 
-Using inequality~\eqref{bound_on_v}, we obtain 
-\begin{align*}
-\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
-& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
-\end{align*}
-Again by left-hand-side of inequaltiy~\eqref{bound_on_v}, we arrive at 
-\begin{align*}
-\norm{\mu^{\text{sc}}}_1 %&= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
-%& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
-& \overset{}{\geq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n -n_b) \Big(\frac{mm_b\varepsilon^2 K_{\min}^2 \min_{j\in J_{\varepsilon, \kappa}} \nu_j}{ (n-n_b)m\kappa \varepsilon^2 K_{\min} + n_b\kappa^2 \max_{i\in I_{\varepsilon,\kappa}}\mu_i }+ (m-m_b)\varepsilon^2K_{\min}\Big),
-\end{align*}
-which gives the claimed result.
-Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
-
-\section{Proof of Proposition~\ref{proposition_error_in_marginals}}
-
-We define the distance function $\varrho: \R_+ \times \R_+ \mapsto [0, \infty]$ by $\varrho(a,b) = b - a + a \log(\frac ab).$
-While $\varrho$ is not a metric, it is easy to see that $\varrho$ is not nonnegative and satisfies $\varrho(a,b) =0$ iff $a=b$.
-The violations are computed through the following function: 
-\begin{equation*}
-	d_{\varrho}(\gamma,\beta) = \sum_{i=1}^n \varrho(\gamma_i,\beta_i), \text{ for } \gamma, \beta \in \R^n_+.
-\end{equation*}
-Note that if $\gamma,\beta$ are two vectors of positive entries, $d_{\varrho}(\gamma,\beta)$ will return some measurement on how far they are from each other.
-The next Lemma is from~\cite{khalilabid2018} (see Lemma 7 herein).
-\begin{lemma}
-\label{lem:pinsker}
-For any $\gamma, \beta \in \R^n_+$, the following generalized Pinsker inequality holds 
-\begin{align*}
-\norm{\gamma - \beta}_1 \leq \sqrt{7 (\norm{\gamma}_1\wedge \norm{\beta}_1)d_{\varrho}(\gamma,\beta)}
-\end{align*}
-\end{lemma}
 By~\eqref{i-th-marginal-mu}, we have
@@
 \begin{align*}
-\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_b(\kappa-\log(\kappa)-1)\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa\min_{i,j} K_{ij}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
-&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).%\bigg\}^{1/2}
+\norm{{\mu} -{\mu}^{\text{sc}}}^2_1 \leq & n_bc_{\kappa}\max_{i} \mu_i + 7(n-n_b)\bigg(\frac{m_b\max_{j}\nu_j}{n\kappa K_{\min}} + (m- m_b) \varepsilon^2 - \min_{i}\mu_i\\
+&+ \max_{i} \mu_i\log\Big(\frac{\kappa(n-n_b+ 1)\max_{i} \mu_i}{m_bK_{\min}\min_{j \in J_{\varepsilon,\kappa}}\nu_j} + \frac{n_b\kappa^2(\max_{i} \mu_i)^2}{mm_b\varepsilon^2K_{\min}^2\min_{j \in J_{\varepsilon,\kappa}}\nu_j}\Big).
 \end{align*}
-Proof of the upper bound for $\norm{\nu - {\nu}^{\text{sc}}}^2_1$ follows the same lines as above.
+Following the same lines as above, we also have
+\begin{align*}
+\norm{{\nu} -{\nu}^{\text{sc}}}^2_1 \leq & m_bc_{\frac 1\kappa}\max_{i} \mu_i + 7(m-m_b)\bigg(\frac{n_b\kappa\max_{i}\mu_i}{mK_{\min}} + (n- n_b) \varepsilon^2 - \min_{j}\nu_j\\
+&+ \max_{j} \nu_j\log\Big(\frac{(m-m_b+ 1)\max_{j} \nu_j}{n_b\kappa K_{\min}\min_{i \in I_{\varepsilon,\kappa}}\mu_i} + \frac{m_b(\max_{j} \nu_j)^2}{nn_b\varepsilon^2\kappa^2K_{\min}^2\min_{i \in I_{\varepsilon,\kappa}}\mu_i}\Big).%\bigg\}^{1/2}
+\end{align*}
+To get the closed forms~\eqref{marginal-error-mu} and~\eqref{marginal-error-nu}, we used the follwoing facts:
+\begin{remark}
+\label{rem:orders_of_epsilonappa}
+ We have 
+$\varepsilon = \bigO((mnK_{\min}^2)^{-1/4})$, $\kappa= \bigO(\sqrt{m/(nc_{\mu\nu}K_{\min})}),$ $\kappa^{-1} = \bigO(\sqrt{n/(mK_{\min}c_{\mu\nu}})$, $(\kappa/\varepsilon)^2 = \bigO( m^{3/2} / \sqrt{nK_{\min}}(c_{\mu\nu})^{3/2})$, and $(\varepsilon\kappa)^{-2} = \bigO(n^{3/2}/\sqrt{mK_{\min}}c^{3/2}_{\mu\nu}).$
+\end{remark}
 
+\section{Proof of Proposition~\ref{prop:objective-error}}
+
+We first define $\widetilde{K}$ a rearrgement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
+\begin{equation*}
+\widetilde{K} = 
+\begin{bmatrix}
+K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
+K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &K_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
+\end{bmatrix}.
+\end{equation*}
+Setting $\dt{\mu} = (\mu_{I_{\varepsilon,\kappa}}^\top, \mu_{I^\complement_{\varepsilon,\kappa}}^\top)^\top$, $\dt{\nu} = (\nu_{J_{\varepsilon,\kappa}}^\top, \nu_{J^\complement_{\varepsilon,\kappa}}^\top)^\top$ and for each vectors $u \in \R^n$ and $v\in \R^m$ we set $\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top  \text{ and } \dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top.$
+We then have 
+\begin{equation*}
+\Psi_{\varepsilon, \kappa} (u,v) = \mathbf 1_n^\top \widetilde{K}(\dt{u}, \dt{v}) \mathbf 1_m - \kappa \dt{\mu}^\top \dt{u} - \kappa^{-1} \dt{\nu}^\top \dt{v},
+\end{equation*}
+and 
+\begin{equation*}
+\Psi_{} (u,v) = \mathbf 1_n^\top \widetilde{K}(\dt{u}, \dt{v}) \mathbf 1_m - \dt{\mu}^\top \dt{u} - \dt{\nu}^\top \dt{v},
+\end{equation*}
+where
+\begin{equation*}
+  \widetilde{B}(\dt{u}, \dt{v}) = \Delta(e^{\dt{u}})\widetilde{K} \Delta(e^{\dt{v}}).
+\end{equation*}
+Let us consider the convex function
+\begin{equation*}
+	(\hat u, \hat v) \mapsto \inr{\mathbf 1_n, \widetilde{B}(\dt{\hat u}^{\text{}} ,\dt{\hat v}^{\text{}})\mathbf 1_m} - \inr{\kappa\dt{\hat u}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{\hat v}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
+\end{equation*}
+Gradient inequality of any convex function g at point $x_o$ reads as $g(x_o) \geq g(x) + \inr{\nabla g(x), x_o - x}, \text{ for all } x \in \textbf{dom}(g).$
+Applying the latter fact to the above function at point ($u^{\star}, v^{\star})$ we obtain
+\begin{align*}
+\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} &- \inr{\kappa\dt{u}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+& - \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
+&\qquad \qquad  \leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
+\end{align*}
+Moreover,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&= \inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}, \widetilde{B}(\dt{u}^{\text{sc}}, \dt{v}^{\text{sc}})\mathbf 1_n^\top}\\
+&\qquad - \big( 
+\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
+&\qquad + \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}.
+\end{align*}
+Hence,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
++& \big( \inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m} \\
+&- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)\\
+& \qquad -\inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} -\inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
+& \leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\qquad + \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big).
+\end{align*}
+Then,
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&\leq \inr{\dt{u}^{\text{sc}} - \dt{u}^\star, (1-\kappa) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
++ \inr{\dt{v}^{\text{sc}} - \dt{v}^\star, (1-\kappa^{-1}) \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\qquad + \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\kappa\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\kappa^{-1}\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n} \big)
+\\
+&\qquad + \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
+&\qquad - \big(\inr{\mathbf 1_n, \widetilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
+- \inr{\dt{u}^{\star{}}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} 
+- \inr{\dt{v}^\star, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top \mathbf 1_n} \big),
+\end{align*}
+which yields 
+\begin{align*}
+\Psi_{\varepsilon, \kappa} (u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&\leq  \inr{\kappa \dt{u}^{\text{sc}} - \dt{u}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}} +\inr{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^{\star}, \widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}.
+\end{align*}
+Applying Holder's inequality gives 
+\begin{align*}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
+&\leq \norm{\kappa \dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\leq \norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+\end{align*}
+Note that
+\begin{align*}
+\begin{cases}
+\norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty = \norm{{u}^{\text{sc}} - {u}^\star}_\infty,\\
+\norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty = \norm{{v}^{\text{sc}} - {v}^\star}_\infty,
+\end{cases}
+\text{ and }
+\begin{cases}
+\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 = \norm{{B}({u}^{\text{sc}} ,{v}^{\text{sc}})\mathbf 1_m - {\mu}}_1 = \norm{\mu^{\text{sc}} - \mu}_1,\\
+\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1 = \norm{{B}({u}^{\text{sc}} ,{v}^{\text{sc}})^\top\mathbf 1_n - {\nu}}_1 = \norm{\nu^{\text{sc}} - \nu}_1.
+\end{cases}
+\end{align*}
+Then
+\begin{align}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) &
+\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty \norm{\nu^{\text{sc}} - \nu}_1\nonumber\\
+&\qquad + (1- \kappa)\inr{{u}^{\text{sc}} ,{\mu}^{\text{sc}}} + (1- \kappa^{-1})\inr{{v}^{\text{sc}} ,{\nu}^{\text{sc}}}\nonumber\\
+&\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty\norm{\nu^{\text{sc}} - \nu}_1 \nonumber\\
+&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{priori_bounds_induction}
+\end{align}
+
+\paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.
+
+If $r \in I^\complement_{\varepsilon, \kappa}$, then we have 
+\begin{align*}
+|({u}^{\text{sc}})_{r} - {u}^\star_r| 
+&= \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m \frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
+& \overset{(\star)}{\leq} \bigg|\log\bigg(\max_{1\leq i \leq m} \frac{K_{rj}e^{v^\star_j}}{\frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
+& \leq \big|\max_{1\leq j \leq m} (v_j^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})\big|\\
+& \leq \norm{v^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
+& \leq \norm{v^\star - {v}^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}}).
+\end{align*}
+where the inequality $(\star)$ comes from the fact that $\frac{\sum_{j=1}^na_j}{\sum_{j'=1}^nb_{j'}} \leq \max_{1\leq j \leq n} \frac{a_j}{b_j}, \forall a_j, b_j>0.$
+Now, if $r \in I_{\varepsilon, \kappa}$, we get 
+\begin{align*}
+|{u}^{\text{sc}}_{r} - {u}^\star_r|
+= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
+\leq \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}})_j}}\bigg)\bigg|
+\overset{(\star)}{\leq}\norm{v^{\text{sc}} - v^\star}_\infty.
+\end{align*}
+If $s \in J^\complement_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|{v}^{\text{sc}}_{s} - {v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
+& \leq \bigg|\log\bigg(\max_{1\leq i \leq n} \frac{K_{is}e^{u^\star_i}}{\frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
+& \overset{(\star)}{\leq} \big|\max_{1\leq i \leq n} (u_i^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})\big|\\
+& \leq \norm{u^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})}_\infty \\
+& \leq \norm{u^\star - u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}).
+\end{align*}
+If $s \in J_{\varepsilon, \kappa}$ then 
+\begin{align*}
+|{v}^{\text{sc}}_{s} - {v}^\star_s| 
+= \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{u^\star_i}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
+ \leq \bigg|\log\bigg(\frac{\kappa\sum_{i=1}^m K_{ri}e^{v^\star_j}}{\sum_{i=1}^m K_{ri}e^{(u^{\text{sc}})_i}}\bigg)\bigg|
+\overset{(\star)}{\leq} \norm{u^{\text{sc}} - u^\star}_\infty.
+\end{align*}
+Therefore, we obtain the followoing bound:
+\begin{align}
+\label{induction_uppers_bounds}
+\max\{\norm{u^\star - u^{\text{sc}}}_\infty, \norm{v^\star - v^{\text{sc}}}_\infty\} %&\leq \max\{\norm{u^\star - u^{\text{sc}}_0}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star - v^{\text{sc}}_0}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\}\nonumber\\
+&\leq \max\Big\{\norm{u^\star}_\infty + \norm{u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star}_\infty + \norm{v^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\Big\}\nonumber\\
+&\leq 2\Big(\norm{u^\star}_\infty + \norm{v^\star}_\infty +  \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}}\big)\Big).
+\end{align}
+%where we used $u^{\text{sc}}_0 = \mathbf 0_n$ and $v^{\text{sc}}_0 = \mathbf 0_m.$ 
+Now, Lemma 3.2 in~\cite{lin2019} provides an upper bound for the $\ell_\infty$ of the optimal solution pair $(u^\star, v^\star)$ of problem~\eqref{sinkhorn-dual} as follows:
+$\norm{u^\star}_\infty \leq R$ and $\norm{v^\star}_\infty\leq R,$ where 
+\begin{align}
+\label{R_constant}
+R = \frac{\norm{C}_\infty}{\eta} + \log\big(\frac{n\vee m}{c^2_{\mu\nu}}\big).
+\end{align}
+Plugging~\eqref{induction_uppers_bounds} and~\eqref{R_constant} in~\eqref{priori_bounds_induction}, we obtain
+\begin{align}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
+&\leq 2\big(R + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
+&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{post_bounds_induction_2}
+\end{align}
+By Proposition~\ref{prop:bounds_of_usc_and_vsc}, we have 
+\begin{align*} %\max_{i \in I_{\varepsilon,\kappa}} \mu_i %\max_{j \in J_{\varepsilon,\kappa}} \nu_j
+\norm{u^{\text{sc}}}_\infty \leq \log\big(\frac \varepsilon\kappa\vee \frac{1}{m\varepsilon K_{\min}}\big) \text{ and } \norm{v^{\text{sc}}}_\infty \leq \log\big(\varepsilon\kappa \vee \frac{1}{n\varepsilon K_{\min} }\big)
+\end{align*}
+and hence by Remark~\ref{rem:orders_of_epsilonappa}, 
+\begin{equation*}
+\norm{u^{\text{sc}}}_\infty = \bigO\big(\log({n^{1/4}}/{(mK_{\min})^{3/4}c_{\mu\nu}^{1/4}})\big) \text{ and }\norm{u^{\text{sc}}}_\infty =\bigO\big(\log({m^{1/4}}/{(nK_{\min})^{3/4}c_{\mu\nu}^{1/4}})\big).
+\end{equation*}
+Hence, we have 
+\begin{align*}
+R + \norm{u^{\text{sc}}}_\infty  + \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) = \bigO\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big).
+\end{align*}
+Letting $\omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1,$
+Moreover, we have 
+\begin{align*}
+\omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1
+\end{align*}
+We arrive at 
+\begin{align*}
+\Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
+& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1) + \omega_{\kappa}\Big).
+\end{align*}
+Note that $\omega_{\kappa}$ tends to zeros as $(n_b,m_b)$ tends to $(n,m)$ (i.e., $\kappa \rightarrow 1)$. To more characterize $\omega_\kappa$, the following 
+lemma expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 
+\begin{lemma}
+\label{lemma_bounds_on_marginals}
+Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}.
+Then one has 
+\begin{align}
+\label{l1-norm-mu-sc}
+\norm{\mu^{\text{sc}}}_1 = \bigO\Big(\frac{n_b\sqrt{m}}{\sqrt{nK_{\min}c_{\mu\nu}}} + (n-n_b)\Big(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} + \frac{m-m_b}{\sqrt{nm}K_{\min}}\Big)\Big),
+\end{align}
+and
+\begin{align}
+\label{l1-norm-nu-sc}
+\norm{\nu^{\text{sc}}}_1 = \bigO\Big(\frac{m_b\sqrt{n}}{\sqrt{mK_{\min}c_{\mu\nu}}} + (m-m_b)\Big(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} + \frac{n-n_b}{\sqrt{nm}K_{\min}}\Big)\Big).
+\end{align}
+\end{lemma}
+
+\begin{proof}
+Using inequality~\eqref{bound_on_v}, we obtain 
+\begin{align*}
+\norm{\mu^{\text{sc}}}_1 &= \sum_{i \in I_{\varepsilon,\kappa}} \mu^{\text{sc}}_i +  \sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu^{\text{sc}}_i\\
+& \overset{\eqref{i-th-marginal-mu}}{=} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + \frac \varepsilon\kappa \sum_{i \in I^\complement}\Big( \sum_{j \in J_{\varepsilon,\kappa}} K_{ij} e^{v^{\text{sc}}_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{ij}\Big)\\
+& \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
+% &\leq n_b\kappa + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
+\end{align*}
+Using Remark~\ref{rem:orders_of_epsilonappa}, we get the desired closed form in~\eqref{l1-norm-mu-sc}.
+Similarly, we can prove the same statement for $\norm{\nu^{\text{sc}}}_1$.
+\end{proof}
+
+\section{Additional experimental results}
+
+\begin{figure*}[htbp]
+	\centering
+	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/wda_accur_toy.pdf}~\hfill~
+	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
+	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem and, (right) MNIST).
+We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance.
+		\label{fig:wda_gain}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+	\centering
+	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~
+	\includegraphics[width=6.cm]{./figs/da_accur_toy_regcl100.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_time_toy_regcl100.pdf}
+	~\hfill~\includegraphics[width=6.cm]{./figs/da_gain_toy_regcl100.pdf}~\hfill~\\
+	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem.
+(top-left) Examples of source and target samples.
+(top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples.
+(bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
+	factors.
+(bottom-right).
+Gain in computation time.
+This toy problem is a problem in which classes are overlapping and distance between samples are rather limited.
+According to our analysis, this may be a situation in which \emph{Screenkhorn} may
+	result in smaller computational gain. We can remark that with respect to the accuracy
+	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance.
+Regarding computational time, for this example, small decimation factors does not  result in gain.
+However for above  $5$-factor decimation, the gain goes from  $2$ to $10$ depending on
+	the number of samples. 
+	\label{fig:otda:extra}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
+	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$.
+Note that this
+	value impacts the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
+	also report the performance of a $1$-NN when no-adaptation is performed.  
+	We remark that the strenght of the class-based regularization has influence on the performance of \emph{Screenkhorn} given a decimation factor.
+For small value on the left, \emph{Screenkhorn} slightly performs better than Sinkhorn, while for large value, some
+	decimation factors leads to loss of performances.
+	Regarding, running time, we can note that Sinkhorn is far less efficient than
+	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
+	\label{fig:otda:mnist:extra}}
+\end{figure*}
+
+\newpage
 \small

### 2019-05-22 tex/v3/section_4_marginal_viols.tex
update

@@
 \end{proposition}
-Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma 1 in supplementary).
+Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma~\ref{lem:pinsker} in supplementary).
 Note that $c_\kappa$ and $c_{\frac 1\kappa}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 
-We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
+We compare \emph{Screenkhorn} to Sinkhorn as implemented in POT toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example.
 The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means.

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
running time

@@
 % and, whether the cost matrix $C$ is normalized or not.
- We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
+ We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{Sinkhorn}}}{T_{\text{\emph{Screenkhorn}}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
 Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings.

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

@@
 Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Screenkorn} problem.
-Analysis of the quality of the subspace have been deported to the supplementary material (see Figure 1), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
+Analysis of the quality of the subspace have been deported to the supplementary material (see Figure~\ref{fig:wda_gain}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
 for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
@@
 
-For the optimal transport based domain adaptation problem, we have considered the
+For the OT based domain adaptation problem, we have considered the
 OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 

### 2019-05-22 tex/v3/section_1_introduction.tex
small modif intro

@@
 Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-Furthermore, the dual of the entropic problem, referred to as {dual of Sinkhorn divergence}, was studied in~\cite{cuturinips13} and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
-Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.
+%Furthermore, the dual of the entropic problem, referred to as {dual of Sinkhorn divergence}, was studied in~\cite{cuturinips13} and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
+More importantly, this regularized OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.
 
-Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
+%Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
+%The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
+Several works have considered further improvements in the resolution of this regularized OT problem.
 A greedy version of Sinkhorn, called Greenkhorn algorithm and proposed in~\cite{altschulernips17}, allows to select columns and rows to be updated that most violate the constraints.                   
@@
 that a  transport plan resulting from an OT problem is sparse or presents a large
-number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization.
+number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization while not altering too much the solution of the problem.
 Within this global context, our contributions are the following:

### 2019-05-22 tex/v3/section_3_algorithm.tex
update
customize figures
small modif intro

@@
 
-\begin{wrapfigure}{o}{0.44\textwidth}
+\begin{wrapfigure}{o}{0.4\textwidth}
 \vspace{-15pt}
 \centering
-\includegraphics[width=0.45\textwidth]{./figs/motivations.pdf}
+\includegraphics[width=0.4\textwidth]{./figs/motivations.pdf}
 \caption{Plots of $(e^{u^\star}, e^{v^\star})$ with $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} and the thresholds $\alpha_u, \alpha_v$.}
@@
 
-The key idea of our approach is motivated by the so-called \emph{static screening test}~\citep{Ghaoui2010SafeFE} in supervised learning, which is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector.
+The key idea of our approach is motivated by the so-called \emph{static screening test}~\citep{Ghaoui2010SafeFE} in supervised learning, which is a method able to  identify inactive features, i.e., features that have zero components in the solution vector.
 Then, these inactive features can be removed from the optimization problem to reduce its scale.
 Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
-Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
-In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ where $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
-We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.
+Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}:  e^{w_i} \geq \alpha\}$.
+In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ where $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds to the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
+We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard.
+\rev{If we are able to identify these indices before solving the problem, we
+	can fix them at the threshold and remove then from the optimization procedure yielding to an approximate solution.}.
 
-\paragraph{Static screening test.} The core of the static screening test developed in this paper aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
-$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
-The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
-Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
-
-In the following, the parameters $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ where $\varepsilon > 0$ and $\kappa > 0$ are fixed numeric constants to be given later. 
-Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, defined by:
-
+\paragraph{Static screening test.} Based on this idea, we define a so-called \emph{approximate dual of Sinkhorn divergence} 
 \begin{equation} 
@@
 \end{equation}
+which is simply a dual Sinkhorn with lower-bounded variables, where the bounds
+are $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ with $\varepsilon > 0$ and $\kappa > 0$ being fixed numeric constants which values will be
+clear latter. 
 The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
-Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows:
+Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} when $\varepsilon=0$ and $\kappa=1$.
+ \rev{Intuitively, our hope is to gain efficiency in the resolution of
+this problem compared to the original one in Equation \eqref{sinkhorn-dual} by avoiding optimizing variables smaller than the threshold and by identifying
+those that make the constraints active. } More formally, 
+ the core of the static screening test aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i} > \alpha_u, \text{ and } e^{v_j} > \alpha_v, \text{ for all } (i,j) \in I \times J$ and
+$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
+\rev{The following key result states sufficient conditions for identifying variables in $I^\complement$ and $J^\complement$.}
+%The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
+
+%Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, defined by:
+
+%\paragraph{Static screening test.} The core of the static screening test developed in this paper aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
+%$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
+%The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
+%Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
+%
+%In the following, the parameters $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ where $\varepsilon > 0$ and $\kappa > 0$ are fixed numeric constants to be given later. 
+%Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, defined by:
+%
+%\begin{equation} 
+%\label{screen-sinkhorn}
+%\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
+%\end{equation}
+%The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
+%Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
+%As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows:
 
@@
 
-Proof of Lemma~\ref{I_epsilon_kappa_J_epsilon_kappa} is postponed to the supplementary material.
+Proof of Lemma~\ref{lemma_actives_sets} is postponed to the supplementary material.
 It is worth to note that first order optimality conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\citep{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.
@@
 \paragraph{Screening with a fixed number budget of points.}
-
-Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$, where its values depend on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$.
-In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.
-More precisely, we change the domain of the objective function $\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
+The approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. \rev{As those parameters are
+	difficult to interpret, we exhibit their relations with  \emph{fixed  budget of points} from the supports of $\mu$ and $\nu$}.
+In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points \rev{that are going to be optimized in problem  problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we can not guaranteed
+that  $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ }. 
+%More precisely, we change the domain of the objective function %$\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
 
@@
 
-In this spirit, let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
+Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
 To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 

### 2019-05-22 tex/v3/section_3_algorithm.tex
update

@@
 	difficult to interpret, we exhibit their relations with  \emph{fixed  budget of points} from the supports of $\mu$ and $\nu$}.
-In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points \rev{that are going to be optimized in problem  problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we can not guaranteed
+In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points \rev{that are going to be optimized in problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we can not guaranteed
 that  $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ }. 

### 2019-05-22 tex/v3/section_3_algorithm.tex
small modif intro

--- 2019-05-22 tex/v3/section_3_algorithm.tex
@@
 %More precisely, we change the domain of the objective function %$\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
-
 \begin{wrapfigure}{o}{0.44\textwidth}
-\vspace{-18pt}
+\vspace{-12pt}
 \centering
@@
 \end{wrapfigure}
-
 Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
@@
 \end{equation}
-Note that in one hand we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction.
-On the other hand, when $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$.
+This guarantees that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction.
+In addition,  $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, when the couple parameters $(\varepsilon, \kappa)$ converges to $(0,1)$.
 In Figure~\ref{fig:kappa_epsilon}, we plot these convergences, and hence the objective in problem \eqref{screen-sinkhorn} converges to the objective of dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.

### 2019-05-22 tex/v3/section_3_algorithm.tex
update

@@
 In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ where $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds to the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
-We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard.
-\rev{If we are able to identify these indices before solving the problem, we
-	can fix them at the threshold and remove then from the optimization procedure yielding to an approximate solution.}.
+We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discarded.
+\rev{If we are able to identify these indices before solving the problem, they can be fixed at the threshold and removed then from the optimization procedure yielding to an approximate solution.}
 
@@
 Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} when $\varepsilon=0$ and $\kappa=1$.
- \rev{Intuitively, our hope is to gain efficiency in the resolution of
-this problem compared to the original one in Equation \eqref{sinkhorn-dual} by avoiding optimizing variables smaller than the threshold and by identifying
+ \rev{Intuitively, our hope is to gain efficiency in solving
+this problem compared to the original one in Equation \eqref{sinkhorn-dual} by avoiding optimization of variables smaller than the threshold and by identifying
 those that make the constraints active. } More formally, 

### 2019-05-22 tex/v3/section_3_algorithm.tex
small modif intro

@@
 that  $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ }.
-%More precisely, we change the domain of the objective function %$\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
+
 \begin{wrapfigure}{o}{0.44\textwidth}
@@
 
-Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$,
+%More precisely, we change the domain of the objective function %$\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
+
+\rev{We are now in position to formulate the
+optimization problem related to the screened dual of Sinkhorn.} Indeed, using the above analyses, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
+\rev{Hence, we can restrict the problem \eqref{screen-sinkhorn} to 
+variables in $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$}. This boils down
+to restricting the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$,
 \begin{equation*}
@@
 % \end{equation*}
-where the vector comparison $\succeq$ has to be understood elementwise.
-Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as
+where the vector comparison $\succeq$ has to be understood elementwise. \rev{And,
+	  by replacing in Equation \eqref{screen-sinkhorn}, the variables belonging to $(I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$ by $\varepsilon\kappa^{-1}$ and
+$\varepsilon\kappa$}, we derive the \emph{screened dual of Sinkhorn divergence problem} as
 \begin{align}
@@
 
+ The above problem uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$.
+Hence, a gradient descent scheme will also need only those row/column of $K$.
+This is in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K$.
+In summary, \emph{Screenkhorn} consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$.
+The second one consists in solving Equation \eqref{screen-sinkhorn_second_def}
+using a constrained L-BFGS-B \cite{byrd1995L-BFGS-B} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
 Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
-It is worth to note that \emph{Screenkhorn} algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
-Furthermore, \emph{Screenkhorn} consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
-The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-L-BFGS-B handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
+Note that L-BFGS-B handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
 The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of \emph{Screenkhorn}.
@@
 \LinesNotNumbered
-\begin{algorithm}[htbp]
+\begin{algorithm}[tbp]
 \SetNlSty{textbf}{}{.}

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
small modif intro

@@
 	\end{center}
-	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix.
+	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix \emph{i.e} $\|C\|_\infty$.
 Top panel: marginal violations in relation with the budget of points.
@@
 	\includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
-	\caption{OT Domain adaptation : running time gain for a toy dataset and for MNIST as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}.}
+	\caption{OT Domain adaptation : running time gain  for MNIST as a function of the number of examples and the data decimation factor \emph{Screenkhorn}.
+Hyperparameter values (left) $1$.
+(right) $10$.}
 	\label{fig:otda}
@@
 OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
-for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/\emph{Screenkhorn} has to be computed. As a domain-adaptation problem, we have
+for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/\emph{Screenkhorn} has to be computed and the number of iteration is
+sensitive to the regularizer strength.  As a domain-adaptation problem, we have
 used a MNIST to USPS problem in which features have been extracted from the

### 2019-05-22 figure_da.py

@@ -16,7 +16,7 @@ color_pal = color_pal_t.copy()
 
 
 colors = ["black", "salmon pink", "neon pink", "cornflower","cobalt blue"
-          ,"blue green", "aquamarine", "bright yellow", "golden yellow", "reddish pink" , "reddish purple"]
+          ,"blue green", "aquamarine", "dark yellow", "golden yellow", "reddish pink" , "reddish purple"]
 
 color_pal = sns.xkcd_palette(colors)
 
@@ -24,7 +24,7 @@ plt.close("all")
 
 pathres = './resultat/da/'
 
-data = 'toy'
+data = 'mnist'
 if data == 'toy':
     n_vec = [200,500,1000,2000,3000,5000]
     nb_p_vec = 7
@@ -35,7 +35,7 @@ else:
     n_vec = [200,500,1000,2000,3000,4000]
     nb_p_vec = 7
     p = 20
-    regcl = 1
+    regcl = 10
 
 method_vec = ['wda', 'swda']
 legend_vec_accur = ['Sinkhorn','dec=1.5','dec=2','dec=5','dec=10','dec=20','dec=50','dec=100','No Adapt']

### 2019-05-22 figure_wda.py

@@ -16,7 +16,7 @@ color_pal = color_pal_t.copy()
 
 
 colors = ["black", "salmon pink", "neon pink", "cornflower","cobalt blue"
-          ,"blue green", "aquamarine", "bright yellow", "golden yellow", "reddish pink" , "reddish purple"]
+          ,"blue green", "aquamarine", "dark yellow", "golden yellow", "reddish pink" , "reddish purple"]
 
 color_pal = sns.xkcd_palette(colors)
 
@@ -24,7 +24,7 @@ plt.close("all")
 
 pathres = './resultat/wda/'
 
-data = 'mnist'
+data = 'toy'
 if data == 'toy':
     n_vec = [200,500,1000,2000,3500,5000]
     nb_p_vec = 7

### 2019-05-23 tex/v3/appendix.tex
update suppl
update
modif in appendix

--- 2019-05-21 tex/v3/appendix.tex
@@
 \end{align}
-
-\paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.
-
+Next, we bound the two terms $\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty.$
+% \paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.
 If $r \in I^\complement_{\varepsilon, \kappa}$, then we have 
@@
 Note that $\omega_{\kappa}$ tends to zeros as $(n_b,m_b)$ tends to $(n,m)$ (i.e., $\kappa \rightarrow 1)$. To more characterize $\omega_\kappa$, the following 
-lemma expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 
+lemma expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 
 \begin{lemma}

### 2019-05-23 tex/v3/section_3_algorithm.tex
small modif intro
correction

@@
 We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discarded.
-\rev{If we are able to identify these indices before solving the problem, they can be fixed at the threshold and removed then from the optimization procedure yielding to an approximate solution.}
+{If we are able to identify these indices before solving the problem, they can be fixed at the thresholds and removed then from the optimization procedure yielding to an approximate solution.}
 
@@
 Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} when $\varepsilon=0$ and $\kappa=1$.
- \rev{Intuitively, our hope is to gain efficiency in solving
+ {Intuitively, our hope is to gain efficiency in solving
 this problem compared to the original one in Equation \eqref{sinkhorn-dual} by avoiding optimization of variables smaller than the threshold and by identifying
@@
 $e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
-\rev{The following key result states sufficient conditions for identifying variables in $I^\complement$ and $J^\complement$.}
+{The following key result states sufficient conditions for identifying variables in $I^\complement$ and $J^\complement$.}
 %The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
@@
 \paragraph{Screening with a fixed number budget of points.}
-The approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. \rev{As those parameters are
-	difficult to interpret, we exhibit their relations with  \emph{fixed  budget of points} from the supports of $\mu$ and $\nu$}.
-In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points \rev{that are going to be optimized in problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we can not guaranteed
+The approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. {As those parameters are
+	difficult to interpret, we exhibit their relations with  a {fixed number budget of points} from the supports of $\mu$ and $\nu$}.
+In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points {that are going to be optimized in problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we can not guaranteed
 that  $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ }.
@@
 
-\rev{We are now in position to formulate the
+{We are now in position to formulate the
 optimization problem related to the screened dual of Sinkhorn.} Indeed, using the above analyses, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
-\rev{Hence, we can restrict the problem \eqref{screen-sinkhorn} to 
+{Hence, we can restrict the problem \eqref{screen-sinkhorn} to 
 variables in $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$}. This boils down
@@
 % \end{equation*}
-where the vector comparison $\succeq$ has to be understood elementwise. \rev{And,
+where the vector comparison $\succeq$ has to be understood elementwise. {And,
 	  by replacing in Equation \eqref{screen-sinkhorn}, the variables belonging to $(I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$ by $\varepsilon\kappa^{-1}$ and
@@
  The above problem uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$.
-Hence, a gradient descent scheme will also need only those row/column of $K$.
+Hence, a gradient descent scheme will also need only those rows/columns of $K$.
 This is in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K$.

### 2019-05-23 tex/v3/section_5_numeric_expes.tex
update
correction

@@
 	\end{center}
-	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix \emph{i.e} $\|C\|_\infty$.
+	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix \emph{i.e.} $\norm{C}_\infty=1$.
 Top panel: marginal violations in relation with the budget of points.
@@
 Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$.
-Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a  divergence $\inr{C, P}$ close to the one of Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
-\emph{Screenkhorn} will be practically useful in cases when modest accuracy on the divergence is sufficient as a loss function a gradient descent method optimizes over (see next section).
+Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a  divergence $\inr{C, P}$ close to the one of Sinkhorn showing that our static screening test provides a
+reasonable approximation of the Sinkhorn divergence.
+As such, we believe that  \emph{Screenkhorn} will be practically useful in cases where modest accuracy on the divergence is sufficient.
+This may be the case of a loss function for a gradient descent method (see next section).
 

### 2019-09-24 screenkhorn.py
update README

@@ -1,7 +1,8 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-__author__ = 'Mokhtar Z. Alaya'
+__author__ = 'Mokhtar Z. Alaya' \
+             'Maxime Bérar'
 
 import numpy as np
 import bottleneck

### 2019-09-24 screenkhorn.py
update on the Screenkhorn class

@@ -1,8 +1,7 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-__author__ = 'Mokhtar Z. Alaya' \
-             'Maxime Bérar'
+__author__ = 'Mokhtar Z. Alaya and Maxime Bérar'
 
 import numpy as np
 import bottleneck

### 2019-09-24 final_NeurIPS/pointbypoint_SCREENKHORN.tex
camera ready version NeurIPS

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{color}
\usepackage{algorithmic, algorithm}
\usepackage[a4paper, margin={.15\paperwidth,.08\paperheight},
marginratio=1:1]{geometry}

\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{algorithmic, algorithm}

\begin{document}

\title{Point-by-point reply to the referees' reports on NeurIPS2019}

% \author{}

\date{}

\maketitle

\begin{flushleft}

  \textsc{Paper ID :} 6597

  \textsc{Paper title:} Screening Sinkhorn Algorithm for Regularized Optimal Transport
\end{flushleft}

\maketitle

We thank the Reviewers for their careful reports and for their positive comments.
Below are our replies.

\section{Answers to Reviewer \#1}

\paragraph{Question.}

\emph{The method is not compared to Greenkhorn or any improved solver
for this optimization problems.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{The beauty of Sinkhorn is that it can be accelerated by GPU computations.
It is unclear how the new algorithm would compete with a GPU-accelerated
Sinkhorn algorithm.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{The term "somewhat equivalent" at the end of the paper is not very scientific.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{In Fig $6$ even the smallest decimation leads to an immediate drop of performance. This suggests a fundamental and uncontroled difference in the solvers used. This
observation is consistent with Figure $7$ (low left on OTDA toy) where a decimation of $2$ or less is slower to converge than a regular Sinkhorn.
}

\paragraph{Answer.}

\paragraph{Question.}

\emph{There are quite weird results in Figure $8$ too where a decimation of $1.5$ or $2$ leads to a drop in accuracy while the more strigent decimation factors do not incure any performance drop.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{For figures when the legend and lines follow an order you should use
a continuous paletter of colors and not categorical colors like here. It's
then easier to see the gradient of speed gain with decimation.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{Typos}

\paragraph{Answer.}

All the typos notified by the reviewer are corrected. We did also a whole rereading of the manuscript.

\section{Answers to Reviewer \#2}

Thank you for taking time in reviewing our paper. Here are our point-by-point answers.

\subsection{Main concerns}

\paragraph{Question.}
\begin{itemize}

	\item \emph{The first quantity in the bound, $C_{\max}/\eta$, is only small when $\eta$ is large, which is the highly regularized regime. But in this regime, the Sinkhorn divergence is a poor estimate of OT. Indeed, it is known that $\eta$ must be taken of size $O(\delta/\log n)$ for the Sinkhorn divergence to be within $\pm \delta$ of the OT value. But in this regime, the $C_{\max}/\eta$ term in your bound scales in the accuracy $\delta$ extremely poorly as $1/\delta$. }

	\item \emph{For example, in practice, $\eta$ is typically taken to be around $1/10$ or $1/20$ (if not smaller). Even in this so-called “moderately regularized regime”, $C_{\max}/\eta$ is extremely large, e.g. $10*C_{\max}$ or $20*C_{\max}$… (Of course there is the hidden constant in the big-O in your bound. It would be helpful to know what this constant is, but I suspect it is not much smaller than $1$, if at all. This would be unfortunate since approximating OT within $C_{\max}$ is trivial, and can be done without even looking at the data: simply output the independent coupling $\mu*\nu^\top$.)}

	\item \emph{To summarize, in the regularization regime where the Sinkhorn divergence actually approximates OT well (i.e. $\delta \ll 1$ small, and $\eta\approx\delta$), the error in the presented bound appears to be so big (namely $C_{\max}/\eta$), to the extent that it is perhaps bigger than $C_{\max}$ (which would then be a meaningless bound, see above comment). Am I missing something?}
\end{itemize}

\paragraph{Answer.}

\paragraph{Question.}

\begin{itemize}

	\item  \emph{I am concerned that the terms $||\mu-\mu^{sc}||_1$ and $||\nu-\nu^{sc}||_1$ in the bound, can be large. My concern arises from the fact that for matrix scaling (which is exactly the dual Sinkhorn divergence), there are matrices for which the dual optimal solutions $u$ and $v$ are s.t. the range of $e^{u_i}$ and $e^{v_j}$ is exponentially large in $n$. See e.g., page $10$ of the paper.}

\item  \emph{Kalantari-Khachiyan $1996$ “On the complexity of non-negative matrix scaling”
(For further discussion of such issues, see also e.g. Cohen et al. $2017$ “Matrix scaling and balancing…”)}

\item  \emph{From what I remember, these hard examples also apply for `approximate’ scaling, i.e. whenever $u,v$ do not have exponentially large ranges, then $\text{diag}(e^u) K \text{diag}(e^v)$ has marginals which are very far from the desired marginals $\mu,\nu$. In other words, for such inputs, $||\mu-\mu^{sc}||_1$ and $||\nu-\nu^{sc}||_1$ can only be small if the thresholds in $(4)$ are exponentially small in $n$. But this requires taking your screening parameter eps to be exponentially small in $n$, which means that $c_{\mu,\nu}$ will also be exponentially small in $n$, yielding a dependence of $\log(1/c_{\mu,\nu}) = poly(n)$ in the Proposition $3$ bound, which is an extremely massive error bound. Am I missing something?}

\end{itemize}

\paragraph{Answer.}

\paragraph{Question.}

\emph{It is unsatisfactory that $\omega_\kappa$ in the bound is not defined in the proposition statement, and is only stated to decay as $o(1)$ as the screening parameter $\kappa$ tends to $1$. It is critical to understand how fast this error term decays in terms of this parameter choice, since the point of this proposed screening approach is to trade off runtime (i.e. screen more aggressively, partially done by taking $\kappa$ { *far from* } $1$) with accuracy (i.e. ensure screening does not change the value of the Sinkhorn divergence much, partially done by taking $\kappa$ {*close*} to $1$).}

\paragraph{Answer.}

\subsection{Other comments}

\paragraph{Question.}

\emph{The proposed approach is to solve the screened (i.e. smaller-size) Sinkhorn divergence problem via L-BGFS. Why not use the standard Sinkhorn alternating minimization typically used for Sinkhorn divergences? Changing two things (screening for pre-processing, and L-BFGS for solving) makes it difficult for the reader to understand the affect of each change.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{Something seems a bit suspect about the proposed formulation $(3)$, in that (unless you set the parameter $\kappa=1$, which you purposely do not do) this optimization problem is not invariant under adding a constant times the all-ones vector to $u$, and subtracting the same from $v$. This is an important feature of matrix scaling / standard Sinkhorn divergences.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{Section $3$: the plots are not reproducible (or as informative as they should be) since it is not stated what the distribution of $x_i$ and $y_j$ are/look like.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{L45: I suggest changing “reformulation” to a “new formulation”, as the proposed formulation is not the same as Sinkhorn divergences, but rather is an altered formulation of it. (This is written a few times in the paper; the same comment applies throughout.)}

\paragraph{Answer.}

\paragraph{Question.}

\emph{I believe the term $\log(1/K_{\min}^2)$ in the bound can be removed, as it is equal to $\log(1/e^{-2*C_{\max}/\eta}) = 2 C_{\max} /\eta,$ and thus absorbed by the first term in the bound.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{L64: that is entropy, not negative entropy}

\paragraph{Answer.}

\paragraph{Question.}

\emph{When describing the preliminaries in Section $2$, it should be briefly mentioned that everything there is expository.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{End of first paragraph: technically, the LP solver in [Lee-Sidford $2014$] can solve OT exactly in $\tilde{O}(n^{2.5})$ time. Granted, there is currently no practical implementation of this complicated algorithm, but it should be mentioned there while you are describing runtimes of existing methods.}

\paragraph{Answer.}

\subsection{Comments on exposition}

\paragraph{Question.}

\emph{Typos:\\
— L31-32: sentence should be re-written\\
— L103-104: problems with tense\\
- References: missing capitalization in some (but not all) titles, e.g. pca, wasserstein, lagrangian.}

\paragraph{Answer.}

\section{Answers to Reviewer \#3}

\paragraph{Question.}

\emph{The article is interesting and participates to a growing literature on fast
approximations of optimal transport. The experiments are quite convincing: the
proposed method can provide a way of reducing the cost while maintaining a
reasonable accuracy. The gains are not always groundbreaking but clearly
significant and the method appears to be widely applicable. It is also very
nice that users can specify the approximation parameters in terms of $n_b$ and
$m_b$, rather than $\varepsilon$ and $\kappa.$}

\paragraph{Answer.}

\paragraph{Question.}

\emph{One criticism is that the method is compared only with the "vanilla"
Sinkhorn algorithm, so it is not easy to see whether the proposed method would
provide gains compared to other recently proposed variants, such as the
Greenkhorn algorithm mentioned in the introduction. It is also unclear whether
the proposed thresholding strategy could be combined with these alternative techniques, e.g. with Greenkhorn, for further gains, or whether it is incompatible.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{In terms of presentation, it would be helpful to have a self-contained
pseudocode, that would not rely on a routine such as "L-BFGS-B", although that
can be considered to be quite standard. I also wonder whether L-BFGS-B is the
only algorithm applicable for step $2$ of Algorithm $1$, or if there are other
sensible alternatives there; L-BFGS-B is presented as the only option.}

\paragraph{Answer.}

\paragraph{Question.}

\emph{Typos}

\paragraph{Answer.} 
All the typos notified by the reviewer are corrected. We did also a whole rereading of the manuscript.

p$8$: "features have been extracted from the feature extractor" is awkward.

\end{document}

### 2019-09-24 final_NeurIPS/appendix.tex
camera ready version NeurIPS

--- 2019-05-23 tex/v3/appendix.tex
@@
 
-We first define $\widetilde{K}$ a rearrgement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
+We first define $\widetilde{K}$ a rearrangement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
 \begin{equation*}
@@
 &\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
-&\leq \norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1 + \norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
-&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}\\
+&\leq \big(\norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty + (1 - \kappa) \norm{\dt{u}^{\text{sc}}}_\infty\big)\norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m - \dt{\mu}}_1\\
+&\qquad + \big(\norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty + (\kappa^{-1} -1) \norm{\dt{v}^{\text{sc}}}_\infty\big) \norm{\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n - \dt{\nu}}_1\\
+&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})\mathbf 1_m} + (\kappa^{-1}- 1)\inr{\dt{v}^{\text{sc}} ,\widetilde{B}(\dt{u}^{\text{sc}} ,\dt{v}^{\text{sc}})^\top\mathbf 1_n}
 \end{align*}
-Note that
+where, in the last inequality, we use the facts that $\norm{\kappa\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty \leq \norm{\dt{u}^{\text{sc}} - \dt{u}^\star}_\infty + (1 - \kappa) \norm{\dt{u}^{\text{sc}}}_\infty$ and $\norm{\kappa^{-1}\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty \leq \norm{\dt{v}^{\text{sc}} - \dt{v}^\star}_\infty + (\kappa^{-1} -1) \norm{\dt{v}^{\text{sc}}}_\infty.$
+Moreover, note that 
 \begin{align*}
@@
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) &
-\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty \norm{\nu^{\text{sc}} - \nu}_1\nonumber\\
-&\qquad + (1- \kappa)\inr{{u}^{\text{sc}} ,{\mu}^{\text{sc}}} + (1- \kappa^{-1})\inr{{v}^{\text{sc}} ,{\nu}^{\text{sc}}}\nonumber\\
-&\leq \norm{{u}^{\text{sc}} - {u}^\star}_\infty \norm{\mu^{\text{sc}} - \mu}_1 + \norm{{v}^{\text{sc}} - {v}^\star}_\infty\norm{\nu^{\text{sc}} - \nu}_1 \nonumber\\
-&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{priori_bounds_induction}
+\leq \big(\norm{{u}^{\text{sc}} - {u}^\star}_\infty + (1- \kappa) \norm{{u}^{\text{sc}}}_\infty\big)\norm{\mu^{\text{sc}} - \mu}_1\nonumber\\
+&\qquad + \big(\norm{{v}^{\text{sc}} - {v}^\star}_\infty + (\kappa^{-1} - 1) \norm{{v}^{\text{sc}}}_\infty\big) \norm{\nu^{\text{sc}} - \nu}_1\nonumber\\
+&\qquad + (1- \kappa)\inr{{u}^{\text{sc}} ,{\mu}^{\text{sc}}} + (\kappa^{-1} -1)\inr{{v}^{\text{sc}} ,{\nu}^{\text{sc}}}\nonumber\\
+&\leq \big(\norm{{u}^{\text{sc}} - {u}^\star}_\infty + (1- \kappa) \norm{{u}^{\text{sc}}}_\infty\big)\norm{\mu^{\text{sc}} - \mu}_1\nonumber\\
+&\qquad + \big(\norm{{v}^{\text{sc}} - {v}^\star}_\infty + (\kappa^{-1} - 1) \norm{{v}^{\text{sc}}}_\infty\big) \norm{\nu^{\text{sc}} - \nu}_1 \label{priori_bounds_induction}\\
+&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\nonumber
 \end{align}
@@
 \end{align*}
-where the inequality $(\star)$ comes from the fact that $\frac{\sum_{j=1}^na_j}{\sum_{j'=1}^nb_{j'}} \leq \max_{1\leq j \leq n} \frac{a_j}{b_j}, \forall a_j, b_j>0.$
+where the inequality $(\star)$ comes from the fact that $\frac{\sum_{j=1}^na_j}{\sum_{j=1}^nb_{j}} \leq \max_{1\leq j \leq n} \frac{a_j}{b_j}, \forall a_j, b_j>0.$
 Now, if $r \in I_{\varepsilon, \kappa}$, we get 
@@
 &\leq 2\big(R + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
-&\qquad + (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1.\label{post_bounds_induction_2}
+&\qquad + (1- \kappa)\big(\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 +\norm{\mu^{\text{sc}} - \mu}_1\big)\label{post_bounds_induction_2}\\
+&\qquad  + (\kappa^{-1} - 1)\big(\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1+\norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber.
 \end{align}
@@
 \end{equation*}
-Hence, we have 
+Acknowledging that $\log(1/ K_{\min}^2) = 2\norm{C}_\infty/\eta$, we have 
 \begin{align*}
-R + \norm{u^{\text{sc}}}_\infty  + \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) = \bigO\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big).
+R + \norm{u^{\text{sc}}}_\infty  + \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) = \bigO\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big).
 \end{align*}
-Letting $\omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1,$
-Moreover, we have 
+Letting $\Omega_{\kappa} := (1- \kappa)\big(\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 +\norm{\mu^{\text{sc}} - \mu}_1\big) + (\kappa^{-1} - 1)\big(\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1+\norm{\nu^{\text{sc}} - \nu}_1\big).$
+% Moreover, we have 
+% \begin{align*}
+% \omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1
+% \end{align*}
+We have that 
 \begin{align*}
-\omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1
+\Omega_{\kappa} &=\bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\big(\frac{1}{(nm)^{3/4} c_{\mu\nu}^{1/2}}\big)\Big)\Big((1- \kappa)(\norm{{\mu}^{\text{sc}}}_1 +\norm{\mu^{\text{sc}} - \mu}_1\big) + (\kappa^{-1} - 1)(\norm{{\nu}^{\text{sc}}}_1+\norm{\nu^{\text{sc}} - \nu}_1)\Big)\Big)\\
+&= \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big)\big((1- \kappa)\norm{\mu^{\text{sc}}}_1 + (\kappa^{-1} - 1)\norm{\nu^{\text{sc}}}_1 + \kappa^{-1} - \kappa\big)\Big).
 \end{align*}
-We arrive at 
+% Setting $\omega_\kappa := (1- \kappa)\norm{\mu^{\text{sc}}}_1 + (\kappa^{-1} - 1)\norm{\nu^{\text{sc}}}_1 + \kappa^{-1} - \kappa,$ 
+Hence, we arrive at 
 \begin{align*}
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
-& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1) + \omega_{\kappa}\Big).
+& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1 + \omega_{\kappa}\Big).
 \end{align*}
-Note that $\omega_{\kappa}$ tends to zeros as $(n_b,m_b)$ tends to $(n,m)$ (i.e., $\kappa \rightarrow 1)$. To more characterize $\omega_\kappa$, the following 
+$\hfill\square$
+
+Note that $\omega_{\kappa}$ tends to zero as $(n_b,m_b)$ tends to $(n,m)$ (i.e., $\kappa \rightarrow 1)$. To more characterize $\omega_\kappa$, the following 
 lemma expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 
@@
 
+\ar{
+
+\subsection{Additional remarks}
+
+\paragraph{On the use of a constrained L-BFGS-B solver.}
+
+It is worth to note that standard Sinkhorn's alternating minimization cannot be applied for the constrained screened dual problem~\eqref{screen-sinkhorn_second_def}.
+This appears more clearly while writing its optimality conditions (see Equations~\eqref{i-th-marginal-nu} and~\eqref{i-th-marginal-mu} ).
+We resort to a L-BFGS-B algorithm to solve the constrained convex optimization problem on the screened variables~\eqref{screen-sinkhorn_second_def}, but any other efficient solver (e.g., proximal based method or Newton method) could be used.
+We further  emphasize that, as for the \textsc{Sinkhorn} algorithm, the \textsc{Screenkhorn} algorithm can be accelerated using a GPU implementation\footnote{\url{https://github.com/nepluno/lbfgsb-gpu}} of the L-BFGS-B algorithm~\cite{fei2014-GPU-L-BFGS-B}.
+
+\paragraph{Comparison with other solvers.}
+
+We have considered experiments with \textsc{Greenkhorn} algorithm~\cite{altschulernips17} but the implementation in POT library and our Python version of Matlab Alschuler's Greenkhorn code\footnote{\url{https://github.com/JasonAltschuler/OptimalTransportNIPS17}} were not competitive with \textsc{Sinkhorn}.
+Hence, for both versions, \textsc{Screenkhorn} is more competitive than \textsc{Greenkhorn}.
+The computation time gain reaches an order of $30$ when comparing our method with \textsc{Greenkhorn} while \textsc{Screenkhorn} is almost $2$ times faster than $\textsc{Sinkhorn}$.
+
 \subsection{Additional experimental results}
+
+\paragraph{Experimental setup.}
+
+	All computations have been run on each single core of an Intel Xeon E5-2630 processor clocked at
+	2.4 GHz in a Linux machine with 144 Gb of memory.
+	The code that generates all figures given in the paper is available from \url{https://github.com/mzalaya/screenkhorn}.
+
+}
 
@@
 (top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples.
-(bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
+(bottom-left) Running time of the \textsc{Sinkhorn} and \textsc{Screenkhorn} for different decimation
 	factors.
@@
 This toy problem is a problem in which classes are overlapping and distance between samples are rather limited.
-According to our analysis, this may be a situation in which \emph{Screenkhorn} may
+According to our analysis, this may be a situation in which \textsc{Screenkhorn} may
 	result in smaller computational gain. We can remark that with respect to the accuracy
-	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance.
+	\textsc{Screenkhorn} with decimation factors up to $10$ are competitive with \textsc{Sinkhorn}, although a slight loss of performance.
 Regarding computational time, for this example, small decimation factors does not  result in gain.
@@
 	\centering
-	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
-	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
-	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
-	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
-	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$.
+	\includegraphics[width=6.5cm]{./figs/da_accur_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{./figs/da_accur_mnist_regcl10.pdf}
+	\includegraphics[width=6.5cm]{./figs/da_time_mnist_regcl1.pdf}
+	\includegraphics[width=6.5cm]{./figs/da_time_mnist_regcl10.pdf}
+	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of \textsc{Sinkhorn} and \textsc{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$.
 Note that this
@@
 	also report the performance of a $1$-NN when no-adaptation is performed.  
-	We remark that the strenght of the class-based regularization has influence on the performance of \emph{Screenkhorn} given a decimation factor.
-For small value on the left, \emph{Screenkhorn} slightly performs better than Sinkhorn, while for large value, some
+	We remark that the strenght of the class-based regularization has influence on the performance of \textsc{Screenkhorn} given a decimation factor.
+For small value on the left, \textsc{Screenkhorn} slightly performs better than \textsc{Sinkhorn}, while for large value, some
 	decimation factors leads to loss of performances.
-	Regarding, running time, we can note that Sinkhorn is far less efficient than
-	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
+	Regarding, running time, we can note that \textsc{Sinkhorn} is far less efficient than
+	\textsc{Screenkhorn}  with an order of magnitude for intermediate number of samples.
 	\label{fig:otda:mnist:extra}}

### 2019-09-24 final_NeurIPS/main.tex
camera ready version NeurIPS

--- 2019-05-21 tex/v3/main.tex
@@
 % ready for submission
-\usepackage{neurips_2019}
+% \usepackage{neurips_2019}
 
@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[]{neurips_2019}
+\usepackage[final]{neurips_2019}
 
@@
 %% algorithms
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage[ruled,linesnumbered,vlined,scleft]{algorithm2e} 
+\usepackage{adjustbox}
+
+\newsavebox{\tempbox}
+
+\makeatletter
+\let\oldnl\nl% Store \nl in \oldnl
+\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}% Remove line number for one line
+\makeatother
+
+\let\oldalgorithm\algorithm
+\let\oldendalgorithm\endalgorithm
+
+\newcommand\SetAlgoFig{
+  \let\algorithm\figure
+  \let\endalgorithm\endfigure
+}
+
+\newcommand\SetAlgoNoFig{
+  \let\algorithm\oldalgorithm
+  \let\endalgorithm\oldendalgorithm
+}
+%%
+
 \usepackage{enumitem}
@@
 \DeclareMathOperator*{\argmax}{\arg\!\max}
+
+% small pmatrix
+% \usepackage{amsmath}
+% \newenvironment{psmallmatrix}
+%   {\left(\begin{smallmatrix}}
+%   {\end{smallmatrix}\right)}
 %--------------------------------------------------------------------------------------------------------------------------------%
@@
 LITIS EA4108\\
-University of Rouen\\
+University of Rouen Normandy\\
 \texttt{mokhtarzahdi.alaya@gmail.com} 
@@
 LITIS EA4108\\
-University of Rouen\\
+University of Rouen Normandy\\
 \texttt{maxime.berar@univ-rouen.fr} \\
@@
 LITIS EA4108\\
-INSA, University of Rouen\\
+INSA, University of Rouen Normandy\\
 \texttt{gilles.gasso@insa-rouen.fr} 
@@
 LITIS EA4108 \\
-University of Rouen\\
+University of Rouen Normandy\\
 and Criteo AI Lab, Criteo Paris \\
@@
 \begin{abstract}
-We introduce in this paper a novel strategy for efficiently approximate the Sinkhorn distance between two discrete measures. After identifying neglectible components
+We introduce in this paper a novel strategy for efficiently approximating the Sinkhorn distance between two discrete measures. After identifying neglectable components
 of the dual solution of the regularized Sinkhorn problem, we propose to screen those components by directly setting them at that value before entering the Sinkhorn problem.
 This allows us to solve a smaller Sinkhorn problem while ensuring approximation with provable guarantees.
-More formally, the approach is based on a reformulation of \emph{dual of Sinkhorn divergence problem} and on the KKT optimality conditions of this problem, which enable identification of dual components to be screened.
-This new analysis leads to the \emph{Screenkhorn} algorithm.
-We illustrate the efficiency of Screenkhorn on complex tasks such as dimensionality reduction or domain adaptation involving regularized optimal transport.
+More formally, the approach is based on a new formulation of \emph{dual of Sinkhorn divergence problem} and on the KKT optimality conditions of this problem, which enable identification of dual components to be screened.
+This new analysis leads to the \textsc{Screenkhorn} algorithm.
+We illustrate the efficiency of \textsc{Screenkhorn} on complex tasks such as dimensionality reduction and domain adaptation involving regularized optimal transport.
 \end{abstract}
@@
 some theoretical guarantees of the quality of the approximation with respect to
-the number of variables that has been screened. Numerical experiments show 
-the behaviour of our \emph{Screenkhorn} algorithm and computational time gain it can
+the number of variables that have been screened. Numerical experiments show 
+the behaviour of our \textsc{Screenkhorn} algorithm and computational time gain it can
 achieve when integrated in some complex machine learning pipelines.
 
-% \subsubsection*{Acknowledgments}
+\subsubsection*{Acknowledgments}
 
-% Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
+This work was supported by grants from the Normandie Projet GRR-DAISI, European funding FEDER DAISI and OATMIL ANR-17-CE23-0012 Project of the French National Research Agency (ANR).
 
@@
 \bibliography{biblio}
-\bibliographystyle{chicago}
+\bibliographystyle{plain}
 %well as with those for harvard, apalike, chicago, astron, authordate, and of course natbib.

### 2019-09-24 final_NeurIPS/section_2_setup_OT.tex
camera ready version NeurIPS

--- 2019-05-21 tex/v3/section_2_setup_OT.tex
@@
 
-We briefly present in this section the setup of OT between two discrete measures.
+We briefly expose in this section the setup of OT between two discrete measures.
 We then consider the case when those distributions are only available through a finite number of samples, that is $\mu = \sum_{i=1}^n \mu_i \delta_{x_i} \in \Sigma_n$ and $\nu = \sum_{j=1}^m \nu_i \delta_{y_j} \in \Sigma_m$, where $\Sigma_n$ is the probability simplex with $n$ bins, namely the set of probability vectors in $\R_+^n$, i.e., $\Sigma_n = \{w \in \R_+^n: \sum_{i=1}^n w_i = 1\}.$
@@
 The entropic regularization of OT distances~\citep{cuturinips13} relies on the addition of a penalty term as follows:
-\begin{equation*}
+\begin{equation}
 \label{sinkhorn-primal}
   \mathcal{S}_\eta(\mu, \nu) =  \min_{P\in \Pi(\mu, \nu)} \{\inr{C, P} - \eta H(P)\},
-\end{equation*}
+\end{equation}
 where $\eta > 0$ is a regularization parameter. We refer to $\mathcal{S}_\eta(\mu, \nu) $ as the \emph{Sinkhorn divergence}~\citep{cuturinips13}.
@@
 
-Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function :
+Below we provide the derivation of the dual problem for the regularized OT problem~\eqref{sinkhorn-primal}. Towards this end, we begin with writing its Lagrangian dual function:
 \begin{equation*}
-  \mathscr{L}(P,y, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{y, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
+  \mathscr{L}(P,w, z) = \inr{C,P} + \eta \inr{\log P, P} + \inr{w, P\mathbf{1}_m - \mu} + \inr{z,P^\top \mathbf{1}_n - \nu}.
 \end{equation*}
-The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,y, z)$.
-It is easy to check that objective function $P\mapsto \mathscr{L}(P,y, z)$ is strongly convex and differentiable.
-Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,y, z)$ to $\mathbf{0}_{n\times m}$.
-Therefore, we get
-\begin{equation*}
-  P^\star_{ij} = \exp\Big(- \frac{1}{\eta} (y_i + z_j + C_{ij}) - 1\Big), 
-\end{equation*}
-for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -y/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
+The dual of Sinkhorn divergence can be derived by solving $\min_{P \in \R_+^{n\times m}}\mathscr{L}(P,w, z)$.
+It is easy to check that objective function $P\mapsto \mathscr{L}(P,w, z)$ is strongly convex and differentiable.
+Hence, one can solve the latter minimum by setting $\nabla_P \mathscr{L}(P,w, z)$ to $\mathbf{0}_{n\times m}$.
+Therefore, we get $  P^\star_{ij} = \exp\big(- \frac{1}{\eta} (w_i + z_j + C_{ij}) - 1\big),
+$ for all $i=1, \ldots, n$ and $j=1, \ldots, m$. Plugging this solution,  and setting the change of variables $u = -w/\eta - 1/2$ and $v = - z/\eta - 1/2$, the dual problem is given by
 \begin{equation}
@@
 where $B(u,v) := \Delta(e^{u}) K \Delta(e^{v})$ and $K := e^{-C/\eta}$ stands for the Gibbs kernel associated to the cost matrix $C$. 
-We refer to problem~\eqref{sinkhorn-dual} as the \emph{dual of Sinkhorn divergence}, and its optimal solution $P^\star$ takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
+We refer to problem~\eqref{sinkhorn-dual} as the \emph{dual of Sinkhorn divergence}.
+Then, the optimal solution $P^\star$ of the primal problem~\eqref{sinkhorn-primal} takes the form $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$
 where the couple $(u^\star, v^\star)$ satisfies:
@@
 Note that the matrices $\Delta(e^{u^\star})$ and $\Delta(e^{v^\star})$ are unique up to a constant factor~\citep{sinkhorn1967}.
-Moreover, $P^\star$ can be solved efficiently by iterative Bregman projections~\citep{benamou2015IterativeBP} referred as Sinkhorn iterations, and the method is referred as Sinkhorn algorithm which, recently, is proven to achieve a near-$\bigO(n^2)$ complexity~\citep{altschulernips17}.
+Moreover, $P^\star$ can be solved efficiently by iterative Bregman projections~\citep{benamou2015IterativeBP} referred to as Sinkhorn iterations, and the method is referred to as \textsc{Sinkhorn} algorithm which, recently, has been proven to achieve a near-$\bigO(n^2)$ complexity~\citep{altschulernips17}.
 

### 2019-09-24 final_NeurIPS/section_3_algorithm.tex
camera ready version NeurIPS

--- 2019-05-23 tex/v3/section_3_algorithm.tex
@@
 
-\begin{wrapfigure}{o}{0.4\textwidth}
+\begin{wrapfigure}{o}{0.3\textwidth}
 \vspace{-15pt}
 \centering
-\includegraphics[width=0.4\textwidth]{./figs/motivations.pdf}
-\caption{Plots of $(e^{u^\star}, e^{v^\star})$ with $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} and the thresholds $\alpha_u, \alpha_v$.}
+\includegraphics[width=0.3\textwidth]{./figs/motivations.pdf}
+\caption{Plots of $(e^{u^\star}, e^{v^\star})$ with $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~\eqref{sinkhorn-dual} and the thresholds $\alpha_u, \alpha_v$.}
 \label{fig:motivations}
@@
 Then, these inactive features can be removed from the optimization problem to reduce its scale.
-Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
+Before diving into detailed algorithmic analysis, let us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
 Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}:  e^{w_i} \geq \alpha\}$.
-In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ where $(u^\star, v^\star)$ is the pair solution of dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ corresponds to the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
-We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discarded.
-{If we are able to identify these indices before solving the problem, they can be fixed at the thresholds and removed then from the optimization procedure yielding to an approximate solution.}
+In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ where $(u^\star, v^\star)$ is the pair solution of the dual of Sinkhorn divergence~(\ref{sinkhorn-dual}) in the particular case of: $n=m=500, \eta=1, \mu = \nu = \frac 1n \mathbf 1_n, x_i \sim\mathcal{N}((0,0)^\top, \begin{psmallmatrix}1 & 0\\0 & 1\end{psmallmatrix}), y_j \sim\mathcal{N}((3,3)^\top, \begin{psmallmatrix}1 &-0.8 \\ -0.8 &1 \end{psmallmatrix})$ and the cost matrix $C$ corresponds to the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$.
+We also plot two lines corresponding to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, choosing randomly and playing the role of thresholds to select indices to be discarded.
+{If we are able to identify these indices before solving the problem, they can be fixed at the thresholds and removed then from the optimization procedure yielding an approximate solution.}
 
@@
 \end{equation}
-which is simply a dual Sinkhorn with lower-bounded variables, where the bounds
+which is simply a dual of Sinkhorn divergence with lower-bounded variables, where the bounds
 are $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ with $\varepsilon > 0$ and $\kappa > 0$ being fixed numeric constants which values will be
-clear latter. 
-The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
-Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} when $\varepsilon=0$ and $\kappa=1$.
+clear later. 
+\ar{The new formulation~\eqref{screen-sinkhorn} has the form of $(\kappa\mu, \nu / \kappa)$-scaling problem under constraints on the variables $u$ and $v$.
+However, it differs significantly from the standard scaling-problems~\cite{KALANTARI199687}.
+We further emphasize that $\kappa$ plays a key role in our screening strategy for the dual of Sinkhorn divergence.
+Indeed, without $\kappa$, $e^u$ and $e^v$ can have inversely related scale  that may lead in,  for instance $e^u$ being too large and $e^v$ being too small, situation in which the screening test would apply only to coefficients of $e^u$ or $e^v$ and not for both of them.
+}
+% The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
+Moreover, it is clear that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} when $\varepsilon=0$ and $\kappa=1$.
  {Intuitively, our hope is to gain efficiency in solving
@@
 	difficult to interpret, we exhibit their relations with  a {fixed number budget of points} from the supports of $\mu$ and $\nu$}.
-In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points {that are going to be optimized in problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we can not guaranteed
+In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number of points {that are going to be optimized in problem~\eqref{screen-sinkhorn}, \emph{i.e}, the points we cannot guarantee
 that  $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ }.
 
-\begin{wrapfigure}{o}{0.44\textwidth}
+\begin{wrapfigure}{o}{0.28\textwidth}
 \vspace{-12pt}
 \centering
-\includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
+\includegraphics[width=0.25\textwidth]{./figs/kappa_epsilon.pdf}
 \caption{Plots of $\varepsilon$ and $\kappa$ as a function of number budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are set as in Figure~\eqref{fig:motivations}.
@@
 This is in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K$.
-In summary, \emph{Screenkhorn} consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$.
+In summary, \textsc{Screenkhorn} consists of two steps: the first one is a screening pre-processing providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$.
 The second one consists in solving Equation \eqref{screen-sinkhorn_second_def}
@@
 Note that L-BFGS-B handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
-The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of \emph{Screenkhorn}.
+The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of \textsc{Screenkhorn}.
 \begin{proposition}
@@
 \end{proposition}
+
 \LinesNotNumbered
@@
 \DontPrintSemicolon
-\caption{\emph{Screenkhorn}$(C,\eta,\mu,\nu,n_b,m_b)$}
+\caption{\textsc{Screenkhorn}$(C,\eta,\mu,\nu,n_b,m_b)$}
 \label{screenkhorn}
 
-\textbf{Step 1:} \textcolor{black}{Initialization}\\
+\textbf{Step 1:} \textcolor{black}{\ar{Screening pre-processing}}\\
 
@@
 \nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
-\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
-\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\ 
-\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
-\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
+\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\}, J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\ 
+\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i, \underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \nu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \nu_i$; \\
 \nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
@@
 
-\noindent \textbf{Step 2:} \textcolor{black}{L-BFGS-B}\\
+\vspace{.2cm}
+\noindent \textbf{Step 2:} \textcolor{black}{\ar{L-BFGS-B solver on the screened variables}}\\
 
@@
 
+% \savebox{\tempbox}{% create image
+% \begin{minipage}[c]{0.45\textwidth}%
+%    \textbf{Step 1:} \textcolor{black}{Initialization: screening pre-processing}\\
+
+% \nl   $\xi \gets \texttt{sort}(\mu \oslash r(K)),$ $\zeta \gets \texttt{sort}(\nu \oslash c(K));$ //(decreasing order)\\
+% % \nl   $\zeta \gets \texttt{sort}(\nu \oslash c(K));$\\
+% % \nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
+% % \nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
+% \nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
+% \nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
+% \nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\ 
+% \nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
+% \nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \nu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \nu_i$; \\
+% \nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big)$; \\
+% \nl $\bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
+% \nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big)$; \\
+% \nl $\bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
+% \nl   $ \bar{\theta} \gets \texttt{stack}(\bar{u}\mathbf 1_{n_b} \bar{v}\mathbf 1_{m_b});$ \\
+% \nl $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
+% % \nl   $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
+
+% % \vspace{.2cm}
+% \noindent \textbf{Step 2:} \textcolor{black}{L-BFGS-B solver on screened variables}\\
+
+% \nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b},$ $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b},$ $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
+% % \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
+% % \nl  $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
+% \nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
+% \nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
+% \nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
+% \nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
+% \nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}     
+% \end{minipage}}
+
+% \SetAlgoNoFig % use the standard algorithm
+
+% \LinesNotNumbered
+% \begin{algorithm}[tbp]
+% \SetNlSty{textbf}{}{.}
+% \DontPrintSemicolon
+% % \nonl %switch off line numbers
+% \clipbox{-15pt {\depth} 15pt {\baselineskip}}{\usebox{\tempbox}}\hfill
+% \raisebox{\depth}{\clipbox{15pt 1ex -15pt {\height}}{\usebox{\tempbox}}}
+% \caption{\textsc{Screenkhorn}$(C,\eta,\mu,\nu,n_b,m_b)$}
+% \end{algorithm}
+
 % section screened_dual_of_sinkhorn_divergence (end)

### 2019-09-24 final_NeurIPS/section_4_marginal_viols.tex
camera ready version NeurIPS

--- 2019-05-22 tex/v3/section_4_marginal_viols.tex
@@
 
-\section{Analysis of marginal violations} % (fold)
+\section{Theoretical analysis and guarantees} % (fold)
 \label{sec:analysis_of_marginal_violations}
@@
 % We derive in this section 
-This section is devoted to establishing theoretical guarantees for \emph{Screenkhorn} algorithm. %the marginal violations of
+This section is devoted to establishing theoretical guarantees for \textsc{Screenkhorn} algorithm. %the marginal violations of
 We first define the screened marginals $\mu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}}) \mathbf 1_m$ and $\nu^{\text{sc}} = B(u^{\text{sc}}, v^{\text{sc}})^\top \mathbf 1_n.$ 
@@
 \end{proposition}
-Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and its is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma 1 in supplementary).
+Proof of Proposition~\ref{proposition_error_in_marginals} is presented in supplementary material and it is based on first order optimality conditions for problem~\eqref{screen-sinkhorn_second_def} and on a generalization of Pinsker inequality (see Lemma~\ref{lem:pinsker} in supplementary).
 Note that $c_\kappa$ and $c_{\frac 1\kappa}$ tend to zeros as $\kappa$ goes to one, which is the case when the number budget of points $(n_b,m_b)$ tends to the full one $(n,m)$.
 
-Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of \emph{Screenkhorn} and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
+Our second theoretical result, Proposition~\ref{prop:objective-error}, is an upper bound of the difference between objective values of \textsc{Screenkhorn} and dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.
 \begin{proposition}
@@
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star)
-= \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmK_{\min}^{2}c_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1)  + \omega_{\kappa}\Big).
+= \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - \mu^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1 + \omega_{\kappa}\Big).
 \end{align*}
-where $\omega_{\kappa} = o(1)$  as $\kappa$ tends to $1.$
+where $\omega_{\kappa} = (1- \kappa)\norm{\mu^{\text{sc}}}_1 + (\kappa^{-1} - 1)\norm{\nu^{\text{sc}}}_1 + \kappa^{-1} - \kappa$.
 \end{proposition}
 Proof of Proposition~\ref{prop:objective-error} is exposed in the supplementary material.
-Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$, that tends to zero as the pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
+Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$ (with $\omega_1 =0)$, that tends to zero as the pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
+\ar{To more characterize $\omega_\kappa$, a control of the $\ell_1$-norms of the screened marginals $\mu^{\text{sc}}$ and $\nu^{\text{sc}}$ are given in Equations~\eqref{l1-norm-mu-sc} and~\eqref{l1-norm-nu-sc} in Lemma~\ref{lemma_bounds_on_marginals} in the supplementary material.}
+
 % section analysis_of_marginal_violations (end)

### 2019-09-24 final_NeurIPS/section_5_numeric_expes.tex
camera ready version NeurIPS

%!TEX root = main.tex

\section{Numerical experiments} % (fold)
\label{sec:numerical_experiments}

In this section, we present some numerical analyses of our
\textsc{Screenkhorn} algorithm and show how it behaves when
integrated into some complex machine learning pipelines.

\subsection{Setup}

We have implemented our \textsc{Screenkhorn} algorithm in Python and used the L-BFGS-B of
Scipy. Regarding the machine-learning based comparison, we have based our code
on the ones of Python Optimal Transport toolbox (POT)~\citep{flamary2017pot} and just replaced the Sinkhorn function call with a \textsc{Screenkhorn} one. We have considered the POT's default Sinkhorn stopping criterion parameters and for \textsc{Screenkhorn}, the L-BFGS-B algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-6}$, when the number of iterations of number of objective function evaluations reach $10^{5}$. For all applications, we have set $\eta=1$ unless otherwise specified.

\subsection{Analysing on toy problem}

We compare \textsc{Screenkhorn} to Sinkhorn as implemented in POT toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example. The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means. We consider an unsupervised domain adaptation using optimal transport with entropic regularization.  Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$.
% and, whether the cost matrix $C$ is normalized or not.
 We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\textsc{Sinkhorn}}}{T_{\text{\textsc{Screenkhorn}}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \textsc{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings. We choose to only report results for $n=m=1000$ as we get similar findings for other values of $n$ and $m$.

\begin{figure*}[t]
	\begin{center}
		% \includegraphics[width=0.33\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
		\includegraphics[width=0.28\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
		\includegraphics[width=0.28\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} \\
		\includegraphics[width=0.28\textwidth]{./figs/norm_M_time_toy_n1000}\hspace{2cm}
		\includegraphics[width=0.28\textwidth]{./figs/norm_M_div_toy_n1000}
	\end{center}
	\caption{Empirical evaluation of \textsc{Screenkhorn} vs \textsc{Sinkhorn} for normalized cost matrix \emph{i.e.} $\norm{C}_\infty=1$. Top panel: marginal violations in relation with the budget of points. Bottom panel: (left) ratio of computation times    $\frac{T_{\textsc{Sinkhorn}}}{T_{\text{\textsc{Screenkhorn}}}}$ and, (right) relative divergence variation. The results are averaged over $30$ trials.} 
		\label{fig:margin_expe}
\end{figure*}
%
\textsc{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for ``high'' values of the regularization parameter $\eta$ ($\eta > 1$). The approximation quality diminishes for small $\eta$. As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge towards zero when increasing the budget of points. Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.  According to computation gain, \textsc{Screenkhorn} is almost  2 times faster than Sinkhorn at high decimation factor $n/n_b$ (low budget) while the reverse holds when $n/n_b$ gets close to 1.  Computational benefit of \textsc{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$. Finally except for $\eta=0.1$ \textsc{Screenkhorn} achieves a  divergence $\inr{C, P}$ close to the one of Sinkhorn showing that our static screening test provides a
reasonable approximation of the Sinkhorn divergence. As such, we believe that  \textsc{Screenkhorn} will be practically useful in cases where modest accuracy on the divergence is sufficient. This may be the case of a loss function for a gradient descent method (see next section).

\subsection{Integrating \textsc{Screenkhorn} into machine learning pipelines}

Here, we analyse the impact of using \textsc{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \citep{flamary2018WDA} and a domain-adaptation using optimal transport mapping \citep{courty2017optimal}, named OTDA.

WDA aims at finding a linear projection which minimize the ratio of distance between intra-class samples and distance inter-class samples, where the distance is understood
in a Sinkhorn divergence sense. We have used a toy problem involving Gaussian classes with $2$ discriminative features and $8$ noisy features and the MNIST dataset. For the
former problem, we aim at find the best two-dimensional linear subspace in a WDA sense whereas for MNIST, we look for a subspace of dimension $20$ starting from the original
$728$ dimensions.  Quality of the retrieved subspace are evaluated using classification task based on a $1$-nearest neighbour approach.

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \textsc{Screenkhorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material (see Figure~\ref{fig:wda_gain}), but we can remark a small loss of performance of \textsc{Screenkhorn} for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.

\begin{figure*}[t]
	\centering
%	\includegraphics[width=4.cm]{./figs/wda_accur_toy.pdf}
%	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
	% --- \includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}\hspace{1.5cm}
	% --- \includegraphics[width=0.39\textwidth]{./figs/wda_gain_mnist.pdf}

	\includegraphics[width=0.31\textwidth]{./figs/wda_gain_toy.pdf}\hspace{1.5cm}
	\includegraphics[width=0.31\textwidth]{./figs/wda_gain_mnist.pdf}

	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for MNIST as a function of the number of examples and the data decimation factor in \textsc{Screenkhorn}.}
	\label{fig:wda}
\end{figure*}
\begin{figure*}[t]
	\centering

	% --- \includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
	% --- \includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
	\includegraphics[width=0.35\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
	\includegraphics[width=0.35\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain  for MNIST as a function of the number of examples and the data decimation factor \textsc{Screenkhorn}. Hyperparameter values (left) $1$. (right) $10$.}
	\label{fig:otda}
\end{figure*}

For the OT based domain adaptation problem, we have considered the
OTDA with $\ell_{\frac 12,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using a majorization-minimization approach 
for handling the non-convexity of the problem. Hence, at each iteration, a \textsc{Sinkhorn}/\textsc{Screenkhorn} has to be computed and the number of iteration is
sensitive to the regularizer strength.  As a domain-adaptation problem, we have
used a MNIST to USPS problem in which features have been extracted from the
feature extractor of a domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
Figure \ref{fig:otda} reports the gain in running time for $2$ different values
of the group-lasso regularizer hyperparameter, while the curves of performances are
reported in the supplementary material. We can note that for all the  \textsc{Screenkhorn} with different decimation factors, the gain in computation goes from a factor of $4$ to $12$, while accuracies are somewhat equivalent.

% section numerical_experiments (end)

### 2019-09-24 final_NeurIPS/appendix.tex
update appendix
add final NeurIPS

@@
 
-\subsection{Additional remarks}
+\subsection{Additional experimental results}
+
+\paragraph{Experimental setup.}
+
+	All computations have been run on each single core of an Intel Xeon E5-2630 processor clocked at
+	2.4 GHz in a Linux machine with 144 Gb of memory.
 
@@
 We resort to a L-BFGS-B algorithm to solve the constrained convex optimization problem on the screened variables~\eqref{screen-sinkhorn_second_def}, but any other efficient solver (e.g., proximal based method or Newton method) could be used.
+In our implementation, we use a tricky method, called \emph{restricted Sinkhorn} (see Algorithm~\ref{restricted_sinkhorn}) as a warm-start initialized point for the L-BFGS-B.
 We further  emphasize that, as for the \textsc{Sinkhorn} algorithm, the \textsc{Screenkhorn} algorithm can be accelerated using a GPU implementation\footnote{\url{https://github.com/nepluno/lbfgsb-gpu}} of the L-BFGS-B algorithm~\cite{fei2014-GPU-L-BFGS-B}.
+
+\LinesNotNumbered
+\begin{algorithm}[tbp]
+\SetNlSty{textbf}{}{.}
+\DontPrintSemicolon
+\caption{\textsc{Restricted \textsc{Sinkhorn}}$(K,\mu, \nu, u, v)$}
+\label{restricted_sinkhorn}
+\nl \textbf{set: } $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}}), \bar{f}_v  = \varepsilon\kappa^{-1} \,r(K_{I^\complement_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}});$\\
+% \nl $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}});$\\
+% \nl $\bar{f}_v  = \varepsilon\kappa^{-1} \,r(K_{I^\complement_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}});$\\
+\nl \For{$t=1,2,3$}{
+	$f^{(t)}_v \gets K^\top_{I_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}} u + \bar{f}_v;$\\
+	$v^{(t)} \gets \frac{\nu_{J_{\varepsilon, \kappa}}}{\kappa f^{(t)}_v} ;$\\% / (\kappa K{IJ}_v);$\\
+	$f^{(t)}_u \gets K_{I_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}} v + \bar{f}_u;$\\
+	$u^{(t)} \gets \frac{\kappa \mu_{I_{\varepsilon, \kappa}}}{f^{(t)}_u};$\\
+	$u \gets u^{(t)}$, $v \gets v^{(t)}$;
+}
+\nl \Return{$(u^{(t)}, v^{(t)})$}
+\end{algorithm}
 
@@
 The computation time gain reaches an order of $30$ when comparing our method with \textsc{Greenkhorn} while \textsc{Screenkhorn} is almost $2$ times faster than $\textsc{Sinkhorn}$.
+}
 
-\subsection{Additional experimental results}
-
-\paragraph{Experimental setup.}
-
-	All computations have been run on each single core of an Intel Xeon E5-2630 processor clocked at
-	2.4 GHz in a Linux machine with 144 Gb of memory.
-	The code that generates all figures given in the paper is available from \url{https://github.com/mzalaya/screenkhorn}.
-
-}
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=6.cm]{./figs/timegain_Screenkhorn_Greenkhorn.pdf}
+	\caption{\ar{$\frac{T_{\textsc{Greenkhorn}}}{T_{\text{\textsc{Screenkhorn}}}}$: Running time gain  for the toy problem (see Section~\ref{subsec:analysing_toy_problem}) as a function of the data decimation factor in \textsc{Screenkhorn}, for different settings of the regularization parameter $\eta$.
+		\label{fig:screenkhorn_greenkhorn_gain}}}
+\end{figure*}
 

### 2019-09-24 final_NeurIPS/section_4_marginal_viols.tex
add final NeurIPS

@@
 Comparing to some other analysis results of this quantity, see for instance Lemma 2 in~\cite{dvurechensky18aICML} and Lemma 3.1 in~\cite{lin2019}, our bound involves an additional term $\omega_{\kappa}$ (with $\omega_1 =0)$, that tends to zero as the pair budget $(n_b,m_b)$ goes to the full number budget of points $(n,m)$ (i.e., $\kappa$ goes to $1).$
-\ar{To more characterize $\omega_\kappa$, a control of the $\ell_1$-norms of the screened marginals $\mu^{\text{sc}}$ and $\nu^{\text{sc}}$ are given in Equations~\eqref{l1-norm-mu-sc} and~\eqref{l1-norm-nu-sc} in Lemma~\ref{lemma_bounds_on_marginals} in the supplementary material.}
+\ar{To more characterize $\omega_\kappa$, a control of the $\ell_1$-norms of the screened marginals $\mu^{\text{sc}}$ and $\nu^{\text{sc}}$ are given in Lemma~\ref{lemma_bounds_on_marginals} in the supplementary material.}
+% Equations~\eqref{l1-norm-mu-sc} and~\eqref{l1-norm-nu-sc} in
 

### 2019-09-24 final_NeurIPS/section_5_numeric_expes.tex
add final NeurIPS

@@
 \subsection{Analysing on toy problem}
+\label{subsec:analysing_toy_problem}
 
@@
 	\includegraphics[width=0.35\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
-	\caption{OT Domain adaptation : running time gain  for MNIST as a function of the number of examples and the data decimation factor \textsc{Screenkhorn}.
+	\caption{OT Domain adaptation : running time gain  for MNIST as a function of the number of examples and the data decimation factor in \textsc{Screenkhorn}.
 Hyperparameter values (left) $1$.

### 2019-09-24 final_NeurIPS/appendix.tex
add final NeurIPS

@@
 \end{align*}
-To get the closed forms~\eqref{marginal-error-mu} and~\eqref{marginal-error-nu}, we used the follwoing facts:
+To get the closed forms~\eqref{marginal-error-mu} and~\eqref{marginal-error-nu}, we used the following facts:
 \begin{remark}
 \label{rem:orders_of_epsilonappa}
- We have 
+ We have $\log(1/K_{\min}^r) = r\norm{C}_\infty /\eta,$ for every $r \in \mathbb{N}$. Using~\eqref{epsilon_kappa}, we further derive: 
 $\varepsilon = \bigO((mnK_{\min}^2)^{-1/4})$, $\kappa= \bigO(\sqrt{m/(nc_{\mu\nu}K_{\min})}),$ $\kappa^{-1} = \bigO(\sqrt{n/(mK_{\min}c_{\mu\nu}})$, $(\kappa/\varepsilon)^2 = \bigO( m^{3/2} / \sqrt{nK_{\min}}(c_{\mu\nu})^{3/2})$, and $(\varepsilon\kappa)^{-2} = \bigO(n^{3/2}/\sqrt{mK_{\min}}c^{3/2}_{\mu\nu}).$
@@
 \end{align*}
-Therefore, we obtain the followoing bound:
+Therefore, we obtain the following bound:
 \begin{align}
@@
 We resort to a L-BFGS-B algorithm to solve the constrained convex optimization problem on the screened variables~\eqref{screen-sinkhorn_second_def}, but any other efficient solver (e.g., proximal based method or Newton method) could be used.
-In our implementation, we use a tricky method, called \emph{restricted Sinkhorn} (see Algorithm~\ref{restricted_sinkhorn}) as a warm-start initialized point for the L-BFGS-B.
+In our implementation, we use a tricky method for almost $3$-calls, named \emph{restricted Sinkhorn} (see Algorithm~\ref{restricted_sinkhorn}) as a warm-start initialized point for the L-BFGS-B.
 We further  emphasize that, as for the \textsc{Sinkhorn} algorithm, the \textsc{Screenkhorn} algorithm can be accelerated using a GPU implementation\footnote{\url{https://github.com/nepluno/lbfgsb-gpu}} of the L-BFGS-B algorithm~\cite{fei2014-GPU-L-BFGS-B}.
@@
 	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
-	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem and, (right) MNIST).
+	\caption{Accuracy of a $1$-nearest-neighbor after WDA for the (left) toy problem and, (right) MNIST).
 We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance.
@@
 (top-left) Examples of source and target samples.
-(top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples.
+(top-right) Evolution of the accuracy of a 1-nearest-neighbor classifier with respect to the number of samples.
 (bottom-left) Running time of the \textsc{Sinkhorn} and \textsc{Screenkhorn} for different decimation
@@
 	also report the performance of a $1$-NN when no-adaptation is performed.  
-	We remark that the strenght of the class-based regularization has influence on the performance of \textsc{Screenkhorn} given a decimation factor.
+	We remark that the strength of the class-based regularization has influence on the performance of \textsc{Screenkhorn} given a decimation factor.
 For small value on the left, \textsc{Screenkhorn} slightly performs better than \textsc{Sinkhorn}, while for large value, some

### 2019-09-24 final_NeurIPS/section_4_marginal_viols.tex
add final NeurIPS

@@
 \label{marginal-error-mu}
-{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Big(n_bc_\kappa + (n- n_b) \Big(\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}K_{\min}}
- + \log\Big(\frac{\sqrt{nm}}{m_b(c_{\mu\nu}K_{\min})^{5/2}} 
+{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Big(n_bc_\kappa + (n- n_b) \Big(\frac{\norm{C}_\infty}{\eta} + \frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}K_{\min}}
+ + \log\Big(\frac{\sqrt{nm}}{m_bc_{\mu\nu}^{5/2}} 
 \Big)\Big)\Big)
@@
 \label{marginal-error-nu}
-{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} = \bigO\Big(m_bc_{\frac1\kappa} + (m- m_b) \Big(\frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{n-n_b}{\sqrt{nm}K_{\min}}
- + \log\Big(\frac{\sqrt{nm}}{n_b (c_{\mu\nu}K_{\min})^{5/2}}
+{\norm{{\nu} -{\nu}^{\text{sc}}}^2_1} = \bigO\Big(m_bc_{\frac1\kappa} + (m- m_b) \Big(\frac{\norm{C}_\infty}{\eta} + \frac{n_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{n-n_b}{\sqrt{nm}K_{\min}}
+ + \log\Big(\frac{\sqrt{nm}}{n_b c_{\mu\nu}^{5/2}}
 \Big)\Big)\Big),

### 2019-09-25 final_NeurIPS/appendix.tex
clean comment texts ion the whole paper

@@
 Next, we bound the two terms $\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty.$
-% \paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.
 If $r \in I^\complement_{\varepsilon, \kappa}$, then we have 
@@
 \label{induction_uppers_bounds}
-\max\{\norm{u^\star - u^{\text{sc}}}_\infty, \norm{v^\star - v^{\text{sc}}}_\infty\} %&\leq \max\{\norm{u^\star - u^{\text{sc}}_0}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star - v^{\text{sc}}_0}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\}\nonumber\\
+\max\{\norm{u^\star - u^{\text{sc}}}_\infty, \norm{v^\star - v^{\text{sc}}}_\infty\} 
 &\leq \max\Big\{\norm{u^\star}_\infty + \norm{u^{\text{sc}}}_\infty +  \log(\frac{n\varepsilon^2}{c_{\mu\nu}}), \norm{v^\star}_\infty + \norm{v^{\text{sc}}}_\infty + \log(\frac{m\varepsilon^2}{c_{\mu\nu}})\Big\}\nonumber\\
@@
 \end{align}
-%where we used $u^{\text{sc}}_0 = \mathbf 0_n$ and $v^{\text{sc}}_0 = \mathbf 0_m.$ 
 Now, Lemma 3.2 in~\cite{lin2019} provides an upper bound for the $\ell_\infty$ of the optimal solution pair $(u^\star, v^\star)$ of problem~\eqref{sinkhorn-dual} as follows:
@@
 By Proposition~\ref{prop:bounds_of_usc_and_vsc}, we have 
-\begin{align*} %\max_{i \in I_{\varepsilon,\kappa}} \mu_i %\max_{j \in J_{\varepsilon,\kappa}} \nu_j
+\begin{align*} 
 \norm{u^{\text{sc}}}_\infty \leq \log\big(\frac \varepsilon\kappa\vee \frac{1}{m\varepsilon K_{\min}}\big) \text{ and } \norm{v^{\text{sc}}}_\infty \leq \log\big(\varepsilon\kappa \vee \frac{1}{n\varepsilon K_{\min} }\big)
@@
 Letting $\Omega_{\kappa} := (1- \kappa)\big(\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 +\norm{\mu^{\text{sc}} - \mu}_1\big) + (\kappa^{-1} - 1)\big(\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1+\norm{\nu^{\text{sc}} - \nu}_1\big).$
-% Moreover, we have 
-% \begin{align*}
-% \omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1
-% \end{align*}
 We have that 
@@
 \end{align*}
-% Setting $\omega_\kappa := (1- \kappa)\norm{\mu^{\text{sc}}}_1 + (\kappa^{-1} - 1)\norm{\nu^{\text{sc}}}_1 + \kappa^{-1} - \kappa,$ 
 Hence, we arrive at 
@@
 & \overset{\eqref{bound_on_v}}{\leq} \kappa \norm{\mu_{I_{\varepsilon,\kappa}}^{\text{sc}}}_1 + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big).
-% &\leq n_b\kappa + (n-n_b) \Big(\frac{m_b\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\kappa K_{\min}} + (m-m_b)\varepsilon^2 \Big)
 \end{align*}
@@
 \LinesNotNumbered
-\begin{algorithm}[tbp]
+\begin{algorithm}[htbp]
 \SetNlSty{textbf}{}{.}
@@
 \nl \textbf{set: } $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}}), \bar{f}_v  = \varepsilon\kappa^{-1} \,r(K_{I^\complement_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}});$\\
-% \nl $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}});$\\
-% \nl $\bar{f}_v  = \varepsilon\kappa^{-1} \,r(K_{I^\complement_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}});$\\
 \nl \For{$t=1,2,3$}{
@@
 	\centering
-	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
 	~\hfill~\includegraphics[width=6.cm]{./figs/wda_accur_toy.pdf}~\hfill~
@@
 	\centering
-	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
 	~\hfill~\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~

### 2019-09-25 final_NeurIPS/main.tex
clean comment texts ion the whole paper

@@
 
-\newsavebox{\tempbox}
-
-\makeatletter
-\let\oldnl\nl% Store \nl in \oldnl
-\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}% Remove line number for one line
-\makeatother
-
-\let\oldalgorithm\algorithm
-\let\oldendalgorithm\endalgorithm
-
-\newcommand\SetAlgoFig{
-  \let\algorithm\figure
-  \let\endalgorithm\endfigure
-}
-
-\newcommand\SetAlgoNoFig{
-  \let\algorithm\oldalgorithm
-  \let\endalgorithm\oldendalgorithm
-}
-%%
-
 \usepackage{enumitem}
@@
 \DeclareMathOperator*{\argmax}{\arg\!\max}
-
-% small pmatrix
-% \usepackage{amsmath}
-% \newenvironment{psmallmatrix}
-%   {\left(\begin{smallmatrix}}
-%   {\end{smallmatrix}\right)}
-%--------------------------------------------------------------------------------------------------------------------------------%
 
@@
 \section{Conclusion}
+
 The paper introduces a novel efficient approximation of the Sinkhorn divergence
@@
 \bibliographystyle{plain}
-%well as with those for harvard, apalike, chicago, astron, authordate, and of course natbib.
 

### 2019-09-25 final_NeurIPS/section_1_introduction.tex
clean comment texts ion the whole paper

--- 2019-05-22 tex/v3/section_1_introduction.tex
@@
 In many of these problems, OT exploits the geometric features of the objects at hand in the underlying spaces to be leveraged in comparing probability measures.
-This effectively leads to improve performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
+This effectively leads to improved performance of methods that are oblivious to the geometry, for example the chi-squared distances or the Kullback-Leibler divergence.
 Unfortunately, this advantage comes at the price of an enormous computational cost of solving the OT problem, that can be prohibitive in large scale applications.
-For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^3)$~\citep{pele2009} arithmetic operations, which is problematic when $n$ is larger than $10^3.$
+For instance, the OT between two histograms with supports of equal size $n$ can be formulated as a linear programming problem that requires generally super $\bigO(n^{2.5})$~\citep{leeSidford2013PathFI} arithmetic operations, which is problematic when $n$ becomes larger.
 
-A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\citep{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
+A remedy to the heavy computation burden of OT lies in a prevalent approach referred to as regularized OT~\citep{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.
 Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
-%Furthermore, the dual of the entropic problem, referred to as {dual of Sinkhorn divergence}, was studied in~\cite{cuturinips13} and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
 More importantly, this regularized OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.
 
-%Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
-%The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
 Several works have considered further improvements in the resolution of this regularized OT problem.
-A greedy version of Sinkhorn, called Greenkhorn algorithm and proposed in~\cite{altschulernips17}, allows to select columns and rows to be updated that most violate the constraints.                   
-Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\citep{altschuler2018Nystrom}. 
-Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\citep{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi Newton methods~\citep{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\citep{genevay2016stochOT,khalilabid2018}.
+A greedy version of Sinkhorn algorithm, called Greenkhorn~\cite{altschulernips17}, allows to select and update columns and rows that most violate the polytope constraints.                   
+Another approach based on low-rank approximation of the cost matrix using the Nystr\"om method induces the Nys-Sink algorithm~\citep{altschuler2018Nystrom}. 
+Other classical optimization algorithms have been considered for approximating the OT, for instance accelerated gradient descent~\citep{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi-Newton methods~\citep{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\citep{genevay2016stochOT,khalilabid2018}.
 
@@
 
-	\item From a methodological point of view, we propose a reformulation of the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
+	\item From a methodological point of view, we propose a new formulation of the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
 	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to  strictly satisfy its constraint, leading then to
@@
 	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
-	\item From an algorithmic standpoint, we use a constrained L-BFGS-B algorithm \citep{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
+	\item From an algorithmic standpoint, we use a constrained L-BFGS-B algorithm \citep{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower and upper bounds of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \textsc{Screenkhorn}.
 	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning
-	pipelines, we show that \emph{Screenkhorn} can lead to strong gain in efficiency
+	pipelines, we show that \textsc{Screenkhorn} can lead to strong gain in efficiency
 	while not compromising on accuracy.
 \end{itemize}}
-%	
-%
-%These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
-%We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
-%Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
-%We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
-%Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences.
-%L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.}
 
 The remainder of the paper is organized as follow. In Section~\ref{sec:regularized_discrete_ot} we briefly review the basic setup of regularized discrete OT. 
-Section~\ref{sec:screened_dual_of_sinkhorn_divergence} contains our main contribution, that is, the \emph{Screenkhorn} algorithm. 
-Section~\ref{sec:analysis_of_marginal_violations} devotes to theoretical guarantees for marginal violations of \emph{Screenkhorn}. 
+Section~\ref{sec:screened_dual_of_sinkhorn_divergence} contains our main contribution, that is, the \textsc{Screenkhorn} algorithm. 
+Section~\ref{sec:analysis_of_marginal_violations} is devoted to theoretical guarantees for marginal violations of \textsc{Screenkhorn}. 
 In Section~\ref{sec:numerical_experiments} we present numerical results for the proposed algorithm, compared with the state-of-art Sinkhorn algorithm as implemented in~\cite{flamary2017pot}. 
@@
 
-\emph{Notation.} For any positive matrix $T \in \R^{n\times m}$, we define its negative entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
+\emph{Notation.} For any positive matrix $T \in \R^{n\times m}$, we define its entropy as $H(T) = -\sum_{i,j} T_{ij} \log(T_{ij}).$
 Let $r(T) = T\mathbf 1_m \in \R^n$ and $c(T) = T^\top\mathbf 1_n \in \R^m$ denote the rows and columns sums of $T$ respectively.

### 2019-09-25 final_NeurIPS/section_3_algorithm.tex
add final NeurIPS
clean comment texts ion the whole paper

@@
 }
-% The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
 Moreover, it is clear that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} when $\varepsilon=0$ and $\kappa=1$.
@@
 {The following key result states sufficient conditions for identifying variables in $I^\complement$ and $J^\complement$.}
-%The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
-
-%Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, defined by:
-
-%\paragraph{Static screening test.} The core of the static screening test developed in this paper aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and
-%$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
-%The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
-%Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.
-%
-%In the following, the parameters $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ where $\varepsilon > 0$ and $\kappa > 0$ are fixed numeric constants to be given later. 
-%Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, defined by:
-%
-%\begin{equation} 
-%\label{screen-sinkhorn}
-%\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
-%\end{equation}
-%The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential components $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these components.
-%Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
-%As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows:
 
@@
 
-%More precisely, we change the domain of the objective function %$\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$.
-
-{We are now in position to formulate the
-optimization problem related to the screened dual of Sinkhorn.} Indeed, using the above analyses, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
+We are now in position to formulate the optimization problem related to the screened dual of Sinkhorn.
+Indeed, using the above analyses, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfies $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
 {Hence, we can restrict the problem \eqref{screen-sinkhorn} to 
@@
 \begin{equation*}
-\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
+\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}
 \end{equation*}
-% and 
-% \begin{equation*}
-% 	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.
-%, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
-% \end{equation*}
 where the vector comparison $\succeq$ has to be understood elementwise. {And,
@@
 using a constrained L-BFGS-B \cite{byrd1995L-BFGS-B} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
-Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
+Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. 
 Note that L-BFGS-B handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
@@
 
-\textbf{Step 1:} \textcolor{black}{\ar{Screening pre-processing}}\\
+\textbf{Step 1:} \textcolor{black}{{Screening pre-processing}}\\
 
 \nl   $\xi \gets \texttt{sort}(\mu \oslash r(K)),$ $\zeta \gets \texttt{sort}(\nu \oslash c(K));$ //(decreasing order)\\
-% \nl   $\zeta \gets \texttt{sort}(\nu \oslash c(K));$\\
-% \nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-% \nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
 \nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
@@
 \nl   $ \bar{\theta} \gets \texttt{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b}),$ $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
-% \nl   $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
-
 \vspace{.2cm}
-\noindent \textbf{Step 2:} \textcolor{black}{\ar{L-BFGS-B solver on the screened variables}}\\
+\noindent \textbf{Step 2:} \textcolor{black}{{L-BFGS-B solver on the screened variables}}\\
 
 \nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b},$ $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b},$ $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
-% \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-% \nl  $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
 \nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
@@
 \end{algorithm}
-
-% \savebox{\tempbox}{% create image
-% \begin{minipage}[c]{0.45\textwidth}%
-%    \textbf{Step 1:} \textcolor{black}{Initialization: screening pre-processing}\\
-
-% \nl   $\xi \gets \texttt{sort}(\mu \oslash r(K)),$ $\zeta \gets \texttt{sort}(\nu \oslash c(K));$ //(decreasing order)\\
-% % \nl   $\zeta \gets \texttt{sort}(\nu \oslash c(K));$\\
-% % \nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
-% % \nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
-% \nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
-% \nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
-% \nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\ 
-% \nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
-% \nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \nu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \nu_i$; \\
-% \nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big)$; \\
-% \nl $\bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
-% \nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big)$; \\
-% \nl $\bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
-% \nl   $ \bar{\theta} \gets \texttt{stack}(\bar{u}\mathbf 1_{n_b} \bar{v}\mathbf 1_{m_b});$ \\
-% \nl $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
-% % \nl   $ \underline{\theta} \gets \texttt{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\
-
-% % \vspace{.2cm}
-% \noindent \textbf{Step 2:} \textcolor{black}{L-BFGS-B solver on screened variables}\\
-
-% \nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b},$ $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b},$ $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
-% % \nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
-% % \nl  $\theta^{(0)} \gets \texttt{stack}(u^{(0)}, v^{(0)});$\\
-% \nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
-% \nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
-% \nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
-% \nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
-% \nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}     
-% \end{minipage}}
-
-% \SetAlgoNoFig % use the standard algorithm
-
-% \LinesNotNumbered
-% \begin{algorithm}[tbp]
-% \SetNlSty{textbf}{}{.}
-% \DontPrintSemicolon
-% % \nonl %switch off line numbers
-% \clipbox{-15pt {\depth} 15pt {\baselineskip}}{\usebox{\tempbox}}\hfill
-% \raisebox{\depth}{\clipbox{15pt 1ex -15pt {\height}}{\usebox{\tempbox}}}
-% \caption{\textsc{Screenkhorn}$(C,\eta,\mu,\nu,n_b,m_b)$}
-% \end{algorithm}
-
+s
 % section screened_dual_of_sinkhorn_divergence (end)

### 2019-09-25 final_NeurIPS/section_5_numeric_expes.tex
clean comment texts ion the whole paper

@@
 	\begin{center}
-		% \includegraphics[width=0.33\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
-		\includegraphics[width=0.28\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
-		\includegraphics[width=0.28\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} \\
-		\includegraphics[width=0.28\textwidth]{./figs/norm_M_time_toy_n1000}\hspace{2cm}
-		\includegraphics[width=0.28\textwidth]{./figs/norm_M_div_toy_n1000}
+		\includegraphics[width=0.3\textwidth]{./figs/norm_M_Mu_marginals_toy_n1000}\hspace{2cm}
+		\includegraphics[width=0.3\textwidth]{./figs/norm_M_Nu_marginals_toy_n1000} \\
+		\includegraphics[width=0.3\textwidth]{./figs/norm_M_time_toy_n1000}\hspace{2cm}
+		\includegraphics[width=0.3\textwidth]{./figs/norm_M_div_toy_n1000}
 	\end{center}
@@
 	\centering
-%	\includegraphics[width=4.cm]{./figs/wda_accur_toy.pdf}
-%	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
-	% --- \includegraphics[width=0.39\textwidth]{./figs/wda_gain_toy.pdf}\hspace{1.5cm}
-	% --- \includegraphics[width=0.39\textwidth]{./figs/wda_gain_mnist.pdf}
-
 	\includegraphics[width=0.31\textwidth]{./figs/wda_gain_toy.pdf}\hspace{1.5cm}
@@
 	\centering
-
-	% --- \includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
-	% --- \includegraphics[width=0.43\textwidth]{./figs/da_gain_mnist_regcl10.pdf}
-	\includegraphics[width=0.35\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
+s	\includegraphics[width=0.35\textwidth]{./figs/da_gain_mnist_regcl1.pdf}\hspace{1cm}
 	\includegraphics[width=0.35\textwidth]{./figs/da_gain_mnist_regcl10.pdf}

### 2019-10-21 final_NeurIPS/appendix.tex
Modify presentation of Proposition 3
correct typo
update

--- 2019-09-24 final_NeurIPS/appendix.tex
@@
 Now, Lemma 3.2 in~\cite{lin2019} provides an upper bound for the $\ell_\infty$ of the optimal solution pair $(u^\star, v^\star)$ of problem~\eqref{sinkhorn-dual} as follows:
-$\norm{u^\star}_\infty \leq R$ and $\norm{v^\star}_\infty\leq R,$ where 
+$\norm{u^\star}_\infty \leq A$ and $\norm{v^\star}_\infty\leq A,$ where 
 \begin{align}
 \label{R_constant}
-R = \frac{\norm{C}_\infty}{\eta} + \log\big(\frac{n\vee m}{c^2_{\mu\nu}}\big).
+A = \frac{\norm{C}_\infty}{\eta} + \log\big(\frac{n\vee m}{c^2_{\mu\nu}}\big).
 \end{align}
@@
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
-&\leq 2\big(R + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
+&\leq 2\big(A + \norm{u^{\text{sc}}}_\infty +  \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) \big(\norm{\mu^{\text{sc}} - \mu}_1+ \norm{\nu^{\text{sc}} - \nu}_1\big)\nonumber\\
 &\qquad + (1- \kappa)\big(\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 +\norm{\mu^{\text{sc}} - \mu}_1\big)\label{post_bounds_induction_2}\\
@@
 \begin{align*}
-R + \norm{u^{\text{sc}}}_\infty  + \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) = \bigO\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big).
+A + \norm{u^{\text{sc}}}_\infty  + \norm{v^{\text{sc}}}_\infty + \log\big(\frac{(n\vee m)\varepsilon^2}{c_{\mu\nu}})\big) = \bigO\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big).
 \end{align*}
 Letting $\Omega_{\kappa} := (1- \kappa)\big(\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 +\norm{\mu^{\text{sc}} - \mu}_1\big) + (\kappa^{-1} - 1)\big(\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1+\norm{\nu^{\text{sc}} - \nu}_1\big).$
-% Moreover, we have 
-% \begin{align*}
-% \omega_{\kappa} := (1- \kappa)\norm{{u}^{\text{sc}}}_\infty\norm{{\mu}^{\text{sc}}}_1 + (1- \kappa^{-1})\norm{{v}^{\text{sc}}}_\infty\norm{{\nu}^{\text{sc}}}_1
-% \end{align*}
 We have that 
@@
 \Psi_{\varepsilon, \kappa}(u^{\text{sc}} ,v^{\text{sc}}) -\Psi(u^\star, v^\star) 
-& = \bigO\Big(\Big(\frac{\norm{C}_\infty}{\eta} + \log\Big(\frac{(n\vee m)^2}{nmc_{\mu\nu}^{7/2}}\Big)\Big)(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1 + \omega_{\kappa}\Big).
+& = \bigO\big(R(\norm{\mu - {\mu}^{\text{sc}}}_1 + \norm{\nu - \nu^{\text{sc}}}_1 + \omega_{\kappa})\big).
 \end{align*}
@@
 lemma expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$.
+
 \begin{lemma}
@@
 We resort to a L-BFGS-B algorithm to solve the constrained convex optimization problem on the screened variables~\eqref{screen-sinkhorn_second_def}, but any other efficient solver (e.g., proximal based method or Newton method) could be used.
-In our implementation, we use a tricky method, called \emph{restricted Sinkhorn} (see Algorithm~\ref{restricted_sinkhorn}) as a warm-start initialized point for the L-BFGS-B.
-We further  emphasize that, as for the \textsc{Sinkhorn} algorithm, the \textsc{Screenkhorn} algorithm can be accelerated using a GPU implementation\footnote{\url{https://github.com/nepluno/lbfgsb-gpu}} of the L-BFGS-B algorithm~\cite{fei2014-GPU-L-BFGS-B}.
+In our implementation, we choose a clever starting point of the L-BFGS-B algorithm based on a method, called \emph{restricted Sinkhorn} (see Algorithm~\ref{restricted_sinkhorn}), which is a Sinkhorn algorithm applied on
+the active dual variables. While simple and efficient the solution of this 
+\emph{restricted Sinkhorn} algorithm does not satisfy the lower bound constraints of Problem \eqref{screen-sinkhorn_second_def}.
+
+We further  not that, as for the \textsc{Sinkhorn} algorithm, our \textsc{Screenkhorn} algorithm can be accelerated using a GPU implementation\footnote{\url{https://github.com/nepluno/lbfgsb-gpu}} of the L-BFGS-B algorithm~\cite{fei2014-GPU-L-BFGS-B}.
 
@@
 \label{restricted_sinkhorn}
-\nl \textbf{set: } $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}}), \bar{f}_v  = \varepsilon\kappa^{-1} \,r(K_{I^\complement_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}});$\\
+\nl \textbf{set:} $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}}), \bar{f}_v  = \varepsilon\kappa^{-1} \,r(K_{I^\complement_{\varepsilon, \kappa}, J_{\varepsilon, \kappa}});$\\
 % \nl $\bar{f}_u = \varepsilon\kappa\, c(K_{I_{\varepsilon, \kappa}, J^\complement_{\varepsilon, \kappa}});$\\
@@
 	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
-	~\hfill~\includegraphics[width=6.cm]{./figs/wda_accur_toy.pdf}~\hfill~
-	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
+	~\hfill~\includegraphics[width=6.5cm]{./figs/wda_accur_toy.pdf}~\hfill~
+	\includegraphics[width=6.5cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
 	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem and, (right) MNIST).
@@
 		\label{fig:wda_gain}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+
+\begin{center}
+
+	~\hfill~\includegraphics[width=6.6cm]{./figs/wda_accur_toy_eta01_K1.pdf}~\hfill~
+	\includegraphics[width=6.5cm]{./figs/wda_gain_toy_eta01_K1.pdf}~\hfill~\\
+
+	~\hfill~\includegraphics[width=6.5cm]{./figs/wda_accur_toy_eta01_K5.pdf}~\hfill~
+	\includegraphics[width=6.5cm]{./figs/wda_gain_toy_eta01_K5.pdf}~\hfill~\\
+
+	\caption{(top-left) Accuracy and (bottom-right) computational time gain on the toy dataset for $\eta=0.1$ and $1$-nearest-neighbour.
+(bottom) accuracy and gain but for a $5$-nearest-neighbour.
+We can note that a  slight loss of performances occur for larger training set sizes especially for $1$-nearest-neighbour.
+Computational gains increase with the dataset size and
+		is on average of the order of magnitude. \ar{Checker 3500 K5(plus d'iter)} 
+		\label{fig:wda_gain_toy_eta01}}
+
+\end{center}
+
 \end{figure*}
@@
 \end{figure*}
+
+\begin{figure*}[htbp]
+	\centering
+
+	\includegraphics[width=6.5cm]{./figs/da_regpath_accur_mnist_reg1.pdf}
+	\includegraphics[width=6.5cm]{./figs/da_regpath_time_mnist_reg1.pdf}
+
+	\caption{OT Domain adaptation MNIST to USPS : (left) Accuracy and (right) running time of \textsc{Sinkhorn} and \textsc{Screenkhorn} for the best performing (on average of $10$ trials) hyperparameter $\ell_{p,1}$ chosen among the set $\{0.1, 1,5,10 \}$.
+We can note that in this situation, there is not loss of accuracy while our \textsc{Screenkhorn} is still about an order of magnitude more efficient than Sinkhorn.}
+\end{figure*}

### 2019-10-21 final_NeurIPS/section_5_numeric_expes.tex
update

--- 2019-09-24 final_NeurIPS/section_5_numeric_expes.tex
@@
 
-	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for MNIST as a function of the number of examples and the data decimation factor in \textsc{Screenkhorn}.}
+	\caption{Wasserstein Discriminant Analysis : running time gain for (left) a toy dataset and (right) MNIST as a function of the number of examples and the data decimation factor in \textsc{Screenkhorn}.}
 	\label{fig:wda}
@@
 	\caption{OT Domain adaptation : running time gain  for MNIST as a function of the number of examples and the data decimation factor in \textsc{Screenkhorn}.
-Hyperparameter values (left) $1$.
+Group-lasso hyperparameter values (left) $1$.
 (right) $10$.}

### 2019-10-21 screenkhorn.py

@@ -1,7 +1,8 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-__author__ = 'Mokhtar Z. Alaya and Maxime Bérar'
+__author__ = 'Mokhtar Z. Alaya: mokhtarzahdi.alaya@gmail.com'\
+             'Maxime Bérar: maxime.bérar@univ.rouen.fr'
 
 import numpy as np
 import bottleneck
